\DefineJournal{aqjor}{1619-4500}
{4OR}
{4OR. A Quarterly Journal of Operations Research}
\DefineJournal{cbm}{?cbm}
{30$\sp {\rm o}$ Coloq. Bras. Mat.}
{30$\sp {\rm o}$ Coloquio Brasileiro de Matematica}
\DefineJournal{cbm}{?cbm}
{31$\sp {\rm o}$ Coloq. Bras. Mat.}
{31$\sp {\rm o}$ Coloquio Brasileiro de Matematica}
\DefineJournal{aems}{1406-4316}
{Aastaraam. Eesti Mat. Selts}
{Aastaraamat. Eesti Matemaatika Selts}
\DefineJournal{as}{2193-2808}
{Abel Symp.}
{Abel Symposia}
\DefineJournal{aawgnf}{0930-4304}
{Abh. Akad. Wiss. Gottingen Neue Folge}
{Abhandlungen der Akademie der Wissenschaften zu Gottingen. Neue Folge}
\DefineJournal{aawh}{2193-1933}
{Abh. Akad. Wiss. Hamburg}
{Abhandlungen der Akademie der Wissenschaften in Hamburg}
\DefineJournal{amsuh}{0025-5858}
{Abh. Math. Semin. Univ. Hambg.}
{Abhandlungen aus dem Mathematischen Seminar der Universitat Hamburg}
\DefineJournal{apg}{?apg}
{Abh. Philos. Gesch.}
{Abhandlungen zur Philosophie und ihrer Geschichte}
\DefineJournal{aaa}{1085-3375}
{Abstr. Appl. Anal.}
{Abstract and Applied Analysis}
\DefineJournal{apscp}{?apscp}
{Academic Press Ser. Cognition and Perception}
{Academic Press Series in Cognition and Perception}
\DefineJournal{ap}{?ap}
{Accel. Phys.}
{Accelerator Physics}
\DefineJournal{ab}{?ab}
{ACM Books}
{ACM Books}
\DefineJournal{acca}{1932-2232}
{ACM Commun. Comput. Algebra}
{ACM Communications in Computer Algebra}
\DefineJournal{ajea}{1084-6654}
{ACM J. Exp. Algorithmics}
{ACM Journal of Experimental Algorithmics}
\DefineJournal{asn}{0163-5700}
{ACM SIGACT News}
{ACM SIGACT News}
\DefineJournal{ata}{1549-6325}
{ACM Trans. Algorithms}
{ACM Transactions on Algorithms}
\DefineJournal{atcl}{1529-3785}
{ACM Trans. Comput. Log.}
{ACM Transactions on Computational Logic}
\DefineJournal{atct}{1942-3454}
{ACM Trans. Comput. Theory}
{ACM Transactions of Computation Theory}
\DefineJournal{atds}{0362-5915}
{ACM Trans. Database Syst.}
{ACM Transactions on Database Systems}
\DefineJournal{atec}{2167-8375}
{ACM Trans. Econ. Comput.}
{ACM Transactions on Economics and Computation}
\DefineJournal{acmtms}{0098-3500}
{ACM Trans. Math. Software}
{Association for Computing Machinery. Transactions on Mathematical Software}
\DefineJournal{atmcs}{1049-3301}
{ACM Trans. Model. Comput. Simul.}
{ACM Transactions on Modeling and Computer Simulation}
\DefineJournal{aast}{?aast}
{Acta Acad. Sci. Taurinensis}
{Acta Academiae Scientiarum Taurinensis}
\DefineJournal{aafaayfx}{1009-1327}
{Acta Anal. Funct. Appl.}
{Acta Analysis Functionalis Applicata. AAFA. Yingyong Fanhanfenxi Xuebao}
\DefineJournal{aam}{0167-8019}
{Acta Appl. Math.}
{Acta Applicandae Mathematicae}
\DefineJournal{aa}{0065-1036}
{Acta Arith.}
{Acta Arithmetica}
\DefineJournal{acvavac}{0001-5504}
{Acta Cient. Venezolana}
{Acta Cientifica Venezolana. Asociacion Venezolana para el Avance de la Ciencia}
\DefineJournal{acutm}{1406-2283}
{Acta Comment. Univ. Tartu. Math.}
{Acta et Commentationes Universitatis Tartuensis de Mathematica}
\DefineJournal{acsafa}{0108-7673}
{Acta Crystallogr. Sect. A}
{Acta Crystallographica Section A. Foundations and Advances}
\DefineJournal{ac}{0324-721X}
{Acta Cybernet.}
{Acta Cybernetica}
\DefineJournal{ai}{0001-5903}
{Acta Inform.}
{Acta Informatica}
\DefineJournal{am}{0001-5962}
{Acta Math.}
{Acta Mathematica}
\DefineJournal{amapnns}{1786-0091}
{Acta Math. Acad. Paedagog. Nyhazi. (N.S.)}
{Acta Mathematica. Academiae Paedagogicae Nyiregyhaziensis. New Series}
\DefineJournal{amasysx}{0254-3079}
{Acta Math. Appl. Sin.}
{Acta Mathematicae Applicatae Sinica. Yingyong Shuxue Xuebao}
\DefineJournal{amases}{0168-9673}
{Acta Math. Appl. Sin. Engl. Ser.}
{Acta Mathematicae Applicatae Sinica. English Series}
\DefineJournal{amh}{0236-5294}
{Acta Math. Hungar.}
{Acta Mathematica Hungarica}
\DefineJournal{amssaswxce}{1003-3998}
{Acta Math. Sci. Ser. A (Chin. Ed.)}
{Acta Mathematica Scientia. Series A. Shuxue Wuli Xuebao. Chinese Edition}
\DefineJournal{amssbee}{0252-9602}
{Acta Math. Sci. Ser. B (Engl. Ed.)}
{Acta Mathematica Scientia. Series B. English Edition}
\DefineJournal{amss}{1439-8516}
{Acta Math. Sin. (Engl. Ser.)}
{Acta Mathematica Sinica (English Series)}
\DefineJournal{amscs}{0583-1431}
{Acta Math. Sinica (Chin. Ser.)}
{Acta Mathematica Sinica. Chinese Series}
\DefineJournal{amucns}{0862-9544}
{Acta Math. Univ. Comenian. (N.S.)}
{Acta Mathematica Universitatis Comenianae. New Series}
\DefineJournal{amv}{0251-4184}
{Acta Math. Vietnam.}
{Acta Mathematica Vietnamica}
\DefineJournal{am}{0001-5970}
{Acta Mech.}
{Acta Mechanica}
\DefineJournal{ams}{0567-7718}
{Acta Mech. Sin.}
{Acta Mechanica Sinica}
\DefineJournal{an}{0962-4929}
{Acta Numer.}
{Acta Numerica}
\DefineJournal{juipappb}{0587-4254}
{Acta Phys. Polon. B}
{Jagellonian University. Institute of Physics. Acta Physica Polonica B}
\DefineJournal{ausasm}{0001-6969}
{Acta Sci. Math. (Szeged)}
{Acta Universitatis Szegediensis. Acta Scientiarum Mathematicarum}
\DefineJournal{}{?}
{Acta Sci. Natur. Univ. Intramongolicae}
{nan}
\DefineJournal{}{?}
{Acta Sci. Natur. Univ. Pekinensis}
{nan}
\DefineJournal{asnuszdxzkb}{0529-6579}
{Acta Sci. Natur. Univ. Sunyatseni}
{Acta Scientiarum Naturalium Universitatis Sunyatseni. Zhongshan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{at}{0001-7043}
{Acta Tech.}
{Acta Technica}
\DefineJournal{auami}{1582-5329}
{Acta Univ. Apulensis Math. Inform.}
{Acta Universitatis Apulensis. Mathematics. Informatics}
\DefineJournal{aumbsm}{1338-712X}
{Acta Univ. M. Belii Ser. Math.}
{Acta Universitatis Matthiae Belii. Series Mathematics}
\DefineJournal{aupofm}{?aupofm}
{Acta Univ. Palack. Olomuc. Fac. Med.}
{Acta Universitatis Palackianae Olomucensis Facultatis Medicae}
\DefineJournal{aupofrnm}{0231-9721}
{Acta Univ. Palack. Olomuc. Fac. Rerum Natur. Math.}
{Acta Universitatis Palackianae Olomucensis. Facultas Rerum Naturalium. Mathematica}
\DefineJournal{ausmaisjsu}{1844-6094}
{Acta Univ. Sapientiae Math.}
{Acta Universitatis Sapientiae. Mathematica. An International Scientific Journal of Sapientia University}
\DefineJournal{acaarm}{0327-9170}
{Actas Congr. ``Dr. Antonio A. R. Monteiro''}
{Actas del Congreso ``Dr. Antonio A. R. Monteiro''}
\DefineJournal{aas}{?aas}
{ACTEX Acad. Ser.}
{ACTEX Academic Series}
\DefineJournal{aps}{?aps}
{ACTEX Prof. Ser.}
{ACTEX Professional Series}
\DefineJournal{asa}{?asa}
{Actualites Sci. Agronom. INRA}
{Actualites Scientifiques et Agronomiques de l'INRA}
\DefineJournal{acml}{?acml}
{Adapt. Comput. Mach. Learn.}
{Adaptive Computation and Machine Learning}
\DefineJournal{alo}{1867-4534}
{Adapt. Learn. Optim.}
{Adaptation, Learning, and Optimization}
\DefineJournal{ascsip}{?ascsip}
{Addison-Wesley Ser. Comput. Sci. Inform. Process.}
{Addison-Wesley Series in Computer Science and Information Processing}
\DefineJournal{asm}{?asm}
{Addison-Wesley Ser. Math.}
{Addison-Wesley Series in Mathematics}
\DefineJournal{ass}{?ass}
{Addison-Wesley Ser. Statist.}
{Addison-Wesley Series in Statistics}
\DefineJournal{aaca}{0188-7009}
{Adv. Appl. Clifford Algebr.}
{Advances in Applied Clifford Algebras}
\DefineJournal{aam}{?aam}
{Adv. Appl. Math.}
{Advances in Applied Mathematics}
\DefineJournal{aamm}{2070-0733}
{Adv. Appl. Math. Mech.}
{Advances in Applied Mathematics and Mechanics}
\DefineJournal{aams}{0974-6803}
{Adv. Appl. Math. Sci.}
{Advances and Applications in Mathematical Sciences}
\DefineJournal{aapr}{?aapr}
{Adv. Appl. Pattern Recogn.}
{Advanced Applications in Pattern Recognition}
\DefineJournal{aass}{0974-6811}
{Adv. Appl. Stat. Sci.}
{Advances and Applications in Statistical Sciences}
\DefineJournal{acv}{?acv}
{Adv. CAD VLSI}
{Advances in CAD for VLSI}
\DefineJournal{acv}{1864-8258}
{Adv. Calc. Var.}
{Advances in Calculus of Variations}
\DefineJournal{acsamj}{0219-5259}
{Adv. Complex Syst.}
{Advances in Complex Systems. A Multidisciplinary Journal}
\DefineJournal{acfd}{?acfd}
{Adv. Comput. Fluid Dyn.}
{Advances in Computational Fluid Dynamics}
\DefineJournal{acirbs}{2327-0411}
{Adv. Comput. Intell. Robot. ACIR Book Ser.}
{Advances in Computational Intelligence and Robotics (ACIR) Book Series}
\DefineJournal{acms}{1388-4301}
{Adv. Comput. Manag. Sci.}
{Advances in Computational Management Science}
\DefineJournal{acm}{1019-7168}
{Adv. Comput. Math.}
{Advances in Computational Mathematics}
\DefineJournal{acst}{2198-2686}
{Adv. Comput. Sci. Technol.}
{Advances in Computer Science and Technology}
\DefineJournal{acvpr}{2191-6586}
{Adv. Comput. Vis. Pattern Recognit.}
{Advances in Computer Vision and Pattern Recognition}
\DefineJournal{aacne}{2195-3708}
{Adv. Course Nucl. Eng.}
{An Advanced Course in Nuclear Engineering}
\DefineJournal{acmcb}{2297-0304}
{Adv. Courses Math. CRM Barcelona}
{Advanced Courses in Mathematics. CRM Barcelona}
\DefineJournal{adaca}{1862-5347}
{Adv. Data Anal. Classif.}
{Advances in Data Analysis and Classification. ADAC}
\DefineJournal{adsaa}{2424-922X}
{Adv. Data Sci. Adapt. Anal.}
{Advances in Data Science and Adaptive Analysis}
\DefineJournal{ads}{2090-3359}
{Adv. Decis. Sci.}
{Advances in Decision Sciences}
\DefineJournal{add}{2197-117X}
{Adv. Delays Dyn.}
{Advances in Delays and Dynamics}
\DefineJournal{adc}{?adc}
{Adv. Des. Control}
{Advances in Design and Control}
\DefineJournal{ade}{1687-1847}
{Adv. Difference Equ.}
{Advances in Difference Equations}
\DefineJournal{ade}{1079-9389}
{Adv. Differential Equations}
{Advances in Differential Equations}
\DefineJournal{adsa}{0973-5321}
{Adv. Dyn. Syst. Appl.}
{Advances in Dynamical Systems and Applications}
\DefineJournal{ae}{0731-9053}
{Adv. Econom.}
{Advances in Econometrics}
\DefineJournal{aemb}{0065-2598}
{Adv. Exp. Med. Biol.}
{Advances in Experimental Medicine and Biology}
\DefineJournal{afs}{1687-7101}
{Adv. Fuzzy Syst.}
{Advances in Fuzzy Systems}
\DefineJournal{ag}{1615-715X}
{Adv. Geom.}
{Advances in Geometry}
\DefineJournal{agemm}{1866-8348}
{Adv. Geophys. Environ. Mech. Math.}
{Advances in Geophysical and Environmental Mechanics and Mathematics}
\DefineJournal{agdn}{1871-935X}
{Adv. Group Decis. Negot.}
{Advances in Group Decision and Negotiation}
\DefineJournal{agta}{2499-1287}
{Adv. Group Theory Appl.}
{Advances in Group Theory and Applications}
\DefineJournal{ahep}{1687-7357}
{Adv. High Energy Phys.}
{Advances in High Energy Physics}
\DefineJournal{aic}{?aic}
{Adv. Image Comm.}
{Advances in Image Communication}
\DefineJournal{aam}{0196-8858}
{Adv. in Appl. Math.}
{Advances in Applied Mathematics}
\DefineJournal{aap}{0001-8678}
{Adv. in Appl. Probab.}
{Advances in Applied Probability}
\DefineJournal{aic}{1430-9491}
{Adv. Ind. Control}
{Advances in Industrial Control}
\DefineJournal{aikp}{1610-3947}
{Adv. Inf. Knowl. Process.}
{Advanced Information and Knowledge Processing}
\DefineJournal{aisc}{2194-5357}
{Adv. Intell. Syst. Comput.}
{Advances in Intelligent Systems and Computing}
\DefineJournal{ajbe}{2197-8859}
{Adv. Jpn. Bus. Econ.}
{Advances in Japanese Business and Economics}
\DefineJournal{alm}{2379-3589}
{Adv. Lect. Math. (ALM)}
{Advanced Lectures in Mathematics (ALM)}
\DefineJournal{am}{0001-8708}
{Adv. Math.}
{Advances in Mathematics}
\DefineJournal{amsj}{1000-0917}
{Adv. Math. (China)}
{Advances in Mathematics (China). Shuxue Jinzhan}
\DefineJournal{amc}{1930-5346}
{Adv. Math. Commun.}
{Advances in Mathematics of Communications}
\DefineJournal{ame}{1866-2226}
{Adv. Math. Econ.}
{Advances in Mathematical Economics}
\DefineJournal{ame}{1869-4918}
{Adv. Math. Educ.}
{Advances in Mathematics Education}
\DefineJournal{amfm}{2297-0320}
{Adv. Math. Fluid Mech.}
{Advances in Mathematical Fluid Mechanics}
\DefineJournal{amp}{1687-9120}
{Adv. Math. Phys.}
{Advances in Mathematical Physics}
\DefineJournal{ams}{?ams}
{Adv. Math. Sci.}
{Advances in the Mathematical Sciences}
\DefineJournal{amsa}{1343-4373}
{Adv. Math. Sci. Appl.}
{Advances in Mathematical Sciences and Applications}
\DefineJournal{amm}{1571-8689}
{Adv. Mech. Math.}
{Advances in Mechanics and Mathematics}
\DefineJournal{ammebs}{2328-8205}
{Adv. Mechatron. Mech. Eng. (AMME) Book Ser.}
{Advances in Mechatronics and Mechanical Engineering (AMME) Book Series}
\DefineJournal{ana}{2191-9496}
{Adv. Nonlinear Anal.}
{Advances in Nonlinear Analysis}
\DefineJournal{ans}{1536-1365}
{Adv. Nonlinear Stud.}
{Advanced Nonlinear Studies}
\DefineJournal{aor}{1687-9147}
{Adv. Oper. Res.}
{Advances in Operations Research}
\DefineJournal{aot}{2538-225X}
{Adv. Oper. Theory}
{Advances in Operator Theory}
\DefineJournal{apde}{?apde}
{Adv. Partial Differ. Equ. (Basel)}
{Advances in Partial Differential Equations (Basel)}
\DefineJournal{apt}{?apt}
{Adv. Probab. Theory}
{Advances in Probability Theory}
\DefineJournal{ap}{?ap}
{Adv. Psych.}
{Advances in Psychology}
\DefineJournal{apam}{1867-1152}
{Adv. Pure Appl. Math.}
{Advances in Pure and Applied Mathematics}
\DefineJournal{aqafa}{1793-0952}
{Adv. Quant. Anal. Finance Account.}
{Advances in Quantitative Analysis of Finance and Accounting}
\DefineJournal{astucs}{?astucs}
{Adv. Sci. Tech. USSR Chem. Ser.}
{Advances in Science and Technology in the USSR: Chemistry Series}
\DefineJournal{asap}{?asap}
{Adv. Ser. Appl. Phys.}
{Advanced Series in Applied Physics}
\DefineJournal{asdhep}{0218-0324}
{Adv. Ser. Dir. High Energy Phys.}
{Advanced Series on Directions in High Energy Physics}
\DefineJournal{asmp}{?asmp}
{Adv. Ser. Math. Psychol.}
{Advanced Series on Mathematical Psychology}
\DefineJournal{asnd}{?asnd}
{Adv. Ser. Nonlinear Dynam.}
{Advanced Series in Nonlinear Dynamics}
\DefineJournal{asssap}{?asssap}
{Adv. Ser. Stat. Sci. Appl. Probab.}
{Advanced Series on Statistical Science & Applied Probability}
\DefineJournal{ass}{1430-9602}
{Adv. Spat. Sci.}
{Advances in Spatial Science}
\DefineJournal{asm}{1869-8433}
{Adv. Struct. Mater.}
{Advanced Structured Materials}
\DefineJournal{aspm}{?aspm}
{Adv. Stud. Pure Math.}
{Advanced Studies in Pure Mathematics}
\DefineJournal{aspm}{?aspm}
{Adv. Stud. Pure Math.}
{Advanced Studies in Pure Mathematics}
\DefineJournal{astae}{1570-5811}
{Adv. Stud. Theoret. Appl. Econometrics}
{Advanced Studies in Theoretical and Applied Econometrics}
\DefineJournal{atcsp}{1439-2232}
{Adv. Textb. Control Signal Process.}
{Advanced Textbooks in Control and Signal Processing}
\DefineJournal{atm}{2059-769X}
{Adv. Textb. Math.}
{Advanced Textbooks in Mathematics}
\DefineJournal{atmp}{1095-0761}
{Adv. Theor. Math. Phys.}
{Advances in Theoretical and Mathematical Physics}
\DefineJournal{atmes}{?atmes}
{Adv. Topics Mech. Engrg. Ser.}
{Advanced Topics in Mechanical Engineering Series}
\DefineJournal{am}{0001-9054}
{Aequationes Math.}
{Aequationes Mathematicae}
\DefineJournal{ai}{?ai}
{Afd. Inform.}
{Afdeling Informatica}
\DefineJournal{anw}{?anw}
{Afd. Numer. Wisk.}
{Afdeling Numerieke Wiskunde}
\DefineJournal{acp}{?acp}
{AFIPS Conf. Proc.}
{AFIPS Conference Proceedings}
\DefineJournal{adjm}{1539-854X}
{Afr. Diaspora J. Math.}
{African Diaspora Journal of Mathematics}
\DefineJournal{am}{1012-9405}
{Afr. Mat.}
{Afrika Matematika}
\DefineJournal{amaaapajm}{2305-3836}
{Afr. Math. Ann. AFMA}
{Africa Mathematics Annals. AFMA. A Pan African Journal of Mathematics}
\DefineJournal{as}{2316-090X}
{Afr. Stat.}
{Afrika Statistika}
\DefineJournal{am}{?am}
{Agora Math.}
{Agora Mathematica}
\DefineJournal{actejai}{0921-7126}
{AI Commun.}
{AI Communications. The European Journal on Artificial Intelligence}
\DefineJournal{aimls}{?aimls}
{AIMS Libr. Ser.}
{African Institute of Mathematics (AIMS) Library Series}
\DefineJournal{asam}{?asam}
{AIMS Ser. Appl. Math.}
{AIMS Series on Applied Mathematics}
\DefineJournal{asdeds}{?asdeds}
{AIMS Ser. Differ. Equ. Dyn. Syst.}
{AIMS Series on Differential Equations & Dynamical Systems}
\DefineJournal{asrcd}{?asrcd}
{AIMS Ser. Random Comput. Dyn.}
{AIMS Series on Random and Computational Dynamics}
\DefineJournal{aijgc}{0972-8600}
{AKCE Int. J. Graphs Comb.}
{AKCE International Journal of Graphs and Combinatorics}
\DefineJournal{ajm}{1930-1235}
{Albanian J. Math.}
{Albanian Journal of Mathematics}
\DefineJournal{ap}{?ap}
{Alber-Reihe Philos.}
{Alber-Reihe: Philosophie}
\DefineJournal{alajpms}{1980-0436}
{ALEA Lat. Am. J. Probab. Math. Stat.}
{ALEA. Latin American Journal of Probability and Mathematical Statistics}
\DefineJournal{a}{?a}
{ALEF}
{ALEF}
\DefineJournal{aa}{1572-5553}
{Algebr. Appl.}
{Algebra and Applications}
\DefineJournal{ac}{2589-5486}
{Algebr. Comb.}
{Algebraic Combinatorics}
\DefineJournal{ag}{2214-2584}
{Algebr. Geom.}
{Algebraic Geometry}
\DefineJournal{agt}{1472-2747}
{Algebr. Geom. Topol.}
{Algebraic & Geometric Topology}
\DefineJournal{art}{1386-923X}
{Algebr. Represent. Theory}
{Algebras and Representation Theory}
\DefineJournal{lacm}{?lacm}
{Algebra Appl. Class. Mod.}
{L'Algebra e le sue Applicazioni tra Classico e Moderno}
\DefineJournal{ac}{1005-3867}
{Algebra Colloq.}
{Algebra Colloquium}
\DefineJournal{adm}{1726-3255}
{Algebra Discrete Math.}
{Algebra and Discrete Mathematics}
\DefineJournal{ranaa}{0234-0852}
{Algebra i Analiz}
{Rossiiskaya Akademiya Nauk. Algebra i Analiz}
\DefineJournal{al}{0002-5232}
{Algebra Logic}
{Algebra and Logic}
\DefineJournal{alidmi}{0373-9252}
{Algebra Logika}
{Algebra i Logika. Institut Diskretnoi Matematiki i Informatiki}
\DefineJournal{ant}{1937-0652}
{Algebra Number Theory}
{Algebra & Number Theory}
\DefineJournal{au}{0002-5240}
{Algebra Universalis}
{Algebra Universalis}
\DefineJournal{af}{2158-5571}
{Algorithmic Finance}
{Algorithmic Finance}
\DefineJournal{aaijcs}{0178-4617}
{Algorithmica}
{Algorithmica. An International Journal in Computer Science}
\DefineJournal{a}{1999-4893}
{Algorithms (Basel)}
{Algorithms (Basel)}
\DefineJournal{ac}{0937-5511}
{Algorithms Combin.}
{Algorithms and Combinatorics}
\DefineJournal{a}{?a}
{Algoritmica}
{Algoritmica}
\DefineJournal{tabm}{0304-9787}
{Aligarh Bull. Math.}
{The Aligarh Bulletin of Mathematics}
\DefineJournal{tajs}{0971-0388}
{Aligarh J. Statist.}
{The Aligarh Journal of Statistics}
\DefineJournal{aml}{0133-3399}
{Alkalmaz. Mat. Lapok}
{Alkalmazott Matematikai Lapok}
\DefineJournal{a}{?a}
{AMD}
{AMD}
\DefineJournal{ajm}{0002-9327}
{Amer. J. Math.}
{American Journal of Mathematics}
\DefineJournal{amm}{0002-9890}
{Amer. Math. Monthly}
{American Mathematical Monthly}
\DefineJournal{amscp}{0065-9258}
{Amer. Math. Soc. Colloq. Publ.}
{American Mathematical Society Colloquium Publications}
\DefineJournal{amsts}{0065-9290}
{Amer. Math. Soc. Transl. Ser. 2}
{American Mathematical Society Translations, Series 2}
\DefineJournal{apqms}{?apqms}
{Amer. Philos. Quart. Monogr. Ser.}
{American Philosophical Quarterly Monograph Series}
\DefineJournal{tas}{0003-1305}
{Amer. Statist.}
{The American Statistician}
\DefineJournal{ascln}{?ascln}
{AMS Short Course Lecture Notes}
{AMS Short Course Lecture Notes}
\DefineJournal{asthlssishls}{?asthlssishls}
{Amst. Stud. Theory Hist. Linguist. Sci. Ser. III Stud. Hist. Lang. Sci.}
{Amsterdam Studies in the Theory and History of Linguistic Science. Series III: Studies in the History of the Language Sciences}
\DefineJournal{aabcabas}{0001-3765}
{An. Acad. Brasil. Cienc.}
{Anais da Academia Brasileira de Ciencias. Annals of the Brazilian Academy of Sciences}
\DefineJournal{asuicisnmaacum}{1221-8421}
{An. Stiint. Univ. Al. I. Cuza Iasi. Mat. (N.S.)}
{Analele Stiintifice ale Universitatii ``Al. I. Cuza'' din Iasi. Serie Noua. Matematica. Annals of the Alexandru Cuza University. Mathematics}
\DefineJournal{asucsmmjouc}{1224-1784}
{An. Stiint. Univ. ``Ovidius'' Constanta Ser. Mat.}
{Analele Stiintifice ale Universitatii ``Ovidius'' Constanta. Seria Matematica. Mathematical Journal of the Ovidius University of Constantza}
\DefineJournal{aubi}{1224-7170}
{An. Univ. Bucur. Inform.}
{Analele Universitatii Bucuresti. Informatica}
\DefineJournal{aucsmaucmcss}{1223-6934}
{An. Univ. Craiova Ser. Mat. Inform.}
{Analele Universitatii din Craiova. Seria Matematica-Informatica. Annals of the University of Craiova. Mathematics and Computer Science Series}
\DefineJournal{aujgfimfmtajugfimptm}{2067-2071}
{An. Univ. Dunarea de Jos Galati Fasc. II Mat. Fiz. Mec. Teor.}
{Analele Universitatii ``Dunarea de Jos'' din Galati. Fascicula II. Matematica, Fizica, Mecanica Teoretica. Annals of the ``Dunarea de Jos'' University of Galati. Fascicle II. Mathematics, Physics, Theoretical Mechanics}
\DefineJournal{auofm}{1221-1265}
{An. Univ. Oradea Fasc. Mat.}
{Analele Universitatii din Oradea. Fascicola Matematica}
\DefineJournal{aushsmashums}{1841-7833}
{An. Univ. Spiru Haret. Ser. Mat.-Inform.}
{Analele Universitatii Spiru Haret. Seria Matematica-Informatica. Annals of Spiru Haret University. Mathematics-Informatics Series}
\DefineJournal{auvtsmawutmcs}{1841-3293}
{An. Univ. Vest Timis. Ser. Mat.-Inform.}
{Analele. Universitatii de Vest din Timisoara. Seria Matematica-Informatica. Annals of West University of Timisoara. Mathematics and Computer Science}
\DefineJournal{aa}{0219-5305}
{Anal. Appl. (Singap.)}
{Analysis and Applications}
\DefineJournal{agms}{2299-3274}
{Anal. Geom. Metr. Spaces}
{Analysis and Geometry in Metric Spaces}
\DefineJournal{agntaij}{2531-7741}
{Anal. Geom. Number Theory}
{Analysis, Geometry and Number Theory. An International Journal}
\DefineJournal{am}{0133-3852}
{Anal. Math.}
{Analysis Mathematica}
\DefineJournal{amp}{1664-2368}
{Anal. Math. Phys.}
{Analysis and Mathematical Physics}
\DefineJournal{amsr}{?amsr}
{Anal. Methods Soc. Res.}
{Analytical Methods for Social Research}
\DefineJournal{ap}{2157-5045}
{Anal. PDE}
{Analysis & PDE}
\DefineJournal{asl}{?asl}
{Anal. Spectrosc. Lib.}
{Analytical Spectroscopy Library}
\DefineJournal{ata}{1672-4070}
{Anal. Theory Appl.}
{Analysis in Theory and Applications}
\DefineJournal{acsp}{1872-082X}
{Analog Circuits Signal Process.}
{Analog Circuits and Signal Processing}
\DefineJournal{aimjaa}{0174-4747}
{Analysis (Berlin)}
{Analysis. International Mathematical Journal of Analysis and its Applications}
\DefineJournal{a}{0003-2638}
{Analysis (Oxford)}
{Analysis}
\DefineJournal{ammtc}{?ammtc}
{Anc. Mediterr. Mediev. Texts Contexts}
{Ancient Mediterranean and Medieval Texts and Contexts}
\DefineJournal{}{?}
{Anhui Daxue Xuebao. Ziran Kexue Ban}
{nan}
\DefineJournal{aarssma}{2066-5997}
{Ann. Acad. Rom. Sci. Ser. Math. Appl.}
{Annals of the Academy of Romanian Scientists. Series on Mathematics and its Applications}
\DefineJournal{aasfm}{1239-629X}
{Ann. Acad. Sci. Fenn. Math.}
{Annales Academiae Scientiarum Fennicae. Mathematica}
\DefineJournal{asfamd}{1239-6303}
{Ann. Acad. Sci. Fenn. Math. Diss.}
{Academiae Scientiarum Fennicae. Annales. Mathematica. Dissertationes}
\DefineJournal{aamysn}{2096-0174}
{Ann. Appl. Math.}
{Annals of Applied Mathematics. Yingyong Shuxue Niankan}
\DefineJournal{taap}{1050-5164}
{Ann. Appl. Probab.}
{The Annals of Applied Probability}
\DefineJournal{taas}{1932-6157}
{Ann. Appl. Stat.}
{The Annals of Applied Statistics}
\DefineJournal{ac}{0218-0006}
{Ann. Comb.}
{Annals of Combinatorics}
\DefineJournal{afstms}{0240-2963}
{Ann. Fac. Sci. Toulouse Math. (6)}
{Annales de la Faculte des Sciences de Toulouse. Mathematiques. Serie 6}
\DefineJournal{af}{1614-2446}
{Ann. Finance}
{Annals of Finance}
\DefineJournal{flba}{0182-4295}
{Ann. Fond. Louis de Broglie}
{Fondation Louis de Broglie. Annales}
\DefineJournal{afa}{2008-8752}
{Ann. Funct. Anal.}
{Annals of Functional Analysis}
\DefineJournal{afmi}{2093-9310}
{Ann. Fuzzy Math. Inform.}
{Annals of Fuzzy Mathematics and Informatics}
\DefineJournal{agag}{0232-704X}
{Ann. Global Anal. Geom.}
{Annals of Global Analysis and Geometry}
\DefineJournal{ahpajtmp}{1424-0637}
{Ann. Henri Poincare}
{Annales Henri Poincare. A Journal of Theoretical and Mathematical Physics}
\DefineJournal{a}{1626-1607}
{Ann. I.S.U.P.}
{Annales de l'I.S.U.P.}
\DefineJournal{ugaf}{0373-0956}
{Ann. Inst. Fourier (Grenoble)}
{Universite de Grenoble. Annales de l'Institut Fourier}
\DefineJournal{ahpanl}{0294-1449}
{Ann. Inst. H. Poincare Anal. Non Lineaire}
{Annales de l'Institut Henri Poincare. Analyse Non Lineaire}
\DefineJournal{ahpdcpi}{2308-5827}
{Ann. Inst. Henri Poincare D}
{Annales de l'Institut Henri Poincare D. Combinatorics, Physics and their Interactions}
\DefineJournal{ahpps}{0246-0203}
{Ann. Inst. Henri Poincare Probab. Stat.}
{Annales de l'Institut Henri Poincare Probabilites et Statistiques}
\DefineJournal{aism}{0020-3157}
{Ann. Inst. Statist. Math.}
{Annals of the Institute of Statistical Mathematics}
\DefineJournal{aisdg}{2474-0179}
{Ann. Internat. Soc. Dynam. Games}
{Annals of the International Society of Dynamic Games}
\DefineJournal{ajaps}{0453-0691}
{Ann. Japan Assoc. Philos. Sci.}
{Annals of the Japan Association for Philosophy of Science}
\DefineJournal{ak}{2379-1683}
{Ann. K-Theory}
{Annals of K-Theory}
\DefineJournal{ampasi}{0373-3114}
{Ann. Mat. Pura Appl. (4)}
{Annali di Matematica Pura ed Applicata. Series IV}
\DefineJournal{amai}{1012-2443}
{Ann. Math. Artif. Intell.}
{Annals of Mathematics and Artificial Intelligence}
\DefineJournal{ambp}{1259-1734}
{Ann. Math. Blaise Pascal}
{Annales Mathematiques Blaise Pascal}
\DefineJournal{ami}{1787-5021}
{Ann. Math. Inform.}
{Annales Mathematicae et Informaticae}
\DefineJournal{amq}{2195-4755}
{Ann. Math. Que.}
{Annales Mathematiques du Quebec}
\DefineJournal{amsa}{2380-288X}
{Ann. Math. Sci. Appl.}
{Annals of Mathematical Sciences and Applications}
\DefineJournal{ams}{0860-2107}
{Ann. Math. Sil.}
{Annales Mathematicae Silesianae}
\DefineJournal{amss}{0003-486X}
{Ann. of Math. (2)}
{Annals of Mathematics. Second Series}
\DefineJournal{ams}{?ams}
{Ann. of Math. Stud.}
{Annals of Mathematics Studies}
\DefineJournal{as}{0003-3790}
{Ann. of Sci.}
{Annals of Science}
\DefineJournal{aor}{0254-5330}
{Ann. Oper. Res.}
{Annals of Operations Research}
\DefineJournal{apjdapps}{2199-2576}
{Ann. PDE}
{Annals of PDE. Journal Dedicated to the Analysis of Problems from Physical Sciences}
\DefineJournal{ap}{0003-3804}
{Ann. Phys.}
{Annalen der Physik}
\DefineJournal{ap}{0003-4916}
{Ann. Physics}
{Annals of Physics}
\DefineJournal{apm}{0066-2216}
{Ann. Polon. Math.}
{Annales Polonici Mathematici}
\DefineJournal{tap}{0091-1798}
{Ann. Probab.}
{The Annals of Probability}
\DefineJournal{apal}{0168-0072}
{Ann. Pure Appl. Logic}
{Annals of Pure and Applied Logic}
\DefineJournal{arap}{?arap}
{Ann. Rev. Automat. Programming}
{Annual Review in Automatic Programming}
\DefineJournal{arnps}{0163-8998}
{Ann. Rev. Nuclear Particle Sci.}
{Annual Review of Nuclear and Particle Science}
\DefineJournal{asnspcssv}{0391-173X}
{Ann. Sc. Norm. Super. Pisa Cl. Sci. (5)}
{Annali della Scuola Normale Superiore di Pisa. Classe di Scienze. Serie V}
\DefineJournal{asnsqs}{0012-9593}
{Ann. Sci. Ec. Norm. Super. (4)}
{Annales Scientifiques de l'Ecole Normale Superieure. Quatrieme Serie}
\DefineJournal{tas}{0090-5364}
{Ann. Statist.}
{The Annals of Statistics}
\DefineJournal{atpsfeac}{1584-4536}
{Ann. Tiberiu Popoviciu Semin. Funct. Equ. Approx. Convexity}
{Annals of the Tiberiu Popoviciu Seminar of Functional Equations, Approximation and Convexity}
\DefineJournal{aubms}{2067-9009}
{Ann. Univ. Buchar. Math. Ser.}
{Annals of the University of Bucharest. Mathematical Series}
\DefineJournal{afsvsm}{0430-3202}
{Ann. Univ. Ferrara Sez. VII Sci. Mat.}
{Annali dell'Universita di Ferrara. Sezione VII. Scienze Matematiche}
\DefineJournal{aumcsam}{0365-1029}
{Ann. Univ. Mariae Curie-Sklodowska Sect. A}
{Annales. Universitatis Mariae Curie-Sklodowska. Sectio A. Mathematica}
\DefineJournal{aumcsai}{1732-1360}
{Ann. Univ. Mariae Curie-Sklodowska Sect. AI-Inform.}
{Annales Universitatis Mariae Curie-Sklodowska. Sectio AI. Informatica}
\DefineJournal{aupcsm}{2081-545X}
{Ann. Univ. Paedagog. Crac. Stud. Math.}
{Annales Universitatis Paedagogicae Cracoviensis. Studia Mathematica}
\DefineJournal{ausbrensm}{0524-9007}
{Ann. Univ. Sci. Budapest. Eotvos Sect. Math.}
{Annales Universitatis Scientiarum Budapestinensis de Rolando Eotvos Nominatae. Sectio Mathematica}
\DefineJournal{ausbrensc}{0138-9491}
{Ann. Univ. Sci. Budapest. Sect. Comput.}
{Annales Universitatis Scientiarum Budapestinensis de Rolando Eotvos Nominatae. Sectio Computatorica}
\DefineJournal{alnml}{?alnml}
{Anneli Lax New Math. Libr.}
{Anneli Lax New Mathematical Library}
\DefineJournal{arc}{1367-5788}
{Annu. Rev. Control}
{Annual Reviews in Control}
\DefineJournal{arfm}{0066-4189}
{Annu. Rev. Fluid Mech.}
{Annual Review of Fluid Mechanics}
\DefineJournal{arsa}{2326-8298}
{Annu. Rev. Stat. Appl.}
{Annual Review of Statistics and its Application}
\DefineJournal{as}{2522-039X}
{Anticip. Sci.}
{Anticipation Science}
\DefineJournal{amrptmsv}{1898-5203}
{Antiq. Math.}
{Antiquitates Mathematicae. Roczniki Polskiego Towarzystwa Matematycznego. Seria VI}
\DefineJournal{am}{?am}
{Anwend.orientier. Math.}
{Anwendungsorientierte Mathematik}
\DefineJournal{aoawpk}{0378-8652}
{Anz. Osterr. Akad. Wiss. Philos.-Hist. Kl.}
{Anzeiger. Osterreichische Akademie der Wissenschaften. Philosophisch-Historiche Klasse}
\DefineJournal{tajtanziamj}{1446-1811}
{ANZIAM J.}
{The ANZIAM Journal. The Australian & New Zealand Industrial and Applied Mathematics Journal}
\DefineJournal{a}{?a}
{Apercu}
{Apercu}
\DefineJournal{am}{?am}
{Aportaciones Mat.}
{Aportaciones Matematicas}
\DefineJournal{amc}{1870-2112}
{Aportaciones Mat. Comun.}
{Aportaciones Matematicas: Comunicaciones}
\DefineJournal{ami}{?ami}
{Aportaciones Mat. Investig.}
{Aportaciones Matematicas: Investigacion}
\DefineJournal{aaecc}{0938-1279}
{Appl. Algebra Engrg. Comm. Comput.}
{Applicable Algebra in Engineering, Communication and Computing}
\DefineJournal{aaaij}{0003-6811}
{Appl. Anal.}
{Applicable Analysis. An International Journal}
\DefineJournal{aadm}{1452-8630}
{Appl. Anal. Discrete Math.}
{Applicable Analysis and Discrete Mathematics}
\DefineJournal{aao}{2432-1656}
{Appl. Anal. Optim.}
{Applied Analysis and Optimization}
\DefineJournal{aamaij}{1932-9466}
{Appl. Appl. Math.}
{Applications and Applied Mathematics. An International Journal (AAM)}
\DefineJournal{acsajdacmaaotcs}{0927-2852}
{Appl. Categ. Structures}
{Applied Categorical Structures. A Journal Devoted to Applications of Categorical Methods in Algebra, Analysis, Order, Topology and Computer Science}
\DefineJournal{achattawnaa}{1063-5203}
{Appl. Comput. Harmon. Anal.}
{Applied and Computational Harmonic Analysis. Time-Frequency and Time-Scale Analysis, Wavelets, Numerical Algorithms, and Applications}
\DefineJournal{acmaij}{1683-3511}
{Appl. Comput. Math.}
{Applied and Computational Mathematics. An International Journal}
\DefineJournal{acsbpi}{?acsbpi}
{Appl. Comput. Sci.}
{Applied Computer Science. Berichte zur Praktischen Informatik}
\DefineJournal{agt}{1576-9402}
{Appl. Gen. Topol.}
{Applied General Topology}
\DefineJournal{ams}{0276-8976}
{Appl. Manag. Sci.}
{Applications of Management Science}
\DefineJournal{am}{0862-7940}
{Appl. Math.}
{Applications of Mathematics}
\DefineJournal{amc}{0096-3003}
{Appl. Math. Comput.}
{Applied Mathematics and Computation}
\DefineJournal{ame}{1607-2510}
{Appl. Math. E-Notes}
{Applied Mathematics E-Notes}
\DefineJournal{amf}{1350-486X}
{Appl. Math. Finance}
{Applied Mathematical Finance}
\DefineJournal{amis}{1935-0090}
{Appl. Math. Inf. Sci.}
{Applied Mathematics & Information Sciences}
\DefineJournal{amim}{1512-0074}
{Appl. Math. Inform. Mech.}
{Applied Mathematics, Informatics and Mechanics}
\DefineJournal{amajcusagysx}{1000-4424}
{Appl. Math. J. Chinese Univ. Ser. A}
{Applied Mathematics. A Journal of Chinese Universities. Series A. Gaoxiao Yingyong Shuxue Xuebao}
\DefineJournal{amajcusb}{1005-1031}
{Appl. Math. J. Chinese Univ. Ser. B}
{Applied Mathematics. A Journal of Chinese Universities. Ser. B}
\DefineJournal{amlaijrp}{0893-9659}
{Appl. Math. Lett.}
{Applied Mathematics Letters. An International Journal of Rapid Publication}
\DefineJournal{ammee}{0253-4827}
{Appl. Math. Mech. (English Ed.)}
{Applied Mathematics and Mechanics. English Edition}
\DefineJournal{ammscees}{0307-904X}
{Appl. Math. Model.}
{Applied Mathematical Modelling. Simulation and Computation for Engineering and Environmental Systems}
\DefineJournal{amns}{2444-8656}
{Appl. Math. Nonlinear Sci.}
{Applied Mathematics and Nonlinear Sciences}
\DefineJournal{amo}{0095-4616}
{Appl. Math. Optim.}
{Applied Mathematics and Optimization}
\DefineJournal{ams}{0066-5452}
{Appl. Math. Sci.}
{Applied Mathematical Sciences}
\DefineJournal{am}{1233-7234}
{Appl. Math. (Warsaw)}
{Applicationes Mathematicae}
\DefineJournal{amtb}{?amtb}
{Appl. Modern Tech. Business}
{Applications of Modern Technology in Business}
\DefineJournal{anha}{2296-5009}
{Appl. Numer. Harmon. Anal.}
{Applied and Numerical Harmonic Analysis}
\DefineJournal{anmaij}{0168-9274}
{Appl. Numer. Math.}
{Applied Numerical Mathematics. An IMACS Journal}
\DefineJournal{ao}{1384-6485}
{Appl. Optim.}
{Applied Optimization}
\DefineJournal{aqf}{?aqf}
{Appl. Quant. Finance}
{Applied Quantitative Finance}
\DefineJournal{aas}{1454-5101}
{Appl. Sci.}
{APPS. Applied Sciences}
\DefineJournal{ase}{2363-4995}
{Appl. Sci. Eng.}
{Applied Sciences and Engineering}
\DefineJournal{asm}{?asm}
{Appl. Sci. Monogr.}
{Applied Sciences. Monographs}
\DefineJournal{asrms}{?asrms}
{Appl. Soc. Res. Methods Ser.}
{Applied Social Research Methods Series}
\DefineJournal{asms}{?asms}
{Appl. Stoch. Methods Ser.}
{Applied Stochastic Methods Series}
\DefineJournal{asmbi}{1524-1904}
{Appl. Stoch. Models Bus. Ind.}
{Applied Stochastic Models in Business and Industry}
\DefineJournal{as}{?as}
{Approaches Semiotics}
{Approaches to Semiotics}
\DefineJournal{asnsps}{?asnsps}
{Appunti. Sc. Norm. Super. Pisa (N. S.)}
{Appunti. Scuola Normale Superiore di Pisa (Nuova Serie)}
\DefineJournal{ajms}{1319-5166}
{Arab J. Math. Sci.}
{Arab Journal of Mathematical Sciences}
\DefineJournal{ajm}{2193-5343}
{Arab. J. Math. (Springer)}
{Arabian Journal of Mathematics}
\DefineJournal{aspahj}{0957-4239}
{Arabic Sci. Philos.}
{Arabic Sciences and Philosophy. A Historical Journal}
\DefineJournal{aimmdb}{?aimmdb}
{Arbeitsber. Inst. Math. Masch. Datenverarb., Band 15}
{Arbeitsberichte des Instituts fur Mathematische Maschinen und Datenverarbeitung, Band 15}
\DefineJournal{asbwraa}{?asbwraa}
{Arbor Scientiarum: Beitrage Wissenschaftsgeschichte, Reihe A: Abhandlungen}
{Arbor Scientiarum: Beitrage Wissenschaftsgeschichte, Reihe A: Abhandlungen}
\DefineJournal{acmesar}{1134-3060}
{Arch. Comput. Methods Eng.}
{Archives of Computational Methods in Engineering. State of the Art Reviews}
\DefineJournal{acspascacr}{1230-2384}
{Arch. Control Sci.}
{Archives of Control Sciences. Polish Academy of Sciences. Committee of Automatic Control and Robotics}
\DefineJournal{ahes}{0003-9519}
{Arch. Hist. Exact Sci.}
{Archive for History of Exact Sciences}
\DefineJournal{am}{0003-889X}
{Arch. Math. (Basel)}
{Archiv der Mathematik}
\DefineJournal{umbfsnam}{0044-8753}
{Arch. Math. (Brno)}
{Universitatis Masarykianae Brunensis. Facultas Scientiarum Naturalium. Archivum Mathematicum}
\DefineJournal{aml}{0933-5846}
{Arch. Math. Logic}
{Archive for Mathematical Logic}
\DefineJournal{pasiftramms}{0373-2029}
{Arch. Mech. (Arch. Mech. Stos.)}
{Polish Academy of Sciences. Institute of Fundamental Technological Research. Archives of Mechanics (Archiwum Mechaniki Stosowanej)}
\DefineJournal{arma}{0003-9527}
{Arch. Ration. Mech. Anal.}
{Archive for Rational Mechanics and Analysis}
\DefineJournal{anshpst}{1385-0180}
{Archimedes}
{Archimedes: New Studies in the History and Philosophy of Science and Technology}
\DefineJournal{al}{?al}
{Argum. Libr.}
{Argumentation Library}
\DefineJournal{al}{1566-7650}
{Argum. Libr.}
{Argumentation Library}
\DefineJournal{ararima}{1638-5713}
{ARIMA Rev. Afr. Rech. Inform. Math. Appl.}
{ARIMA. Revue Africaine de la Recherche en Informatique et Mathematiques Appliquees}
\DefineJournal{am}{0004-2080}
{Ark. Mat.}
{Arkiv for Matematik}
\DefineJournal{a}{0004-1920}
{Arkhimedes}
{Arkhimedes}
\DefineJournal{ajm}{1829-1163}
{Armen. J. Math.}
{Armenian Journal of Mathematics}
\DefineJournal{amtcs}{?amtcs}
{Army Materials Tech. Conf. Ser.}
{Army Materials Technology Conference Series}
\DefineJournal{armls}{?armls}
{Arne Ryde Meml. Lect. Ser.}
{Arne Ryde Memorial Lectures Series}
\DefineJournal{aas}{?aas}
{Arnold Appl. Stat.}
{Arnold Applications of Statistics}
\DefineJournal{amj}{2199-6792}
{Arnold Math. J.}
{Arnold Mathematical Journal}
\DefineJournal{ac}{0381-7032}
{Ars Combin.}
{Ars Combinatoria}
\DefineJournal{amc}{1855-3966}
{Ars Math. Contemp.}
{Ars Mathematica Contemporanea}
\DefineJournal{tahml}{?tahml}
{Artech House Microw. Lib.}
{The Artech House Microwave Library}
\DefineJournal{ahtl}{?ahtl}
{Artech House Telecommun. Libr.}
{Artech House Telecommunications Library}
\DefineJournal{aifta}{2365-3051}
{Artif. Intell. Found. Theory Algorithms}
{Artificial Intelligence: Foundations, Theory, and Algorithms}
\DefineJournal{ai}{0004-3702}
{Artificial Intelligence}
{Artificial Intelligence}
\DefineJournal{ait}{?ait}
{Artificial Intelligence Texts}
{Artificial Intelligence Texts}
\DefineJournal{assrss}{?assrss}
{ASA-CRC Ser. Stat. Reason. Sci. Soc.}
{ASA-CRC Series on Statistical Reasoning in Science and Society}
\DefineJournal{assap}{?assap}
{ASA-SIAM Ser. Stat. Appl. Probab.}
{ASA-SIAM Series on Statistics and Applied Probability}
\DefineJournal{apmn}{2010-3484}
{Asia Pac. Math. Newsl.}
{Asia Pacific Mathematics Newsletter}
\DefineJournal{ajor}{0217-5959}
{Asia-Pac. J. Oper. Res.}
{Asia-Pacific Journal of Operational Research}
\DefineJournal{ajc}{1561-8625}
{Asian J. Control}
{Asian Journal of Control}
\DefineJournal{ajm}{1093-6106}
{Asian J. Math.}
{Asian Journal of Mathematics}
\DefineJournal{ajm}{1793-5571}
{Asian-Eur. J. Math.}
{Asian-European Journal of Mathematics}
\DefineJournal{aa}{2522-5162}
{Asset Anal.}
{Asset Analytics}
\DefineJournal{aapems}{?aapems}
{Assoc. American Publ. Electron. Manuscript Ser.}
{Association of American Publishers Electronic Manuscript Series}
\DefineJournal{awms}{2364-5733}
{Assoc. Women Math. Ser.}
{Association for Women in Mathematics Series}
\DefineJournal{aasaajgss}{1863-8171}
{AStA Adv. Stat. Anal.}
{AStA. Advances in Statistical Analysis. A Journal of the German Statistical Society}
\DefineJournal{a}{0303-1179}
{Asterisque}
{Asterisque}
\DefineJournal{abtjiaa}{0515-0361}
{Astin Bull.}
{Astin Bulletin. The Journal of the International Actuarial Association}
\DefineJournal{aal}{0941-7834}
{Astronom. Astrophys. Lib.}
{Astronomy and Astrophysics Library}
\DefineJournal{a}{0202-0742}
{Astronomiya}
{Astronomiya}
\DefineJournal{assaijaass}{0004-640X}
{Astrophys. Space Sci.}
{Astrophysics and Space Science. An International Journal of Astronomy, Astrophysics and Space Science}
\DefineJournal{assl}{0067-0057}
{Astrophys. Space Sci. Libr.}
{Astrophysics and Space Science Library}
\DefineJournal{aa}{0921-7134}
{Asymptot. Anal.}
{Asymptotic Analysis}
\DefineJournal{asocs}{?asocs}
{Athena Sci. Optim. Comput. Ser.}
{Athena Scientific Optimization and Computation Series}
\DefineJournal{ae}{?ae}
{Athenaeum Econom.}
{Athenaeum Economics}
\DefineJournal{amp}{?amp}
{Athenaum Monogr. Philos.}
{Athenaum Monografien. Philosophie}
\DefineJournal{at}{?at}
{Athenaum Taschenbucher}
{Athenaum Taschenbucher}
\DefineJournal{abde}{2405-6405}
{Atlantis Briefs Differ. Equ.}
{Atlantis Briefs in Differential Equations}
\DefineJournal{acis}{1875-7650}
{Atlantis Comput. Intell. Syst.}
{Atlantis Computational Intelligence Systems}
\DefineJournal{asapc}{1879-6923}
{Atlantis Stud. Astropart. Phys. Cosmol.}
{Atlantis Studies in Astroparticle Physics and Cosmology}
\DefineJournal{asc}{2212-8557}
{Atlantis Stud. Comput.}
{Atlantis Studies in Computing}
\DefineJournal{ascffe}{2352-3255}
{Atlantis Stud. Comput. Finance Financ. Eng.}
{Atlantis Studies in Computational Finance and Financial Engineering}
\DefineJournal{asde}{2214-6253}
{Atlantis Stud. Differ. Equ.}
{Atlantis Studies in Differential Equations}
\DefineJournal{asds}{2213-3526}
{Atlantis Stud. Dyn. Syst.}
{Atlantis Studies in Dynamical Systems}
\DefineJournal{asm}{1875-7634}
{Atlantis Stud. Math.}
{Atlantis Studies in Mathematics}
\DefineJournal{asmes}{1875-7642}
{Atlantis Stud. Math. Eng. Sci.}
{Atlantis Studies in Mathematics for Engineering and Science}
\DefineJournal{asmpta}{2211-8055}
{Atlantis Stud. Math. Phys. Theory Appl.}
{Atlantis Studies in Mathematical Physics: Theory and Applications}
\DefineJournal{asps}{1879-6893}
{Atlantis Stud. Probab. Stat.}
{Atlantis Studies in Probability and Statistics}
\DefineJournal{assce}{2352-0590}
{Atlantis Stud. Sci. Comput. Electromagn.}
{Atlantis Studies in Scientific Computing in Electromagnetics}
\DefineJournal{asvg}{2214-0700}
{Atlantis Stud. Var. Geom.}
{Atlantis Studies in Variational Geometry}
\DefineJournal{atg}{?atg}
{Atlantis Trans. Geom.}
{Atlantis Transactions in Geometry}
\DefineJournal{aosl}{1383-8601}
{Atmos. Oceanogr. Sci. Libr.}
{Atmospheric and Oceanographic Sciences Library}
\DefineJournal{aanlrlma}{1120-6330}
{Atti Accad. Naz. Lincei Rend. Lincei Mat. Appl.}
{Atti della Accademia Nazionale dei Lincei. Rendiconti Lincei. Matematica e Applicazioni}
\DefineJournal{aappcsfmnapmns}{1825-1242}
{Atti Accad. Peloritana Pericolanti Cl. Sci. Fis. Mat. Natur.}
{Atti della Accademia Peloritana dei Pericolanti. Classe di Scienze, Fisiche, Matematiche e Naturali. AAPP. Physical, Mathematical, and Natural Sciences}
\DefineJournal{abma}{?abma}
{Auctores Britannici Medii Aevi}
{Auctores Britannici Medii Aevi}
\DefineJournal{am}{?am}
{Aufbaukurs Math.}
{Aufbaukurs Mathematik}
\DefineJournal{admmo}{?admmo}
{Aurora Dover Mod. Math Orig.}
{Aurora Dover Modern Math Originals}
\DefineJournal{tajmaa}{1449-5910}
{Aust. J. Math. Anal. Appl.}
{The Australian Journal of Mathematical Analysis and Applications}
\DefineJournal{anzjs}{1369-1473}
{Aust. N. Z. J. Stat.}
{Australian & New Zealand Journal of Statistics}
\DefineJournal{acsc}{0157-3055}
{Austral. Comput. Sci. Commun.}
{Australian Computer Science Communications}
\DefineJournal{acsc}{?acsc}
{Austral. Comput. Sci. Commun.}
{Australian Computer Science Communications}
\DefineJournal{tamsg}{0311-0729}
{Austral. Math. Soc. Gaz.}
{The Australian Mathematical Society. Gazette}
\DefineJournal{amsls}{?amsls}
{Austral. Math. Soc. Lect. Ser.}
{Australian Mathematical Society Lecture Series}
\DefineJournal{tajc}{1034-4942}
{Australas. J. Combin.}
{The Australasian Journal of Combinatorics}
\DefineJournal{tajl}{1448-5052}
{Australas. J. Log.}
{The Australasian Journal of Logic}
\DefineJournal{apr}{2474-0500}
{Australas. Philos. Rev.}
{Australasian Philosophical Review}
\DefineJournal{a}{?a}
{Auswahl}
{Auswahl}
\DefineJournal{arc}{0005-1179}
{Autom. Remote Control}
{Automation and Remote Control}
\DefineJournal{aies}{?aies}
{Autom.-Control Ind. Eng. Ser.}
{Automation-Control and Industrial Engineering Series}
\DefineJournal{acamsj}{1221-437X}
{Automat. Comput. Appl. Math.}
{Automation Computers Applied Mathematics. Scientific Journal}
\DefineJournal{aajiifac}{0005-1098}
{Automatica J. IFAC}
{Automatica. A Journal of IFAC, the International Federation of Automatic Control}
\DefineJournal{as}{2504-3862}
{Auton. Syst.}
{Autonomic Systems}
\DefineJournal{ranat}{0005-2310}
{Avtomat. i Telemekh.}
{Rossiiskaya Akademiya Nauk. Avtomatika i Telemekhanika}
\DefineJournal{ajm}{2218-6816}
{Azerb. J. Math.}
{Azerbaijan Journal of Mathematics}
\DefineJournal{a}{?a}
{AZimuth}
{AZimuth}
\DefineJournal{tbejte}{2194-6124}
{B. E. J. Theor. Econ.}
{The B. E. Journal of Theoretical Economics}
\DefineJournal{bjga}{1224-2780}
{Balkan J. Geom. Appl.}
{Balkan Journal of Geometry and its Applications}
\DefineJournal{bcp}{0137-6934}
{Banach Center Publ.}
{Banach Center Publications}
\DefineJournal{bjma}{1735-8787}
{Banach J. Math. Anal.}
{Banach Journal of Mathematical Analysis}
\DefineJournal{bnab}{?bnab}
{Bantam New Age Books}
{Bantam New Age Books}
\DefineJournal{b}{0982-5657}
{Basics}
{Basics of}
\DefineJournal{bsw}{?bsw}
{Basiswissen Statist. Wirtschaftswiss.}
{Basiswissen Statistik fur Wirtschaftswissenschaftler}
\DefineJournal{ba}{1936-0975}
{Bayesian Anal.}
{Bayesian Analysis}
\DefineJournal{bbbgnt}{?bbbgnt}
{BBGNT. Berliner Beitr. Gesch. Naturwiss. Tech.}
{BBGNT. Berliner Beitrage zur Geschichte der Naturwissenschaften und der Technik}
\DefineJournal{bs}{?bs}
{BCAM SpringerBriefs}
{BCAM SpringerBriefs}
\DefineJournal{bdxzkbasnup}{0479-8023}
{Beijing Daxue Xuebao Ziran Kexue Ban}
{Beijing Daxue Xuebao. Ziran Kexue Ban. Acta Scientiarum Naturalium Universitatis Pekinensis}
\DefineJournal{}{?}
{Beijing Gongye Daxue Xuebao}
{nan}
\DefineJournal{}{?}
{Beijing Ligong Daxue Xuebao}
{nan}
\DefineJournal{bsdxzkbjbnus}{0476-0301}
{Beijing Shifan Daxue Xuebao}
{Beijing Shifan Daxue Xuebao. Ziran Kexue Ban. Journal of Beijing Normal University (Natural Science)}
\DefineJournal{}{?}
{Beijing Univ. J. Nat. Sci. Ed.}
{nan}
\DefineJournal{bagcag}{0138-4821}
{Beitr. Algebra Geom.}
{Beitrage zur Algebra und Geometrie. Contributions to Algebra and Geometry}
\DefineJournal{bb}{?bb}
{Beitr. Bolzano-Forsch.}
{Beitrage zur Bolzano-Forschung}
\DefineJournal{bdu}{?bdu}
{Beitr. Datenverarb. Unternehmensforsch.}
{Beitrage Datenverarbeitung und Unternehmensforschung}
\DefineJournal{bf}{?bf}
{Beitr. Forschungstech.}
{Beitrage zur Forschungstechnologie}
\DefineJournal{bm}{1610-7578}
{Beitr. Math.}
{Beitrage zur Mathematik}
\DefineJournal{bgr}{?bgr}
{Beltz Grune Reihe}
{Beltz Grune Reihe}
\DefineJournal{ba}{?ba}
{Ber. ATWD}
{Bericht ATWD}
\DefineJournal{bm}{0945-0882}
{Ber. Math.}
{Berichte aus der Mathematik}
\DefineJournal{bw}{0170-6233}
{Ber. Wiss.gesch.}
{Berichte zur Wissenschaftsgeschichte}
\DefineJournal{bgca}{?bgca}
{Berichte German Chapter ACM}
{Berichte des German Chapter of the ACM}
\DefineJournal{bphs}{?bphs}
{Berkeley Papers Hist. Sci.}
{Berkeley Papers in History of Science}
\DefineJournal{bsm}{?bsm}
{Berliner Studienreihe Math.}
{Berliner Studienreihe zur Mathematik}
\DefineJournal{bojbsmsp}{1350-7265}
{Bernoulli}
{Bernoulli. Official Journal of the Bernoulli Society for Mathematical Statistics and Probability}
\DefineJournal{bscn}{2520-159X}
{Bernstein Ser. Comput. Neurosci.}
{Bernstein Series in Computational Neuroscience}
\DefineJournal{b}{?b}
{BestMasters}
{BestMasters}
\DefineJournal{ba}{?ba}
{Bibl. Avtomat.}
{Biblioteka po Avtomatike}
\DefineJournal{ba}{?ba}
{Bibl. Avtomat.}
{Biblioteka po Avtomatike}
\DefineJournal{be}{?be}
{Bibl. Ekonom.}
{Biblioteka Ekonometryczna}
\DefineJournal{bi}{?bi}
{Bibl. Inzh.}
{Biblioteka Inzhenera}
\DefineJournal{bp}{1122-5505}
{Bibl. Physis}
{Biblioteca di Physis}
\DefineJournal{bs}{0224-5159}
{Bibl. Sci.}
{Bibliotheque Scientifique}
\DefineJournal{bta}{?bta}
{Bibl. Techn. Allgemeinwiss.}
{Bibliothek des Technischen Allgemeinwissens}
\DefineJournal{bum}{?bum}
{Bibl. Uchitelya Mat.}
{Biblioteka Uchitelya Matematiki}
\DefineJournal{b}{?b}
{Bibl. ``Znanie''}
{Biblioteka ``Znanie''}
\DefineJournal{tbq}{?tbq}
{Big Quest.}
{The Big Questions}
\DefineJournal{bc}{0340-1200}
{Biol. Cybernet.}
{Biological Cybernetics}
\DefineJournal{bmpbe}{1618-7210}
{Biol. Med. Phys. Biomed. Eng.}
{Biological and Medical Physics, Biomedical Engineering}
\DefineJournal{bj}{0323-3847}
{Biom. J.}
{Biometrical Journal}
\DefineJournal{bijmmmb}{1314-684X}
{BIOMATH}
{BIOMATH. International Journal on Mathematical Methods and Models in Biosciences}
\DefineJournal{bt}{?bt}
{Biomed. Tech.}
{Biomedizinische Technik}
\DefineJournal{bjibs}{0006-341X}
{Biometrics}
{Biometrics. Journal of the International Biometric Society}
\DefineJournal{b}{0006-3444}
{Biometrika}
{Biometrika}
\DefineJournal{b}{1468-4357}
{Biostatistics}
{Biostatistics}
\DefineJournal{bb}{2195-3562}
{Biosyst. Biorobot.}
{Biosystems & Biorobotics}
\DefineJournal{batbl}{1019-6242}
{Birkhauser Adv. Texts Basler Lehrbucher}
{Birkhauser Advanced Texts: Basler Lehrbucher}
\DefineJournal{bs}{?bs}
{Birkhauser Skr.}
{Birkhauser Skripten}
\DefineJournal{kkbamcsthi}{?kkbamcsthi}
{Birla Acad. Monogr. Cult. Sci. Technol. Herit. India}
{K. K. Birla Academy Monographs on the Cultural, Scientific and Technological Heritage of India}
\DefineJournal{bnm}{0006-3835}
{BIT}
{BIT. Numerical Mathematics}
\DefineJournal{bcice}{?bcice}
{Bloomsbury Crit. Introd. Contemp. Epistemol.}
{Bloomsbury Critical Introductions to Contemporary Epistemology}
\DefineJournal{bsat}{?bsat}
{Bloomsbury Stud. Aristot. Tradit.}
{Bloomsbury Studies in the Aristotelian Tradition}
\DefineJournal{ibs}{2239-7477}
{Blu Pagine Sci.}
{I Blu---Pagine di Scienza}
\DefineJournal{bss}{2039-1471}
{Bocconi Springer Ser.}
{Bocconi & Springer Series}
\DefineJournal{bsp}{1384-668X}
{Boch. Stud. Philos.}
{Bochumer Studien zur Philosophie}
\DefineJournal{bamv}{1315-4125}
{Bol. Asoc. Mat. Venez.}
{Boletin de la Asociacion Matematica Venezolana}
\DefineJournal{bmns}{0120-0380}
{Bol. Mat.}
{Boletin de Matematicas. Nueva Serie}
\DefineJournal{bsmmts}{1405-213X}
{Bol. Soc. Mat. Mex. (3)}
{Boletin de la Sociedad Matematica Mexicana. Third Series}
\DefineJournal{bspms}{0037-8712}
{Bol. Soc. Parana. Mat. (3)}
{Boletim da Sociedade Paranaense de Matematica. 3rd Serie}
\DefineJournal{bspm}{0872-3672}
{Bol. Soc. Port. Mat.}
{Boletim da Sociedade Portuguesa de Matematica}
\DefineJournal{bssm}{0392-4432}
{Boll. Stor. Sci. Mat.}
{Bollettino di Storia delle Scienze Matematiche}
\DefineJournal{bmi}{1972-6724}
{Boll. Unione Mat. Ital.}
{Bollettino dell'Unione Matematica Italiana}
\DefineJournal{b}{?b}
{Bonn-IR}
{Bonn-IR}
\DefineJournal{bp}{?bp}
{Books Print}
{Books in Print}
\DefineJournal{bsphs}{0068-0346}
{Boston Stud. Philos. Hist. Sci.}
{Boston Studies in the Philosophy and History of Science}
\DefineJournal{bvp}{1687-2770}
{Bound. Value Probl.}
{Boundary Value Problems}
\DefineJournal{bjps}{0103-0752}
{Braz. J. Probab. Stat.}
{Brazilian Journal of Probability and Statistics}
\DefineJournal{bshsbjhs}{0007-0874}
{British J. Hist. Sci.}
{British Society for the History of Science. British Journal for the History of Science}
\DefineJournal{tbjps}{0007-0882}
{British J. Philos. Sci.}
{The British Journal for the Philosophy of Science}
\DefineJournal{bm}{?bm}
{Brucken Math.}
{Brucken zur Mathematik}
\DefineJournal{bpmas}{2240-2829}
{Bruno Pini Math. Anal. Semin.}
{Bruno Pini Mathematical Analysis Seminar}
\DefineJournal{bp}{1843-2654}
{BSG Proc.}
{BSG Proceedings}
\DefineJournal{bbjbshm}{1749-8430}
{BSHM Bull.}
{BSHM Bulletin. Journal of the British Society for the History of Mathematics}
\DefineJournal{bcgets}{?bcgets}
{BTS Compt.-IUT Gestion Enseign. Tech. Super.}
{BTS Comptable-IUT de Gestion. Enseignement Technique Superieur}
\DefineJournal{basrmmianrmm}{1024-7696}
{Bul. Acad. Stiinte Repub. Mold. Mat.}
{Buletinul Academiei de Stiinte a Republicii Moldova. Matematica. Izvestiya Akademii Nauk Respubliki Moldova. Matematika}
\DefineJournal{bsutsmsbputtmp}{1224-6069}
{Bul. Stiint. Univ. Politeh. Timis. Ser. Mat. Fiz.}
{Buletinul Stiintific al Universitatii ``Politehnica'' din Timisoara. Seria Matematica-Fizica. Scientific Bulletin of the Politehnica University of Timisoara. Transactions on Mathematics & Physics}
\DefineJournal{bams}{0971-0493}
{Bull. Allahabad Math. Soc.}
{Bulletin of the Allahabad Mathematical Society}
\DefineJournal{amsbns}{0273-0979}
{Bull. Amer. Math. Soc. (N.S.)}
{American Mathematical Society. Bulletin. New Series}
\DefineJournal{bams}{0004-9727}
{Bull. Aust. Math. Soc.}
{Bulletin of the Australian Mathematical Society}
\DefineJournal{bbmsss}{1370-1444}
{Bull. Belg. Math. Soc. Simon Stevin}
{Bulletin of the Belgian Mathematical Society. Simon Stevin}
\DefineJournal{bbmsnsbsbm}{1678-7544}
{Bull. Braz. Math. Soc. (N.S.)}
{Bulletin of the Brazilian Mathematical Society. New Series. Boletim da Sociedade Brasileira de Matematica}
\DefineJournal{bcms}{0008-0659}
{Bull. Calcutta Math. Soc.}
{Bulletin of the Calcutta Mathematical Society}
\DefineJournal{bcsmnsm}{0561-7332}
{Bull. Cl. Sci. Math. Nat. Sci. Math.}
{Bulletin. Classe des Sciences Mathematiques et Naturelles. Sciences Mathematiques}
\DefineJournal{bcam}{2244-8659}
{Bull. Comput. Appl. Math.}
{Bulletin of Computational Applied Mathematics}
\DefineJournal{ber}{0307-3378}
{Bull. Econ. Res.}
{Bulletin of Economic Research}
\DefineJournal{beatcse}{0252-9742}
{Bull. Eur. Assoc. Theor. Comput. Sci. EATCS}
{Bulletin of the European Association for Theoretical Computer Science. EATCS}
\DefineJournal{bfekuns}{0389-6692}
{Bull. Fac. Ed. Kagoshima Univ. Natur. Sci.}
{Bulletin of the Faculty of Education. Kagoshima University. Natural Science}
\DefineJournal{wufebns}{1342-4645}
{Bull. Fac. Ed. Wakayama Univ. Natur. Sci.}
{Wakayama University. Faculty of Education. Bulletin. Natural Science}
\DefineJournal{bfsur}{0286-9640}
{Bull. Fac. Sci. Univ. Ryukyus}
{Bulletin of the Faculty of Science. University of the Ryukyus}
\DefineJournal{bgnasns}{0132-1447}
{Bull. Georgian Natl. Acad. Sci. (N.S.)}
{Bulletin of the Georgian National Academy of Sciences. New Series}
\DefineJournal{bhms}{?bhms}
{Bull. Hellenic Math. Soc.}
{Bulletin of the Hellenic Mathematical Society}
\DefineJournal{bic}{0286-522X}
{Bull. Inform. Cybernet.}
{Bulletin of Informatics and Cybernetics}
\DefineJournal{bica}{1183-1278}
{Bull. Inst. Combin. Appl.}
{Bulletin of the Institute of Combinatorics and its Applications}
\DefineJournal{bimasns}{2304-7909}
{Bull. Inst. Math. Acad. Sin. (N.S.)}
{Bulletin of the Institute of Mathematics. Academia Sinica. New Series}
\DefineJournal{bimvi}{2303-4874}
{Bull. Int. Math. Virtual Inst.}
{Bulletin of International Mathematical Virtual Institute}
\DefineJournal{imsb}{1017-060X}
{Bull. Iranian Math. Soc.}
{Iranian Mathematical Society. Bulletin}
\DefineJournal{bkma}{0973-2721}
{Bull. Kerala Math. Assoc.}
{Bulletin of Kerala Mathematics Association}
\DefineJournal{bkms}{1015-8634}
{Bull. Korean Math. Soc.}
{Bulletin of the Korean Mathematical Society}
\DefineJournal{bkitpam}{1343-8670}
{Bull. Kyushu Inst. Technol. Pure Appl. Math.}
{Bulletin of the Kyushu Institute of Technology. Pure and Applied Mathematics}
\DefineJournal{blms}{0024-6093}
{Bull. Lond. Math. Soc.}
{Bulletin of the London Mathematical Society}
\DefineJournal{bmmss}{0126-6705}
{Bull. Malays. Math. Sci. Soc.}
{Bulletin of the Malaysian Mathematical Sciences Society}
\DefineJournal{bmaa}{1821-1291}
{Bull. Math. Anal. Appl.}
{Bulletin of Mathematical Analysis and Applications}
\DefineJournal{bmb}{0092-8240}
{Bull. Math. Biol.}
{Bulletin of Mathematical Biology}
\DefineJournal{bms}{1664-3607}
{Bull. Math. Sci.}
{Bulletin of Mathematical Sciences}
\DefineJournal{bmssmrns}{1220-3874}
{Bull. Math. Soc. Sci. Math. Roumanie (N.S.)}
{Bulletin Mathematique de la Societe des Sciences Mathematiques de Roumanie. Nouvelle Serie}
\DefineJournal{bnuens}{0547-2407}
{Bull. Nara Univ. Ed. Natur. Sci.}
{Bulletin of Nara University of Education. Natural Science}
\DefineJournal{bopuct}{2186-2826}
{Bull. Osaka Prefect. Univ. Coll. Technol.}
{Bulletin of Osaka Prefectural University College of Technology}
\DefineJournal{bpasm}{0239-7269}
{Bull. Pol. Acad. Sci. Math.}
{Bulletin of the Polish Academy of Sciences. Mathematics}
\DefineJournal{bpam}{0973-5933}
{Bull. Pure Appl. Math.}
{Bulletin of Pure and Applied Mathematics}
\DefineJournal{brasp}{1062-8738}
{Bull. Russ. Acad. Sci. Phys.}
{Bulletin of the Russian Academy of Sciences. Physics}
\DefineJournal{bsm}{0007-4497}
{Bull. Sci. Math.}
{Bulletin des Sciences Mathematiques}
\DefineJournal{uldlbsl}{0138-0680}
{Bull. Sect. Logic Univ. Lodz}
{University of Lodz. Department of Logic. Bulletin of the Section of Logic}
\DefineJournal{bsmf}{0037-9484}
{Bull. Soc. Math. France}
{Bulletin de la Societe Mathematique de France}
\DefineJournal{bsmfsm}{?bsmfsm}
{Bull. Soc. Math. France Suppl. Mem.}
{Bulletin de la Societe Mathematique de France. Supplement Memoire}
\DefineJournal{bssllsrd}{0459-6854}
{Bull. Soc. Sci. Lett. Lodz Ser. Rech. Deform.}
{Bulletin de la Societe des Sciences et des Lettres de Lodz. Serie: Recherches sur les Deformations}
\DefineJournal{tbsl}{1079-8986}
{Bull. Symb. Log.}
{The Bulletin of Symbolic Logic}
\DefineJournal{bticmi}{1512-0082}
{Bull. TICMI}
{Bulletin. Tbilisi International Centre of Mathematics and Informatics}
\DefineJournal{btguns}{1880-4330}
{Bull. Tokyo Gakugei Univ. Nat. Sci.}
{Bulletin of Tokyo Gakugei University. Natural Sciences}
\DefineJournal{btubsimip}{2065-2151}
{Bull. Transilv. Univ. Brasov Ser. III}
{Bulletin of the Transilvania University of Brasov. Series III. Mathematics, Informatics, Physics}
\DefineJournal{butefpimnst}{0532-811X}
{Bull. Univ. Teach. Educ. Fukuoka. III}
{Bulletin of University of Teacher Education Fukuoka. Part III. Mathematics, Natural Sciences and Technology}
\DefineJournal{bms}{?bms}
{Burg Monogr. in Sci.}
{Burg Monographs in Science}
\DefineJournal{bscm}{0214-316X}
{Butl. Soc. Catalana Mat.}
{Butlleti de la Societat Catalana de Matematiques}
\DefineJournal{bb}{?bb}
{Byte Books}
{Byte Books}
\DefineJournal{dbancrbs}{1310-1331}
{C. R. Acad. Bulgare Sci.}
{Dokladi na Blgarskata Akademiya na Naukite. Comptes Rendus de l'Academie Bulgare des Sciences}
\DefineJournal{crmasp}{1631-073X}
{C. R. Math. Acad. Sci. Paris}
{Comptes Rendus Mathematique. Academie des Sciences. Paris}
\DefineJournal{crmslsrcmrastrsc}{0706-1994}
{C. R. Math. Acad. Sci. Soc. R. Can.}
{Comptes Rendus Mathematiques de l'Academie des Sciences. La Societe Royale du Canada. Mathematical Reports of the Academy of Science. The Royal Society of Canada}
\DefineJournal{cimess}{?cimess}
{C.I.M.E. Summer Sch.}
{Centro Internazionale Matematico Estivo (C.I.M.E.) Summer Schools}
\DefineJournal{clc}{?clc}
{Cad. Log. Comput.}
{Cadernos de Logica e Computacao}
\DefineJournal{clf}{?clf}
{Cad. Log. Filos.}
{Cadernos de Logica e Filosofia}
\DefineJournal{cv}{?cv}
{Cafe Voltaire}
{Cafe Voltaire}
\DefineJournal{cl}{?cl}
{Cah. Log. Epistemol.}
{Cahiers de Logique et d'Epistemologie}
\DefineJournal{ctgdc}{1245-530X}
{Cah. Topol. Geom. Differ. Categ.}
{Cahiers de Topologie et Geometrie Differentielle Categoriques}
\DefineJournal{cas}{?cas}
{Cahiers Art Sci.}
{Cahiers Art et Science}
\DefineJournal{cs}{?cs}
{Cahiers SNV}
{Cahiers SNV}
\DefineJournal{cvpde}{0944-2669}
{Calc. Var. Partial Differential Equations}
{Calculus of Variations and Partial Differential Equations}
\DefineJournal{caqnatc}{0008-0624}
{Calcolo}
{Calcolo. A Quarterly on Numerical Analysis and Theory of Computation}
\DefineJournal{csab}{0008-0683}
{Calcutta Stat. Assoc. Bull.}
{Calcutta Statistical Association Bulletin}
\DefineJournal{cas}{?cas}
{Camb. Aerosp. Ser.}
{Cambridge Aerospace Series}
\DefineJournal{ccp}{?ccp}
{Camb. Companions Philos.}
{Cambridge Companions to Philosophy}
\DefineJournal{cs}{?cs}
{Camb. IISc Ser.}
{Cambridge-IISc Series}
\DefineJournal{cip}{?cip}
{Camb. Introd. Philos.}
{Cambridge Introductions to Philosophy}
\DefineJournal{cjm}{2168-0930}
{Camb. J. Math.}
{Cambridge Journal of Mathematics}
\DefineJournal{clc}{?clc}
{Camb. Libr. Collect.}
{Cambridge Library Collection}
\DefineJournal{cohra}{?cohra}
{Camb. Obs. Handb. Res. Astron.}
{Cambridge Observing Handbooks for Research Astronomers}
\DefineJournal{cpc}{?cpc}
{Camb. Philos. Class.}
{Cambridge Philosophy Classics}
\DefineJournal{cshi}{?cshi}
{Camb. Ser. Hum. Comput. Interact.}
{Cambridge Series on Human-Computer Interaction}
\DefineJournal{csspm}{?csspm}
{Camb. Ser. Stat. Probab. Math.}
{Cambridge Series in Statistical and Probabilistic Mathematics}
\DefineJournal{cmt}{?cmt}
{Cambridge Math. Textbooks}
{Cambridge Mathematical Textbooks}
\DefineJournal{cmacm}{?cmacm}
{Cambridge Monogr. Appl. Comput. Math.}
{Cambridge Monographs on Applied and Computational Mathematics}
\DefineJournal{cmmp}{?cmmp}
{Cambridge Monogr. Math. Phys.}
{Cambridge Monographs on Mathematical Physics}
\DefineJournal{cmm}{?cmm}
{Cambridge Monogr. Mech.}
{Cambridge Monographs on Mechanics}
\DefineJournal{cssss}{?cssss}
{Cambridge Solid State Sci. Ser.}
{Cambridge Solid State Science Series}
\DefineJournal{csam}{?csam}
{Cambridge Stud. Adv. Math.}
{Cambridge Studies in Advanced Mathematics}
\DefineJournal{csae}{?csae}
{Cambridge Stud. Appl. Econom.}
{Cambridge Studies in Applied Econometrics}
\DefineJournal{csmo}{?csmo}
{Cambridge Stud. Modern Optics}
{Cambridge Studies in Modern Optics}
\DefineJournal{ctam}{?ctam}
{Cambridge Texts Appl. Math.}
{Cambridge Texts in Applied Mathematics}
\DefineJournal{ctm}{?ctm}
{Cambridge Tracts in Math.}
{Cambridge Tracts in Mathematics}
\DefineJournal{cttcs}{?cttcs}
{Cambridge Tracts Theoret. Comput. Sci.}
{Cambridge Tracts in Theoretical Computer Science}
\DefineJournal{camq}{1073-1849}
{Can. Appl. Math. Q.}
{Canadian Applied Mathematics Quarterly}
\DefineJournal{cc}{?cc}
{Can. Collect.}
{Canadian Collection}
\DefineJournal{cjmjcm}{0008-414X}
{Canad. J. Math.}
{Canadian Journal of Mathematics. Journal Canadien de Mathematiques}
\DefineJournal{tcjslrcs}{0319-5724}
{Canad. J. Statist.}
{The Canadian Journal of Statistics. La Revue Canadienne de Statistique}
\DefineJournal{cmbbcm}{0008-4395}
{Canad. Math. Bull.}
{Canadian Mathematical Bulletin. Bulletin Canadien de Mathematiques}
\DefineJournal{cmcp}{1875-0745}
{Carbon Mater.: Chem. Phys.}
{Carbon Materials: Chemistry and Physics}
\DefineJournal{tcghls}{?tcghls}
{Carl G. Hempel Lect. Ser.}
{The Carl G. Hempel Lecture Series}
\DefineJournal{cls}{?cls}
{Carolina Lecture Ser.}
{Carolina Lecture Series}
\DefineJournal{cjm}{1584-2851}
{Carpathian J. Math.}
{Carpathian Journal of Mathematics}
\DefineJournal{cmpkmp}{2075-9827}
{Carpathian Math. Publ.}
{Carpathian Mathematical Publications. Karpatski Matematichni Publikatsii}
\DefineJournal{cmm}{?cmm}
{Carus Math. Monogr.}
{Carus Mathematical Monographs}
\DefineJournal{cjms}{1735-0611}
{Casp. J. Math. Sci.}
{Caspian Journal of Mathematical Sciences}
\DefineJournal{cgasa}{2345-5853}
{Categ. Gen. Algebr. Struct. Appl.}
{Categories and General Algebraic Structures with Applications}
\DefineJournal{crcsm}{0160-7642}
{CBMS Reg. Conf. Ser. Math.}
{CBMS Regional Conference Series in Mathematics}
\DefineJournal{crcsam}{?crcsam}
{CBMS-NSF Regional Conf. Ser. in Appl. Math.}
{CBMS-NSF Regional Conference Series in Applied Mathematics}
\DefineJournal{cejor}{1435-246X}
{CEJOR Cent. Eur. J. Oper. Res.}
{Central European Journal of Operations Research (CEJOR)}
\DefineJournal{cmdaaijsd}{0923-2958}
{Celestial Mech. Dynam. Astronom.}
{Celestial Mechanics & Dynamical Astronomy. An International Journal of Space Dynamics}
\DefineJournal{cs}{?cs}
{CEMPI Ser.}
{CEMPI Series}
\DefineJournal{caijhsca}{0008-8994}
{Centaurus}
{Centaurus. An International Journal of the History of Science and its Cultural Aspects}
\DefineJournal{crmp}{?crmp}
{Centre Rech. Math. Proc.}
{Centre de Recherches Mathematiques Proceedings}
\DefineJournal{c}{?c}
{CERN 83}
{CERN 83}
\DefineJournal{caccp}{2542-4491}
{Chall. Adv. Comput. Chem. Phys.}
{Challenges and Advances in Computational Chemistry and Physics}
\DefineJournal{cjm}{1906-554X}
{Chamchuri J. Math.}
{Chamchuri Journal of Mathematics}
\DefineJournal{ce}{?ce}
{Champs Essais}
{Champs Essais}
\DefineJournal{caijns}{1054-1500}
{Chaos}
{Chaos. An Interdisciplinary Journal of Nonlinear Science}
\DefineJournal{csf}{0960-0779}
{Chaos Solitons Fractals}
{Chaos, Solitons & Fractals}
\DefineJournal{chbds}{?chbds}
{Chapman & Hall/CRC Big Data Ser.}
{Chapman & Hall/CRC Big Data Series}
\DefineJournal{chbs}{?chbs}
{Chapman & Hall/CRC Biostat. Ser.}
{Chapman & Hall/CRC Biostatistics Series}
\DefineJournal{chciss}{?chciss}
{Chapman & Hall/CRC Comput. Inf. Sci. Ser.}
{Chapman & Hall/CRC Computer and Information Science Series}
\DefineJournal{chcsdas}{?chcsdas}
{Chapman & Hall/CRC Comput. Sci. Data Anal. Ser.}
{Chapman & Hall/CRC Computer Science and Data Analysis Series}
\DefineJournal{chcss}{?chcss}
{Chapman & Hall/CRC Comput. Sci. Ser.}
{Chapman & Hall/CRC Computational Science Series}
\DefineJournal{chcns}{?chcns}
{Chapman & Hall/CRC Cryptogr. Netw. Secur.}
{Chapman & Hall/CRC Cryptography and Network Security}
\DefineJournal{chdmkds}{?chdmkds}
{Chapman & Hall/CRC Data Min. Knowl. Discov. Ser.}
{Chapman & Hall/CRC Data Mining and Knowledge Discovery Series}
\DefineJournal{chfms}{?chfms}
{Chapman & Hall/CRC Financ. Math. Ser.}
{Chapman & Hall/CRC Financial Mathematics Series}
\DefineJournal{chhmsm}{?chhmsm}
{Chapman & Hall/CRC Handb. Mod. Stat. Methods}
{Chapman & Hall/CRC Handbooks of Modern Statistical Methods}
\DefineJournal{chiss}{?chiss}
{Chapman & Hall/CRC Interdiscip. Stat. Ser.}
{Chapman & Hall/CRC Interdisciplinary Statistics Series}
\DefineJournal{chmlprs}{?chmlprs}
{Chapman & Hall/CRC Mach. Learn. Pattern Recogn. Ser.}
{Chapman & Hall/CRC Machine Learning & Pattern Recognition Series}
\DefineJournal{chmcbs}{?chmcbs}
{Chapman & Hall/CRC Math. Comput. Biol. Ser.}
{Chapman & Hall/CRC Mathematical and Computational Biology Series}
\DefineJournal{chmcis}{?chmcis}
{Chapman & Hall/CRC Math. Comput. Imaging Sci.}
{Chapman & Hall/CRC Mathematical and Computational Imaging Sciences}
\DefineJournal{chnasc}{?chnasc}
{Chapman & Hall/CRC Numer. Anal. Sci. Comput.}
{Chapman & Hall/CRC Numerical Analysis and Scientific Computing}
\DefineJournal{chtsss}{?chtsss}
{Chapman & Hall/CRC Texts Stat. Sci. Ser.}
{Chapman & Hall/CRC Texts in Statistical Science Series}
\DefineJournal{acst}{?acst}
{Chartwell-Bratt Student Text}
{A Chartwell-Bratt Student Text}
\DefineJournal{cs}{2226-8383}
{Chebyshevskii Sb.}
{Chebyshevskii Sbornik}
\DefineJournal{cfz}{2500-0101}
{Chelyab. Fiz.-Mat. Zh.}
{Chelyabinskii Fiziko-Matematicheskii Zhurnal}
\DefineJournal{ca}{?ca}
{Chem. Anal.}
{Chemical Analysis}
\DefineJournal{ces}{?ces}
{Chem. Eng. Ser.}
{Chemical Engineering Series}
\DefineJournal{crss}{?crss}
{Chemometrics Res. Stud. Ser.}
{Chemometrics Research Studies Series}
\DefineJournal{cjtcs}{1073-0486}
{Chic. J. Theoret. Comput. Sci.}
{Chicago Journal of Theoretical Computer Science}
\DefineJournal{cjs}{0718-7912}
{Chil. J. Stat.}
{Chilean Journal of Statistics}
\DefineJournal{camsb}{0252-9599}
{Chin. Ann. Math. Ser. B}
{Chinese Annals of Mathematics. Series B}
\DefineJournal{ccastlsp}{?ccastlsp}
{China Center Adv. Sci. Tech. World Lab. Sympos. Workshop Proc.}
{China Center of Advanced Science and Technology (World Laboratory) Symposium/Workshop Proceedings}
\DefineJournal{camsasnaj}{1000-8314}
{Chinese Ann. Math. Ser. A}
{Chinese Annals of Mathematics. Series A. Shuxue Niankan. A Ji}
\DefineJournal{cjapsygt}{1001-4268}
{Chinese J. Appl. Probab. Statist.}
{Chinese Journal of Applied Probability and Statistics. Yingyong Gailu Tongji}
\DefineJournal{cjcjx}{0254-4164}
{Chinese J. Comput.}
{Chinese Journal of Computers. Jisuanji Xuebao}
\DefineJournal{cjcm}{0898-5111}
{Chinese J. Contemp. Math.}
{Chinese Journal of Contemporary Mathematics}
\DefineJournal{}{?}
{Chinese J. Engrg. Math.}
{nan}
\DefineJournal{cjp}{0577-9073}
{Chinese J. Phys.}
{Chinese Journal of Physics}
\DefineJournal{cqjmsj}{1002-0462}
{Chinese Quart. J. Math.}
{Chinese Quarterly Journal of Mathematics. Shuxue Jikan}
\DefineJournal{cs}{?cs}
{Churchill/Brown Ser.}
{Churchill/Brown Series}
\DefineJournal{csms}{2364-950X}
{CIM Ser. Math. Sci.}
{CIM Series in Mathematical Sciences}
\DefineJournal{cssp}{0278-081X}
{Circuits Systems Signal Process.}
{Circuits, Systems, and Signal Processing}
\DefineJournal{cjs}{?cjs}
{CIRM Jean-Morlet Ser.}
{CIRM Jean-Morlet Series}
\DefineJournal{cicmscl}{0254-1971}
{CISM Courses and Lect.}
{CISM International Centre for Mechanical Sciences. Courses and Lectures}
\DefineJournal{cts}{?cts}
{Class. Texts Sci.}
{Classic Texts in the Sciences}
\DefineJournal{cqg}{0264-9381}
{Classical Quantum Gravity}
{Classical and Quantum Gravity}
\DefineJournal{c}{?c}
{Classici Econom.}
{Classici dell'Economia}
\DefineJournal{cam}{?cam}
{Classics Appl. Math.}
{Classics in Applied Mathematics}
\DefineJournal{crms}{?crms}
{Classr. Res. Mater. Ser.}
{Classroom Resource Materials Series}
\DefineJournal{cln}{?cln}
{Clay Lect. Notes}
{Clay Lecture Notes}
\DefineJournal{cmp}{1534-6455}
{Clay Math. Proc.}
{Clay Mathematics Proceedings}
\DefineJournal{cpn}{?cpn}
{Clustering Phenom. Nuclei}
{Clustering Phenomena in Nuclei}
\DefineJournal{c}{?c}
{CMA-MR}
{CMA-MR}
\DefineJournal{c}{?c}
{CMA-SR}
{CMA-SR}
\DefineJournal{cbmms}{1613-5237}
{CMS Books Math./Ouvrages Math. SMC}
{CMS Books in Mathematics/Ouvrages de Mathematiques de la SMC}
\DefineJournal{cn}{1193-9273}
{CMS Notes}
{CMS Notes}
\DefineJournal{cms}{2574-2558}
{Cogent Math. Stat.}
{Cogent Mathematics & Statistics}
\DefineJournal{cir}{2520-1956}
{Cogn. Intell. Robot.}
{Cognitive Intelligence and Robotics}
\DefineJournal{cst}{2195-3988}
{Cogn. Sci. Technol.}
{Cognitive Science and Technology}
\DefineJournal{cma}{?cma}
{Colec. Mat. Apl.}
{Colecao Matematica e Aplicacoes}
\DefineJournal{ce}{?ce}
{Colecc. Estud.}
{Coleccion Estudio}
\DefineJournal{cos}{?cos}
{Colecc. Obra Sel.}
{Coleccion Obra Selecta}
\DefineJournal{cu}{?cu}
{Colect. Univ. (Cluj-Napoca)}
{Colectia Universitaria (Cluj-Napoca)}
\DefineJournal{cn}{?cn}
{Coll. NABLA}
{Collection NABLA}
\DefineJournal{csm}{?csm}
{Coll. Sci. Mat.}
{Collana di Scienze Matematiche}
\DefineJournal{ch}{?ch}
{Colleccio Homenatges}
{Colleccio Homenatges}
\DefineJournal{cab}{?cab}
{Collect. Autom. Base}
{Collection Automatique de Base}
\DefineJournal{cbfm}{?cbfm}
{Collect. Blain Faye Martin}
{Collection Blain Faye Martin}
\DefineJournal{cdl}{?cdl}
{Collect. Droit Adm. Locale}
{Collection Droit de l'Administration Locale}
\DefineJournal{ce}{?ce}
{Collect. Essais}
{Collection Essais}
\DefineJournal{c}{?c}
{Collect. I.M.E.}
{Collection de l'I.M.E.}
\DefineJournal{ci}{?ci}
{Collect. Idees}
{Collection Idees}
\DefineJournal{cim}{?cim}
{Collect. Indust. Mec.}
{Collection des Industries Mecaniques}
\DefineJournal{cis}{1142-8198}
{Collect. Info Sup}
{Collection Info Sup}
\DefineJournal{ci}{?ci}
{Collect. Inform.}
{Collection Informatique}
\DefineJournal{cip}{?cip}
{Collect. Inform. Prepas-Univ.}
{Collection Informatique Prepas-Universite}
\DefineJournal{cm}{0010-0757}
{Collect. Math.}
{Collectanea Mathematica}
\DefineJournal{cnidermit}{1161-059X}
{Collect. Notes Internes Dir. Etudes Rech. Math. Inform. Telecomm.}
{Collection de Notes Internes de la Direction des Etudes et Recherches: Mathematiques, Informatique, Telecommunications}
\DefineJournal{cpss}{?cpss}
{Collect. Points Ser. Sci.}
{Collection Points: Serie Sciences}
\DefineJournal{csl}{?csl}
{Collect. Sci. Hist.}
{Collection Sciences dans L'Histoire}
\DefineJournal{csi}{?csi}
{Collect. Sem. INRIA}
{Collection Seminaires INRIA}
\DefineJournal{cvs}{?cvs}
{Collect. Vis. Sci.}
{Collection Visions des Sciences}
\DefineJournal{tcmj}{0746-8342}
{College Math. J.}
{The College Mathematics Journal}
\DefineJournal{cm}{0010-1354}
{Colloq. Math.}
{Colloquium Mathematicum}
\DefineJournal{cncnrs}{?cncnrs}
{Colloq. Nat. CNRS}
{Colloques Nationaux du Centre National de la Recherche Scientifique}
\DefineJournal{c}{?c}
{Colloquia}
{Colloquia}
\DefineJournal{cpc}{0963-5483}
{Combin. Probab. Comput.}
{Combinatorics, Probability and Computing}
\DefineJournal{caijctc}{0209-9683}
{Combinatorica}
{Combinatorica. An International Journal on Combinatorics and the Theory of Computing}
\DefineJournal{ctm}{1364-7830}
{Combust. Theory Model.}
{Combustion Theory and Modelling}
\DefineJournal{ca}{0092-7872}
{Comm. Algebra}
{Communications in Algebra}
\DefineJournal{cag}{1019-8385}
{Comm. Anal. Geom.}
{Communications in Analysis and Geometry}
\DefineJournal{cana}{1074-133X}
{Comm. Appl. Nonlinear Anal.}
{Communications on Applied Nonlinear Analysis}
\DefineJournal{ccm}{?ccm}
{Comm. Cognition Monogr.}
{Communication & Cognition Monographies}
\DefineJournal{cces}{0178-5354}
{Comm. Control Engrg. Ser.}
{Communications and Control Engineering Series}
\DefineJournal{cmp}{0010-3616}
{Comm. Math. Phys.}
{Communications in Mathematical Physics}
\DefineJournal{cpde}{0360-5302}
{Comm. Partial Differential Equations}
{Communications in Partial Differential Equations}
\DefineJournal{cpam}{0010-3640}
{Comm. Pure Appl. Math.}
{Communications on Pure and Applied Mathematics}
\DefineJournal{cssc}{0361-0918}
{Comm. Statist. Simulation Comput.}
{Communications in Statistics. Simulation and Computation}
\DefineJournal{cstm}{0361-0926}
{Comm. Statist. Theory Methods}
{Communications in Statistics. Theory and Methods}
\DefineJournal{cmapmssi}{2080-1211}
{Comment. Math.}
{Commentationes Mathematicae. Annals of the Polish Mathematical Society. Series I}
\DefineJournal{cmhajsms}{0010-2571}
{Comment. Math. Helv.}
{Commentarii Mathematici Helvetici. A Journal of the Swiss Mathematical Society}
\DefineJournal{cmuc}{0010-2628}
{Comment. Math. Univ. Carolin.}
{Commentationes Mathematicae Universitatis Carolinae}
\DefineJournal{cmusp}{0010-258X}
{Comment. Math. Univ. St. Pauli}
{Commentarii Mathematici Universitatis Sancti Pauli}
\DefineJournal{caim}{2038-0909}
{Commun. Appl. Ind. Math.}
{Communications in Applied and Industrial Mathematics}
\DefineJournal{camcysjsx}{1006-6330}
{Commun. Appl. Math. Comput.}
{Communication on Applied Mathematics and Computation. Yingyong Shuxue yu Jisuan Shuxue Xuebao}
\DefineJournal{camcs}{1559-3940}
{Commun. Appl. Math. Comput. Sci.}
{Communications in Applied Mathematics and Computational Science}
\DefineJournal{cco}{2538-2128}
{Commun. Comb. Optim.}
{Communications in Combinatorics and Optimization}
\DefineJournal{ccis}{1865-0929}
{Commun. Comput. Inf. Sci.}
{Communications in Computer and Information Science}
\DefineJournal{ccp}{1815-2406}
{Commun. Comput. Phys.}
{Communications in Computational Physics}
\DefineJournal{ccm}{0219-1997}
{Commun. Contemp. Math.}
{Communications in Contemporary Mathematics}
\DefineJournal{cfsuasams}{1303-5991}
{Commun. Fac. Sci. Univ. Ank. Ser. A1. Math. Stat.}
{Communications. Faculty of Sciences. University of Ankara. Series A1. Mathematics and Statistics}
\DefineJournal{cis}{1526-7555}
{Commun. Inf. Syst.}
{Communications in Information and Systems}
\DefineJournal{kmsc}{1225-1763}
{Commun. Korean Math. Soc.}
{Korean Mathematical Society. Communications}
\DefineJournal{cm}{1804-1388}
{Commun. Math.}
{Communications in Mathematics}
\DefineJournal{cma}{1938-9787}
{Commun. Math. Anal.}
{Communications in Mathematical Analysis}
\DefineJournal{cmr}{1674-5647}
{Commun. Math. Res.}
{Communications in Mathematical Research}
\DefineJournal{cms}{1539-6746}
{Commun. Math. Sci.}
{Communications in Mathematical Sciences}
\DefineJournal{cms}{2194-6701}
{Commun. Math. Stat.}
{Communications in Mathematics and Statistics}
\DefineJournal{cnsns}{1007-5704}
{Commun. Nonlinear Sci. Numer. Simul.}
{Communications in Nonlinear Science and Numerical Simulation}
\DefineJournal{cntp}{1931-4523}
{Commun. Number Theory Phys.}
{Communications in Number Theory and Physics}
\DefineJournal{cna}{2193-4215}
{Commun. Numer. Anal.}
{Communications in Numerical Analysis}
\DefineJournal{cpaa}{1534-0392}
{Commun. Pure Appl. Anal.}
{Communications on Pure and Applied Analysis}
\DefineJournal{csa}{0973-9599}
{Commun. Stoch. Anal.}
{Communications on Stochastic Analysis}
\DefineJournal{ctp}{0253-6102}
{Commun. Theor. Phys. (Beijing)}
{Communications in Theoretical Physics}
\DefineJournal{ccn}{?ccn}
{Comp. Cogn. Neurosci.}
{Comparative Cognition and Neuroscience}
\DefineJournal{ctm}{2296-4568}
{Compact Textb. Math.}
{Compact Textbooks in Mathematics}
\DefineJournal{caot}{1661-8254}
{Complex Anal. Oper. Theory}
{Complex Analysis and Operator Theory}
\DefineJournal{cas}{2197-120X}
{Complex Anal. Synerg.}
{Complex Analysis and its Synergies}
\DefineJournal{cm}{2300-7443}
{Complex Manifolds}
{Complex Manifolds}
\DefineJournal{cnds}{2195-724X}
{Complex Netw. Dyn. Syst.}
{Complex Networks and Dynamic Systems}
\DefineJournal{cs}{0891-2513}
{Complex Systems}
{Complex Systems}
\DefineJournal{cveeaij}{1747-6933}
{Complex Var. Elliptic Equ.}
{Complex Variables and Elliptic Equations. An International Journal}
\DefineJournal{cm}{0010-437X}
{Compos. Math.}
{Compositio Mathematica}
\DefineJournal{acca}{?acca}
{Compr. Course Anal.}
{A Comprehensive Course in Analysis}
\DefineJournal{ca}{0335-4628}
{Comprendre et Appliquer}
{Comprendre et Appliquer}
\DefineJournal{cagd}{0167-8396}
{Comput. Aided Geom. Design}
{Computer Aided Geometric Design}
\DefineJournal{cam}{0101-8205}
{Comput. Appl. Math.}
{Computational & Applied Mathematics}
\DefineJournal{cb}{1568-2684}
{Comput. Biol.}
{Computational Biology}
\DefineJournal{cbc}{1476-9271}
{Comput. Biol. Chem.}
{Computational Biology and Chemistry}
\DefineJournal{ccn}{1617-7975}
{Comput. Commun. Netw.}
{Computer Communications and Networks}
\DefineJournal{cc}{1016-3328}
{Comput. Complexity}
{Computational Complexity}
\DefineJournal{ces}{?ces}
{Comput. Eng. Ser.}
{Computer Engineering Series}
\DefineJournal{cems}{?cems}
{Comput. Exp. Methods Struct.}
{Computational and Experimental Methods in Structures}
\DefineJournal{cfaij}{0045-7930}
{Comput. & Fluids}
{Computers & Fluids. An International Journal}
\DefineJournal{cgta}{0925-7721}
{Comput. Geom.}
{Computational Geometry. Theory and Applications}
\DefineJournal{cg}{1420-0597}
{Comput. Geosci.}
{Computational Geosciences}
\DefineJournal{civ}{1381-6446}
{Comput. Imaging Vision}
{Computational Imaging and Vision}
\DefineJournal{ci}{1335-9150}
{Comput. Inform.}
{Computing and Informatics}
\DefineJournal{ciaij}{0824-7935}
{Comput. Intell.}
{Computational Intelligence. An International Journal}
\DefineJournal{tcj}{0010-4620}
{Comput. J.}
{The Computer Journal}
\DefineJournal{cl}{?cl}
{Comput. Life}
{Computer Life}
\DefineJournal{cl}{0891-2017}
{Comput. Linguist.}
{Computational Linguistics}
\DefineJournal{cms}{1619-697X}
{Comput. Manag. Sci.}
{Computational Management Science}
\DefineJournal{cmaaij}{0898-1221}
{Comput. Math. Appl.}
{Computers & Mathematics with Applications. An International Journal}
\DefineJournal{cmb}{2544-7297}
{Comput. Math. Biophys.}
{Computational and Mathematical Biophysics}
\DefineJournal{cmmp}{0965-5425}
{Comput. Math. Math. Phys.}
{Computational Mathematics and Mathematical Physics}
\DefineJournal{cmmm}{1748-670X}
{Comput. Math. Methods Med.}
{Computational and Mathematical Methods in Medicine}
\DefineJournal{cmm}{1046-283X}
{Comput. Math. Model.}
{Computational Mathematics and Modeling}
\DefineJournal{cm}{0178-7675}
{Comput. Mech.}
{Computational Mechanics}
\DefineJournal{cmam}{1609-4840}
{Comput. Methods Appl. Math.}
{Computational Methods in Applied Mathematics}
\DefineJournal{cmame}{0045-7825}
{Comput. Methods Appl. Mech. Engrg.}
{Computer Methods in Applied Mechanics and Engineering}
\DefineJournal{cmas}{1871-3033}
{Comput. Methods Appl. Sci.}
{Computational Methods in Applied Sciences}
\DefineJournal{cmde}{2345-3982}
{Comput. Methods Differ. Equ.}
{Computational Methods for Differential Equations}
\DefineJournal{cmft}{1617-9447}
{Comput. Methods Funct. Theory}
{Computational Methods and Function Theory}
\DefineJournal{cms}{1868-0305}
{Comput. Music Sci.}
{Computational Music Science}
\DefineJournal{cor}{0305-0548}
{Comput. Oper. Res.}
{Computers & Operations Research}
\DefineJournal{coaaij}{0926-6003}
{Comput. Optim. Appl.}
{Computational Optimization and Applications. An International Journal}
\DefineJournal{cps}{?cps}
{Comput. People Ser.}
{Computers and People Series}
\DefineJournal{cpc}{0010-4655}
{Comput. Phys. Commun.}
{Computer Physics Communications}
\DefineJournal{cs}{0946-2767}
{Comput. Sci.}
{Computer Science}
\DefineJournal{cse}{?cse}
{Comput. Sci. Eng.}
{Computational Science & Engineering}
\DefineJournal{asmimcscsjm}{1561-4042}
{Comput. Sci. J. Moldova}
{Academy of Sciences of Moldova. Institute of Mathematics and Computer Science. Computer Science Journal of Moldova}
\DefineJournal{tcsl}{?tcsl}
{Comput. Sci. Lib.}
{The Computer Science Library}
\DefineJournal{csm}{?csm}
{Comput. Sci. Monogr.}
{Computer Science Monographs}
\DefineJournal{csr}{1574-0137}
{Comput. Sci. Rev.}
{Computer Science Review}
\DefineJournal{csrt}{?csrt}
{Comput. Sci. Rev. Trends}
{Computer Science Reviews and Trends}
\DefineJournal{cscad}{?cscad}
{Comput. Sci.: Comput. Archit. Design}
{Computer Science: Computer Architecture and Design}
\DefineJournal{cssp}{?cssp}
{Comput. Sci.: Systems Programming}
{Computer Science: Systems Programming}
\DefineJournal{css}{2509-9574}
{Comput. Soc. Sci.}
{Computational Social Sciences}
\DefineJournal{cs}{0943-4062}
{Comput. Statist.}
{Computational Statistics}
\DefineJournal{csda}{0167-9473}
{Comput. Statist. Data Anal.}
{Computational Statistics & Data Analysis}
\DefineJournal{cscw}{1431-1496}
{Comput. Support. Coop. Work}
{Computer Supported Cooperative Work}
\DefineJournal{cvs}{1432-9360}
{Comput. Vis. Sci.}
{Computing and Visualization in Science}
\DefineJournal{cd}{0010-4485}
{Comput.-Aided Des.}
{Computer-Aided Design}
\DefineJournal{ctjac}{2211-3568}
{Computability}
{Computability. The Journal of the Association CiE}
\DefineJournal{casc}{0010-485X}
{Computing}
{Computing. Archives for Scientific Computing}
\DefineJournal{co}{2299-3282}
{Concr. Oper.}
{Concrete Operators}
\DefineJournal{cplnap}{?cplnap}
{Conf. Proc. Lecture Notes Appl. Phys.}
{Conference Proceedings and Lecture Notes in Applied Physics}
\DefineJournal{cpsems}{2191-5644}
{Conf. Proc. Soc. Exp. Mech. Ser.}
{Conference Proceedings of the Society for Experimental Mechanics Series}
\DefineJournal{cptc}{?cptc}
{Conf. Proc. Theory Comput.}
{Conference Proceedings on Theory of Computing}
\DefineJournal{cm}{1793-7434}
{Confluentes Math.}
{Confluentes Mathematici}
\DefineJournal{cgdaejams}{1088-4173}
{Conform. Geom. Dyn.}
{Conformal Geometry and Dynamics. An Electronic Journal of the American Mathematical Society}
\DefineJournal{cnacjnt}{0384-9864}
{Congr. Numer.}
{Congressus Numerantium. A Conference Journal on Numerical Themes}
\DefineJournal{ca}{?ca}
{Connaiss. Egypte Anc.}
{Connaissance de l'Egypte Ancienne}
\DefineJournal{caaijae}{0176-4276}
{Constr. Approx.}
{Constructive Approximation. An International Journal for Approximations and Expansions}
\DefineJournal{caij}{1383-7133}
{Constraints}
{Constraints. An International Journal}
\DefineJournal{caam}{2147-3730}
{Contemp. Anal. Appl. Math.}
{Contemporary Analysis and Applied Mathematics}
\DefineJournal{cer}{?cer}
{Contemp. Evaluation Res.}
{Contemporary Evaluation Research}
\DefineJournal{cm}{0271-4132}
{Contemp. Math.}
{Contemporary Mathematics}
\DefineJournal{cmiameln}{?cmiameln}
{Contemp. Math. Appl. Monogr. Expo. Lect. Notes}
{Contemporary Mathematics and Its Applications: Monographs, Expositions and Lecture Notes}
\DefineJournal{cm}{?cm}
{Contemp. Mathematicians}
{Contemporary Mathematicians}
\DefineJournal{cp}{?cp}
{Contemp. Phys.}
{Contemporary Physicists}
\DefineJournal{cst}{1568-2846}
{Contemp. Syst. Think.}
{Contemporary Systems Thinking}
\DefineJournal{cmt}{0935-1175}
{Contin. Mech. Thermodyn.}
{Continuum Mechanics and Thermodynamics}
\DefineJournal{cclisma}{?cclisma}
{Contrib. Centro Linceo Interdiscip. Sci. Mat. Appl.}
{Contributi del Centro Linceo Interdisciplinare di Scienze Matematiche e loro Applicazioni}
\DefineJournal{cdm}{1715-0868}
{Contrib. Discrete Math.}
{Contributions to Discrete Mathematics}
\DefineJournal{ce}{1431-1933}
{Contrib. Econ.}
{Contributions to Economics}
\DefineJournal{cms}{1431-1941}
{Contrib. Manag. Sci.}
{Contributions to Management Science}
\DefineJournal{cmcs}{2191-303X}
{Contrib. Math. Comput. Sci.}
{Contributions in Mathematical and Computational Sciences}
\DefineJournal{cp}{0923-9545}
{Contrib. Phenomenol.}
{Contributions to Phenomenology}
\DefineJournal{cp}{?cp}
{Contrib. Philos.}
{Contributions in Philosophy}
\DefineJournal{cs}{1431-1968}
{Contrib. Stat.}
{Contributions to Statistics}
\DefineJournal{cs}{1431-1968}
{Contrib. Statist.}
{Contributions to Statistics}
\DefineJournal{cc}{0324-8569}
{Control Cybernet.}
{Control and Cybernetics}
\DefineJournal{ce}{2373-7719}
{Control Eng.}
{Control Engineering}
\DefineJournal{cis}{1480-1752}
{Control Intell. Syst.}
{Control and Intelligent Systems}
\DefineJournal{crss}{?crss}
{Control Robot. Sens. Ser.}
{Control, Robotics and Sensors Series}
\DefineJournal{ctt}{2095-6983}
{Control Theory Technol.}
{Control Theory and Technology}
\DefineJournal{c}{?c}
{Convergenze}
{Convergenze}
\DefineJournal{c}{2034-5976}
{Conversations}
{Conversations}
\DefineJournal{cbam}{?cbam}
{Core Books in Adv. Math.}
{Core Books in Advanced Mathematics}
\DefineJournal{ceas}{1050-2955}
{Cornell East Asia Ser.}
{Cornell East Asia Series}
\DefineJournal{clnm}{?clnm}
{Courant Lect. Notes Math.}
{Courant Lecture Notes in Mathematics}
\DefineJournal{cs}{1284-6090}
{Cours Spec.}
{Cours Specialises}
\DefineJournal{cpes}{2520-8853}
{CPSS Power Electron. Ser.}
{CPSS Power Electronics Series}
\DefineJournal{cr}{?cr}
{CRC Revivals}
{CRC Revivals}
\DefineJournal{csacm}{?csacm}
{CRC Ser. Applied Comput. Mech.}
{CRC Series in Applied and Computational Mechanics}
\DefineJournal{cmi}{1584-286X}
{Creat. Math. Inform.}
{Creative Mathematics and Informatics}
\DefineJournal{c}{?c}
{Crittografia}
{Crittografia}
\DefineJournal{cms}{1065-8599}
{CRM Monogr. Ser.}
{CRM Monograph Series}
\DefineJournal{csmp}{?csmp}
{CRM Ser. Math. Phys.}
{CRM Series in Mathematical Physics}
\DefineJournal{crmedgs}{?crmedgs}
{CRM Series}
{Centro di Ricerca Matematica Ennio De Giorgi (CRM) Series}
\DefineJournal{csc}{2522-5200}
{CRM Short Courses}
{CRM Short Courses}
\DefineJournal{corrc}{1848-0225}
{Croat. Oper. Res. Rev. CRORR}
{Croatian Operational Research Review. CRORR}
\DefineJournal{chsge}{?chsge}
{Croom Helm Ser. Geogr. Environment}
{Croom Helm Series in Geography and Environment}
\DefineJournal{cms}{?cms}
{Cryogenic Materials Ser.}
{Cryogenic Materials Series}
\DefineJournal{cc}{1936-2447}
{Cryptogr. Commun.}
{Cryptography and Communications}
\DefineJournal{cln}{?cln}
{CSLI Lecture Notes}
{CSLI Lecture Notes}
\DefineJournal{cctm}{?cctm}
{CTM. Class. Top. Math.}
{CTM. Classical Topics in Mathematics}
\DefineJournal{clel}{?clel}
{Cuad. Log. Epistemol. Leng.}
{Cuadernos de Logica, Epistemologia y Lenguaje}
\DefineJournal{camj}{0716-7776}
{Cubo}
{Cubo. A Mathematical Journal}
\DefineJournal{ccme}{?ccme}
{Cult. Civiliz. Middle East}
{Culture and Civilization in the Middle East}
\DefineJournal{cdms}{2589-2711}
{Curr. Dev. Math. Sci.}
{Current Developments in Mathematical Sciences}
\DefineJournal{cnn}{?cnn}
{CWI Notes NM}
{CWI Notes NM}
\DefineJournal{}{?}
{CWI Syllabus}
{nan}
\DefineJournal{cit}{1311-9702}
{Cybern. Inf. Technol.}
{Cybernetics and Information Technologies}
\DefineJournal{csa}{1060-0396}
{Cybernet. Systems Anal.}
{Cybernetics and Systems Analysis}
\DefineJournal{cmj}{0011-4642}
{Czechoslovak Math. J.}
{Czechoslovak Mathematical Journal}
\DefineJournal{df}{1868-8977}
{Dagstuhl Follow-Ups}
{Dagstuhl Follow-Ups}
\DefineJournal{}{?}
{Dalian Lilong Daxue Xuebao}
{nan}
\DefineJournal{dmzfemj}{1608-845X}
{Dalnevost. Mat. Zh.}
{Dalnevostochnyi Matematicheskii Zhurnal. Far Eastern Mathematical Journal}
\DefineJournal{dmkd}{1384-5810}
{Data Min. Knowl. Discov.}
{Data Mining and Knowledge Discovery}
\DefineJournal{dhlfmp}{?dhlfmp}
{David Hilbert's Lect. Found. Math. Phys. 1891--1933}
{David Hilbert's Lectures on the Foundations of Mathematics and Physics 1891--1933}
\DefineJournal{dda}{?dda}
{De Diversis Artibus}
{De Diversis Artibus}
\DefineJournal{dgem}{0938-6572}
{De Gruyter Exp. Math.}
{De Gruyter Expositions in Mathematics}
\DefineJournal{dgg}{?dgg}
{De Gruyter Grad.}
{De Gruyter Graduate}
\DefineJournal{gl}{?gl}
{de Gruyter Lehrbuch}
{de Gruyter Lehrbuch}
\DefineJournal{dgpm}{?dgpm}
{De Gruyter Proc. Math.}
{De Gruyter Proceedings in Mathematics}
\DefineJournal{dgsanm}{2512-1820}
{De Gruyter Ser. Appl. Numer. Math.}
{De Gruyter Series in Applied and Numerical Mathematics}
\DefineJournal{dgsdma}{2195-5557}
{De Gruyter Ser. Discrete Math. Appl.}
{De Gruyter Series in Discrete Mathematics and Applications}
\DefineJournal{dgsla}{1438-1893}
{De Gruyter Ser. Log. Appl.}
{De Gruyter Series in Logic and its Applications}
\DefineJournal{dgsmls}{2195-5530}
{De Gruyter Ser. Math. Life Sci.}
{De Gruyter Series in Mathematics and Life Sciences}
\DefineJournal{dgsnaa}{0941-813X}
{De Gruyter Ser. Nonlinear Anal. Appl.}
{De Gruyter Series in Nonlinear Analysis and Applications}
\DefineJournal{dgs}{?dgs}
{De Gruyter Stud.}
{De Gruyter Studium}
\DefineJournal{dgsm}{0179-0986}
{De Gruyter Stud. Math.}
{De Gruyter Studies in Mathematics}
\DefineJournal{dgsmp}{2194-3532}
{De Gruyter Stud. Math. Phys.}
{De Gruyter Studies in Mathematical Physics}
\DefineJournal{dgt}{?dgt}
{De Gruyter Textbook}
{De Gruyter Textbook}
\DefineJournal{dpd}{?dpd}
{De Petrarque a Descartes}
{De Petrarque a Descartes}
\DefineJournal{da}{1545-8490}
{Decis. Anal.}
{Decision Analysis}
\DefineJournal{defajam}{1593-8883}
{Decis. Econ. Finance}
{Decisions in Economics and Finance. A Journal of Applied Mathematics}
\DefineJournal{de}{1619-5736}
{Decis. Eng.}
{Decision Engineering}
\DefineJournal{dmms}{1896-8325}
{Decis. Mak. Manuf. Serv.}
{Decision Making in Manufacturing and Services}
\DefineJournal{ds}{?ds}
{Decision Sci.}
{Decision Science}
\DefineJournal{dmm}{?dmm}
{Dej. Mat./Hist. Math.}
{Dejiny Matematiky/History of Mathematics}
\DefineJournal{drm}{1613-5520}
{Demogr. Res. Monogr.}
{Demographic Research Monographs}
\DefineJournal{dm}{0420-1213}
{Demonstr. Math.}
{Demonstratio Mathematica}
\DefineJournal{doawpk}{?doawpk}
{Denkschr. Osterr. Akad. Wiss. Philos.-Hist. Kl.}
{Denkschriften Osterreichische Akademie der Wissenschaften, Philosophisch-Historische Klasse}
\DefineJournal{dm}{2300-2298}
{Depend. Model.}
{Dependence Modeling}
\DefineJournal{dccaij}{0925-1022}
{Des. Codes Cryptogr.}
{Designs, Codes and Cryptography. An International Journal}
\DefineJournal{dbjrs}{2367-0967}
{Dev. Bank Jpn. Res. Ser.}
{Development Bank of Japan Research Series}
\DefineJournal{dht}{1369-7331}
{Dev. Heat Transf.}
{Developments in Heat Transfer}
\DefineJournal{dm}{1389-2177}
{Dev. Math.}
{Developments in Mathematics}
\DefineJournal{dp}{?dp}
{Develop. Petrol.}
{Developments in Petrology}
\DefineJournal{ddgsm}{?ddgsm}
{DGDS Differ. Geom. Dyn. Syst. Monogr.}
{DGDS. Differential Geometry---Dynamical Systems. Monographs}
\DefineJournal{d}{0012-2017}
{Dialectica}
{Dialectica}
\DefineJournal{dgl}{?dgl}
{Dialog. Games Log.}
{Dialogues and Games of Logic}
\DefineJournal{dpe}{?dpe}
{Didatt. Propos. Esper.}
{Didattica: Proposte ed Esperienze}
\DefineJournal{de}{0012-2661}
{Differ. Equ.}
{Differential Equations}
\DefineJournal{dea}{1847-120X}
{Differ. Equ. Appl.}
{Differential Equations & Applications}
\DefineJournal{deds}{0971-3514}
{Differ. Equ. Dyn. Syst.}
{Differential Equations and Dynamical Systems}
\DefineJournal{dgs}{1454-511X}
{Differ. Geom. Dyn. Syst.}
{Differential Geometry---Dynamical Systems}
\DefineJournal{dupudecp}{1817-2172}
{Differ. Uravn. Protsessy Upr.}
{Differentsialnye Uravneniya i Protsessy Upravleniya. Differential Equations and Control Processes}
\DefineJournal{def}{2199-7497}
{Differ.-Algebr. Equ. Forum}
{Differential-Algebraic Equations Forum}
\DefineJournal{dga}{0926-2245}
{Differential Geom. Appl.}
{Differential Geometry and its Applications}
\DefineJournal{dieaijta}{0893-4983}
{Differential Integral Equations}
{Differential and Integral Equations. An International Journal for Theory & Applications}
\DefineJournal{dgmf}{0321-4796}
{Differentsialnaya Geom. Mnogoobraz. Figur}
{Differentsialnaya Geometriya Mnogoobrazii Figur}
\DefineJournal{dsp}{1051-2004}
{Digit. Signal Process.}
{Digital Signal Processing}
\DefineJournal{dsp}{1612-1457}
{Digit. Signal Process.}
{Digital Signal Processing}
\DefineJournal{dsdmtcs}{1052-1798}
{DIMACS Ser. Discrete Math. Theoret. Comput. Sci.}
{DIMACS Series in Discrete Mathematics and Theoretical Computer Science}
\DefineJournal{dmmmsa}{?dmmmsa}
{Dip. Metodi Modelli Mat. Sci. Appl.}
{Dipartimento di Metodi e Modelli Matematici per le Scienze Applicate}
\DefineJournal{da}{2397-3129}
{Discrete Anal.}
{Discrete Analysis}
\DefineJournal{damtjcaics}{0166-218X}
{Discrete Appl. Math.}
{Discrete Applied Mathematics. The Journal of Combinatorial Algorithms, Informatics and Computational Sciences}
\DefineJournal{dcgaijmcs}{0179-5376}
{Discrete Comput. Geom.}
{Discrete & Computational Geometry. An International Journal of Mathematics and Computer Science}
\DefineJournal{dcdssa}{1078-0947}
{Discrete Contin. Dyn. Syst.}
{Discrete and Continuous Dynamical Systems. Series A}
\DefineJournal{dcdssbajbms}{1531-3492}
{Discrete Contin. Dyn. Syst. Ser. B}
{Discrete and Continuous Dynamical Systems. Series B. A Journal Bridging Mathematics and Sciences}
\DefineJournal{dcdsss}{1937-1632}
{Discrete Contin. Dyn. Syst. Ser. S}
{Discrete and Continuous Dynamical Systems. Series S}
\DefineJournal{ddnsaimrrj}{1026-0226}
{Discrete Dyn. Nat. Soc.}
{Discrete Dynamics in Nature and Society. An International Multidisciplinary Research and Review Journal}
\DefineJournal{dedsta}{0924-6703}
{Discrete Event Dyn. Syst.}
{Discrete Event Dynamic Systems: Theory and Applications}
\DefineJournal{dm}{0012-365X}
{Discrete Math.}
{Discrete Mathematics}
\DefineJournal{dmaa}{1793-8309}
{Discrete Math. Algorithms Appl.}
{Discrete Mathematics, Algorithms and Applications}
\DefineJournal{dma}{0924-9265}
{Discrete Math. Appl.}
{Discrete Mathematics and Applications}
\DefineJournal{dmar}{?dmar}
{Discrete Math. Appl. (Boca Raton)}
{Discrete Mathematics and its Applications (Boca Raton)}
\DefineJournal{dmtcsd}{1365-8050}
{Discrete Math. Theor. Comput. Sci.}
{Discrete Mathematics & Theoretical Computer Science. DMTCS.}
\DefineJournal{dmtcsp}{1365-8050}
{Discrete Math. Theor. Comput. Sci. Proc.}
{Discrete Mathematics & Theoretical Computer Science Proceedings}
\DefineJournal{do}{1572-5286}
{Discrete Optim.}
{Discrete Optimization}
\DefineJournal{dmdico}{1509-9407}
{Discuss. Math. Differ. Incl. Control Optim.}
{Discussiones Mathematicae. Differential Inclusions, Control and Optimization}
\DefineJournal{dmgaa}{1509-9415}
{Discuss. Math. Gen. Algebra Appl.}
{Discussiones Mathematicae. General Algebra and Applications}
\DefineJournal{dmgt}{1234-3099}
{Discuss. Math. Graph Theory}
{Discussiones Mathematicae. Graph Theory}
\DefineJournal{dmps}{1509-9423}
{Discuss. Math. Probab. Stat.}
{Discussiones Mathematicae. Probability and Statistics}
\DefineJournal{ddki}{0941-5769}
{DISKI}
{DISKI. Dissertationen zur Kunstlichen Intelligenz}
\DefineJournal{dm}{0234-0860}
{Diskret. Mat.}
{Diskretnaya Matematika}
\DefineJournal{daio}{1560-7542}
{Diskretn. Anal. Issled. Oper.}
{Diskretnyi Analiz i Issledovanie Operatsii}
\DefineJournal{de}{?de}
{Diss. ETH}
{Dissertation ETH}
\DefineJournal{dm}{0012-3862}
{Dissertationes Math.}
{Dissertationes Mathematicae}
\DefineJournal{dc}{0178-2770}
{Distrib. Comput.}
{Distributed Computing}
\DefineJournal{d}{0939-298X}
{DLR-Mitteilung}
{DLR-Mitteilung}
\DefineJournal{dm}{1431-0635}
{Doc. Math.}
{Documenta Mathematica}
\DefineJournal{dm}{1629-4939}
{Doc. Math. (Paris)}
{Documents Mathematiques (Paris)}
\DefineJournal{randan}{0869-5652}
{Dokl. Akad. Nauk}
{Rossiiskaya Akademiya Nauk. Doklady Akademii Nauk}
\DefineJournal{dm}{1064-5624}
{Dokl. Math.}
{Doklady Mathematics}
\DefineJournal{dnanarnasa}{0321-1339}
{Dokl. Nats. Akad. Nauk Armen.}
{Doklady. Natsionalnaya Akademiya Nauk Armenii. Reports. National Academy of Sciences of Armenia}
\DefineJournal{dnanb}{1561-8323}
{Dokl. Nats. Akad. Nauk Belarusi}
{Doklady Natsionalnoi Akademii Nauk Belarusi}
\DefineJournal{tdme}{?tdme}
{Dolciani Math. Exp.}
{The Dolciani Mathematical Expositions}
\DefineJournal{drna}{2035-6803}
{Dolomites Res. Notes Approx.}
{Dolomites Research Notes on Approximation}
\DefineJournal{}{?}
{Dongbei Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Dongbei Shuxue}
{nan}
\DefineJournal{}{?}
{Dongnan Daxue Xuebao. Ziran Kexue Ban}
{nan}
\DefineJournal{dnanumptn}{ Kiev."}
{Dopov. Nats. Akad. Nauk Ukr. Mat. Prirodozn. Tekh. Nauki}
{Dopovidi Natsionalnoi Akademii Nauk Ukraini. Matematika. Prirodoznavstvo. Tekhnichni Nauki}
\DefineJournal{dp}{?dp}
{DTV Portrait}
{DTV Portrait}
\DefineJournal{dmj}{0012-7094}
{Duke Math. J.}
{Duke Mathematical Journal}
\DefineJournal{tdthsop}{?tdthsop}
{Durham Thomas Harriot Sem.}
{The Durham Thomas Harriot Seminar. Occasional Paper}
\DefineJournal{das}{?das}
{Duxbury Adv. Ser.}
{Duxbury Advanced Series}
\DefineJournal{tdassds}{?tdassds}
{Duxbury Adv. Ser. Statist. Decis. Sci.}
{The Duxbury Advanced Series in Statistics and Decision Sciences}
\DefineJournal{dcdissama}{1201-3390}
{Dyn. Contin. Discrete Impuls. Syst. Ser. A Math. Anal.}
{Dynamics of Continuous, Discrete & Impulsive Systems. Series A. Mathematical Analysis}
\DefineJournal{dcdissbaa}{1492-8760}
{Dyn. Contin. Discrete Impuls. Syst. Ser. B Appl. Algorithms}
{Dynamics of Continuous, Discrete & Impulsive Systems. Series B. Applications & Algorithms}
\DefineJournal{dga}{2153-0785}
{Dyn. Games Appl.}
{Dynamic Games and Applications}
\DefineJournal{dmeef}{1566-0419}
{Dyn. Model. Econom. Econ. Finance}
{Dynamic Modeling and Econometrics in Economics and Finance}
\DefineJournal{dpde}{1548-159X}
{Dyn. Partial Differ. Equ.}
{Dynamics of Partial Differential Equations}
\DefineJournal{dscs}{2059-6987}
{Dyn. Stat. Clim. Syst.}
{Dynamics and Statistics of the Climate System}
\DefineJournal{dsaij}{1468-9367}
{Dyn. Syst.}
{Dynamical Systems. An International Journal}
\DefineJournal{deta}{?deta}
{Dynam. Econom. Theory and Appl.}
{Dynamic Economics: Theory and Applications}
\DefineJournal{dsa}{1056-2176}
{Dynam. Systems Appl.}
{Dynamic Systems and Applications}
\DefineJournal{eaas}{1869-6929}
{EAA Ser.}
{European Actuarial Academy (EAA) Series}
\DefineJournal{eicc}{2522-8595}
{EAI/Springer Innov. Commun. Comput.}
{EAI/Springer Innovations in Communication and Computing}
\DefineJournal{esmajsstmpp}{1383-7427}
{Early Sci. Med.}
{Early Science and Medicine. A Journal for the Study of Science, Technology and Medicine in the Pre-modern Period}
\DefineJournal{eajam}{2079-7362}
{East Asian J. Appl. Math.}
{East Asian Journal on Applied Mathematics}
\DefineJournal{ejm}{1513-489X}
{East-West J. Math.}
{East-West Journal of Mathematics}
\DefineJournal{eps}{0721-5363}
{Ec. Ete Probab. St.-Flour}
{Ecole d'Ete de Probabilites de Saint-Flour}
\DefineJournal{eis}{1389-6970}
{Eco-Effic. Ind. Sci.}
{Eco-Efficiency in Industry and Science}
\DefineJournal{teice}{1868-0453}
{Econ. Inf. Commun. Entertain.}
{The Economics of Information, Communication and Entertainment}
\DefineJournal{eipp}{?eipp}
{Econ. Issues Probl. Perspect.}
{Economic Issues, Problems and Perspectives}
\DefineJournal{esti}{?esti}
{Econ. Sci. Technol. Innov.}
{Economics of Science, Technology and Innovation}
\DefineJournal{essniesr}{?essniesr}
{Econ. Soc. Stud. Natl. Inst. Econ. Soc. Res.}
{Economic and Social Studies. National Institute of Economic and Social Research}
\DefineJournal{esisew}{2364-107X}
{Econ. Stud. Inequal. Soc. Exclusion Well-Being}
{Economic Studies in Inequality, Social Exclusion and Well-Being}
\DefineJournal{etb}{2196-1085}
{Econ. Theory Bull.}
{Economic Theory Bulletin}
\DefineJournal{tej}{1368-4221}
{Econom. J.}
{The Econometrics Journal}
\DefineJournal{el}{0165-1765}
{Econom. Lett.}
{Economics Letters}
\DefineJournal{esm}{?esm}
{Econom. Soc. Monogr.}
{Econometric Society Monographs}
\DefineJournal{es}{2452-3062}
{Econom. Stat.}
{Econometrics and Statistics}
\DefineJournal{et}{0938-2259}
{Econom. Theory}
{Economic Theory}
\DefineJournal{etil}{?etil}
{Econom. Tinbergen Inst. Lect.}
{Econometric and Tinbergen Institutes Lectures}
\DefineJournal{er}{0747-4938}
{Econometric Rev.}
{Econometric Reviews}
\DefineJournal{et}{0266-4666}
{Econometric Theory}
{Econometric Theory}
\DefineJournal{ejes}{0012-9682}
{Econometrica}
{Econometrica. Journal of the Econometric Society}
\DefineJournal{ens}{0013-0427}
{Economica (N.S.)}
{Economica. New Series}
\DefineJournal{ea}{1866-248X}
{Ed. Angew.}
{Edition Angewandte}
\DefineJournal{aeb}{?aeb}
{Ed. Belin}
{Aux Editions Belin}
\DefineJournal{egl}{?egl}
{Ed. Gutenbergplatz Leipz. (EAGLE)}
{Edition am Gutenbergplatz Leipzig (EAGLE)}
\DefineJournal{eatl}{?eatl}
{Edinb. Adv. Textb. Linguist.}
{Edinburgh Advanced Textbooks in Linguistics}
\DefineJournal{ef}{?ef}
{Educ. Form.}
{Education et Formation}
\DefineJournal{es}{2381-5833}
{Einstein Stud.}
{Einstein Studies}
\DefineJournal{eu}{?eu}
{Ekonom. Upravl.}
{Ekonomika i Upravlenie}
\DefineJournal{eeasps}{?eeasps}
{Electr. Eng. Appl. Signal Process. Ser.}
{Electrical Engineering and Applied Signal Processing Series}
\DefineJournal{eecsps}{?eecsps}
{Electr. Engrg. Commun. Signal Process. Ser.}
{Electrical Engineering Communications and Signal Processing Series}
\DefineJournal{ewrm}{?ewrm}
{Electromagn. Wirel. Radar Microw.}
{Electromagnetics, Wireless, Radar, and Microwaves}
\DefineJournal{ecp}{1083-589X}
{Electron. Commun. Probab.}
{Electronic Communications in Probability}
\DefineJournal{eeerseas}{?eeerseas}
{Electron. Electric. Engrg. Res. Stud. Electromagnet. Appl. Ser.}
{Electronic & Electrical Engineering Research Studies: Electromagnetic Applications Series}
\DefineJournal{ejasa}{2070-5948}
{Electron. J. Appl. Stat. Anal.}
{Electronic Journal of Applied Statistical Analysis}
\DefineJournal{ejbe}{1542-3891}
{Electron. J. Bound. Elem.}
{Electronic Journal of Boundary Elements}
\DefineJournal{ejc}{1077-8926}
{Electron. J. Combin.}
{Electronic Journal of Combinatorics}
\DefineJournal{ejdec}{?ejdec}
{Electron. J. Differ. Equ. Conf.}
{Electronic Journal of Differential Equations Conference}
\DefineJournal{ejde}{1072-6691}
{Electron. J. Differential Equations}
{Electronic Journal of Differential Equations}
\DefineJournal{ejgtae}{2338-2287}
{Electron. J. Graph Theory Appl. (EJGTA)}
{Electronic Journal of Graph Theory and Applications. EJGTA}
\DefineJournal{ejla}{1081-3810}
{Electron. J. Linear Algebra}
{Electronic Journal of Linear Algebra}
\DefineJournal{ejmaae}{2090-729X}
{Electron. J. Math. Anal. Appl.}
{Electronic Journal of Mathematical Analysis and Applications. EJMAA}
\DefineJournal{ejp}{1083-6489}
{Electron. J. Probab.}
{Electronic Journal of Probability}
\DefineJournal{ejqtde}{1417-3875}
{Electron. J. Qual. Theory Differ. Equ.}
{Electronic Journal of Qualitative Theory of Differential Equations}
\DefineJournal{ejs}{1935-7524}
{Electron. J. Stat.}
{Electronic Journal of Statistics}
\DefineJournal{empmdms}{?empmdms}
{Electron. Magn. Photonic Mater. Div. (EMPMD) Monogr. Ser.}
{Electronic, Magnetic and Photonic Materials Division (EMPMD) Monograph Series}
\DefineJournal{endm}{1571-0653}
{Electron. Notes Discrete Math.}
{Electronic Notes in Discrete Mathematics}
\DefineJournal{entcs}{1571-0661}
{Electron. Notes Theor. Comput. Sci.}
{Electronic Notes in Theoretical Computer Science}
\DefineJournal{eptcs}{2075-2180}
{Electron. Proc. Theor. Comput. Sci. (EPTCS)}
{Electronic Proceedings in Theoretical Computer Science (EPTCS)}
\DefineJournal{erams}{1935-9179}
{Electron. Res. Announc. Math. Sci.}
{Electronic Research Announcements in Mathematical Sciences}
\DefineJournal{etes}{?etes}
{Electron. Texts Engrs. Sci.}
{Electronics Texts for Engineers and Scientists}
\DefineJournal{etna}{1068-9613}
{Electron. Trans. Numer. Anal.}
{Electronic Transactions on Numerical Analysis}
\DefineJournal{ewc}{?ewc}
{Electron. Workshops Comput.}
{Electronic Workshops in Computing}
\DefineJournal{em}{0013-6018}
{Elem. Math.}
{Elemente der Mathematik}
\DefineJournal{ehspa}{?ehspa}
{Ellis Horwood Ser. Phys. Appl.}
{Ellis Horwood Series in Physics and its Applications}
\DefineJournal{ei}{?ei}
{Elsevier Insights}
{Elsevier Insights}
\DefineJournal{eos}{?eos}
{Elsevier Oceanogr. Ser.}
{Elsevier Oceanography Series}
\DefineJournal{ese}{?ese}
{ELTEX Studientexte Elektrotech.}
{ELTEX Studientexte Elektrotechnik}
\DefineJournal{ecc}{2194-7287}
{Emerg. Complex. Comput.}
{Emergence, Complexity and Computation}
\DefineJournal{emm}{2523-5192}
{EMS Monogr. Math.}
{EMS Monographs in Mathematics}
\DefineJournal{escr}{2523-515X}
{EMS Ser. Congr. Rep.}
{EMS Series of Congress Reports}
\DefineJournal{esiam}{2523-5087}
{EMS Ser. Ind. Appl. Math.}
{EMS Series in Industrial and Applied Mathematics}
\DefineJournal{eslm}{2523-5176}
{EMS Ser. Lect. Math.}
{EMS Series of Lectures in Mathematics}
\DefineJournal{esms}{2308-2151}
{EMS Surv. Math. Sci.}
{EMS Surveys in Mathematical Sciences}
\DefineJournal{etm}{?etm}
{EMS Textbk. Math.}
{EMS Textbooks in Mathematics}
\DefineJournal{etm}{?etm}
{EMS Tracts Math.}
{EMS Tracts in Mathematics}
\DefineJournal{ems}{0938-0396}
{Encyclopaedia Math. Sci.}
{Encyclopaedia of Mathematical Sciences}
\DefineJournal{ema}{?ema}
{Encyclopedia Math. Appl.}
{Encyclopedia of Mathematics and its Applications}
\DefineJournal{es}{1867-8998}
{Energy Syst.}
{Energy Systems}
\DefineJournal{esee}{2199-8582}
{Energy Syst. Electr. Eng.}
{Energy Systems in Electrical Engineering}
\DefineJournal{eabe}{0955-7997}
{Eng. Anal. Bound. Elem.}
{Engineering Analysis with Boundary Elements}
\DefineJournal{em}{1612-1317}
{Eng. Mater.}
{Engineering Materials}
\DefineJournal{emp}{1619-0181}
{Eng. Mater. Process.}
{Engineering Materials and Processes}
\DefineJournal{eo}{0305-215X}
{Eng. Optim.}
{Engineering Optimization}
\DefineJournal{esss}{?esss}
{Eng. Syst. Sustain. Ser.}
{Engineering Systems and Sustainability Series}
\DefineJournal{era}{?era}
{Enke Reihe AO[A]}
{Enke Reihe zur AO[A]}
\DefineJournal{em}{0103-8141}
{Ensaios Mat.}
{Ensaios Matematicos}
\DefineJournal{eao}{?eao}
{Enseign. Assiste Ordinateur}
{Enseignement Assiste par Ordinateur}
\DefineJournal{em}{1269-7842}
{Enseign. Math.}
{Enseignement des Mathematiques}
\DefineJournal{lm}{0013-8584}
{Enseign. Math.}
{L'Enseignement Mathematique}
\DefineJournal{eaiijeis}{1099-4300}
{Entropy}
{Entropy. An International and Interdisciplinary Journal of Entropy and Information Studies}
\DefineJournal{epel}{?epel}
{Entropy Prod. Everyday Live}
{Entropy Production in Everyday Live}
\DefineJournal{ees}{1352-8505}
{Environ. Ecol. Stat.}
{Environmental and Ecological Statistics}
\DefineJournal{ems}{?ems}
{Environmental Monogr. Sympos.}
{Environmental Monographs & Symposia}
\DefineJournal{e}{1180-4009}
{Environmetrics}
{Environmetrics}
\DefineJournal{esc}{2398-7340}
{EPiC Ser. Comput.}
{EPiC Series in Computing}
\DefineJournal{egae}{2491-6765}
{Epijournal Geom. Algebrique}
{Epijournal de Geometrie Algebrique. EPIGA}
\DefineJournal{e}{1777-4144}
{Episteme}
{Episteme}
\DefineJournal{e}{?e}
{Epistemologia}
{Epistemologia}
\DefineJournal{emgfasmsm}{0071-1136}
{Ergeb. Math. Grenzgeb. (3)}
{Ergebnisse der Mathematik und ihrer Grenzgebiete. 3. Folge. A Series of Modern Surveys in Mathematics}
\DefineJournal{etds}{0143-3857}
{Ergodic Theory Dynam. Systems}
{Ergodic Theory and Dynamical Systems}
\DefineJournal{eaijap}{0165-0106}
{Erkenntnis}
{Erkenntnis. An International Journal of Analytic Philosophy}
\DefineJournal{ef}{?ef}
{Ertrage der Forschung}
{Ertrage der Forschung}
\DefineJournal{ecocv}{1292-8119}
{ESAIM Control Optim. Calc. Var.}
{ESAIM. Control, Optimisation and Calculus of Variations}
\DefineJournal{emmna}{0764-583X}
{ESAIM Math. Model. Numer. Anal.}
{ESAIM. Mathematical Modelling and Numerical Analysis}
\DefineJournal{eps}{1292-8100}
{ESAIM Probab. Stat.}
{ESAIM. Probability and Statistics}
\DefineJournal{ep}{1270-900X}
{ESAIM Proc.}
{ESAIM Proceedings}
\DefineJournal{eps}{2267-3059}
{ESAIM Proc. Surveys}
{ESAIM: Proceedings and Surveys}
\DefineJournal{em}{?em}
{Esercit. Mat.}
{Esercitazioni di Matematica}
\DefineJournal{em}{?em}
{Esquisses Math.}
{Esquisses Mathematiques}
\DefineJournal{ecp}{0959-4479}
{Essays Cogn. Psych.}
{Essays in Cognitive Psychology}
\DefineJournal{tecs}{?tecs}
{Essence Comput. Ser.}
{The Essence of Computing Series}
\DefineJournal{etm}{2059-7657}
{Essent. Textb. Math.}
{Essential Textbooks in Mathematics}
\DefineJournal{ersiie}{0014-1135}
{Estadistica}
{Estadistica. Revista Semestral del Instituto Interamericano de Estadistica}
\DefineJournal{e}{?e}
{Estudos}
{Estudos}
\DefineJournal{e}{?e}
{ETH/TH}
{ETH/TH}
\DefineJournal{eaj}{2190-9733}
{Eur. Actuar. J.}
{European Actuarial Journal}
\DefineJournal{ecmi}{?ecmi}
{Eur. Consort. Math. Ind. (Berl.)}
{European Consortium for Mathematics in Industry (Berlin)}
\DefineJournal{ejcm}{1779-7179}
{Eur. J. Comput. Mech.}
{European Journal of Computational Mechanics}
\DefineJournal{ejc}{0947-3580}
{Eur. J. Control}
{European Journal of Control}
\DefineJournal{ejm}{2199-675X}
{Eur. J. Math.}
{European Journal of Mathematics}
\DefineJournal{ejmas}{0997-7538}
{Eur. J. Mech. A Solids}
{European Journal of Mechanics. A. Solids}
\DefineJournal{ejmbf}{0997-7546}
{Eur. J. Mech. B Fluids}
{European Journal of Mechanics. B. Fluids}
\DefineJournal{ejps}{1879-4912}
{Eur. J. Philos. Sci.}
{European Journal for Philosophy of Science}
\DefineJournal{ejpam}{1307-5543}
{Eur. J. Pure Appl. Math.}
{European Journal of Pure and Applied Mathematics}
\DefineJournal{emsn}{1027-488X}
{Eur. Math. Soc. Newsl.}
{European Mathematical Society. Newsletter}
\DefineJournal{emris}{1613-7388}
{Eur. Mem. Reihe I Stud.}
{Europaea Memoria. Reihe I. Studien}
\DefineJournal{tepjbcmcs}{1434-6028}
{Eur. Phys. J. B}
{The European Physical Journal B. Condensed Matter and Complex Systems}
\DefineJournal{esps}{2365-4228}
{Eur. Stud. Philos. Sci.}
{European Studies in Philosophy of Science}
\DefineJournal{emj}{2077-9879}
{Eurasian Math. J.}
{Eurasian Mathematical Journal}
\DefineJournal{eb}{?eb}
{Eureka Basic}
{Eureka Basic}
\DefineJournal{eator}{2364-687X}
{EURO Adv. Tutor. Oper. Res.}
{EURO Advanced Tutorials on Operational Research}
\DefineJournal{ejco}{2192-4406}
{EURO J. Comput. Optim.}
{EURO Journal on Computational Optimization}
\DefineJournal{ecis}{?ecis}
{Eurocourses Comput. Inform. Sci.}
{Eurocourses. Computer and Information Science}
\DefineJournal{ejam}{0956-7925}
{European J. Appl. Math.}
{European Journal of Applied Mathematics}
\DefineJournal{ejc}{0195-6698}
{European J. Combin.}
{European Journal of Combinatorics}
\DefineJournal{ejor}{0377-2217}
{European J. Oper. Res.}
{European Journal of Operational Research}
\DefineJournal{euisde}{?euisde}
{European Univ. Inst. Ser. D: Econom.}
{European University Institute. Series D: Economics}
\DefineJournal{eescs}{2198-4204}
{Evol. Econ. Soc. Complex. Sci.}
{Evolutionary Economics and Social Complexity Science}
\DefineJournal{eect}{2163-2480}
{Evol. Equ. Control Theory}
{Evolution Equations and Control Theory}
\DefineJournal{e}{?e}
{Evrika}
{Evrika}
\DefineJournal{e}{?e}
{Ex-Aula}
{Ex-Aula}
\DefineJournal{erms}{?erms}
{Excursions Rec. Math. Ser.}
{Excursions in Recreational Mathematics Series}
\DefineJournal{el}{?el}
{Exempla Logica}
{Exempla Logica}
\DefineJournal{em}{1058-6458}
{Exp. Math.}
{Experimental Mathematics}
\DefineJournal{edlapt}{?edlapt}
{Explicit Description Language Automat. Process. Text}
{Explicit Description of Language and Automatic Processing of Text}
\DefineJournal{eccs}{?eccs}
{Explor.: Cours Contrib. Sci. Ed.}
{Exploration: Cours et Contributions pour les Sciences de l'Education}
\DefineJournal{e}{0721-3700}
{Explorationen}
{Explorationen}
\DefineJournal{em}{0723-0869}
{Expo. Math.}
{Expositiones Mathematicae}
\DefineJournal{em}{0213-8743}
{Extracta Math.}
{Extracta Mathematicae}
\DefineJournal{estasee}{1386-1999}
{Extremes}
{Extremes. Statistical Theory and Applications in Science, Engineering and Economics}
\DefineJournal{em}{?em}
{Exxon Monogr.}
{Exxon Monographs}
\DefineJournal{fs}{?fs}
{Fachber. Simul.}
{Fachberichte Simulation}
\DefineJournal{fsfp}{?fsfp}
{Fachbuchreihe Stud. Fortbild. Prax.}
{Fachbuchreihe fur Studium Fortbildung Praxis}
\DefineJournal{fusacr}{1820-6417}
{Facta Univ. Ser. Autom. Control Robot.}
{Facta Universitatis. Series Automatic Control and Robotics}
\DefineJournal{fusmi}{0352-9665}
{Facta Univ. Ser. Math. Inform.}
{Facta Universitatis. Series: Mathematics and Informatics}
\DefineJournal{ppimfm}{0044-4413}
{Fasc. Math.}
{Polytechnica Posnaniensis. Institutum Mathematicum. Fasciculi Mathematici}
\DefineJournal{fdjs}{1306-7575}
{Fen Derg.}
{Fen Dergisi. Journal of Science}
\DefineJournal{fc}{?fc}
{Fenetre Cours}
{Fenetre sur Cours}
\DefineJournal{fiss}{2522-8900}
{FIAS Interdiscip. Sci. Ser.}
{FIAS Interdisciplinary Science Series}
\DefineJournal{tfqtojfa}{0015-0517}
{Fibonacci Quart.}
{The Fibonacci Quarterly. The Official Journal of the Fibonacci Association}
\DefineJournal{fic}{1069-5265}
{Fields Inst. Commun.}
{Fields Institute Communications}
\DefineJournal{fim}{1069-5273}
{Fields Inst. Monogr.}
{Fields Institute Monographs}
\DefineJournal{unpff}{0354-5180}
{Filomat}
{Univerzitet u Nisu. Prirodno-Matematicki Fakultet. Filomat}
\DefineJournal{fchf}{?fchf}
{Filosofia (London)}
{Filosofia---Filosofia Contemporanea e Historia da Filosofia (London)}
\DefineJournal{fee}{?fee}
{Financ. Eng. Explain.}
{Financial Engineering Explained}
\DefineJournal{fm}{?fm}
{Financ. Math.}
{Financial Mathematics}
\DefineJournal{fma}{2217-7795}
{Financ. Math. Appl.}
{Financial Mathematics and Applications}
\DefineJournal{fs}{0949-2984}
{Finance Stoch.}
{Finance and Stochastics}
\DefineJournal{fead}{0168-874X}
{Finite Elem. Anal. Des.}
{Finite Elements in Analysis and Design}
\DefineJournal{ffa}{1071-5797}
{Finite Fields Appl.}
{Finite Fields and their Applications}
\DefineJournal{fptaijfptca}{1583-5022}
{Fixed Point Theory}
{Fixed Point Theory. An International Journal on Fixed Point Theory, Computation and Applications}
\DefineJournal{fpta}{1687-1812}
{Fixed Point Theory Appl.}
{Fixed Point Theory and Applications}
\DefineJournal{fp}{?fp}
{Fiz. Plazmy}
{Fizika Plazmy}
\DefineJournal{fn}{ Moscow."}
{Fiz.-Mat. Nasled.}
{Fiziko-Matematicheskoe Nasledie}
\DefineJournal{fd}{0015-4628}
{Fluid Dyn.}
{Fluid Dynamics}
\DefineJournal{fdraij}{0169-5983}
{Fluid Dyn. Res.}
{Fluid Dynamics Research. An International Journal}
\DefineJournal{fma}{0926-5112}
{Fluid Mech. Appl.}
{Fluid Mechanics and its Applications}
\DefineJournal{fmdaaim}{?fmdaaim}
{FMDA Abt. II: Monogr.}
{Forschungen und Materialien zur Deutschen Aufklarung (FMDA). Abteilung II: Monographien}
\DefineJournal{facs}{?facs}
{Focus Autom. Control Ser.}
{Focus. Automation and Control Series}
\DefineJournal{fsdsip}{?fsdsip}
{Focus Ser. Digit. Signal Image Process.}
{Focus Series in Digital Signal and Image Processing}
\DefineJournal{fsfbm}{?fsfbm}
{Focus Ser. Finance Bus. Manag.}
{Focus Series in Finance, Business and Management}
\DefineJournal{fm}{0208-6204}
{Folia Math.}
{Folia Mathematica}
\DefineJournal{fcfs}{?fcfs}
{Fond. CIME/CIME Found. Subser.}
{Fondazione CIME/CIME Foundation Subseries}
\DefineJournal{fac}{0934-5043}
{Form. Asp. Comput.}
{Formal Aspects of Computing}
\DefineJournal{f}{0911-6036}
{Forma}
{Forma}
\DefineJournal{firmfndm}{?firmfndm}
{Forsch. Inst. Realienkd. Mittelalt. Fruhen Neuzeit Diskuss. Mater.}
{Forschungen des Instituts fur Realienkunde des Mittelalters und der Fruhen Neuzeit. Diskussionen und Materialien}
\DefineJournal{fppp}{0015-8208}
{Fortschr. Phys.}
{Fortschritte der Physik. Progress of Physics}
\DefineJournal{fgajcegra}{1534-1178}
{Forum Geom.}
{Forum Geometricorum. A Journal on Classical Euclidean Geometry and Related Areas}
\DefineJournal{fim}{2364-6748}
{Forum Interdiscip. Math.}
{Forum for Interdisciplinary Mathematics}
\DefineJournal{fm}{0933-7741}
{Forum Math.}
{Forum Mathematicum}
\DefineJournal{fmp}{2050-5086}
{Forum Math. Pi}
{Forum of Mathematics. Pi}
\DefineJournal{fms}{2050-5094}
{Forum Math. Sigma}
{Forum of Mathematics. Sigma}
\DefineJournal{fcmtjsfcm}{1615-3375}
{Found. Comput. Math.}
{Foundations of Computational Mathematics. The Journal of the Society for the Foundations of Computational Mathematics}
\DefineJournal{fem}{1612-1384}
{Found. Eng. Mech.}
{Foundations of Engineering Mechanics}
\DefineJournal{fpaijdcbftmp}{0015-9018}
{Found. Phys.}
{Foundations of Physics. An International Journal Devoted to the Conceptual Bases and Fundamental Theories of Modern Physics}
\DefineJournal{fqs}{?fqs}
{Found. Quest. Sci.}
{Foundational Questions in Science}
\DefineJournal{fs}{1233-1821}
{Found. Sci.}
{Foundations of Science}
\DefineJournal{fspcn}{1863-8538}
{Found. Signal. Process. Commun. Netw.}
{Foundations in Signal Processing, Communications and Networking}
\DefineJournal{ftsp}{1932-8346}
{Found. Trends Signal Process.}
{Foundations and Trends${}^\circledR$ in Signal Processing}
\DefineJournal{fttcs}{1551-305X}
{Found. Trends Theor. Comput. Sci.}
{Foundations and Trends${}^\circledR$ in Theoretical Computer Science}
\DefineJournal{furm}{2520-1212}
{Found. Undergrad. Res. Math.}
{Foundations for Undergraduate Research in Mathematics}
\DefineJournal{fcaa}{1311-0454}
{Fract. Calc. Appl. Anal.}
{Fractional Calculus and Applied Analysis}
\DefineJournal{fcase}{2509-7210}
{Fract. Calc. Appl. Sci. Eng.}
{Fractional Calculus in Applied Sciences and Engineering}
\DefineJournal{fdc}{1847-9677}
{Fract. Differ. Calc.}
{Fractional Differential Calculus}
\DefineJournal{fcgpsns}{0218-348X}
{Fractals}
{Fractals. Complex Geometry, Patterns, and Scaling in Nature and Society}
\DefineJournal{fdmsata}{2382-6320}
{Fractals Dyn. Math. Sci. Arts Theory Appl.}
{Fractals and Dynamics in Mathematics, Science, and the Arts: Theory and Applications}
\DefineJournal{tfjfs}{?tfjfs}
{Frank J. Fabozzi Ser.}
{The Frank J. Fabozzi Series}
\DefineJournal{fadsrt}{2364-4532}
{Front. Appl. Dyn. Syst. Rev. Tutor.}
{Frontiers in Applied Dynamical Systems: Reviews and Tutorials}
\DefineJournal{fb}{2199-8515}
{Front. Biomech.}
{Frontiers of Biomechanics}
\DefineJournal{tfc}{1612-3018}
{Front. Coll.}
{The Frontiers Collection}
\DefineJournal{fm}{?fm}
{Front. Math.}
{Frontiers in Mathematics}
\DefineJournal{fmc}{1673-3452}
{Front. Math. China}
{Frontiers of Mathematics in China}
\DefineJournal{fpss}{?fpss}
{Front. Probab. Stat. Sci.}
{Frontiers in Probability and the Statistical Sciences}
\DefineJournal{frcmmb}{2315-4713}
{Front. Res. Comput. Mech. Mater. Biol.}
{Frontier Research in Computation and Mechanics of Materials and Biology}
\DefineJournal{forasa}{?forasa}
{Frontiers Oper. Res. Appl. Systems Anal.}
{Frontiers of Operational Research and Applied Systems Analysis}
\DefineJournal{}{?}
{Fudan Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{fusr}{0386-118X}
{Fukuoka Univ. Sci. Rep.}
{Fukuoka University Science Reports}
\DefineJournal{fc}{?fc}
{Full Circ.}
{Full Circle}
\DefineJournal{faa}{0016-2663}
{Funct. Anal. Appl.}
{Functional Analysis and its Applications}
\DefineJournal{faac}{1821-410X}
{Funct. Anal. Approx. Comput.}
{Functional Analysis, Approximation and Computation}
\DefineJournal{uampwmifacm}{0208-6573}
{Funct. Approx. Comment. Math.}
{Uniwersytet im. Adama Mickiewicza w Poznaniu. Wydzial Matematyki i Informatyki. Functiones et Approximatio Commentarii Mathematici}
\DefineJournal{fde}{0793-1786}
{Funct. Differ. Equ.}
{Functional Differential Equations}
\DefineJournal{fi}{0169-2968}
{Fund. Inform.}
{Fundamenta Informaticae}
\DefineJournal{fm}{0016-2736}
{Fund. Math.}
{Fundamenta Mathematicae}
\DefineJournal{fscs}{?fscs}
{Fund. Stud. Comput. Sci.}
{Fundamental Studies in Computer Science}
\DefineJournal{fa}{?fa}
{Fundam. Algorithms}
{Fundamentals of Algorithms}
\DefineJournal{fanps}{?fanps}
{Fundam. Appl. Nucl. Phys. Ser.}
{Fundamental and Applied Nuclear Physics Series}
\DefineJournal{fpm}{1560-5159}
{Fundam. Prikl. Mat.}
{Fundamentalnaya i Prikladnaya Matematika}
\DefineJournal{ftp}{0168-1222}
{Fundam. Theor. Phys.}
{Fundamental Theories of Physics}
\DefineJournal{fesi}{0532-8721}
{Funkcial. Ekvac.}
{Funkcialaj Ekvacioj. Serio Internacia}
\DefineJournal{ranfap}{0374-1990}
{Funktsional. Anal. i Prilozhen.}
{Rossiiskaya Akademiya Nauk. Funktsionalnyi Analiz i ego Prilozheniya}
\DefineJournal{}{?}
{Fuzhou Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{fie}{1616-8658}
{Fuzzy Inf. Eng.}
{Fuzzy Information and Engineering}
\DefineJournal{fodmajmcuu}{1568-4539}
{Fuzzy Optim. Decis. Mak.}
{Fuzzy Optimization and Decision Making. A Journal of Modeling and Computation Under Uncertainty}
\DefineJournal{fssaijise}{0165-0114}
{Fuzzy Sets and Systems}
{Fuzzy Sets and Systems. An International Journal in Information Science and Engineering}
\DefineJournal{lgrsme}{1138-8927}
{Gac. R. Soc. Mat. Esp.}
{La Gaceta de la Real Sociedad Matematica Espanola}
\DefineJournal{gismsa}{?gismsa}
{GAKUTO Internat. Ser. Math. Sci. Appl.}
{GAKUTO International Series. Mathematical Sciences and Applications}
\DefineJournal{gta}{?gta}
{Game Theory Appl.}
{Game Theory and Applications}
\DefineJournal{g}{2073-4336}
{Games}
{Games}
\DefineJournal{geb}{0899-8256}
{Games Econom. Behav.}
{Games and Economic Behavior}
\DefineJournal{g}{0936-7195}
{GAMM-Mitt.}
{GAMM-Mitteilungen}
\DefineJournal{gjbms}{1606-3694}
{Ganit}
{Ganit. Journal of Bangladesh Mathematical Society}
\DefineJournal{g}{0046-5402}
{Ganita}
{Ganita}
\DefineJournal{gbbishm}{0970-0307}
{Ganita Bharati}
{Ganita Bharati. Bulletin of the Indian Society for History of Mathematics}
\DefineJournal{}{?}
{Gaodeng Xuexiao Jisuan Shuxue Xuebao}
{nan}
\DefineJournal{gm}{0224-8999}
{Gaz. Math.}
{Gazette des Mathematiciens}
\DefineJournal{gt}{?gt}
{Gazodinam. i Teploobmen}
{Gazodinamika i Teploobmen}
\DefineJournal{gijg}{1869-2672}
{GEM Int. J. Geomath.}
{GEM. International Journal on Geomathematics}
\DefineJournal{grg}{0001-7701}
{Gen. Relativity Gravitation}
{General Relativity and Gravitation}
\DefineJournal{gs}{?gs}
{Gendai Sugaku}
{Gendai Sugaku}
\DefineJournal{gses}{?gses}
{Gendai Sugaku Enshu Sosho}
{Gendai Sugaku Enshu Sosho}
\DefineJournal{gecs}{1932-0167}
{Genet. Evol. Comput. Ser.}
{Genetic and Evolutionary Computation Series}
\DefineJournal{gc}{1866-6795}
{Geom. Comput.}
{Geometry and Computing}
\DefineJournal{gd}{0046-5755}
{Geom. Dedicata}
{Geometriae Dedicata}
\DefineJournal{gf}{2353-3382}
{Geom. Flows}
{Geometric Flows}
\DefineJournal{gfa}{1016-443X}
{Geom. Funct. Anal.}
{Geometric and Functional Analysis}
\DefineJournal{gic}{2328-8876}
{Geom. Imaging Comput.}
{Geometry, Imaging and Computing}
\DefineJournal{gt}{1465-3060}
{Geom. Topol.}
{Geometry & Topology}
\DefineJournal{gtm}{1464-8997}
{Geom. Topol. Monogr.}
{Geometry & Topology Monographs}
\DefineJournal{g}{1065-7371}
{Geombinatorics}
{Geombinatorics}
\DefineJournal{gafd}{0309-1929}
{Geophys. Astrophys. Fluid Dyn.}
{Geophysical and Astrophysical Fluid Dynamics}
\DefineJournal{gm}{0065-8448}
{Geophys. Monogr.}
{Geophysical Monograph}
\DefineJournal{gmj}{1072-947X}
{Georgian Math. J.}
{Georgian Mathematical Journal}
\DefineJournal{gm}{2510-1544}
{Geosyst. Math.}
{Geosystems Mathematics}
\DefineJournal{grw}{?grw}
{Gesellschaft, Recht, Wirtschaft}
{Gesellschaft, Recht, Wirtschaft}
\DefineJournal{gmsi}{0017-095X}
{Glas. Mat. Ser. III}
{Glasnik Matematicki. Serija III}
\DefineJournal{gmj}{0017-0895}
{Glasg. Math. J.}
{Glasgow Mathematical Journal}
\DefineJournal{giwp}{2211-0631}
{Glob. Issues Water Policy}
{Global Issues in Water Policy}
\DefineJournal{gjarcmg}{2284-5569}
{Glob. J. Adv. Res. Class. Mod. Geom.}
{Global Journal of Advanced Research on Classical and Modern Geometries}
\DefineJournal{gsukofmiasukofmi}{0205-0808}
{God. Sofii. Univ. ``Sv. Kliment Okhridski. Fac. Mat. Inform."}
{Godishnik na Sofiiskiya Universitet ``Sv. Kliment Okhridski''. Fakultet po Matematika i Informatika. Annual of Sofia University ``St. Kliment Ohridski. Faculty of Mathematics and Informatics"}
\DefineJournal{gzimpfukmsamfskms}{0351-7441}
{God. Zb. Inst. Mat. Prir.-Mat. Fak. Univ. Kiril Metodij Skopje}
{Godishen Zbornik na Institutot za Matematika. Prirodno-Matematichki. Fakultet Universitet ``Sv. Kiril i Metodij''. Skopje. Annuaire de l'Institut des Mathematiques. Faculte des Sciences de l'Universite ``Sts. Kiril et Metodij''. Skopje}
\DefineJournal{gsxcjem}{1005-3085}
{Gongcheng Shuxue Xuebao}
{Gongcheng Shuxue Xuebao. Chinese Journal of Engineering Mathematics}
\DefineJournal{tgjm}{1737-0299}
{Grad. J. Math.}
{The Graduate Journal of Mathematics}
\DefineJournal{gsm}{1065-7339}
{Grad. Stud. Math.}
{Graduate Studies in Mathematics}
\DefineJournal{gtm}{0072-5285}
{Grad. Texts in Math.}
{Graduate Texts in Mathematics}
\DefineJournal{gtp}{1868-4513}
{Grad. Texts Phys.}
{Graduate Texts in Physics}
\DefineJournal{lgnst}{?lgnst}
{Grands Noms Sci. Tech.}
{Les Grands Noms de la Science et de la Technique}
\DefineJournal{ggs}{?ggs}
{Graph. Gems Ser.}
{Graphics Gems Series}
\DefineJournal{gm}{1524-0703}
{Graph. Models}
{Graphical Models}
\DefineJournal{gc}{0911-0119}
{Graphs Combin.}
{Graphs and Combinatorics}
\DefineJournal{gc}{0202-2893}
{Gravit. Cosmol.}
{Gravitation and Cosmology}
\DefineJournal{gmb}{1016-7692}
{Grazer Math. Ber.}
{Grazer Mathematische Berichte}
\DefineJournal{get}{1865-3529}
{Green Energy Technol.}
{Green Energy and Technology}
\DefineJournal{gs}{?gs}
{Grenoble Sci.}
{Grenoble Sciences}
\DefineJournal{gs}{?gs}
{Grenoble Sci.}
{Grenoble Sciences}
\DefineJournal{gsms}{?gsms}
{Griffin's Statist. Monogr. Ser.}
{Griffin's Statistical Monograph Series}
\DefineJournal{gcc}{1867-1144}
{Groups Complex. Cryptol.}
{Groups. Complexity. Cryptology}
\DefineJournal{ggd}{1661-7207}
{Groups Geom. Dyn.}
{Groups, Geometry, and Dynamics}
\DefineJournal{gp}{?gp}
{Grundkurs Phys.}
{Grundkurs Physik}
\DefineJournal{gmi}{?gmi}
{Grundlagen Math. Inform.}
{Grundlagen der Mathematik und Informatik}
\DefineJournal{gmw}{0072-7830}
{Grundlehren Math. Wiss.}
{Grundlehren der Mathematischen Wissenschaften}
\DefineJournal{gjm}{2309-4966}
{Gulf J. Math.}
{Gulf Journal of Mathematics}
\DefineJournal{hjms}{1303-5010}
{Hacet. J. Math. Stat.}
{Hacettepe Journal of Mathematics and Statistics}
\DefineJournal{hggcgt}{?hggcgt}
{Handb. Graph Gramm. Comput. Graph Transform.}
{Handbook of Graph Grammars and Computing by Graph Transformation}
\DefineJournal{hhl}{1874-5857}
{Handb. Hist. Log.}
{Handbook of the History of Logic}
\DefineJournal{hna}{1570-8659}
{Handb. Numer. Anal.}
{Handbook of Numerical Analysis}
\DefineJournal{hpl}{?hpl}
{Handb. Philos. Log.}
{Handbook of Philosophical Logic}
\DefineJournal{hps}{0031-8019}
{Handb. Philos. Sci.}
{Handbook of the Philosophy of Science}
\DefineJournal{hidi}{0939-1959}
{Handbook Internat. Doc. Info.}
{Handbook of International Documentation and Information}
\DefineJournal{hs}{0169-7161}
{Handbook of Statist.}
{Handbook of Statistics}
\DefineJournal{he}{0169-7218}
{Handbooks in Econom.}
{Handbooks in Economics}
\DefineJournal{hp}{?hp}
{Handbuch Phys.}
{Handbuch der Physik}
\DefineJournal{}{?}
{Harbin Gongye Daxue Xuebao}
{nan}
\DefineJournal{hj}{?hj}
{Hardy-Ramanujan J.}
{Hardy-Ramanujan Journal}
\DefineJournal{ht}{?ht}
{Harper Torchbooks}
{Harper Torchbooks}
\DefineJournal{hucmsasm}{?hucmsasm}
{Harv. Univ. Cent. Math. Sci. Appl. Ser. Math.}
{Harvard University Center of Mathematical Sciences and Applications (CMSA) Series in Mathematics}
\DefineJournal{hlnm}{2509-8071}
{HBA Lect. Notes Math.}
{HBA Lecture Notes in Mathematics}
\DefineJournal{his}{2366-0988}
{Health Inf. Sci.}
{Health Information Science}
\DefineJournal{hmt}{1860-4846}
{Heat Mass Transf.}
{Heat and Mass Transfer}
\DefineJournal{htsr}{?htsr}
{Heat Transfer: Soviet Rev.}
{Heat Transfer: Soviet Reviews}
\DefineJournal{}{?}
{Hefei Gongye Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{ahhrb}{?ahhrb}
{Henry Holt Ref. Book}
{A Henry Holt Reference Book}
\DefineJournal{hem}{2523-5214}
{Herit. Eur. Math.}
{Heritage of European Mathematics}
\DefineJournal{hi}{0170-8120}
{Hildesheimer Inform.-Ber.}
{Hildesheimer Informatik-Bericht}
\DefineJournal{hamts}{?hamts}
{Hindu Astronom. Math. Text Ser.}
{Hindu Astronomical and Mathematical Text Series}
\DefineJournal{hmj}{0018-2079}
{Hiroshima Math. J.}
{Hiroshima Mathematical Journal}
\DefineJournal{hap}{?hap}
{Hist. Anal. Philos.}
{History of Analytic Philosophy}
\DefineJournal{hc}{2190-6831}
{Hist. Comput.}
{History of Computing}
\DefineJournal{his}{?his}
{Hist. Inst. Sci.}
{Histoires des Institutions Scientifiques}
\DefineJournal{hm}{0899-2428}
{Hist. Math.}
{History of Mathematics}
\DefineJournal{hme}{2509-9736}
{Hist. Math. Educ.}
{History of Mathematics Education}
\DefineJournal{hmms}{1875-3442}
{Hist. Mech. Mach. Sci.}
{History of Mechanism and Machine Science}
\DefineJournal{hpl}{0144-5340}
{Hist. Philos. Logic}
{History and Philosophy of Logic}
\DefineJournal{hpsci}{2376-6336}
{Hist. Philos. Sci.}
{History and Philosophy of Science---Heresy, Crossroads, and Intersections}
\DefineJournal{hps}{2117-3508}
{Hist. Philos. Sci. (Paris)}
{Histoire et Philosophie des Sciences (Paris)}
\DefineJournal{hs}{?hs}
{Hist. Sci. (Paris)}
{Histoire des Sciences (Paris)}
\DefineJournal{hstrs}{?hstrs}
{Hist. Sci. Tech. Reprint Ser.}
{History of Science and Technology Reprint Series}
\DefineJournal{hm}{0315-0860}
{Historia Math.}
{Historia Mathematica}
\DefineJournal{hm}{?hm}
{Hochschuldidakt. Material.}
{Hochschuldidaktische Materialien}
\DefineJournal{hmj}{0385-4035}
{Hokkaido Math. J.}
{Hokkaido Mathematical Journal}
\DefineJournal{hha}{1532-0073}
{Homology Homotopy Appl.}
{Homology, Homotopy and Applications}
\DefineJournal{hmj}{1225-293X}
{Honam Math. J.}
{Honam Mathematical Journal}
\DefineJournal{hjm}{0362-1588}
{Houston J. Math.}
{Houston Journal of Mathematics}
\DefineJournal{}{?}
{Huadong Shifan Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Huazhong Keji Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Huazhong Shifan Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{his}{1571-5035}
{Hum.-Comput. Interact. Ser.}
{Human-Computer Interaction Series}
\DefineJournal{hcrs}{?hcrs}
{Human Comm. Res. Ser.}
{Human Communication Research Series}
\DefineJournal{}{?}
{Hunan Shifan Daxue Ziran Kexue Ban}
{nan}
\DefineJournal{iijam}{1992-9978}
{IAENG Int. J. Appl. Math.}
{IAENG International Journal of Applied Mathematics}
\DefineJournal{icms}{1079-5634}
{IAS/Park City Math. Ser.}
{IAS/Park City Mathematics Series}
\DefineJournal{itps}{?itps}
{IAS/PCMI Teach. Program Ser.}
{IAS/PCMI---The Teacher Program Series}
\DefineJournal{is}{1743-9213}
{IAU Symp.}
{IAU Symposium}
\DefineJournal{inniccm}{2326-4810}
{ICCM Not.}
{ICCM Notices. Notices of the International Congress of Chinese Mathematicians}
\DefineJournal{is}{?is}
{ICM Ser.}
{ICM Series}
\DefineJournal{im}{2520-8322}
{ICME-13 Monogr.}
{ICME-13 Monographs}
\DefineJournal{isp}{2045-0990}
{ICP Sel. Pap.}
{ICP Selected Papers}
\DefineJournal{ibss}{2199-0980}
{ICSA Book Ser. Stat.}
{ICSA Book Series in Statistics}
\DefineJournal{ims}{?ims}
{IDM Materialien Studien}
{IDM Materialien und Studien}
\DefineJournal{ihts}{?ihts}
{IEE Hist. Tech. Ser.}
{IEE History of Technology Series}
\DefineJournal{ics}{1066-033X}
{IEEE Control Syst.}
{IEEE Control Systems}
\DefineJournal{ipsci}{?ipsci}
{IEEE Press Ser. Comput. Intell.}
{IEEE Press Series on Computational Intelligence}
\DefineJournal{ipspe}{?ipspe}
{IEEE Press Ser. Power Eng.}
{IEEE Press Series on Power Engineering}
\DefineJournal{ipsrmt}{?ipsrmt}
{IEEE Press Ser. RF Microw. Technol.}
{IEEE Press Series on RF and Microwave Technology}
\DefineJournal{ipusts}{?ipusts}
{IEEE Press Underst. Sci. Technol. Ser.}
{IEEE Press Understanding Science & Technology Series}
\DefineJournal{ieeetap}{0018-926X}
{IEEE Trans. Antennas and Propagation}
{Institute of Electrical and Electronics Engineers. Transactions on Antennas and Propagation}
\DefineJournal{ieeetac}{0018-9286}
{IEEE Trans. Automat. Control}
{Institute of Electrical and Electronics Engineers. Transactions on Automatic Control}
\DefineJournal{itcsirp}{1549-8328}
{IEEE Trans. Circuits Syst. I. Regul. Pap.}
{IEEE Transactions on Circuits and Systems. I. Regular Papers}
\DefineJournal{ieeetc}{0018-9340}
{IEEE Trans. Comput.}
{Institute of Electrical and Electronics Engineers. Transactions on Computers}
\DefineJournal{itci}{2333-9403}
{IEEE Trans. Comput. Imaging}
{IEEE Transactions on Computational Imaging}
\DefineJournal{itcns}{2325-5870}
{IEEE Trans. Control Netw. Syst.}
{IEEE Transactions on Control of Network Systems}
\DefineJournal{itip}{1057-7149}
{IEEE Trans. Image Process.}
{IEEE Transactions on Image Processing}
\DefineJournal{ieeetit}{0018-9448}
{IEEE Trans. Inform. Theory}
{Institute of Electrical and Electronics Engineers. Transactions on Information Theory}
\DefineJournal{itnse}{2327-4697}
{IEEE Trans. Network Sci. Eng.}
{IEEE Transactions on Network Science and Engineering}
\DefineJournal{itnnls}{2162-237X}
{IEEE Trans. Neural Netw. Learn. Syst.}
{IEEE Transactions on Neural Networks and Learning Systems}
\DefineJournal{itsipn}{2373-776X}
{IEEE Trans. Signal Inform. Process. Netw.}
{IEEE Transactions on Signal and Information Processing over Networks}
\DefineJournal{itsp}{1053-587X}
{IEEE Trans. Signal Process.}
{IEEE Transactions on Signal Processing}
\DefineJournal{ijas}{2329-9266}
{IEEE/CAA J. Autom. Sin.}
{IEEE/CAA Journal of Automatica Sinica}
\DefineJournal{ices}{?ices}
{IET Control Eng. Ser.}
{IET Control Engineering Series}
\DefineJournal{icta}{1751-8644}
{IET Control Theory Appl.}
{IET Control Theory & Applications}
\DefineJournal{ipes}{?ipes}
{IET Power Energy Ser.}
{IET Power and Energy Series}
\DefineJournal{ijsc}{2468-6018}
{IFAC J. Syst. Control}
{IFAC Journal of Systems and Control}
\DefineJournal{iws}{?iws}
{IFAC Workshop Ser.}
{IFAC Workshop Series}
\DefineJournal{iaict}{1868-4238}
{IFIP Adv. Inf. Commun. Technol.}
{IFIP Advances in Information and Communication Technology}
\DefineJournal{ics}{?ics}
{IFIP Congress Ser.}
{IFIP Congress Series}
\DefineJournal{it}{?it}
{IFIP Trans.}
{IFIP Transactions}
\DefineJournal{itccs}{0926-549X}
{IFIP Trans. C Comm. Systems}
{IFIP Transactions C: Communication Systems}
\DefineJournal{ibqw}{?ibqw}
{Ifo Beitr. Quant. Wirtschaftsforsch.}
{Ifo Beitrage zur Quantitativen Wirtschaftsforschung}
\DefineJournal{iissse}{1574-0463}
{IFSR Internat. Ser. Systems Sci. Engrg.}
{IFSR International Series on Systems Science and Engineering}
\DefineJournal{i}{?i}
{IFVE 82}
{IFVE 82}
\DefineJournal{ips}{?ips}
{IIASA Proc. Ser.}
{IIASA Proceedings Series}
\DefineJournal{ilns}{2010-2402}
{IISc Lect. Notes Ser.}
{IISc Lecture Notes Series}
\DefineJournal{ijm}{0019-2082}
{Illinois J. Math.}
{Illinois Journal of Mathematics}
\DefineJournal{ijam}{0272-4960}
{IMA J. Appl. Math.}
{IMA Journal of Applied Mathematics}
\DefineJournal{ijmm}{1471-678X}
{IMA J. Manag. Math.}
{IMA Journal of Management Mathematics}
\DefineJournal{ijmci}{0265-0754}
{IMA J. Math. Control Inform.}
{IMA Journal of Mathematical Control and Information}
\DefineJournal{ijna}{0272-4979}
{IMA J. Numer. Anal.}
{IMA Journal of Numerical Analysis}
\DefineJournal{tivma}{0940-6573}
{IMA Vol. Math. Appl.}
{The IMA Volumes in Mathematics and its Applications}
\DefineJournal{iasqma}{1580-3139}
{Image Anal. Stereol.}
{Image Analysis & Stereology. Quantitative Methods and Applications}
\DefineJournal{ijampaajpam}{1608-9324}
{IMHOTEP J. Afr. Math. Pures Appl.}
{IMHOTEP. Journal Africain de Mathematiques Pures et Appliquees. African Journal of Pure and Applied Mathematics}
\DefineJournal{imp}{?imp}
{Imhotep Math. Proc.}
{Imhotep Mathematical Proceedings}
\DefineJournal{im}{?im}
{IMPA Monogr.}
{IMPA Monographs}
\DefineJournal{iln}{2353-6578}
{IMPAN Lect. Notes}
{IMPAN Lecture Notes}
\DefineJournal{imst}{?imst}
{IMS Textb.}
{Institute of Mathematical Statistics Textbooks}
\DefineJournal{ilnm}{2509-8098}
{IMSc Lect. Notes Math.}
{IMSc Lecture Notes in Mathematics}
\DefineJournal{iam}{2364-6837}
{Ind. Appl. Math.}
{Industrial and Applied Mathematics}
\DefineJournal{knawimns}{0019-3577}
{Indag. Math. (N.S.)}
{Koninklijke Nederlandse Akademie van Wetenschappen. Indagationes Mathematicae. New Series}
\DefineJournal{ijhs}{0019-5235}
{Indian J. Hist. Sci.}
{Indian Journal of History of Science}
\DefineJournal{ijm}{0019-5324}
{Indian J. Math.}
{Indian Journal of Mathematics}
\DefineJournal{ijpam}{0019-5588}
{Indian J. Pure Appl. Math.}
{Indian Journal of Pure and Applied Mathematics}
\DefineJournal{isis}{2523-3114}
{Indian Stat. Inst. Ser.}
{Indian Statistical Institute Series}
\DefineJournal{iumj}{0022-2518}
{Indiana Univ. Math. J.}
{Indiana University Mathematics Journal}
\DefineJournal{iivii}{?iivii}
{Inf & Ing Vorles. Inform. Ingenieurstud.}
{Inf & Ing: Vorlesungen zum Informatik- und Ingenieurstudium}
\DefineJournal{iiaji}{2049-8764}
{Inf. Inference}
{Information and Inference. A Journal of the IMA}
\DefineJournal{tirs}{1387-5264}
{Inf. Retr. Ser.}
{The Information Retrieval Series}
\DefineJournal{isc}{1619-7100}
{Inf. Secur. Cryptography}
{Information Security and Cryptography}
\DefineJournal{idaqprt}{0219-0257}
{Infin. Dimens. Anal. Quantum Probab. Relat. Top.}
{Infinite Dimensional Analysis, Quantum Probability and Related Topics}
\DefineJournal{iisor}{0315-5986}
{INFOR Inf. Syst. Oper. Res.}
{INFOR. Information Systems and Operational Research}
\DefineJournal{ic}{0890-5401}
{Inform. and Comput.}
{Information and Computation}
\DefineJournal{ib}{?ib}
{Inform. Bull.}
{Information Bulletin}
\DefineJournal{ipl}{0020-0190}
{Inform. Process. Lett.}
{Information Processing Letters}
\DefineJournal{isaij}{0020-0255}
{Inform. Sci.}
{Information Sciences. An International Journal}
\DefineJournal{iaijci}{0350-5596}
{Informatica (Ljubl.)}
{Informatica. An International Journal of Computing and Informatics}
\DefineJournal{i}{0868-4952}
{Informatica (Vilnius)}
{Informatica (Vilnius)}
\DefineJournal{i}{?i}
{Informationselektronik}
{Informationselektronik}
\DefineJournal{id}{?id}
{Informationstech. Datenverarb.}
{Informationstechnik und Datenverarbeitung}
\DefineJournal{ijc}{1091-9856}
{INFORMS J. Comput.}
{INFORMS Journal on Computing}
\DefineJournal{isfs}{2363-6149}
{Infosys Sci. Found. Ser.}
{Infosys Science Foundation Series}
\DefineJournal{isfsms}{2364-4036}
{Infosys Sci. Found. Ser. Math. Sci.}
{Infosys Science Foundation Series in Mathematical Sciences}
\DefineJournal{iig}{1781-6475}
{Innov. Incidence Geom.}
{Innovations in Incidence Geometry}
\DefineJournal{iawts}{?iawts}
{Inst. Angew. Wirtschaftsforsch. Tubingen Schriftenreihe}
{Institut fur Angewandte Wirtschaftsforschung Tubingen Schriftenreihe}
\DefineJournal{imsln}{?imsln}
{Inst. Math. Sci. Lect. Notes}
{Institute of Mathematical Sciences Lecture Notes}
\DefineJournal{imsc}{1939-4039}
{Inst. Math. Stat. (IMS) Collect.}
{Institute of Mathematical Statistics (IMS) Collections}
\DefineJournal{imsm}{?imsm}
{Inst. Math. Stat. Monogr.}
{Institute of Mathematical Statistics (IMS) Monographs}
\DefineJournal{ime}{0167-6687}
{Insurance Math. Econom.}
{Insurance: Mathematics & Economics}
\DefineJournal{ieja}{1306-6048}
{Int. Electron. J. Algebra}
{International Electronic Journal of Algebra}
\DefineJournal{iejg}{1307-5624}
{Int. Electron. J. Geom.}
{International Electronic Journal of Geometry}
\DefineJournal{iejpam}{1314-0744}
{Int. Electron. J. Pure Appl. Math.}
{International Electronic Journal of Pure and Applied Mathematics}
\DefineJournal{igtr}{0219-1989}
{Int. Game Theory Rev.}
{International Game Theory Review}
\DefineJournal{ihis}{?ihis}
{Int. Handb. Inf. Syst.}
{International Handbooks on Information Systems}
\DefineJournal{ijaamm}{2347-2529}
{Int. J. Adv. Appl. Math. Mech.}
{International Journal of Advances in Applied Mathematics and Mechanics}
\DefineJournal{ijaesam}{0975-0770}
{Int. J. Adv. Eng. Sci. Appl. Math.}
{International Journal of Advances in Engineering Sciences and Applied Mathematics}
\DefineJournal{ijacm}{2349-5103}
{Int. J. Appl. Comput. Math.}
{International Journal of Applied and Computational Mathematics}
\DefineJournal{ijaci}{1753-0563}
{Int. J. Appl. Cryptogr.}
{International Journal of Applied Cryptography. IJACT}
\DefineJournal{ijamaa}{0973-3868}
{Int. J. Appl. Math. Anal. Appl.}
{International Journal of Applied Mathematical Analysis and Applications}
\DefineJournal{ijamc}{0974-4665}
{Int. J. Appl. Math. Comput.}
{International Journal of Applied Mathematics and Computation}
\DefineJournal{ijamcs}{1641-876X}
{Int. J. Appl. Math. Comput. Sci.}
{International Journal of Applied Mathematics and Computer Science}
\DefineJournal{ijans}{1752-2862}
{Int. J. Appl. Nonlinear Sci.}
{International Journal of Applied Nonlinear Science}
\DefineJournal{ijb}{1793-5245}
{Int. J. Biomath.}
{International Journal of Biomathematics}
\DefineJournal{tijb}{1557-4679}
{Int. J. Biostat.}
{The International Journal of Biostatistics}
\DefineJournal{ijcfd}{1061-8562}
{Int. J. Comput. Fluid Dyn.}
{International Journal of Computational Fluid Dynamics}
\DefineJournal{ijcm}{0020-7160}
{Int. J. Comput. Math.}
{International Journal of Computer Mathematics}
\DefineJournal{ijcmcst}{2379-9927}
{Int. J. Comput. Math. Comput. Syst. Theory}
{International Journal of Computer Mathematics. Computer Systems Theory}
\DefineJournal{ijcm}{0219-8762}
{Int. J. Comput. Methods}
{International Journal of Computational Methods}
\DefineJournal{ijcmesm}{1550-2287}
{Int. J. Comput. Methods Eng. Sci. Mech.}
{International Journal for Computational Methods in Engineering Science and Mechanics}
\DefineJournal{ijcsm}{1752-5055}
{Int. J. Comput. Sci. Math.}
{International Journal of Computing Science and Mathematics}
\DefineJournal{ijcv}{0920-5691}
{Int. J. Comput. Vis.}
{International Journal of Computer Vision}
\DefineJournal{ijde}{1687-9643}
{Int. J. Differ. Equ.}
{International Journal of Differential Equations}
\DefineJournal{ijde}{0973-6069}
{Int. J. Difference Equ.}
{International Journal of Difference Equations}
\DefineJournal{ijdc}{2195-268X}
{Int. J. Dyn. Control}
{International Journal of Dynamics and Control}
\DefineJournal{ijdsde}{1752-3583}
{Int. J. Dyn. Syst. Differ. Equ.}
{International Journal of Dynamical Systems and Differential Equations}
\DefineJournal{ijet}{1742-7355}
{Int. J. Econ. Theory}
{International Journal of Economic Theory}
\DefineJournal{ijfe}{2424-7863}
{Int. J. Financ. Eng.}
{International Journal of Financial Engineering}
\DefineJournal{ijfv}{1634-0655}
{Int. J. Finite Vol.}
{International Journal on Finite Volumes}
\DefineJournal{ijfs}{1562-2479}
{Int. J. Fuzzy Syst.}
{International Journal of Fuzzy Systems}
\DefineJournal{ijgs}{0308-1079}
{Int. J. Gen. Syst.}
{International Journal of General Systems}
\DefineJournal{ijg}{2247-9880}
{Int. J. Geom.}
{International Journal of Geometry}
\DefineJournal{ijgmmp}{0219-8878}
{Int. J. Geom. Methods Mod. Phys.}
{International Journal of Geometric Methods in Modern Physics}
\DefineJournal{ijgt}{2251-7650}
{Int. J. Group Theory}
{International Journal of Group Theory}
\DefineJournal{ijig}{0219-4678}
{Int. J. Image Graph.}
{International Journal of Image and Graphics}
\DefineJournal{ijicti}{1753-7703}
{Int. J. Inf. Coding Theory}
{International Journal of Information and Coding Theory. IJICOT}
\DefineJournal{ijiss}{1708-296X}
{Int. J. Inf. Syst. Sci.}
{International Journal of Information & Systems Sciences}
\DefineJournal{ijmans}{0973-3604}
{Int. J. Math. Anal. (N.S.)}
{International Journal of Mathematics and Analysis. New Series}
\DefineJournal{ijmcs}{1814-0424}
{Int. J. Math. Comput. Sci.}
{International Journal of Mathematics and Computer Science}
\DefineJournal{ijmms}{0161-1712}
{Int. J. Math. Math. Sci.}
{International Journal of Mathematics and Mathematical Sciences}
\DefineJournal{ijmor}{1757-5850}
{Int. J. Math. Oper. Res.}
{International Journal of Mathematics in Operational Research}
\DefineJournal{ijms}{0974-7117}
{Int. J. Math. Stat.}
{International Journal of Mathematics and Statistics}
\DefineJournal{ijmpcs}{?ijmpcs}
{Int. J. Modern Phys. Conf. Ser.}
{International Journal of Modern Physics: Conference Series}
\DefineJournal{ijmf}{0301-9322}
{Int. J. Multiph. Flow}
{International Journal of Multiphase Flow}
\DefineJournal{ijns}{1749-3889}
{Int. J. Nonlinear Sci.}
{International Journal of Nonlinear Science}
\DefineJournal{ijnsns}{1565-1339}
{Int. J. Nonlinear Sci. Numer. Simul.}
{International Journal of Nonlinear Sciences and Numerical Simulation}
\DefineJournal{ijnt}{1793-0421}
{Int. J. Number Theory}
{International Journal of Number Theory}
\DefineJournal{ijnam}{1705-5105}
{Int. J. Numer. Anal. Model.}
{International Journal of Numerical Analysis and Modeling}
\DefineJournal{ijnmbe}{2040-7939}
{Int. J. Numer. Methods Biomed. Eng.}
{International Journal for Numerical Methods in Biomedical Engineering}
\DefineJournal{ijor}{1745-7645}
{Int. J. Oper. Res.}
{International Journal of Operational Research}
\DefineJournal{ijorni}{2091-1521}
{Int. J. Oper. Res. Nepal}
{International Journal of Operational Research Nepal. IJORN}
\DefineJournal{ijor}{1813-713X}
{Int. J. Oper. Res. (Taichung)}
{International Journal of Operations Research}
\DefineJournal{aijoctai}{2146-0957}
{Int. J. Optim. Control. Theor. Appl. IJOCTA}
{An International Journal of Optimization and Control. Theories & Applications. IJOCTA}
\DefineJournal{ijprai}{0218-0014}
{Int. J. Pattern Recognit. Artif. Intell.}
{International Journal of Pattern Recognition and Artificial Intelligence}
\DefineJournal{ijqi}{0219-7499}
{Int. J. Quantum Inf.}
{International Journal of Quantum Information}
\DefineJournal{ijssd}{0219-4554}
{Int. J. Struct. Stab. Dyn.}
{International Journal of Structural Stability and Dynamics}
\DefineJournal{ijtaf}{0219-0249}
{Int. J. Theor. Appl. Finance}
{International Journal of Theoretical and Applied Finance}
\DefineJournal{ijuq}{2152-5080}
{Int. J. Uncertain. Quantif.}
{International Journal for Uncertainty Quantification}
\DefineJournal{ijwmip}{0219-6913}
{Int. J. Wavelets Multiresolut. Inf. Process.}
{International Journal of Wavelets, Multiresolution and Information Processing}
\DefineJournal{imrni}{1073-7928}
{Int. Math. Res. Not. IMRN}
{International Mathematics Research Notices. IMRN}
\DefineJournal{isas}{?isas}
{Int. Ser. Actuar. Sci.}
{International Series on Actuarial Science}
\DefineJournal{isqm}{0923-6716}
{Int. Ser. Quant. Mark.}
{International Series in Quantitative Marketing}
\DefineJournal{isqm}{?isqm}
{Int. Ser. Quant. Mark.}
{International Series in Quantitative Marketing (ISQM)}
\DefineJournal{isrris}{0306-7734}
{Int. Stat. Rev.}
{International Statistical Review. Revue Internationale de Statistique}
\DefineJournal{isps}{0269-8595}
{Int. Stud. Philos. Sci.}
{International Studies in the Philosophy of Science}
\DefineJournal{itor}{0969-6016}
{Int. Trans. Oper. Res.}
{International Transactions in Operational Research}
\DefineJournal{iejcnt}{1553-1732}
{Integers}
{Integers. Electronic Journal of Combinatorial Number Theory}
\DefineJournal{isis}{1571-0270}
{Integr. Ser. Inf. Syst.}
{Integrated Series in Information Systems}
\DefineJournal{ieot}{0378-620X}
{Integral Equations Operator Theory}
{Integral Equations and Operator Theory}
\DefineJournal{itsfaij}{1065-2469}
{Integral Transforms Spec. Funct.}
{Integral Transforms and Special Functions. An International Journal}
\DefineJournal{iscase}{2213-8986}
{Intell. Syst. Control Autom. Sci. Eng.}
{Intelligent Systems, Control and Automation: Science and Engineering}
\DefineJournal{isrl}{1868-4394}
{Intell. Syst. Ref. Libr.}
{Intelligent Systems Reference Library}
\DefineJournal{imm}{1860-6245}
{Interact. Mech. Math.}
{Interaction of Mechanics and Mathematics}
\DefineJournal{iam}{0939-6047}
{Interdiscip. Appl. Math.}
{Interdisciplinary Applied Mathematics}
\DefineJournal{iis}{1340-9050}
{Interdiscip. Inform. Sci.}
{Interdisciplinary Information Sciences}
\DefineJournal{ims}{1793-1355}
{Interdiscip. Math. Sci.}
{Interdisciplinary Mathematical Sciences}
\DefineJournal{isem}{1615-7362}
{Interdiscip. Stud. Econ. Manag.}
{Interdisciplinary Studies in Economics and Management}
\DefineJournal{isnm}{?isnm}
{Interdiscip. Stud. Nat. Math.}
{Interdisciplinary Studies on the Nature of Mathematics}
\DefineJournal{isr}{?isr}
{Interdiscip. Systems Res.}
{Interdisciplinary Systems Research}
\DefineJournal{ifbmaca}{1463-9963}
{Interfaces Free Bound.}
{Interfaces and Free Boundaries. Mathematical Analysis, Computation and Applications}
\DefineJournal{iam}{1063-7095}
{Internat. Appl. Mech.}
{International Applied Mechanics}
\DefineJournal{ticms}{?ticms}
{Internat. Cryogenics Monogr. Ser.}
{The International Cryogenics Monograph Series}
\DefineJournal{ier}{0020-6598}
{Internat. Econom. Rev.}
{International Economic Review}
\DefineJournal{igs}{?igs}
{Internat. Geophys. Ser.}
{International Geophysics Series}
\DefineJournal{ijacsp}{0890-6327}
{Internat. J. Adapt. Control Signal Process.}
{International Journal of Adaptive Control and Signal Processing}
\DefineJournal{ijac}{0218-1967}
{Internat. J. Algebra Comput.}
{International Journal of Algebra and Computation}
\DefineJournal{ijar}{0888-613X}
{Internat. J. Approx. Reason.}
{International Journal of Approximate Reasoning}
\DefineJournal{ijbcase}{0218-1274}
{Internat. J. Bifur. Chaos Appl. Sci. Engrg.}
{International Journal of Bifurcation and Chaos in Applied Sciences and Engineering}
\DefineJournal{ijcga}{0218-1959}
{Internat. J. Comput. Geom. Appl.}
{International Journal of Computational Geometry & Applications}
\DefineJournal{ijc}{0020-7179}
{Internat. J. Control}
{International Journal of Control}
\DefineJournal{ijes}{0020-7225}
{Internat. J. Engrg. Sci.}
{International Journal of Engineering Science}
\DefineJournal{ijfcs}{0129-0541}
{Internat. J. Found. Comput. Sci.}
{International Journal of Foundations of Computer Science}
\DefineJournal{ijgt}{0020-7276}
{Internat. J. Game Theory}
{International Journal of Game Theory}
\DefineJournal{ijm}{0129-167X}
{Internat. J. Math.}
{International Journal of Mathematics}
\DefineJournal{ijmest}{0020-739X}
{Internat. J. Math. Ed. Sci. Tech.}
{International Journal of Mathematical Education in Science and Technology}
\DefineJournal{ijmpapfgc}{0217-751X}
{Internat. J. Modern Phys. A}
{International Journal of Modern Physics A. Particles and Fields. Gravitation. Cosmology}
\DefineJournal{ijmpb}{0217-9792}
{Internat. J. Modern Phys. B}
{International Journal of Modern Physics B}
\DefineJournal{ijmpccppc}{0129-1831}
{Internat. J. Modern Phys. C}
{International Journal of Modern Physics C. Computational Physics and Physical Computation}
\DefineJournal{ijmpdgac}{0218-2718}
{Internat. J. Modern Phys. D}
{International Journal of Modern Physics. D. Gravitation, Astrophysics, Cosmology}
\DefineJournal{ijnme}{0029-5981}
{Internat. J. Numer. Methods Engrg.}
{International Journal for Numerical Methods in Engineering}
\DefineJournal{ijnmf}{0271-2091}
{Internat. J. Numer. Methods Fluids}
{International Journal for Numerical Methods in Fluids}
\DefineJournal{ijnmhff}{0961-5539}
{Internat. J. Numer. Methods Heat Fluid Flow}
{International Journal of Numerical Methods for Heat & Fluid Flow}
\DefineJournal{ijrnc}{1049-8923}
{Internat. J. Robust Nonlinear Control}
{International Journal of Robust and Nonlinear Control}
\DefineJournal{ijsspasi}{0020-7721}
{Internat. J. Systems Sci.}
{International Journal of Systems Science. Principles and Applications of Systems and Integration}
\DefineJournal{ijtp}{0020-7748}
{Internat. J. Theoret. Phys.}
{International Journal of Theoretical Physics}
\DefineJournal{ijufks}{0218-4885}
{Internat. J. Uncertain. Fuzziness Knowledge-Based Systems}
{International Journal of Uncertainty, Fuzziness and Knowledge-Based Systems}
\DefineJournal{isasa}{?isasa}
{Internat. Ser. Appl. Systems Anal.}
{International Series on Applied Systems Analysis}
\DefineJournal{ismp}{?ismp}
{Internat. Ser. Monogr. Phys.}
{International Series of Monographs on Physics}
\DefineJournal{isnm}{0373-3149}
{Internat. Ser. Numer. Math.}
{International Series of Numerical Mathematics}
\DefineJournal{isorms}{0884-8289}
{Internat. Ser. Oper. Res. Management Sci.}
{International Series in Operations Research & Management Science}
\DefineJournal{ispap}{?ispap}
{Internat. Ser. Pure Appl. Phys.}
{International Series in Pure and Applied Physics}
\DefineJournal{issc}{?issc}
{Internat. Ser. Systems Control}
{International Series on Systems and Control}
\DefineJournal{isem}{?isem}
{Internat. Stud. Econom. Model.}
{International Studies in Economic Modelling}
\DefineJournal{itmt}{?itmt}
{Internat. Trends Manufacturing Tech.}
{International Trends in Manufacturing Technology}
\DefineJournal{iuccs}{?iuccs}
{Internat. Union Cryst. Cryst. Sympos.}
{International Union of Crystallography Crystallographic Symposia}
\DefineJournal{im}{1944-9488}
{Internet Math.}
{Internet Mathematics}
\DefineJournal{itatg}{?itatg}
{Invariant Theory Algebr. Transform. Groups}
{Invariant Theory and Algebraic Transformation Groups}
\DefineJournal{im}{0020-9910}
{Invent. Math.}
{Inventiones Mathematicae}
\DefineJournal{iips}{1381-4524}
{Inverse Ill-posed Probl. Ser.}
{Inverse and Ill-posed Problems Series}
\DefineJournal{ipi}{1930-8337}
{Inverse Probl. Imaging}
{Inverse Problems and Imaging}
\DefineJournal{ipse}{1741-5977}
{Inverse Probl. Sci. Eng.}
{Inverse Problems in Science and Engineering}
\DefineJournal{ipaijtpipimcid}{0266-5611}
{Inverse Problems}
{Inverse Problems. An International Journal on the Theory and Practice of Inverse Problems, Inverse Methods and Computerized Inversion of Data}
\DefineJournal{io}{0257-4306}
{Investigacion Oper.}
{Investigacion Operacional}
\DefineJournal{iajm}{1944-4176}
{Involve}
{Involve. A Journal of Mathematics}
\DefineJournal{icp}{2054-7307}
{IOP Concise Phys.}
{IOP Concise Physics}
\DefineJournal{iep}{2053-2563}
{IOP Expand. Phys.}
{IOP Expanding Physics}
\DefineJournal{isms}{?isms}
{IOP Short Meet. Ser.}
{IOP Short Meetings Series}
\DefineJournal{ijipo}{2105-1232}
{IPOL J. Image Process. Online}
{IPOL Journal. Image Processing Online}
\DefineJournal{ijfs}{1735-0654}
{Iran. J. Fuzzy Syst.}
{Iranian Journal of Fuzzy Systems}
\DefineJournal{ijmsi}{1735-4463}
{Iran. J. Math. Sci. Inform.}
{Iranian Journal of Mathematical Sciences and Informatics}
\DefineJournal{ijsttas}{1028-6276}
{Iran. J. Sci. Technol. Trans. A Sci.}
{Iranian Journal of Science and Technology. Transaction A. Science}
\DefineJournal{imsb}{0791-5578}
{Irish Math. Soc. Bull.}
{Irish Mathematical Society Bulletin}
\DefineJournal{ilmtp}{?ilmtp}
{IRMA Lect. Math. Theor. Phys.}
{IRMA Lectures in Mathematics and Theoretical Physics}
\DefineJournal{iairdhsci}{0021-1753}
{Isis}
{Isis. An International Review Devoted to the History of Science and its Cultural Influences}
\DefineJournal{icmems}{?icmems}
{Ispra Courses Materials, Engrg. Mech. Sci.}
{Ispra Courses on Materials, Engineering and Mechanical Science}
\DefineJournal{icnet}{?icnet}
{Ispra Courses Nuclear Engrg. Tech.}
{Ispra Courses on Nuclear Engineering and Technology}
\DefineJournal{icrra}{?icrra}
{Ispra Courses Reliab. Risk Anal.}
{Ispra Courses on Reliability and Risk Analysis}
\DefineJournal{ijm}{0021-2172}
{Israel J. Math.}
{Israel Journal of Mathematics}
\DefineJournal{imcp}{?imcp}
{Israel Math. Conf. Proc.}
{Israel Mathematical Conference Proceedings}
\DefineJournal{imcp}{?imcp}
{Israel Math. Conf. Proc.}
{Israel Mathematical Conference Proceedings}
\DefineJournal{ipmi}{?ipmi}
{Issled. Prikl. Mat. Inform.}
{Issledovaniya po Prikladnoi Matematike i Informatike}
\DefineJournal{ime}{1047-398X}
{Issues Math. Ed.}
{Issues in Mathematics Education}
\DefineJournal{ists}{?ists}
{Issues Subj. Teach. Ser.}
{Issues in Subject Teaching Series}
\DefineJournal{iusftjmpa}{1300-0713}
{Istanb. Univ. Sci. Fac. J. Math. Phys. Astronom.}
{Istanbul University. Science Faculty. The Journal of Mathematics, Physics and Astronomy}
\DefineJournal{ijtsa}{1300-4077}
{Istatistik}
{Istatistik. Journal of the Turkish Statistical Association}
\DefineJournal{intssmpto}{0233-6723}
{Itogi Nauki Tekh. Ser. Sovrem. Mat. Prilozh. Temat. Obz.}
{Itogi Nauki i Tekhniki. Seriya Sovremennaya Matematika i ee Prilozheniya. Tematicheskie Obzory}
\DefineJournal{inyrmm}{?inyrmm}
{Itogi Nauki. Yug Ross. Ser. Mat. Monogr.}
{Itogi Nauki. Yug Rossii. Matematicheskaya Monografiya}
\DefineJournal{itc}{?itc}
{IUCr Texts Crystallogr.}
{IUCr Texts on Crystallography}
\DefineJournal{ib}{1875-3507}
{IUTAM Bookser.}
{IUTAM Bookseries}
\DefineJournal{ismm}{?ismm}
{Iwanami Ser. Mod. Math.}
{Iwanami Series in Modern Mathematics}
\DefineJournal{ib}{?ib}
{Izdan. Bibl.}
{Izdanja Biblioteke}
\DefineJournal{iimi}{2226-3594}
{Izv. Inst. Mat. Inform.}
{Izvestiya Instituta Matematiki i Informatiki}
\DefineJournal{iigusm}{1997-7670}
{Izv. Irkutsk. Gos. Univ. Ser. Mat.}
{Izvestiya Irkutskogo Gosudarstvennogo Universiteta. Seriya Matematika}
\DefineJournal{im}{1064-5632}
{Izv. Math.}
{Izvestiya. Mathematics}
\DefineJournal{inanampnasam}{0002-3051}
{Izv. Nats. Akad. Nauk Armen. Mekh.}
{Izvestiya Natsionalnoi Akademii Nauk Armenii. Mekhanika. Proceedings of National Academy of Sciences of Armenia. Mechanics}
\DefineJournal{nanaim}{0002-3043}
{Izv. Nats. Akad. Nauk Armenii Mat.}
{Natsionalnaya Akademiya Nauk Armenii. Izvestiya. Matematika}
\DefineJournal{inanrksf}{1991-346X}
{Izv. Nats. Akad. Nauk Resp. Kaz. Ser. Fiz.-Mat.}
{Izvestiya Natsionalnoi Akademii Nauk Respubliki Kazakhstan. Seriya Fiziko-Matematicheskaya}
\DefineJournal{ranimzg}{0568-5281}
{Izv. Ross. Akad. Nauk Mekh. Zhidk. Gaza}
{Rossiiskaya Akademiya Nauk. Izvestiya. Mekhanika Zhidkosti i Gaza}
\DefineJournal{ranism}{1607-0046}
{Izv. Ross. Akad. Nauk Ser. Mat.}
{Rossiiskaya Akademiya Nauk. Izvestiya. Seriya Matematicheskaya}
\DefineJournal{irantsu}{0002-3388}
{Izv. Ross. Akad. Nauk Teor. Sist. Upr.}
{Izvestiya Rossiiskoi Akademii Nauk. Teoriya i Sistemy Upravleniya}
\DefineJournal{isunssmmi}{1816-9791}
{Izv. Sarat. Univ. (N.S.) Ser. Mat. Mekh. Inform.}
{Izvestiya Saratovskogo Universiteta. Novaya Seriya. Seriya. Matematika. Mekhanika. Informatika}
\DefineJournal{ivuzmkgu}{0021-3446}
{Izv. Vyssh. Uchebn. Zaved. Mat.}
{Izvestiya Vysshikh Uchebnykh Zavedenii. Matematika. Kazanskii Gosudarstvennyi Universitet}
\DefineJournal{jadea}{2158-611X}
{J. Abstr. Differ. Equ. Appl.}
{Journal of Abstract Differential Equations and Applications}
\DefineJournal{ja}{0004-5411}
{J. ACM}
{Journal of the ACM}
\DefineJournal{jams}{2065-3506}
{J. Adv. Math. Stud.}
{Journal of Advanced Mathematical Studies}
\DefineJournal{jast}{2090-8288}
{J. Adv. Stud. Topol.}
{Journal of Advanced Studies in Topology}
\DefineJournal{jabes}{1085-7117}
{J. Agric. Biol. Environ. Stat.}
{Journal of Agricultural, Biological, and Environmental Statistics}
\DefineJournal{jas}{1309-3452}
{J. Algebr. Stat.}
{Journal of Algebraic Statistics}
\DefineJournal{jas}{2345-5128}
{J. Algebr. Syst.}
{Journal of Algebraic Systems}
\DefineJournal{ja}{0021-8693}
{J. Algebra}
{Journal of Algebra}
\DefineJournal{jaa}{0219-4988}
{J. Algebra Appl.}
{Journal of Algebra and its Applications}
\DefineJournal{jacdsa}{2148-838X}
{J. Algebra Comb. Discrete Struct. Appl.}
{Journal of Algebra Combinatorics Discrete Structures and Applications}
\DefineJournal{jaca}{2217-6764}
{J. Algebra Comput. Appl.}
{Journal of Algebra and Computational Applications}
\DefineJournal{jart}{2345-3931}
{J. Algebra Relat. Topics}
{Journal of Algebra and Related Topics}
\DefineJournal{jacaij}{0925-9899}
{J. Algebraic Combin.}
{Journal of Algebraic Combinatorics. An International Journal}
\DefineJournal{jag}{1056-3911}
{J. Algebraic Geom.}
{Journal of Algebraic Geometry}
\DefineJournal{jact}{1748-3018}
{J. Algorithms Comput. Technol.}
{Journal of Algorithms & Computational Technology}
\DefineJournal{jams}{0894-0347}
{J. Amer. Math. Soc.}
{Journal of the American Mathematical Society}
\DefineJournal{jasa}{0162-1459}
{J. Amer. Statist. Assoc.}
{Journal of the American Statistical Association}
\DefineJournal{tja}{0971-3611}
{J. Anal.}
{The Journal of Analysis}
\DefineJournal{jaa}{0972-5954}
{J. Anal. Appl.}
{Journal of Analysis and Applications}
\DefineJournal{jm}{0021-7670}
{J. Anal. Math.}
{Journal d'Analyse Mathematique}
\DefineJournal{jaunseadxzkb}{1000-2162}
{J. Anhui Univ. Nat. Sci.}
{Journal of Anhui University. Natural Science Edition. Anhui Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jaa}{1425-6908}
{J. Appl. Anal.}
{Journal of Applied Analysis}
\DefineJournal{tjaac}{2156-907X}
{J. Appl. Anal. Comput.}
{The Journal of Applied Analysis and Computation}
\DefineJournal{jact}{2367-1726}
{J. Appl. Comput. Topol.}
{Journal of Applied and Computational Topology}
\DefineJournal{jae}{0883-7252}
{J. Appl. Econometrics}
{Journal of Applied Econometrics}
\DefineJournal{jafa}{1559-1948}
{J. Appl. Funct. Anal.}
{Journal of Applied Functional Analysis}
\DefineJournal{jaim}{1990-4789}
{J. Appl. Ind. Math.}
{Journal of Applied and Industrial Mathematics}
\DefineJournal{jam}{1110-757X}
{J. Appl. Math.}
{Journal of Applied Mathematics}
\DefineJournal{jamaa}{0973-3884}
{J. Appl. Math. Anal. Appl.}
{Journal of Applied Mathematical Analysis and Applications}
\DefineJournal{jamc}{1598-5865}
{J. Appl. Math. Comput.}
{Journal of Applied Mathematics and Computing}
\DefineJournal{jamcm}{2299-9965}
{J. Appl. Math. Comput. Mech.}
{Journal of Applied Mathematics and Computational Mechanics}
\DefineJournal{jami}{1598-5857}
{J. Appl. Math. Inform.}
{Journal of Applied Mathematics & Informatics}
\DefineJournal{jamm}{0021-8928}
{J. Appl. Math. Mech.}
{Journal of Applied Mathematics and Mechanics}
\DefineJournal{jamsi}{1336-9180}
{J. Appl. Math. Stat. Inform.}
{Journal of Applied Mathematics, Statistics and Informatics}
\DefineJournal{jamtp}{0021-8944}
{J. Appl. Mech. Tech. Phys.}
{Journal of Applied Mechanics and Technical Physics}
\DefineJournal{janl}{1166-3081}
{J. Appl. Non-Class. Log.}
{Journal of Applied Non-Classical Logics}
\DefineJournal{jand}{2164-6457}
{J. Appl. Nonlinear Dyn.}
{Journal of Applied Nonlinear Dynamics}
\DefineJournal{jap}{0021-9002}
{J. Appl. Probab.}
{Journal of Applied Probability}
\DefineJournal{jas}{0266-4763}
{J. Appl. Stat.}
{Journal of Applied Statistics}
\DefineJournal{jat}{0021-9045}
{J. Approx. Theory}
{Journal of Approximation Theory}
\DefineJournal{jair}{1076-9757}
{J. Artificial Intelligence Res.}
{Journal of Artificial Intelligence Research}
\DefineJournal{jaam}{2229-3884}
{J. Assam Acad. Math.}
{Journal of the Assam Academy of Mathematics (JAAM)}
\DefineJournal{jams}{1446-7887}
{J. Aust. Math. Soc.}
{Journal of the Australian Mathematical Society}
\DefineJournal{jalc}{1430-189X}
{J. Autom. Lang. Comb.}
{Journal of Automata, Languages and Combinatorics}
\DefineJournal{jar}{0168-7433}
{J. Automat. Reason.}
{Journal of Automated Reasoning}
\DefineJournal{}{?}
{J. Beijing Normal Univ. (Natur. Sci.)}
{nan}
\DefineJournal{jbutbgdx}{0254-0037}
{J. Beijing Univ. Technol.}
{Journal of Beijing University of Technology. Beijing Gongye Daxue Xuebao}
\DefineJournal{bmsj}{0972-8716}
{J. Bihar Math. Soc.}
{Bihar Mathematical Society. Journal}
\DefineJournal{jbd}{1751-3758}
{J. Biol. Dyn.}
{Journal of Biological Dynamics}
\DefineJournal{jbs}{0218-3390}
{J. Biol. Systems}
{Journal of Biological Systems}
\DefineJournal{jbssx}{1001-9626}
{J. Biomath.}
{Journal of Biomathematics. Shengwu Shuxue Xuebao}
\DefineJournal{jbes}{0735-0015}
{J. Bus. Econom. Statist.}
{Journal of Business & Economic Statistics}
\DefineJournal{jca}{1557-5969}
{J. Cell. Autom.}
{Journal of Cellular Automata}
\DefineJournal{jccnuns}{1000-1190}
{J. Cent. China Norm. Univ. Nat. Sci.}
{Journal of Central China Normal University. Natural Sciences}
\DefineJournal{jcms}{1226-3524}
{J. Chungcheong Math. Soc.}
{Journal of the Chungcheong Mathematical Society}
\DefineJournal{jca}{1848-5979}
{J. Class. Anal.}
{Journal of Classical Analysis}
\DefineJournal{jc}{0176-4268}
{J. Classification}
{Journal of Classification}
\DefineJournal{jc}{2156-3527}
{J. Comb.}
{Journal of Combinatorics}
\DefineJournal{jca}{2415-6302}
{J. Comb. Algebra}
{Journal of Combinatorial Algebra}
\DefineJournal{jciss}{0250-9628}
{J. Comb. Inf. Syst. Sci.}
{Journal of Combinatorics, Information & System Sciences}
\DefineJournal{jcnt}{1942-5600}
{J. Comb. Number Theory}
{Journal of Combinatorics and Number Theory}
\DefineJournal{jco}{1382-6905}
{J. Comb. Optim.}
{Journal of Combinatorial Optimization}
\DefineJournal{jcd}{1063-8539}
{J. Combin. Des.}
{Journal of Combinatorial Designs}
\DefineJournal{jcmcc}{0835-3026}
{J. Combin. Math. Combin. Comput.}
{Journal of Combinatorial Mathematics and Combinatorial Computing}
\DefineJournal{jctsa}{0097-3165}
{J. Combin. Theory Ser. A}
{Journal of Combinatorial Theory. Series A}
\DefineJournal{jctsb}{0095-8956}
{J. Combin. Theory Ser. B}
{Journal of Combinatorial Theory. Series B}
\DefineJournal{jca}{1939-0807}
{J. Commut. Algebra}
{Journal of Commutative Algebra}
\DefineJournal{jcn}{2051-1310}
{J. Complex Netw.}
{Journal of Complex Networks}
\DefineJournal{jc}{0885-064X}
{J. Complexity}
{Journal of Complexity}
\DefineJournal{jcaa}{1521-1398}
{J. Comput. Anal. Appl.}
{Journal of Computational Analysis and Applications}
\DefineJournal{jcam}{0377-0427}
{J. Comput. Appl. Math.}
{Journal of Computational and Applied Mathematics}
\DefineJournal{jcb}{1066-5277}
{J. Comput. Biol.}
{Journal of Computational Biology}
\DefineJournal{jcd}{2158-2491}
{J. Comput. Dyn.}
{Journal of Computational Dynamics}
\DefineJournal{jcem}{2313-8106}
{J. Comput. Eng. Math.}
{Journal of Computational and Engineering Mathematics}
\DefineJournal{jcf}{1460-1559}
{J. Comput. Finance}
{Journal of Computational Finance}
\DefineJournal{jcg}{1920-180X}
{J. Comput. Geom.}
{Journal of Computational Geometry}
\DefineJournal{jcgs}{1061-8600}
{J. Comput. Graph. Statist.}
{Journal of Computational and Graphical Statistics}
\DefineJournal{jcm}{0254-9409}
{J. Comput. Math.}
{Journal of Computational Mathematics}
\DefineJournal{jcmf}{1757-482X}
{J. Comput. Multiph. Flows}
{Journal of Computational Multiphase Flows}
\DefineJournal{jcn}{0929-5313}
{J. Comput. Neurosci.}
{Journal of Computational Neuroscience}
\DefineJournal{jcp}{0021-9991}
{J. Comput. Phys.}
{Journal of Computational Physics}
\DefineJournal{jcs}{1877-7503}
{J. Comput. Sci.}
{Journal of Computational Science}
\DefineJournal{jcsam}{1857-9582}
{J. Comput. Sci. Appl. Math.}
{Journal of Computer Science and Applied Mathematics}
\DefineJournal{jcst}{1000-9000}
{J. Comput. Sci. Tech.}
{Journal of Computer Science and Technology}
\DefineJournal{jcssi}{1064-2307}
{J. Comput. Syst. Sci. Int.}
{Journal of Computer and Systems Sciences International}
\DefineJournal{jcss}{0022-0000}
{J. Comput. System Sci.}
{Journal of Computer and System Sciences}
\DefineJournal{jctt}{2332-4309}
{J. Comput. Theor. Transp.}
{Journal of Computational and Theoretical Transport}
\DefineJournal{jcam}{1548-5390}
{J. Concr. Appl. Math.}
{Journal of Concrete and Applicable Mathematics}
\DefineJournal{jcma}{1068-3623}
{J. Contemp. Math. Anal.}
{Journal of Contemporary Mathematical Analysis}
\DefineJournal{jcd}{2330-7706}
{J. Control Decis.}
{Journal of Control and Decision}
\DefineJournal{jcse}{1687-5249}
{J. Control Sci. Eng.}
{Journal of Control Science and Engineering}
\DefineJournal{jca}{0944-6532}
{J. Convex Anal.}
{Journal of Convex Analysis}
\DefineJournal{jcap}{1475-7516}
{J. Cosmol. Astropart. Phys.}
{Journal of Cosmology and Astroparticle Physics}
\DefineJournal{jctjiacr}{0933-2790}
{J. Cryptology}
{Journal of Cryptology. The Journal of the International Association for Cryptologic Research}
\DefineJournal{jdutdldx}{1000-8608}
{J. Dalian Univ. Technol.}
{Journal of Dalian University of Technology. Dalian Ligon Daxue Xuebao}
\DefineJournal{jdea}{1023-6198}
{J. Difference Equ. Appl.}
{Journal of Difference Equations and Applications}
\DefineJournal{jde}{0022-0396}
{J. Differential Equations}
{Journal of Differential Equations}
\DefineJournal{jdg}{0022-040X}
{J. Differential Geom.}
{Journal of Differential Geometry}
\DefineJournal{jda}{1570-8667}
{J. Discrete Algorithms}
{Journal of Discrete Algorithms}
\DefineJournal{jdmsc}{0972-0529}
{J. Discrete Math. Sci. Cryptogr.}
{Journal of Discrete Mathematical Sciences and Cryptography}
\DefineJournal{jdcs}{1079-2724}
{J. Dyn. Control Syst.}
{Journal of Dynamical and Control Systems}
\DefineJournal{jdg}{2164-6066}
{J. Dyn. Games}
{Journal of Dynamics and Games}
\DefineJournal{jdsgt}{1726-037X}
{J. Dyn. Syst. Geom. Theor.}
{Journal of Dynamical Systems and Geometric Theories}
\DefineJournal{jdde}{1040-7294}
{J. Dynam. Differential Equations}
{Journal of Dynamics and Differential Equations}
\DefineJournal{jecnunsehsdxzkb}{1000-5641}
{J. East China Norm. Univ. Natur. Sci. Ed.}
{Journal of East China Normal University. Natural Science Edition. Huadong Shifan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jm}{2429-7100}
{J. Ec. polytech. Math.}
{Journal de l'Ecole polytechnique. Mathematiques}
\DefineJournal{jedc}{0165-1889}
{J. Econom. Dynam. Control}
{Journal of Economic Dynamics & Control}
\DefineJournal{jem}{2194-6345}
{J. Econom. Methods}
{Journal of Econometric Methods}
\DefineJournal{jet}{0022-0531}
{J. Econom. Theory}
{Journal of Economic Theory}
\DefineJournal{je}{0304-4076}
{J. Econometrics}
{Journal of Econometrics}
\DefineJournal{jetpmss}{0374-3535}
{J. Elasticity}
{Journal of Elasticity. The Physical and Mathematical Science of Solids}
\DefineJournal{jece}{2090-0147}
{J. Electr. Comput. Eng.}
{Journal of Electrical and Computer Engineering}
\DefineJournal{jepe}{2296-9020}
{J. Elliptic Parabol. Equ.}
{Journal of Elliptic and Parabolic Equations}
\DefineJournal{jem}{0022-0833}
{J. Engrg. Math.}
{Journal of Engineering Mathematics}
\DefineJournal{jems}{1435-9855}
{J. Eur. Math. Soc. (JEMS)}
{Journal of the European Mathematical Society (JEMS)}
\DefineJournal{jee}{1424-3199}
{J. Evol. Equ.}
{Journal of Evolution Equations}
\DefineJournal{jfssu}{0583-063X}
{J. Fac. Sci. Shinshu Univ.}
{Journal of the Faculty of Science. Shinshu University}
\DefineJournal{jfpta}{1661-7738}
{J. Fixed Point Theory Appl.}
{Journal of Fixed Point Theory and Applications}
\DefineJournal{jfm}{0022-1120}
{J. Fluid Mech.}
{Journal of Fluid Mechanics}
\DefineJournal{jf}{0277-6693}
{J. Forecast.}
{Journal of Forecasting}
\DefineJournal{jfr}{1972-5787}
{J. Formaliz. Reason.}
{Journal of Formalized Reasoning}
\DefineJournal{tjfaa}{1069-5869}
{J. Fourier Anal. Appl.}
{The Journal of Fourier Analysis and Applications}
\DefineJournal{jfca}{2090-584X}
{J. Fract. Calc. Appl.}
{Journal of Fractional Calculus and Applications}
\DefineJournal{jfgmfrt}{2308-1309}
{J. Fractal Geom.}
{Journal of Fractal Geometry. Mathematics of Fractals and Related Topics}
\DefineJournal{jfieam}{0016-0032}
{J. Franklin Inst.}
{Journal of the Franklin Institute. Engineering and Applied Mathematics}
\DefineJournal{fujnsfxzkb}{0427-7104}
{J. Fudan Univ. Nat. Sci.}
{Fudan University. Journal. Natural Science. Fudan Xuebao. Ziran Kexue Ban}
\DefineJournal{jfa}{0022-1236}
{J. Funct. Anal.}
{Journal of Functional Analysis}
\DefineJournal{jfp}{0956-7968}
{J. Funct. Programming}
{Journal of Functional Programming}
\DefineJournal{jfs}{2314-8896}
{J. Funct. Spaces}
{Journal of Function Spaces}
\DefineJournal{jfunsefdxzkb}{1000-2243}
{J. Fuzhou Univ. Nat. Sci. Ed.}
{Journal of Fuzhou University. Natural Science Edition. Fuzhou Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jgpszaw}{0925-4560}
{J. Gen. Philos. Sci.}
{Journal for General Philosophy of Science. Zeitschrift fur Allgemeine Wissenschaftstheorie}
\DefineJournal{jg}{0047-2468}
{J. Geom.}
{Journal of Geometry}
\DefineJournal{jga}{1050-6926}
{J. Geom. Anal.}
{Journal of Geometric Analysis}
\DefineJournal{jgg}{1433-8157}
{J. Geom. Graph.}
{Journal for Geometry and Graphics}
\DefineJournal{jgm}{1941-4889}
{J. Geom. Mech.}
{Journal of Geometric Mechanics}
\DefineJournal{jgp}{0393-0440}
{J. Geom. Phys.}
{Journal of Geometry and Physics}
\DefineJournal{jgsp}{1312-5192}
{J. Geom. Symmetry Phys.}
{Journal of Geometry and Symmetry in Physics}
\DefineJournal{jgoaijdtcasgotasme}{0925-5001}
{J. Global Optim.}
{Journal of Global Optimization. An International Journal Dealing with Theoretical and Computational Aspects of Seeking Global Optima and Their Applications in Science, Management and Engineering}
\DefineJournal{jggtg}{1935-2565}
{J. Gokova Geom. Topol. GGT}
{Journal of Gokova Geometry Topology. GGT}
\DefineJournal{jgaa}{1526-1719}
{J. Graph Algorithms Appl.}
{Journal of Graph Algorithms and Applications}
\DefineJournal{jglagtrj}{2454-4515}
{J. Graph Label.}
{Journal of Graph Labeling. A Graph Theoretical Research Journal}
\DefineJournal{jgt}{0364-9024}
{J. Graph Theory}
{Journal of Graph Theory}
\DefineJournal{jgt}{1433-5883}
{J. Group Theory}
{Journal of Group Theory}
\DefineJournal{jhithgdx}{0367-6234}
{J. Harbin Inst. Tech.}
{Journal of Harbin Institute of Technology. Harbin Gongye Daxue Xuebao}
\DefineJournal{jhutnshgdxzkb}{1003-5060}
{J. Hefei Univ. Technol. Nat. Sci.}
{Journal of Hefei University of Technology. Natural Science. Hefei Gongye Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jhep}{1126-6708}
{J. High Energy Phys.}
{Journal of High Energy Physics}
\DefineJournal{jhrs}{2193-8407}
{J. Homotopy Relat. Struct.}
{Journal of Homotopy and Related Structures}
\DefineJournal{jhustnsehkdxzkb}{1671-4512}
{J. Huazhong Univ. Sci. Technol. Nat. Sci.}
{Journal of Huazhong University of Science and Technology. Natural Science Edition. Huazhong Keji Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jhm}{2159-8118}
{J. Humanist. Math.}
{Journal of Humanistic Mathematics}
\DefineJournal{jhunshdxzkb}{1674-2974}
{J. Hunan Univ. Nat. Sci.}
{Journal of Hunan University. Natural Sciences. Hunan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jhde}{0219-8916}
{J. Hyperbolic Differ. Equ.}
{Journal of Hyperbolic Differential Equations}
\DefineJournal{jh}{2251-8436}
{J. Hyperstruct.}
{Journal of Hyperstructures}
\DefineJournal{jimo}{1547-5816}
{J. Ind. Manag. Optim.}
{Journal of Industrial and Management Optimization}
\DefineJournal{tjimc}{?tjimc}
{J. Indian Math. Club}
{The Journal of the Indian Mathematical Club}
\DefineJournal{tjimsns}{0019-5839}
{J. Indian Math. Soc. (N.S.)}
{The Journal of the Indian Mathematical Society. New Series}
\DefineJournal{jisas}{0019-6363}
{J. Indian Soc. Agricultural Statist.}
{Journal of the Indian Society of Agricultural Statistics}
\DefineJournal{jisa}{0537-2585}
{J. Indian Statist. Assoc.}
{Journal of the Indian Statistical Association}
\DefineJournal{jims}{2086-8952}
{J. Indones. Math. Soc.}
{Journal of the Indonesian Mathematical Society}
\DefineJournal{jia}{1029-242X}
{J. Inequal. Appl.}
{Journal of Inequalities and Applications}
\DefineJournal{jisf}{2217-4303}
{J. Inequal. Spec. Funct.}
{Journal of Inequalities and Special Functions}
\DefineJournal{jios}{0252-2667}
{J. Inf. Optim. Sci.}
{Journal of Information and Optimization Sciences}
\DefineJournal{jimnunmsdxzkhb}{1001-8735}
{J. Inn. Mong. Norm. Univ. Nat. Sci.}
{Journal of Inner Mongolia Normal University. Nei Mongol Shifan Daxue Xuebao. Ziran Kexue. Hanwen Ban}
\DefineJournal{jimunse}{1000-1638}
{J. Inn. Mong. Univ. Nat. Sci.}
{Journal of Inner Mongolia University. Natural Science Edition}
\DefineJournal{imcsjss}{?imcsjss}
{J. Inst. Math. Comput. Sci. Comput. Sci. Ser.}
{Institute of Mathematics & Computer Sciences. Journal. (Computer Science Series)}
\DefineJournal{jimjjjmj}{1474-7480}
{J. Inst. Math. Jussieu}
{Journal of the Institute of Mathematics of Jussieu. JIMJ. Journal de l'Institut de Mathematiques de Jussieu}
\DefineJournal{jiaps}{0974-9373}
{J. Int. Acad. Phys. Sci.}
{Journal of International Academy of Physical Sciences}
\DefineJournal{jimvi}{2303-4866}
{J. Int. Math. Virtual Inst.}
{Journal of International Mathematical Virtual Institute}
\DefineJournal{jis}{1530-7638}
{J. Integer Seq.}
{Journal of Integer Sequences}
\DefineJournal{jis}{2058-5985}
{J. Integrable Syst.}
{Journal of Integrable Systems}
\DefineJournal{jiea}{0897-3962}
{J. Integral Equations Appl.}
{Journal of Integral Equations and Applications}
\DefineJournal{jiasc}{2194-3907}
{J. Interpolat. Approx. Sci. Comput.}
{Journal of Interpolation and Approximation in Scientific Computing}
\DefineJournal{jiip}{0928-0219}
{J. Inverse Ill-Posed Probl.}
{Journal of Inverse and Ill-Posed Problems}
\DefineJournal{jiss}{1726-4057}
{J. Iran. Stat. Soc. (JIRSS)}
{Journal of the Iranian Statistical Society. (JIRSS)}
\DefineJournal{jjsstgk}{1882-2754}
{J. Japan Statist. Soc.}
{Journal of the Japan Statistical Society (Nihon Tokei Gakkai Kaiho)}
\DefineJournal{jjscs}{0915-2350}
{J. Japanese Soc. Comput. Statist.}
{Journal of the Japanese Society of Computational Statistics}
\DefineJournal{jjusejdxlb}{1671-5489}
{J. Jilin Univ. Sci.}
{Journal of Jilin University. Science Edition. Jilin Daxue Xuebao. Lixue Ban}
\DefineJournal{jjunsmejdxzkyb}{1000-9965}
{J. Jinan Univ. Nat. Sci. Med.}
{Journal of Jinan University. Natural Science & Medicine Edition. Jinan Daxue Xuebao. Ziran Kexue yu Yixue Ban}
\DefineJournal{jjssji}{0389-5602}
{J. Jpn. Stat. Soc. Jpn. Issue}
{Journal of the Japan Statistical Society. Japanese Issue}
\DefineJournal{jktr}{0218-2165}
{J. Knot Theory Ramifications}
{Journal of Knot Theory and its Ramifications}
\DefineJournal{jkms}{0304-9914}
{J. Korean Math. Soc.}
{Journal of the Korean Mathematical Society}
\DefineJournal{jksiam}{1226-9433}
{J. Korean Soc. Ind. Appl. Math.}
{Journal of the Korean Society for Industrial and Applied Mathematics}
\DefineJournal{jksmesbtpam}{1226-0657}
{J. Korean Soc. Math. Educ. Ser. B Pure Appl. Math.}
{Journal of the Korean Society of Mathematical Education. Series B. The Pure and Applied Mathematics}
\DefineJournal{jkss}{1226-3192}
{J. Korean Statist. Soc.}
{Journal of the Korean Statistical Society}
\DefineJournal{jlt}{0949-5932}
{J. Lie Theory}
{Journal of Lie Theory}
\DefineJournal{jlta}{2252-0201}
{J. Linear Topol. Algebra}
{Journal of Linear and Topological Algebra}
\DefineJournal{jlamp}{2352-2208}
{J. Log. Algebr. Methods Program.}
{Journal of Logical and Algebraic Methods in Programming}
\DefineJournal{jla}{1759-9008}
{J. Log. Anal.}
{Journal of Logic and Analysis}
\DefineJournal{jlli}{0925-8531}
{J. Log. Lang. Inf.}
{Journal of Logic, Language and Information}
\DefineJournal{jlc}{0955-792X}
{J. Logic Comput.}
{Journal of Logic and Computation}
\DefineJournal{jlmsss}{0024-6107}
{J. Lond. Math. Soc. (2)}
{Journal of the London Mathematical Society. Second Series}
\DefineJournal{jmlr}{1532-4435}
{J. Mach. Learn. Res.}
{Journal of Machine Learning Research (JMLR)}
\DefineJournal{jm}{2314-4629}
{J. Math.}
{Journal of Mathematics}
\DefineJournal{jma}{2217-3412}
{J. Math. Anal.}
{Journal of Mathematical Analysis}
\DefineJournal{jmaa}{0022-247X}
{J. Math. Anal. Appl.}
{Journal of Mathematical Analysis and Applications}
\DefineJournal{jma}{1733-6775}
{J. Math. Appl.}
{Journal of Mathematics and Applications}
\DefineJournal{jma}{1751-3472}
{J. Math. Arts}
{Journal of Mathematics and the Arts}
\DefineJournal{jmb}{0303-6812}
{J. Math. Biol.}
{Journal of Mathematical Biology}
\DefineJournal{jmc}{0259-9791}
{J. Math. Chem.}
{Journal of Mathematical Chemistry}
\DefineJournal{jmc}{1862-2976}
{J. Math. Cryptol.}
{Journal of Mathematical Cryptology}
\DefineJournal{jme}{0304-4068}
{J. Math. Econom.}
{Journal of Mathematical Economics}
\DefineJournal{jmfm}{1422-6928}
{J. Math. Fluid Mech.}
{Journal of Mathematical Fluid Mechanics}
\DefineJournal{jmfs}{2337-5760}
{J. Math. Fundam. Sci.}
{Journal of Mathematical and Fundamental Sciences}
\DefineJournal{jmiv}{0924-9907}
{J. Math. Imaging Vision}
{Journal of Mathematical Imaging and Vision}
\DefineJournal{jmi}{2190-5983}
{J. Math. Ind.}
{Journal of Mathematics in Industry}
\DefineJournal{jmi}{1846-579X}
{J. Math. Inequal.}
{Journal of Mathematical Inequalities}
\DefineJournal{jml}{0219-0613}
{J. Math. Log.}
{Journal of Mathematical Logic}
\DefineJournal{jmm}{2345-394X}
{J. Math. Model.}
{Journal of Mathematical Modeling}
\DefineJournal{jmmmcamtacp}{1745-9737}
{J. Math. Music}
{Journal of Mathematics & Music. Mathematical and Computational Approaches to Music Theory, Analysis, Composition and Performance}
\DefineJournal{jmn}{2190-8567}
{J. Math. Neurosci.}
{Journal of Mathematical Neuroscience}
\DefineJournal{jmp}{0022-2488}
{J. Math. Phys.}
{Journal of Mathematical Physics}
\DefineJournal{jmp}{0022-2496}
{J. Math. Psych.}
{Journal of Mathematical Psychology}
\DefineJournal{jmpans}{0021-7824}
{J. Math. Pures Appl. (9)}
{Journal de Mathematiques Pures et Appliquees. Neuvieme Serie}
\DefineJournal{jmra}{2095-2651}
{J. Math. Res. Appl.}
{Journal of Mathematical Research with Applications}
\DefineJournal{jmsaa}{0974-5750}
{J. Math. Sci. Adv. Appl.}
{Journal of Mathematical Sciences. Advances and Applications}
\DefineJournal{jms}{0974-5548}
{J. Math. Sci. (Dattapukur)}
{Journal of Mathematical Sciences (Dattapukur)}
\DefineJournal{jmsy}{1072-3374}
{J. Math. Sci. (N.Y.)}
{Journal of Mathematical Sciences (New York)}
\DefineJournal{tutjms}{1340-5705}
{J. Math. Sci. Univ. Tokyo}
{The University of Tokyo. Journal of Mathematical Sciences}
\DefineJournal{jmsj}{0025-5645}
{J. Math. Soc. Japan}
{Journal of the Mathematical Society of Japan}
\DefineJournal{jms}{0022-250X}
{J. Math. Sociol.}
{Journal of Mathematical Sociology}
\DefineJournal{jmssy}{1006-6837}
{J. Math. Study}
{Journal of Mathematical Study. Shuxue Yanjiu}
\DefineJournal{jmtu}{1346-7387}
{J. Math. Tokushima Univ.}
{Journal of Mathematics. Tokushima University}
\DefineJournal{jmms}{1559-3959}
{J. Mech. Mater. Struct.}
{Journal of Mechanics of Materials and Structures}
\DefineJournal{jmps}{0022-5096}
{J. Mech. Phys. Solids}
{Journal of the Mechanics and Physics of Solids}
\DefineJournal{jmd}{1930-5311}
{J. Mod. Dyn.}
{Journal of Modern Dynamics}
\DefineJournal{jmms}{1994-5388}
{J. Mod. Math. Stat.}
{Journal of Modern Mathematics and Statistics}
\DefineJournal{jmmnm}{2090-4770}
{J. Mod. Methods Numer. Math.}
{Journal of Modern Methods in Numerical Mathematics}
\DefineJournal{jmo}{0950-0340}
{J. Modern Opt.}
{Journal of Modern Optics}
\DefineJournal{jmlsc}{1542-3980}
{J. Mult.-Valued Logic Soft Comput.}
{Journal of Multiple-Valued Logic and Soft Computing}
\DefineJournal{jmm}{1756-9737}
{J. Multiscale Model.}
{Journal of Multiscale Modelling}
\DefineJournal{jma}{0047-259X}
{J. Multivariate Anal.}
{Journal of Multivariate Analysis}
\DefineJournal{jnnunsensxzkb}{1001-4616}
{J. Nanjing Norm. Univ. Nat. Sci. Ed.}
{Journal of Nanjing Normal University. Natural Science Edition. Nanjing Shida Xuebao. Ziran Kexue Ban}
\DefineJournal{jnuns}{0469-5097}
{J. Nanjing Univ. Nat. Sci.}
{Journal of Nanjing University. Natural Sciences}
\DefineJournal{jnshnuhsdzkx}{2096-5281}
{J. Nat. Sci. Hunan Norm. Univ.}
{Journal of Natural Science of Hunan Normal University. Hunan Shifan Daxue Ziran Kexue Xuebao}
\DefineJournal{jnsnnu}{1001-4616}
{J. Nat. Sci. Nanjing Norm. Univ.}
{Journal of Natural Science. Nanjing Normal University}
\DefineJournal{jnms}{0189-8965}
{J. Nigerian Math. Soc.}
{Journal of the Nigerian Mathematical Society}
\DefineJournal{jnfm}{0377-0257}
{J. Non-Newton. Fluid Mech.}
{Journal of Non-Newtonian Fluid Mechanics}
\DefineJournal{jng}{1661-6952}
{J. Noncommut. Geom.}
{Journal of Noncommutative Geometry}
\DefineJournal{jnaota}{1906-9685}
{J. Nonlinear Anal. Optim.}
{Journal of Nonlinear Analysis and Optimization. Theory and Applications}
\DefineJournal{jncaaij}{1345-4773}
{J. Nonlinear Convex Anal.}
{Journal of Nonlinear and Convex Analysis. An International Journal}
\DefineJournal{jneea}{2161-3680}
{J. Nonlinear Evol. Equ. Appl.}
{Journal of Nonlinear Evolution Equations and Applications}
\DefineJournal{jnmp}{1402-9251}
{J. Nonlinear Math. Phys.}
{Journal of Nonlinear Mathematical Physics}
\DefineJournal{jns}{0938-8974}
{J. Nonlinear Sci.}
{Journal of Nonlinear Science}
\DefineJournal{jnsaj}{2008-1898}
{J. Nonlinear Sci. Appl.}
{Journal of Nonlinear Sciences and Applications. JNSA}
\DefineJournal{jnsa}{1918-3704}
{J. Nonlinear Syst. Appl.}
{Journal of Nonlinear Systems and Applications}
\DefineJournal{jns}{1048-5252}
{J. Nonparametr. Stat.}
{Journal of Nonparametric Statistics}
\DefineJournal{jnunsddxzkb}{1005-3026}
{J. Northeast. Univ. Nat. Sci.}
{Journal of Northeastern University. Natural Science. Dongbei Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jnunsexdxzkb}{1000-274X}
{J. Northwest Univ. Nat. Sci.}
{Journal of Northwest University. Natural Science Edition. Xibei Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jnt}{0022-314X}
{J. Number Theory}
{Journal of Number Theory}
\DefineJournal{jnaat}{2457-6794}
{J. Numer. Anal. Approx. Theory}
{Journal of Numerical Analysis and Approximation Theory}
\DefineJournal{jnm}{1570-2820}
{J. Numer. Math.}
{Journal of Numerical Mathematics}
\DefineJournal{jnms}{2151-2302}
{J. Numer. Math. Stoch.}
{Journal of Numerical Mathematics and Stochastics}
\DefineJournal{jnmca}{1000-3266}
{J. Numer. Methods Comput. Appl.}
{Journal on Numerical Methods and Computer Applications}
\DefineJournal{jorsc}{2194-668X}
{J. Oper. Res. Soc. China}
{Journal of the Operations Research Society of China}
\DefineJournal{jorsj}{0453-4514}
{J. Oper. Res. Soc. Japan}
{Journal of the Operations Research Society of Japan}
\DefineJournal{jot}{0379-4024}
{J. Operator Theory}
{Journal of Operator Theory}
\DefineJournal{jo}{2356-752X}
{J. Optim.}
{Journal of Optimization}
\DefineJournal{jota}{0022-3239}
{J. Optim. Theory Appl.}
{Journal of Optimization Theory and Applications}
\DefineJournal{jpde}{1000-940X}
{J. Partial Differ. Equ.}
{Journal of Partial Differential Equations}
\DefineJournal{jpl}{0022-3611}
{J. Philos. Logic}
{Journal of Philosophical Logic}
\DefineJournal{jpamt}{1751-8113}
{J. Phys. A}
{Journal of Physics. A. Mathematical and Theoretical}
\DefineJournal{jpcs}{1742-6588}
{J. Phys. Conf. Ser.}
{Journal of Physics. Conference Series}
\DefineJournal{jps}{2350-0352}
{J. Phys. Sci.}
{Journal of Physical Science}
\DefineJournal{jpszfd}{1027-4642}
{J. Phys. Stud.}
{Journal of Physical Studies. Zhurnal Fizichnykh Doslidzhen}
\DefineJournal{jprm}{1817-2725}
{J. Prime Res. Math.}
{Journal of Prime Research in Mathematics}
\DefineJournal{jps}{1687-952X}
{J. Probab. Stat.}
{Journal of Probability and Statistics}
\DefineJournal{jpoa}{1662-9981}
{J. Pseudo-Differ. Oper. Appl.}
{Journal of Pseudo-Differential Operators and Applications}
\DefineJournal{jpaa}{0022-4049}
{J. Pure Appl. Algebra}
{Journal of Pure and Applied Algebra}
\DefineJournal{jpamaa}{0974-9381}
{J. Pure Appl. Math. Adv. Appl.}
{Journal of Pure and Applied Mathematics. Advances and Applications}
\DefineJournal{jpm}{2277-355X}
{J. Pure Math.}
{Journal of Pure Mathematics}
\DefineJournal{jqejs}{1007-1660}
{J. Quant. Econ.}
{Journal of Quantitative Economics. Jingji Shuxue}
\DefineJournal{jrsssbsm}{1369-7412}
{J. R. Stat. Soc. Ser. B. Stat. Methodol.}
{Journal of the Royal Statistical Society. Series B. Statistical Methodology}
\DefineJournal{jrssscas}{0035-9254}
{J. R. Stat. Soc. Ser. C. Appl. Stat.}
{Journal of the Royal Statistical Society. Series C. Applied Statistics}
\DefineJournal{jraps}{0972-6306}
{J. Rajasthan Acad. Phys. Sci.}
{Journal of Rajasthan Academy of Physical Sciences}
\DefineJournal{jrms}{0970-1249}
{J. Ramanujan Math. Soc.}
{Journal of the Ramanujan Mathematical Society}
\DefineJournal{jramj}{0075-4102}
{J. Reine Angew. Math.}
{Journal fur die Reine und Angewandte Mathematik. [Crelle's Journal]}
\DefineJournal{jrsssass}{0964-1998}
{J. Roy. Statist. Soc. Ser. A}
{Journal of the Royal Statistical Society. Series A. Statistics in Society}
\DefineJournal{jsbmc}{1574-0617}
{J. Satisf. Boolean Model. Comput.}
{Journal on Satisfiability, Boolean Modeling and Computation}
\DefineJournal{js}{1094-6136}
{J. Sched.}
{Journal of Scheduling}
\DefineJournal{jsc}{0885-7474}
{J. Sci. Comput.}
{Journal of Scientific Computing}
\DefineJournal{jset}{1816-8752}
{J. Sci. Eng. Technol.}
{Journal of Science, Engineering and Technology}
\DefineJournal{irijs}{1016-1104}
{J. Sci. Islam. Repub. Iran}
{Islamic Republic of Iran. Journal of Sciences}
\DefineJournal{jsjsfs}{2102-6238}
{J. SFdS}
{Journal de la SFdS. Journal de la Societe Francaise de Statistique}
\DefineJournal{snujnsessdxzkb}{1672-4291}
{J. Shaanxi Normal Univ. Nat. Sci. Ed.}
{Shaanxi Normal University. Journal. Natural Science Edition. Shaanxi Shifan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jsunssdxlb}{1671-9352}
{J. Shandong Univ. Nat. Sci.}
{Journal of Shandong University. Natural Science. Shandong Daxue Xuebao. Lixue Ban}
\DefineJournal{jsjucesjdx}{1006-2467}
{J. Shanghai Jiaotong Univ. (Chin. Ed.)}
{Journal of Shanghai Jiaotong University. Chinese Edition. Shanghai Jiaotong Daxue Xuebao}
\DefineJournal{jsunsesdxzkb}{1007-2861}
{J. Shanghai Univ. Nat. Sci.}
{Journal of Shanghai University. Natural Science Edition. Shanghai Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{}{?}
{J. Shanghai Univ. Sci. Tech.}
{nan}
\DefineJournal{jsuesesdxgkb}{1009-3087}
{J. Sichuan Univ. Eng. Sci. Ed.}
{Journal of Sichuan University. Engineering Science Edition. Sichuan Daxue Xuebao. Gongcheng Kexue Ban}
\DefineJournal{js}{1949-2006}
{J. Singul.}
{Journal of Singularities}
\DefineJournal{jsrx}{1000-9825}
{J. Softw.}
{Journal of Software. Ruanjian Xuebao}
\DefineJournal{jsag}{1948-7916}
{J. Softw. Algebra Geom.}
{Journal of Software for Algebra and Geometry}
\DefineJournal{jscnunsehsdxzkb}{1000-5463}
{J. South China Normal Univ. Natur. Sci. Ed.}
{Journal of South China Normal University. Natural Science Edition. Huanan Shifan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jsueeddxyb}{1003-7985}
{J. Southeast Univ. (English Ed.)}
{Journal of Southeast University. English Edition. Dongnan Daxue Xuebao. Yingwen Ban}
\DefineJournal{jsunseddxzkb}{1001-0505}
{J. Southeast Univ. Nat. Sci.}
{Journal of Southeast University. Natural Science Edition. Dongnan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jst}{1664-039X}
{J. Spectr. Theory}
{Journal of Spectral Theory}
\DefineJournal{jscs}{0094-9655}
{J. Stat. Comput. Simul.}
{Journal of Statistical Computation and Simulation}
\DefineJournal{jsmte}{1742-5468}
{J. Stat. Mech. Theory Exp.}
{Journal of Statistical Mechanics: Theory and Experiment}
\DefineJournal{jsp}{0022-4715}
{J. Stat. Phys.}
{Journal of Statistical Physics}
\DefineJournal{jsta}{1538-7887}
{J. Stat. Theory Appl.}
{Journal of Statistical Theory and Applications}
\DefineJournal{jstp}{1559-8608}
{J. Stat. Theory Pract.}
{Journal of Statistical Theory and Practice}
\DefineJournal{jspi}{0378-3758}
{J. Statist. Plann. Inference}
{Journal of Statistical Planning and Inference}
\DefineJournal{jsr}{0256-422X}
{J. Statist. Res.}
{Journal of Statistical Research}
\DefineJournal{}{?}
{J. Sun Yatsen Univ.}
{nan}
\DefineJournal{tjsl}{0022-4812}
{J. Symb. Log.}
{The Journal of Symbolic Logic}
\DefineJournal{jsc}{0747-7171}
{J. Symbolic Comput.}
{Journal of Symbolic Computation}
\DefineJournal{tjsg}{1527-5256}
{J. Symplectic Geom.}
{The Journal of Symplectic Geometry}
\DefineJournal{jssc}{1009-6124}
{J. Syst. Sci. Complex.}
{Journal of Systems Science & Complexity}
\DefineJournal{jssmsxks}{1000-0577}
{J. Systems Sci. Math. Sci.}
{Journal of Systems Science and Mathematical Sciences. Xitong Kexue yu Shuxue}
\DefineJournal{jtp}{0324-8313}
{J. Tech. Phys.}
{Journal of Technical Physics}
\DefineJournal{jts}{0974-5428}
{J. Tensor Soc.}
{Journal of the Tensor Society}
\DefineJournal{jtca}{2591-7285}
{J. Theor. Comput. Acoust.}
{Journal of Theoretical and Computational Acoustics}
\DefineJournal{jtnb}{1246-7405}
{J. Theor. Nombres Bordeaux}
{Journal de Theorie des Nombres de Bordeaux}
\DefineJournal{jtam}{0861-6663}
{J. Theoret. Appl. Mech.}
{Journal of Theoretical and Applied Mechanics}
\DefineJournal{jtb}{0022-5193}
{J. Theoret. Biol.}
{Journal of Theoretical Biology}
\DefineJournal{jtp}{0894-9840}
{J. Theoret. Probab.}
{Journal of Theoretical Probability}
\DefineJournal{jtse}{2194-6507}
{J. Time Ser. Econom.}
{Journal of Time Series Econometrics}
\DefineJournal{jtsa}{0143-9782}
{J. Time Series Anal.}
{Journal of Time Series Analysis}
\DefineJournal{jt}{1753-8416}
{J. Topol.}
{Journal of Topology}
\DefineJournal{jta}{1793-5253}
{J. Topol. Anal.}
{Journal of Topology and Analysis}
\DefineJournal{jtustqdxzkb}{1000-0054}
{J. Tsinghua Univ.}
{Journal of Tsinghua University. Science and Technology. Qinghua Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jt}{1468-5248}
{J. Turbul.}
{Journal of Turbulence}
\DefineJournal{justczkjdx}{0253-2778}
{J. Univ. Sci. Technol. China}
{Journal of University of Science and Technology of China. Zhongguo Kexue Jishu Daxue Xuebao}
\DefineJournal{jvc}{1077-5463}
{J. Vib. Control}
{Journal of Vibration and Control}
\DefineJournal{jwunsewdxlb}{1671-8836}
{J. Wuhan Univ. Natur. Sci. Ed.}
{Journal of Wuhan University. Natural Science Edition. Wuhan Daxue Xuebao. Lixue Ban}
\DefineJournal{}{?}
{J. Xi'an Jiaotong Univ.}
{nan}
\DefineJournal{}{?}
{J. Xiamen Univ. Natur. Sci.}
{nan}
\DefineJournal{jyunsydxzkb}{0258-7971}
{J. Yunnan Univ. Nat. Sci.}
{Journal of Yunnan University. Natural Sciences. Yunnan Daxue Xuebao. Ziran Kexue Ban}
\DefineJournal{jzusezdxlb}{1008-9497}
{J. Zhejiang Univ. Sci. Ed.}
{Journal of Zhejiang University. Science Edition. Zhejiang Daxue Xuebao. Lixue Ban}
\DefineJournal{jzueszdxgb}{1671-6833}
{J. Zhengzhou Univ. Eng. Sci.}
{Journal of Zhengzhou University. Engineering Science. Zhengzhou Daxue Xuebao. Gongxue Ban}
\DefineJournal{jzunsezdxlb}{1671-6841}
{J. Zhengzhou Univ. Nat. Sci. Ed.}
{Journal of Zhengzhou University. Natural Science Edition. Zhengzhou Daxue Xuebao. Lixue Ban}
\DefineJournal{jjucs}{0948-695X}
{J.UCS}
{J.UCS. Journal of Universal Computer Science}
\DefineJournal{jja}{1889-3066}
{Jaen J. Approx.}
{Jaen Journal on Approximation}
\DefineJournal{jdm}{0012-0456}
{Jahresber. Dtsch. Math.-Ver.}
{Jahresbericht der Deutschen Mathematiker-Vereinigung}
\DefineJournal{jarect}{?jarect}
{Japan Annual Rev. Electron. Comput. Telecom. 1982}
{Japan Annual Reviews in Electronics, Computers & Telecommunications 1982}
\DefineJournal{}{?}
{Jilin Daxue Xuebao Lixue Ban}
{nan}
\DefineJournal{}{?}
{Jinan Daxue Xuebao. Ziran Kexue yu Yizue Ban}
{nan}
\DefineJournal{}{?}
{Jingji Shuxue}
{nan}
\DefineJournal{jjise}{1016-2364}
{JISE J. Inf. Sci. Eng.}
{JISE. Journal of Information Science and Engineering}
\DefineJournal{jfc}{?jfc}
{Jisuan Fangfa Congshu}
{Jisuan Fangfa Congshu}
\DefineJournal{}{?}
{Jisuan Shuxue}
{nan}
\DefineJournal{jwcp}{1938-7228}
{JMLR Workshop Conf. Proc.}
{JMLR: Workshop and Conference Proceedings}
\DefineJournal{jjnaiam}{1790-8140}
{JNAIAM. J. Numer. Anal. Ind. Appl. Math.}
{JNAIAM. Journal of Numerical Analysis, Industrial and Applied Mathematics}
\DefineJournal{jhshm}{?jhshm}
{Johns Hopkins Stud. Hist. Math.}
{Johns Hopkins Studies in the History of Mathematics}
\DefineJournal{jbscs}{?jbscs}
{Jones Bartlett Ser. Comput. Sci.}
{Jones and Bartlett Series in Computer Science}
\DefineJournal{jjms}{2075-7905}
{Jordan J. Math. Stat.}
{Jordan Journal of Mathematics and Statistics}
\DefineJournal{tjertjjea}{1352-4739}
{Jpn. Econ. Rev.}
{The Japanese Economic Review. The Journal of the Japanese Economic Association}
\DefineJournal{tjjb}{0385-5481}
{Jpn. J. Behaviormetrics}
{The Japanese Journal of Behaviormetrics}
\DefineJournal{jjiam}{0916-7005}
{Jpn. J. Ind. Appl. Math.}
{Japan Journal of Industrial and Applied Mathematics}
\DefineJournal{jjm}{0289-2316}
{Jpn. J. Math.}
{Japanese Journal of Mathematics}
\DefineJournal{jjpss}{1726-3328}
{JPSS J. Probab. Stat. Sci.}
{JPSS. Journal of Probability and Statistical Science}
\DefineJournal{jl}{1883-0609}
{JSIAM Lett.}
{JSIAM Letters}
\DefineJournal{jrss}{2364-0057}
{JSS Res. Ser. Stat.}
{JSS Research Series in Statistics}
\DefineJournal{kjps}{1647-659X}
{Kairos}
{Kairos. Journal of Philosophy & Science}
\DefineJournal{kcs}{?kcs}
{Keele Cognition Sem.}
{Keele Cognition Seminars}
\DefineJournal{kjm}{2423-4788}
{Khayyam J. Math.}
{Khayyam Journal of Mathematics}
\DefineJournal{nanuikvmgksa}{0023-1274}
{Kibernet. Sistem. Anal.}
{Natsionalnaya Akademiya Nauk Ukrainy. Institut Kibernetiki im. V. M. Glushkova. Kibernetika i Sistemnyi Analiz}
\DefineJournal{ks}{0340-6989}
{Kiel. Stud.}
{Kieler Studien}
\DefineJournal{krm}{1937-5093}
{Kinet. Relat. Models}
{Kinetic and Related Models}
\DefineJournal{kbdm}{?kbdm}
{Klagenf. Beitr. Didakt. Math.}
{Klagenfurter Beitrage zur Didaktik der Mathematik}
\DefineJournal{ktw}{2522-865X}
{Klass. Texte Wiss.}
{Klassische Texte der Wissenschaft}
\DefineJournal{kr}{1865-7095}
{Klostermann RoteReihe}
{Klostermann RoteReihe}
\DefineJournal{tkisse}{?tkisse}
{Kluwer Int. Ser. Softw. Eng.}
{The Kluwer International Series in Software Engineering}
\DefineJournal{tkisecskrles}{?tkisecskrles}
{Kluwer Internat. Ser. Engrg. Comput. Sci. Knowledge Represent., Learn. Expert Systems}
{The Kluwer International Series in Engineering and Computer Science. Knowledge Representation, Learning and Expert Systems}
\DefineJournal{kjm}{0289-9051}
{Kobe J. Math.}
{Kobe Journal of Mathematics}
\DefineJournal{kmj}{0386-5991}
{Kodai Math. J.}
{Kodai Mathematical Journal}
\DefineJournal{k}{1331-1611}
{KoG}
{KoG}
\DefineJournal{kp}{?kp}
{Kolleg Philos.}
{Kolleg Philosophie}
\DefineJournal{k}{?k}
{Kompaktwissen}
{Kompaktwissen}
\DefineJournal{kjm}{2147-625X}
{Konuralp J. Math.}
{Konuralp Journal of Mathematics}
\DefineJournal{kam}{1229-1277}
{Korean Ann. Math.}
{Korean Annals of Mathematics}
\DefineJournal{tkjm}{1976-8605}
{Korean J. Math.}
{The Korean Journal of Mathematics}
\DefineJournal{kjm}{1450-9628}
{Kragujevac J. Math.}
{Kragujevac Journal of Mathematics}
\DefineJournal{rank}{0023-4761}
{Kristallografiya}
{Rossiiskaya Akademiya Nauk. Kristallografiya}
\DefineJournal{kjm}{0914-675X}
{Kumamoto J. Math.}
{Kumamoto Journal of Mathematics}
\DefineJournal{kjs}{2307-4108}
{Kuwait J. Sci.}
{Kuwait Journal of Science}
\DefineJournal{ktijcsms}{0368-492X}
{Kybernetes}
{Kybernetes. The International Journal of Cybernetics, Systems and Management Sciences}
\DefineJournal{k}{0023-5954}
{Kybernetika (Prague)}
{Kybernetika}
\DefineJournal{kjm}{2156-2261}
{Kyoto J. Math.}
{Kyoto Journal of Mathematics}
\DefineJournal{kmj}{1225-6951}
{Kyungpook Math. J.}
{Kyungpook Mathematical Journal}
\DefineJournal{kjm}{1340-6116}
{Kyushu J. Math.}
{Kyushu Journal of Mathematics}
\DefineJournal{lm}{2038-5722}
{La Mat. per il 3+2}
{La Matematica per il 3+2}
\DefineJournal{les}{?les}
{Lang. Ed. Soc.}
{Language, Education and Society}
\DefineJournal{ldsccp}{?ldsccp}
{Learn. Doing Soc. Cogn. Comput. Perspect.}
{Learning in Doing: Social, Cognitive, and Computational Perspectives}
\DefineJournal{lm}{0120-1980}
{Lect. Mat.}
{Lecturas Matematicas}
\DefineJournal{lnacm}{1613-7736}
{Lect. Notes Appl. Comput. Mech.}
{Lecture Notes in Applied and Computational Mechanics}
\DefineJournal{lnamm}{2197-6724}
{Lect. Notes Appl. Math. Mech.}
{Lecture Notes in Applied Mathematics and Mechanics}
\DefineJournal{lnanha}{?lnanha}
{Lect. Notes Appl. Numer. Harmon. Anal.}
{Lecture Notes in Applied and Numerical Harmonic Analysis}
\DefineJournal{lnb}{2195-271X}
{Lect. Notes Bioeng.}
{Lecture Notes in Bioengineering}
\DefineJournal{lncse}{1439-7358}
{Lect. Notes Comput. Sci. Eng.}
{Lecture Notes in Computational Science and Engineering}
\DefineJournal{lncvb}{2212-9391}
{Lect. Notes Comput. Vis. Biomech.}
{Lecture Notes in Computational Vision and Biomechanics}
\DefineJournal{lncis}{0170-8643}
{Lect. Notes Control Inf. Sci.}
{Lecture Notes in Control and Information Sciences}
\DefineJournal{lncisp}{2522-5383}
{Lect. Notes Control Inf. Sci. Proc.}
{Lecture Notes in Control and Information Sciences. Proceedings}
\DefineJournal{lness}{2193-8571}
{Lect. Notes Earth Syst. Sci.}
{Lecture Notes in Earth System Sciences}
\DefineJournal{lnee}{1876-1100}
{Lect. Notes Electr. Eng.}
{Lecture Notes in Electrical Engineering}
\DefineJournal{lne}{2195-1284}
{Lect. Notes Energy}
{Lecture Notes in Energy}
\DefineJournal{lngmc}{?lngmc}
{Lect. Notes Geosyst. Math. Comput.}
{Lecture Notes in Geosystems Mathematics and Computing}
\DefineJournal{lnb}{?lnb}
{Lect. Notes in Bioinform.}
{Lecture Notes in Bioinformatics}
\DefineJournal{lnl}{?lnl}
{Lect. Notes Log.}
{Lecture Notes in Logic}
\DefineJournal{lnmfm}{2510-1374}
{Lect. Notes Math. Fluid Mech.}
{Lecture Notes in Mathematical Fluid Mechanics}
\DefineJournal{lnmmls}{2193-4789}
{Lect. Notes Math. Model. Life Sci.}
{Lecture Notes on Mathematical Modelling in the Life Sciences}
\DefineJournal{lnm}{?lnm}
{Lect. Notes Mech.}
{Lecture Notes in Mechanics}
\DefineJournal{lnm}{2195-1934}
{Lect. Notes Morphog.}
{Lecture Notes in Morphogenesis}
\DefineJournal{lnna}{2082-4335}
{Lect. Notes Nonlinear Anal.}
{Lecture Notes in Nonlinear Analysis}
\DefineJournal{lnnmes}{1877-7341}
{Lect. Notes Numer. Methods Eng. Sci.}
{Lecture Notes on Numerical Methods in Engineering and Sciences}
\DefineJournal{lnsim}{2284-0206}
{Lect. Notes Semin. Interdiscip. Mat.}
{Lecture Notes of Seminario Interdisciplinare di Matematica}
\DefineJournal{lnsimsnus}{1793-0758}
{Lect. Notes Ser. Inst. Math. Sci. Natl. Univ. Singap.}
{Lecture Notes Series. Institute for Mathematical Sciences. National University of Singapore}
\DefineJournal{lnsn}{2190-5428}
{Lect. Notes Soc. Netw.}
{Lecture Notes in Social Networks}
\DefineJournal{lns}{0930-0325}
{Lect. Notes Stat.}
{Lecture Notes in Statistics}
\DefineJournal{lns}{1869-7240}
{Lect. Notes Stat. Proc.}
{Lecture Notes in Statistics---Proceedings}
\DefineJournal{lnticmi}{1512-0511}
{Lect. Notes TICMI}
{Lecture Notes of Tbilisi International Centre of Mathematics and Informatics}
\DefineJournal{lnumi}{1862-9113}
{Lect. Notes Unione Mat. Ital.}
{Lecture Notes of the Unione Matematica Italiana}
\DefineJournal{lpam}{2199-4951}
{Lect. Pure Appl. Math.}
{Lectures in Pure and Applied Mathematics}
\DefineJournal{lnfbsca}{?lnfbsca}
{Lecture Notes First Braz. School Comput. Algebra}
{Lecture Notes from the First Brazilian School on Computer Algebra}
\DefineJournal{lnai}{?lnai}
{Lecture Notes in Artificial Intelligence}
{Lecture Notes in Artificial Intelligence}
\DefineJournal{lncs}{0302-9743}
{Lecture Notes in Comput. Sci.}
{Lecture Notes in Computer Science}
\DefineJournal{lnems}{0075-8442}
{Lecture Notes in Econom. and Math. Systems}
{Lecture Notes in Economics and Mathematical Systems}
\DefineJournal{lnm}{0075-8434}
{Lecture Notes in Math.}
{Lecture Notes in Mathematics}
\DefineJournal{lnp}{0075-8450}
{Lecture Notes in Phys.}
{Lecture Notes in Physics}
\DefineJournal{lnsc}{?lnsc}
{Lecture Notes Ser. Comput.}
{Lecture Notes Series on Computing}
\DefineJournal{lhgbbv}{?lhgbbv}
{Lehr- Handb. Geld Borse Bank Versicher.}
{Lehr- und Handbucher zu Geld, Borse, Bank und Versicherung}
\DefineJournal{lai}{?lai}
{Leitfaden Angew. Inform.}
{Leitfaden der Angewandten Informatik}
\DefineJournal{lkn}{2226-8782}
{Lektsionnye Kursy NOTs}
{Lektsionnye Kursy NOTs}
\DefineJournal{lb}{2373-7867}
{Lett. Biomath.}
{Letters in Biomathematics}
\DefineJournal{lm}{2281-6917}
{Lett. Mat.}
{Lettera Matematica}
\DefineJournal{lmp}{0377-9017}
{Lett. Math. Phys.}
{Letters in Mathematical Physics}
\DefineJournal{loc}{?loc}
{Lett. Orient. Class.}
{Lettres Orientales et Classiques}
\DefineJournal{lm}{2190-6637}
{Levy Matters}
{Levy Matters}
\DefineJournal{lbscs}{?lbscs}
{Lexington Books Ser. Comput. Sci.}
{Lexington Books Series in Computer Science}
\DefineJournal{lem}{?lem}
{Lib. Engrg. Math.}
{Library of Engineering Mathematics}
\DefineJournal{lmns}{0278-5307}
{Lib. Math. (N.S.)}
{Libertas Mathematica. New Series}
\DefineJournal{ldaaijdsmatd}{1380-7870}
{Lifetime Data Anal.}
{Lifetime Data Analysis. An International Journal Devoted to Statistical Methods and Applications for Time-to-Event Data}
\DefineJournal{laa}{0024-3795}
{Linear Algebra Appl.}
{Linear Algebra and its Applications}
\DefineJournal{lma}{0308-1087}
{Linear Multilinear Algebra}
{Linear and Multilinear Algebra}
\DefineJournal{lnaaij}{2188-8159}
{Linear Nonlinear Anal.}
{Linear and Nonlinear Analysis. An International Journal}
\DefineJournal{lols}{?lols}
{Linear Oper. Linear Syst.}
{Linear Operators and Linear Systems}
\DefineJournal{lis}{0165-7569}
{Lingvist. Investig. Suppl.}
{Lingvisticae Investigationes: Supplementa}
\DefineJournal{llipi}{1868-8969}
{LIPIcs. Leibniz Int. Proc. Inform.}
{LIPIcs. Leibniz International Proceedings in Informatics}
\DefineJournal{ll}{?ll}
{Lipsey Lect.}
{Lipsey Lectures}
\DefineJournal{lmtpss}{?lmtpss}
{Liste Abr. Mots Titres Publ. Ser. Suppl.}
{Liste d'Abreviations de Mots des Titres de Publications en Serie. Supplement}
\DefineJournal{l}{?l}
{LiTH-MAT-R}
{LiTH-MAT-R}
\DefineJournal{lmj}{0363-1672}
{Lith. Math. J.}
{Lithuanian Mathematical Journal}
\DefineJournal{lrsehct}{0210-8615}
{LLULL}
{LLULL. Revista de la Sociedad Espanola de Historia de las Ciencias y de las Tecnicas}
\DefineJournal{ljcm}{1461-1570}
{LMS J. Comput. Math.}
{LMS Journal of Computation and Mathematics}
\DefineJournal{ljm}{1995-0802}
{Lobachevskii J. Math.}
{Lobachevskii Journal of Mathematics}
\DefineJournal{lum}{?lum}
{Loescher Universita Manuali}
{Loescher Universita Manueli}
\DefineJournal{lans}{0024-5836}
{Log. Anal. (N.S.)}
{Logique et Analyse. Nouvelle Serie}
\DefineJournal{la}{?la}
{Log. Argum.}
{Logic and Argumentation}
\DefineJournal{lar}{2214-9120}
{Log. Argum. Reason}
{Logic, Argumentation & Reasoning}
\DefineJournal{lasll}{2364-4613}
{Log. Asia Stud. Log. Libr.}
{Logic in Asia: Studia Logica Library}
\DefineJournal{leus}{2214-9775}
{Log. Epistemol. Unity Sci.}
{Logic, Epistemology, and the Unity of Science}
\DefineJournal{li}{2074-1472}
{Log. Issled.}
{Logicheskie Issledovaniya}
\DefineJournal{lili}{2074-1472}
{Log. Issled.}
{Logicheskie Issledovaniya. Logical Investigations}
\DefineJournal{ljiigpal}{1367-0751}
{Log. J. IGPL}
{Logic Journal of the IGPL. Interest Group in Pure and Applied Logics}
\DefineJournal{llp}{1425-3305}
{Log. Log. Philos.}
{Logic and Logical Philosophy}
\DefineJournal{lmcs}{1860-5974}
{Log. Methods Comput. Sci.}
{Logical Methods in Computer Science}
\DefineJournal{lp}{?lp}
{Log. PhDs}
{Logic PhDs}
\DefineJournal{lu}{1661-8297}
{Log. Univers.}
{Logica Universalis}
\DefineJournal{lslsm}{2198-2201}
{Logos}
{Logos. Studien zur Logik, Sprachphilosophie und Metaphysik}
\DefineJournal{lmsn}{2516-3841}
{Lond. Math. Soc. Newsl.}
{London Mathematical Society. Newsletter}
\DefineJournal{lmslns}{?lmslns}
{London Math. Soc. Lecture Note Ser.}
{London Mathematical Society Lecture Note Series}
\DefineJournal{lmsst}{?lmsst}
{London Math. Soc. Stud. Texts}
{London Mathematical Society Student Texts}
\DefineJournal{lams}{?lams}
{LTCC Adv. Math. Ser.}
{LTCC Advanced Mathematics Series}
\DefineJournal{mn}{?mn}
{MAA Notes}
{MAA Notes}
\DefineJournal{mpbs}{?mpbs}
{MAA Probl. Books Ser.}
{MAA Problem Books Series}
\DefineJournal{ms}{?ms}
{MAA Spectrum}
{MAA Spectrum}
\DefineJournal{mt}{?mt}
{MAA Textb.}
{MAA Textbooks}
\DefineJournal{ml}{0885-6125}
{Mach. Learn.}
{Machine Learning}
\DefineJournal{mnes}{?mnes}
{Macmillan New Electron. Ser.}
{Macmillan New Electronics Series}
\DefineJournal{mjk}{?mjk}
{Mala Jazyk. Kn.}
{Mala Jazykova Kniznice}
\DefineJournal{mjm}{2319-3786}
{Malaya J. Mat.}
{Malaya Journal of Matematik}
\DefineJournal{mjms}{1823-8343}
{Malays. J. Math. Sci.}
{Malaysian Journal of Mathematical Sciences}
\DefineJournal{mmpt}{?mmpt}
{Male Monogr. PWN Tech.}
{Male Monografie PWN. Technika}
\DefineJournal{mie}{2265-0532}
{Manag. Ind. Eng}
{Management and Industrial Engineering}
\DefineJournal{mis}{?mis}
{Management and Inform. Systems}
{Management and Information Systems}
\DefineJournal{tmps}{?tmps}
{Manchester Phys. Ser.}
{The Manchester Physics Series}
\DefineJournal{memp}{?memp}
{Manuf. Eng. Mater. Process.}
{Manufacturing Engineering and Materials Processing}
\DefineJournal{mm}{0025-2611}
{Manuscripta Math.}
{Manuscripta Mathematica}
\DefineJournal{mbseic}{?mbseic}
{Mario Boella Ser. Electromagn. Inf. Commun.}
{Mario Boella Series on Electromagnetism in Information and Communication}
\DefineJournal{mprf}{1024-2953}
{Markov Process. Related Fields}
{Markov Processes and Related Fields}
\DefineJournal{mmf}{?mmf}
{Mastering Math. Finance}
{Mastering Mathematical Finance}
\DefineJournal{msacstm}{1515-4904}
{MAT Ser. A Conf. Semin. Trab. Mat.}
{MAT. Serie A: Conferencias, Seminarios y Trabajos de Matematica}
\DefineJournal{mbbmsmrm}{0351-336X}
{Mat. Bilten}
{Matematichki Bilten. Bulletin Mathematique de la Societe des Mathematiciens de la Republique de Macedoine}
\DefineJournal{mc}{?mc}
{Mat. Complement.}
{Matematiche Complementari}
\DefineJournal{mc}{0103-9059}
{Mat. Contemp.}
{Matematica Contemporanea}
\DefineJournal{mcsrmisi}{2499-751X}
{Mat. Cult. Soc. Riv. Unione Mat. Ital. (I)}
{Matematica, Cultura e Societa. Rivista dell'Unione Matematica Italiana. Serie I}
\DefineJournal{mfkmmpcs}{2587-6325}
{Mat. Fiz. Kompyut. Model.}
{Matematicheskaya Fizika i Kompyuternoe Modelirovanie. Mathematical Physics and Computer Simulation}
\DefineJournal{mlns}{0025-519X}
{Mat. Lapok (N.S.)}
{Matematikai Lapok. New Series}
\DefineJournal{ranmm}{0234-0879}
{Mat. Model.}
{Rossiiskaya Akademiya Nauk. Matematicheskoe Modelirovanie}
\DefineJournal{ranms}{0368-8666}
{Mat. Sb.}
{Rossiiskaya Akademiya Nauk. Matematicheskii Sbornik}
\DefineJournal{mss}{?mss}
{Mat. Sem. SNTL}
{Matematicky Seminar SNTL}
\DefineJournal{msplmt}{1027-4634}
{Mat. Stud.}
{Matematichni Studii. Pratsi Lvivskogo Matematichnogo Tovaristva}
\DefineJournal{mtip}{2074-9872}
{Mat. Teor. Igr Prilozh.}
{Matematicheskaya Teoriya Igr i ee Prilozheniya}
\DefineJournal{mt}{1560-750X}
{Mat. Tr.}
{Matematicheskie Trudy}
\DefineJournal{mv}{0025-5165}
{Mat. Vesnik}
{Matematichki Vesnik}
\DefineJournal{mvkmac}{2220-2617}
{Mat. Vopr. Kriptografii}
{Matematicheskie Voprosy Kriptografii. Mathematical Aspects of Cryptography}
\DefineJournal{ranmz}{0025-567X}
{Mat. Zametki}
{Rossiiskaya Akademiya Nauk. Matematicheskie Zametki}
\DefineJournal{m}{0762-5707}
{Matapli}
{Matapli}
\DefineJournal{mcmcc}{0340-6253}
{MATCH Commun. Math. Comput. Chem.}
{MATCH. Communications in Mathematical and in Computer Chemistry}
\DefineJournal{lm}{0373-3505}
{Matematiche (Catania)}
{Le Matematiche}
\DefineJournal{mmjiam}{0127-8274}
{Matematika (Johor)}
{Matematika. Malaysian Journal of Industrial and Applied Mathematics}
\DefineJournal{mfmt}{2195-0911}
{Mater. Form. Mach. Tribol.}
{Materials Forming, Machining and Tribology}
\DefineJournal{mss}{?mss}
{Mater. Sci. Ser.}
{Materials Science Series}
\DefineJournal{msr}{?msr}
{Materials Sci. Res.}
{Materials Science Research}
\DefineJournal{mh}{1072-4117}
{Math Horiz.}
{Math Horizons}
\DefineJournal{mga}{?mga}
{Math, Graeca Antiq.}
{Mathematica Graeca Antiqua}
\DefineJournal{mlns}{2188-1200}
{Math-for-Ind. (MI) Lect. Note Ser.}
{Math-for-Industry (MI) Lecture Note Series}
\DefineJournal{maia}{?maia}
{Math. Anal. Appl.}
{Mathematical Analysis and Its Applications}
\DefineJournal{matae}{1559-7458}
{Math. Anal. Tech. Appl. Eng.}
{Mathematical and Analytical Techniques with Applications to Engineering}
\DefineJournal{ma}{0025-5831}
{Math. Ann.}
{Mathematische Annalen}
\DefineJournal{ma}{?ma}
{Math. Anwend.}
{Mathematik fur Anwendungen}
\DefineJournal{ma}{1154-483X}
{Math. Appl. (Berlin)}
{Mathematiques & Applications (Berlin)}
\DefineJournal{ma}{1805-3610}
{Math. Appl. (Brno)}
{Mathematics for Applications}
\DefineJournal{mas}{?mas}
{Math. Appl. (Soviet Ser.)}
{Mathematics and its Applications (Soviet Series)}
\DefineJournal{mams}{1730-2668}
{Math. Appl. (Warsaw)}
{Mathematica Applicanda. Matematyka Stosowana}
\DefineJournal{mays}{1001-9847}
{Math. Appl. (Wuhan)}
{Mathematica Applicata. Yingyong Shuxue}
\DefineJournal{mbns}{0205-3217}
{Math. Balkanica (N.S.)}
{Mathematica Balkanica. New Series}
\DefineJournal{mb}{?mb}
{Math. Beisp.}
{Mathematik in Beispielen}
\DefineJournal{mb}{0025-5564}
{Math. Biosci.}
{Mathematical Biosciences}
\DefineJournal{mbem}{1547-1063}
{Math. Biosci. Eng.}
{Mathematical Biosciences and Engineering. MBE}
\DefineJournal{mbilssbs}{2364-2297}
{Math. Biosci. Inst. Lect. Ser. Stoch. Biol. Syst.}
{Mathematical Biosciences Institute Lecture Series. Stochastics in Biological Systems}
\DefineJournal{ascrmimb}{0862-7959}
{Math. Bohem.}
{Academy of Sciences of the Czech Republic. Mathematical Institute. Mathematica Bohemica}
\DefineJournal{mbe}{2512-157X}
{Math. Built Environ.}
{Mathematics and the Built Environment}
\DefineJournal{mcwf}{2353-6438}
{Math. Clim. Weather Forecast.}
{Mathematics of Climate and Weather Forecasting}
\DefineJournal{mc}{1331-0623}
{Math. Commun.}
{Mathematical Communications}
\DefineJournal{mc}{0025-5718}
{Math. Comp.}
{Mathematics of Computation}
\DefineJournal{mca}{1300-686X}
{Math. Comput. Appl.}
{Mathematical & Computational Applications}
\DefineJournal{mcbna}{?mcbna}
{Math. Comput. Biol. Numer. Anal.}
{Mathematical and Computational Biology and Numerical Analysis}
\DefineJournal{mcmdsmtaers}{1387-3954}
{Math. Comput. Model. Dyn. Syst.}
{Mathematical and Computer Modelling of Dynamical Systems. Methods, Tools and Applications in Engineering and Related Sciences}
\DefineJournal{mcs}{1661-8270}
{Math. Comput. Sci.}
{Mathematics in Computer Science}
\DefineJournal{mcs}{0378-4754}
{Math. Comput. Simulation}
{Mathematics and Computers in Simulation}
\DefineJournal{mcrf}{2156-8472}
{Math. Control Relat. Fields}
{Mathematical Control and Related Fields}
\DefineJournal{mcss}{0932-4194}
{Math. Control Signals Systems}
{Mathematics of Control, Signals, and Systems}
\DefineJournal{mca}{2520-8578}
{Math. Cult. Arts}
{Mathematics, Culture, and the Arts}
\DefineJournal{me}{2192-4732}
{Math. Eng.}
{Mathematical Engineering}
\DefineJournal{mfe}{1862-9679}
{Math. Financ. Econ.}
{Mathematics and Financial Economics}
\DefineJournal{mfaijmsfe}{0960-1627}
{Math. Finance}
{Mathematical Finance. An International Journal of Mathematics, Statistics and Financial Economics}
\DefineJournal{mf}{0972-9852}
{Math. Forum}
{Mathematical Forum}
\DefineJournal{tmg}{0025-5572}
{Math. Gaz.}
{The Mathematical Gazette}
\DefineJournal{mg}{1874-8961}
{Math. Geosci.}
{Mathematical Geosciences}
\DefineJournal{mi}{1612-3956}
{Math. Ind.}
{Mathematics in Industry}
\DefineJournal{mi}{?mi}
{Math. Ind. (Phila.)}
{Mathematics in Industry (Philadelphia)}
\DefineJournal{mi}{2198-350X}
{Math. Ind. (Tokyo)}
{Mathematics for Industry (Tokyo)}
\DefineJournal{mia}{1331-4343}
{Math. Inequal. Appl.}
{Mathematical Inequalities & Applications}
\DefineJournal{misrsb}{1171-7637}
{Math. Inform. Sci. Rep. Ser. B}
{Mathematical and Information Sciences Report. Series B}
\DefineJournal{minosab}{?minosab}
{Math. Ingen. Naturwiss. Okonom. Sonstige Anwendungsorient. Berufe}
{Mathematik fur Ingenieure, Naturwissenschaftler, Okonomen und Sonstige Anwendungsorientierte Berufe}
\DefineJournal{tmi}{0343-6993}
{Math. Intelligencer}
{The Mathematical Intelligencer}
\DefineJournal{mjiu}{1343-3636}
{Math. J. Ibaraki Univ.}
{Mathematical Journal of Ibaraki University}
\DefineJournal{mjou}{0030-1566}
{Math. J. Okayama Univ.}
{Mathematical Journal of Okayama University}
\DefineJournal{mk}{2504-3846}
{Math. Kompakt}
{Mathematik Kompakt}
\DefineJournal{mk}{2191-074X}
{Math. Kontext}
{Mathematik im Kontext}
\DefineJournal{mlpu}{2197-4209}
{Math. Lect. Peking Univ.}
{Mathematical Lectures from Peking University}
\DefineJournal{mlf}{?mlf}
{Math. Logic Found.}
{Mathematical Logic and Foundations}
\DefineJournal{mm}{0025-570X}
{Math. Mag.}
{Mathematics Magazine}
\DefineJournal{mmcs}{2326-7186}
{Math. Mech. Complex Syst.}
{Mathematics and Mechanics of Complex Systems}
\DefineJournal{mms}{1081-2865}
{Math. Mech. Solids}
{Mathematics and Mechanics of Solids}
\DefineJournal{mmbaji}{1477-8599}
{Math. Med. Biol.}
{Mathematical Medicine and Biology. A Journal of the IMA}
\DefineJournal{mmas}{0170-4214}
{Math. Methods Appl. Sci.}
{Mathematical Methods in the Applied Sciences}
\DefineJournal{mmef}{1971-6419}
{Math. Methods Econ. Finance}
{Mathematical Methods in Economics and Finance}
\DefineJournal{mmm}{2166-3440}
{Math. Methods Model.}
{Mathematical Methods and Modeling}
\DefineJournal{mmor}{1432-2994}
{Math. Methods Oper. Res.}
{Mathematical Methods of Operations Research}
\DefineJournal{mms}{1066-5307}
{Math. Methods Statist.}
{Mathematical Methods of Statistics}
\DefineJournal{mm}{2522-5405}
{Math. Mind}
{Mathematics in Mind}
\DefineJournal{mma}{1392-6292}
{Math. Model. Anal.}
{Mathematical Modelling and Analysis}
\DefineJournal{mmc}{?mmc}
{Math. Model. Comput.}
{Mathematical Modeling and Computation}
\DefineJournal{mmnp}{0973-5348}
{Math. Model. Nat. Phenom.}
{Mathematical Modelling of Natural Phenomena}
\DefineJournal{mmcs}{2070-0482}
{Math. Models Comput. Simul.}
{Mathematical Models and Computer Simulations}
\DefineJournal{mmmas}{0218-2025}
{Math. Models Methods Appl. Sci.}
{Mathematical Models and Methods in Applied Sciences}
\DefineJournal{mmmtg}{0354-2238}
{Math. Montisnigri}
{Mathematica Montisnigri. Matematika Tsrne Gore}
\DefineJournal{mm}{1450-5932}
{Math. Morav.}
{Mathematica Moravica}
\DefineJournal{mn}{0025-584X}
{Math. Nachr.}
{Mathematische Nachrichten}
\DefineJournal{mns}{1314-0272}
{Math. Nat. Sci.}
{Mathematics and Natural Sciences}
\DefineJournal{mn}{?mn}
{Math. Nat.wiss.}
{Mathematik und Naturwissenschaften}
\DefineJournal{mn}{0971-1694}
{Math. Newsl.}
{Mathematics Newsletter}
\DefineJournal{mn}{?mn}
{Math. Notes}
{Mathematical Notes}
\DefineJournal{mn}{0001-4346}
{Math. Notes}
{Mathematical Notes}
\DefineJournal{mnsjs}{0254-7791}
{Math. Numer. Sin.}
{Mathematica Numerica Sinica. Jisuan Shuxue}
\DefineJournal{mos}{1793-8570}
{Math. Olymp. Ser.}
{Mathematical Olympiad Series}
\DefineJournal{mor}{0364-765X}
{Math. Oper. Res.}
{Mathematics of Operations Research}
\DefineJournal{mp}{0865-2090}
{Math. Pannon.}
{Mathematica Pannonica}
\DefineJournal{mpagaijdtaagp}{1385-0172}
{Math. Phys. Anal. Geom.}
{Mathematical Physics, Analysis and Geometry. An International Journal Devoted to the Theory and Applications of Analysis and Geometry to Physics}
\DefineJournal{mpst}{?mpst}
{Math. Phys. Sci. Technol.}
{Mathematics and Physics for Science and Technology}
\DefineJournal{mps}{0921-3767}
{Math. Phys. Stud.}
{Mathematical Physics Studies}
\DefineJournal{mpe}{?mpe}
{Math. Planet Earth}
{Mathematics of Planet Earth}
\DefineJournal{mpsaijmd}{0889-8480}
{Math. Popul. Stud.}
{Mathematical Population Studies. An International Journal of Mathematical Demography}
\DefineJournal{mpcs}{0131-4645}
{Math. Probl. Comput. Sci.}
{Mathematical Problems of Computer Science}
\DefineJournal{mpe}{1024-123X}
{Math. Probl. Eng.}
{Mathematical Problems in Engineering}
\DefineJournal{mpcps}{0305-0041}
{Math. Proc. Cambridge Philos. Soc.}
{Mathematical Proceedings of the Cambridge Philosophical Society}
\DefineJournal{mpria}{1393-7197}
{Math. Proc. R. Ir. Acad.}
{Mathematical Proceedings of the Royal Irish Academy}
\DefineJournal{mp}{0025-5610}
{Math. Program.}
{Mathematical Programming}
\DefineJournal{mpc}{1867-2949}
{Math. Program. Comput.}
{Mathematical Programming Computation}
\DefineJournal{mr}{1582-3067}
{Math. Rep. (Bucur.)}
{Mathematical Reports (Bucuresti)}
\DefineJournal{mrds}{?mrds}
{Math. Res. Dev. Ser.}
{Mathematics Research Developments Series}
\DefineJournal{mrl}{1073-2780}
{Math. Res. Lett.}
{Mathematical Research Letters}
\DefineJournal{ms}{0025-5521}
{Math. Scand.}
{Mathematica Scandinavica}
\DefineJournal{ms}{?ms}
{Math. Schulerbucherei}
{Mathematische Schulerbucherei}
\DefineJournal{tms}{0312-3685}
{Math. Sci.}
{The Mathematical Scientist}
\DefineJournal{msaeaiejm}{2147-6268}
{Math. Sci. Appl. E-Notes}
{Mathematical Sciences & Applications E-Notes. An International Electronic Journal of Mathematics}
\DefineJournal{mse}{0076-5392}
{Math. Sci. Eng.}
{Mathematics in Science and Engineering}
\DefineJournal{mspd}{0737-4356}
{Math. Sci. Prof. Dir.}
{Mathematical Sciences Professional Directory}
\DefineJournal{msrip}{?msrip}
{Math. Sci. Res. Inst. Publ.}
{Mathematical Sciences Research Institute Publications}
\DefineJournal{ms}{2008-1359}
{Math. Sci. (Springer)}
{Mathematical Sciences}
\DefineJournal{ms}{0720-728X}
{Math. Semesterber.}
{Mathematische Semesterberichte}
\DefineJournal{ms}{0139-9918}
{Math. Slovaca}
{Mathematica Slovaca}
\DefineJournal{mss}{0165-4896}
{Math. Social Sci.}
{Mathematical Social Sciences}
\DefineJournal{mss}{?mss}
{Math. Stat. Ser.}
{Mathematics and Statistics Series}
\DefineJournal{mscsajacagmcs}{0960-1295}
{Math. Structures Comput. Sci.}
{Mathematical Structures in Computer Science. A Journal in the Applications of Categorical, Algebraic and Geometric Methods in Computer Science}
\DefineJournal{msms}{?msms}
{Math. Stud. Monogr. Ser.}
{Mathematical Studies Monograph Series}
\DefineJournal{ms}{2346-6502}
{Math. Stud. (Tartu)}
{Mathematics Studies (Tartu)}
\DefineJournal{tms}{0025-5742}
{Math. Student}
{The Mathematics Student}
\DefineJournal{ms}{?ms}
{Math. Studienanfanger}
{Mathematik fur Studienanfanger}
\DefineJournal{mss}{?mss}
{Math. Super. Spec.}
{Mathematiques Superieures et Speciales}
\DefineJournal{msm}{0076-5376}
{Math. Surveys Monogr.}
{Mathematical Surveys and Monographs}
\DefineJournal{mtapa}{?mtapa}
{Math. Teach. Probl-Based Approach}
{Mathematics for Teaching: A Problem-Based Approach}
\DefineJournal{mtse}{2213-0853}
{Math. Textb. Sci. Eng.}
{Mathematics Textbooks for Science and Engineering}
\DefineJournal{mta}{1006-8074}
{Math. Theory Appl. (Changsha)}
{Mathematical Theory and Applications}
\DefineJournal{mt}{1361-2042}
{Math. Today (Southend-on-Sea)}
{Mathematics Today}
\DefineJournal{mv}{1612-3786}
{Math. Vis.}
{Mathematics and Visualization}
\DefineJournal{mw}{?mw}
{Math. Wirtschaftswiss.}
{Mathematik und Wirtschaftswissenschaft}
\DefineJournal{mw}{1055-9426}
{Math. World}
{Mathematical World}
\DefineJournal{mz}{0025-5874}
{Math. Z.}
{Mathematische Zeitschrift}
\DefineJournal{m}{1222-9016}
{Mathematica}
{Mathematica}
\DefineJournal{m}{?m}
{Mathematik}
{Mathematik}
\DefineJournal{majpam}{0025-5793}
{Mathematika}
{Mathematika. A Journal of Pure and Applied Mathematics}
\DefineJournal{m}{1765-8055}
{Mathesis}
{Mathesis}
\DefineJournal{ma}{2102-5754}
{MathS in Action}
{MathematicS in Action}
\DefineJournal{msc}{1134-5632}
{Mathware Soft Comput.}
{Mathware & Soft Computing}
\DefineJournal{mbs}{2523-3041}
{MATRIX Book Ser.}
{MATRIX Book Series}
\DefineJournal{mprlhdkt}{2568-6410}
{Max Planck Res. Libr. Hist. Dev. Knowl., Textb.}
{Max Planck Research Library for the History and Development of Knowledge. Textbooks}
\DefineJournal{mshi}{?mshi}
{McGill-Queen Stud. Hist. Ideas}
{McGill-Queen's Studies in the History of Ideas}
\DefineJournal{msiems}{?msiems}
{McGraw-Hill Ser. Indust. Engrg. Management Sci.}
{McGraw-Hill Series in Industrial Engineering and Management Science}
\DefineJournal{mijtam}{0025-6455}
{Meccanica}
{Meccanica. International Journal of Theoretical and Applied Mechanics}
\DefineJournal{meis}{?meis}
{Mech. Elastic Inelastic Solids}
{Mechanics of Elastic and Inelastic Solids}
\DefineJournal{mesms}{?mesms}
{Mech. Eng. Solid Mech. Ser.}
{Mechanical Engineering and Solid Mechanics Series}
\DefineJournal{mers}{?mers}
{Mech. Engrg. Res. Stud.}
{Mechanical Engineering Research Studies}
\DefineJournal{mes}{?mes}
{Mech. Engrg. Ser.}
{Mechanical Engineering Series}
\DefineJournal{mms}{2211-0984}
{Mech. Mach. Sci.}
{Mechanisms and Machine Science}
\DefineJournal{mmmashsits}{?mmmashsits}
{Mech. Math. Methods. Ser. II: Thermal Stresses}
{Mechanics and Mathematical Methods. A Series of Handbooks. Series II: Thermal Stresses}
\DefineJournal{mf}{?mf}
{Mech. of Fracture}
{Mechanics of Fracture}
\DefineJournal{mis}{0342-4103}
{Med. Inform. Statist.}
{Medizinische Informatik und Statistik}
\DefineJournal{mjm}{1660-5446}
{Mediterr. J. Math.}
{Mediterranean Journal of Mathematics}
\DefineJournal{nanuipmmmtt}{0321-1975}
{Mekh. Tverd. Tela}
{Natsionalnaya Akademiya Nauk Ukrainy. Institut Prikladnoi Matematiki i Mekhaniki. Mekhanika Tverdogo Tela}
\DefineJournal{mams}{0065-9266}
{Mem. Amer. Math. Soc.}
{Memoirs of the American Mathematical Society}
\DefineJournal{mams}{?mams}
{Mem. Amer. Math. Soc.}
{Memoirs of the American Mathematical Society}
\DefineJournal{mdemp}{1512-0015}
{Mem. Differ. Equ. Math. Phys.}
{Memoirs on Differential Equations and Mathematical Physics}
\DefineJournal{mgssesusbm}{1342-7121}
{Mem. Grad. Sch. Sci. Eng. Shimane Univ. Ser. B Math.}
{Memoirs of the Graduate School of Science and Engineering. Shimane University. Series B. Mathematics}
\DefineJournal{miseru}{0370-4254}
{Mem. Inst. Sci. Engrg. Ritsumeikan Univ.}
{Memoirs of the Institute of Science and Engineering. Ritsumeikan University}
\DefineJournal{moit}{2188-9007}
{Mem. Osaka Inst. Tech.}
{Memoirs of Osaka Institute of Technology}
\DefineJournal{mokusinsas}{1345-7209}
{Mem. Osaka Kyoiku Univ. Ser. III Nat. Sci. Appl. Sci.}
{Memoirs of Osaka Kyoiku University. Ser. III. Natural Science and Applied Science}
\DefineJournal{armsssimssrasi}{1224-1407}
{Mem. Sect. Stiint. Acad. Romana Ser. IV}
{Academia Romana. Memoriile Sectiilor Stiintifice. Seria IV. Memoirs of the Scientific Sections. Romanian Academy. Series IV}
\DefineJournal{msmfns}{0249-633X}
{Mem. Soc. Math. Fr. (N.S.)}
{Memoires de la Societe Mathematique de France. Nouvelle Serie}
\DefineJournal{mca}{?mca}
{Meridian Crossing Aesthet.}
{Meridian: Crossing Aesthetics}
\DefineJournal{mijpallpns}{1594-6916}
{Metalogicon (N.S.)}
{Metalogicon. International Journal of Pure and Applied Logic, Linguistics and Philosophy. New Series}
\DefineJournal{mr}{?mr}
{Method. Regelungstech.}
{Methoden der Regelungstechnik}
\DefineJournal{mp}{?mp}
{Methoden Psych.}
{Methoden der Psychologie}
\DefineJournal{mra}{?mra}
{Methoden Regel. Autom.}
{Methoden der Regelungs- und Automatisierungstechnik}
\DefineJournal{mcap}{1387-5841}
{Methodol. Comput. Appl. Probab.}
{Methodology and Computing in Applied Probability}
\DefineJournal{mmr}{1618-842X}
{Methodol. Music Res.}
{Methodology of Music Research}
\DefineJournal{maa}{1073-2772}
{Methods Appl. Anal.}
{Methods and Applications of Analysis}
\DefineJournal{mfat}{1029-3531}
{Methods Funct. Anal. Topology}
{Methods of Functional Analysis and Topology}
\DefineJournal{mmb}{1064-3745}
{Methods Mol. Biol.}
{Methods in Molecular Biology}
\DefineJournal{mse}{2199-319X}
{Methods Stat. Ecol.}
{Methods in Statistical Ecology}
\DefineJournal{mor}{?mor}
{Metody Optim. Reshenii}
{Metody Optimalnykh Reshenii}
\DefineJournal{mro}{?mro}
{Metody Rascheta Obolochek}
{Metody Rascheta Obolochek}
\DefineJournal{mv}{0131-2146}
{Metody Vychisl.}
{Metody Vychislenii}
\DefineJournal{mijtas}{0026-1335}
{Metrika}
{Metrika. International Journal for Theoretical and Applied Statistics}
\DefineJournal{m}{0026-1424}
{Metron}
{Metron}
\DefineJournal{mmj}{0026-2285}
{Michigan Math. J.}
{Michigan Mathematical Journal}
\DefineJournal{mc}{1144-7605}
{Mieux Compr.}
{Mieux Comprende}
\DefineJournal{mjm}{1424-9286}
{Milan J. Math.}
{Milan Journal of Mathematics}
\DefineJournal{maqrp}{0026-4423}
{Mind}
{Mind. A Quarterly Review of Philosophy}
\DefineJournal{maos}{?maos}
{Mind Assoc. Occas. Ser.}
{Mind Association Occasional Series}
\DefineJournal{mta}{2199-1413}
{Minimax Theory Appl.}
{Minimax Theory and its Applications}
\DefineJournal{mescjrgsrpa}{?mescjrgsrpa}
{Minist. Ed. Sci. Cult. Japan Rep. Grant Aid Sci. Res. Prior. Areas}
{Ministry of Education, Science and Culture, Japan. Report of Grant-in-Aid for Scientific Research on Priority Areas}
\DefineJournal{mm}{1665-5478}
{Miscelanea Mat.}
{Miscelanea Matematica}
\DefineJournal{mmnapum}{1787-2405}
{Miskolc Math. Notes}
{Miskolc Mathematical Notes. A Publication of the University of Miskolc}
\DefineJournal{mjms}{0899-6180}
{Missouri J. Math. Sci.}
{Missouri Journal of Mathematical Sciences}
\DefineJournal{mlls}{?mlls}
{MIT Linc. Lab. Ser.}
{MIT Lincoln Laboratory Series}
\DefineJournal{tmpssm}{?tmpssm}
{MIT Press Ser. Structural Mech.}
{The MIT Press Series in Structural Mechanics}
\DefineJournal{mdm}{0947-4471}
{Mitt. Dtsch. Math.-Ver.}
{Mitteilungen der Deutschen Mathematiker-Vereinigung}
\DefineJournal{mmgh}{0340-4358}
{Mitt. Math. Ges. Hamburg}
{Mitteilungen der Mathematischen Gesellschaft in Hamburg}
\DefineJournal{mrre}{?mrre}
{Mitt. Region. Rechenzentrums Erlangen}
{Mitteilungsblatt des Regionalen Rechenzentrums Erlangen}
\DefineJournal{mmlq}{0942-5616}
{MLQ Math. Log. Q.}
{MLQ. Mathematical Logic Quarterly}
\DefineJournal{mbc}{2197-1803}
{Mod. Birkhauser Class.}
{Modern Birkhauser Classics}
\DefineJournal{msta}{2351-6046}
{Mod. Stoch. Theory Appl.}
{Modern Stochastics. Theory and Applications}
\DefineJournal{mtfe}{2424-8371}
{Mod. Trends Financ. Eng.}
{Modern Trends in Financial Engineering}
\DefineJournal{maismais}{1818-1015}
{Model. Anal. Inf. Sist.}
{Modelirovanie i Analiz Informatsionnykh Sistem. Modeling and Analysis of Information Systems}
\DefineJournal{mds}{2199-2606}
{Model. Dyn. Syst.}
{Modeling Dynamic Systems}
\DefineJournal{most}{2196-7326}
{Model. Optim. Sci. Technol.}
{Modeling and Optimization in Science and Technologies}
\DefineJournal{msset}{2164-3679}
{Model. Simul. Sci. Eng. Technol.}
{Modeling and Simulation in Science, Engineering and Technology}
\DefineJournal{masp}{2364-4015}
{Modern Acoust. Signal Process.}
{Modern Acoustics and Signal Processing}
\DefineJournal{mplapfgcnp}{0217-7323}
{Modern Phys. Lett. A}
{Modern Physics Letters A. Particles and Fields, Gravitation, Cosmology, Nuclear Physics}
\DefineJournal{mplbcmpspap}{0217-9849}
{Modern Phys. Lett. B}
{Modern Physics Letters B. Condensed Matter Physics, Statistical Physics, Applied Physics}
\DefineJournal{mls}{?mls}
{Modules Life Sci.}
{Modules in Life Sciences}
\DefineJournal{mmsap}{2364-5083}
{Mol. Model. Simul. Appl. Perspect.}
{Molecular Modeling and Simulation. Applications and Perspectives}
\DefineJournal{mm}{0026-9255}
{Monatsh. Math.}
{Monatshefte fur Mathematik}
\DefineJournal{mmj}{?mmj}
{Mong. Math. J.}
{Mongolian Mathematical Journal}
\DefineJournal{mi}{?mi}
{Monogr. Inequal.}
{Monographs in Inequalities}
\DefineJournal{mlm}{?mlm}
{Monogr. Linguist. Math.}
{Monographies de Linguistique Mathematique}
\DefineJournal{mmg}{?mmg}
{Monogr. Mat. Garcia Galdeano}
{Monografias Matematicas ``Garcia de Galdeano''}
\DefineJournal{mm}{1017-0480}
{Monogr. Math.}
{Monographs in Mathematics}
\DefineJournal{mme}{2364-8279}
{Monogr. Math. Econ.}
{Monographs in Mathematical Economics}
\DefineJournal{mmm}{?mmm}
{Monogr. Modernen Math.}
{Monographien zur Modernen Mathematik}
\DefineJournal{mnt}{1793-8341}
{Monogr. Number Theory}
{Monographs in Number Theory}
\DefineJournal{mracefqnz}{1132-6360}
{Monogr. Real Acad. Ci. Exact. Fis.-Quim. Nat. Zaragoza}
{Monografias de la Real Academia de Ciencias Exactas, Fisicas, Quimicas y Naturales de Zaragoza}
\DefineJournal{mrnm}{?mrnm}
{Monogr. Res. Notes Math.}
{Monographs and Research Notes in Mathematics}
\DefineJournal{mspms}{2446-6026}
{Monogr. Ser. Parana's Math. Soc.}
{Monograph Series of the Parana's Mathematical Society}
\DefineJournal{msap}{?msap}
{Monogr. Statist. Appl. Probab.}
{Monographs on Statistics and Applied Probability}
\DefineJournal{mtcsaes}{1431-2654}
{Monogr. Theoret. Comput. Sci. EATCS Ser.}
{Monographs in Theoretical Computer Science. An EATCS Series}
\DefineJournal{m}{?m}
{Monografia (Gliwice)}
{Monografia (Gliwice)}
\DefineJournal{mngtu}{?mngtu}
{Monografii NGTU}
{Monografii. Novosibirskii Gosudartstvennyi Tekhnicheskii Universitet}
\DefineJournal{mswre}{?mswre}
{Monographs Surveys Water Res. Engrg.}
{Monographs and Surveys in Water Resource Engineering}
\DefineJournal{mcma}{0929-9629}
{Monte Carlo Methods Appl.}
{Monte Carlo Methods and Applications}
\DefineJournal{mlm}{?mlm}
{Morningside Lect. Math.}
{Morningside Lectures in Mathematics}
\DefineJournal{mso}{?mso}
{MOS-SIAM Ser. Optim.}
{MOS-SIAM Series on Optimization}
\DefineJournal{mjcnt}{2220-5438}
{Mosc. J. Comb. Number Theory}
{Moscow Journal of Combinatorics and Number Theory}
\DefineJournal{ml}{2522-0314}
{Mosc. Lect.}
{Moscow Lectures}
\DefineJournal{mmj}{1609-3321}
{Mosc. Math. J.}
{Moscow Mathematical Journal}
\DefineJournal{mucmc}{0278-6419}
{Moscow Univ. Comput. Math. Cybernet.}
{Moscow University Computational Mathematics and Cybernetics}
\DefineJournal{mumb}{0027-1322}
{Moscow Univ. Math. Bull.}
{Moscow University Mathematics Bulletin}
\DefineJournal{mmsa}{2037-5255}
{MS&A. Model. Simul. Appl.}
{MS&A. Modeling, Simulation and Applications}
\DefineJournal{mm}{?mm}
{MSJ Mem.}
{MSJ Memoirs}
\DefineJournal{mmcl}{?mmcl}
{MSRI Math. Circ. Libr.}
{MSRI Mathematical Circles Library}
\DefineJournal{mcdm}{2366-0023}
{Mult. Criteria Decis. Mak.}
{Multiple Criteria Decision Making}
\DefineJournal{msd}{1384-5640}
{Multibody Syst. Dyn.}
{Multibody System Dynamics}
\DefineJournal{msspaij}{0923-6082}
{Multidimens. Syst. Signal Process.}
{Multidimensional Systems and Signal Processing. An International Journal}
\DefineJournal{mm}{1877-0274}
{Multiphys. Model.}
{Multiphysics Modeling}
\DefineJournal{mmsasij}{1540-3459}
{Multiscale Model. Simul.}
{Multiscale Modeling & Simulation. A SIAM Interdisciplinary Journal}
\DefineJournal{mlm}{2523-5230}
{Munst. Lect. Math.}
{Munster Lectures in Mathematics}
\DefineJournal{mjm}{1867-5778}
{Munster J. Math.}
{Munster Journal of Mathematics}
\DefineJournal{naaj}{1092-0277}
{N. Am. Actuar. J.}
{North American Actuarial Journal}
\DefineJournal{nawgimk}{?nawgimk}
{Nachr. Akad. Wiss. Gottingen II. Math. Phys. Kl.}
{Nachrichten der Akademie der Wissenschaften in Gottingen II: Mathematisch-Physikalische Klasse}
\DefineJournal{nawgimk}{?nawgimk}
{Nachr. Akad. Wiss. Gottingen II: Math. Phys. Kl. 1983}
{Nachrichten der Akademie der Wissenschaften in Gottingen II: Mathematisch-Physikalische Klasse 1983}
\DefineJournal{nmj}{0027-7630}
{Nagoya Math. J.}
{Nagoya Mathematical Journal}
\DefineJournal{ndxsbknujmb}{0469-5097}
{Nanjing Daxue Xuebao Shuxue Bannian Kan}
{Nanjing Daxue Xuebao. Shuxue Bannian Kan. Nanjing University. Journal. Mathematical Biquarterly}
\DefineJournal{}{?}
{Nanjing Shida Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Nanjing Univ. J. Math. Biquarterly}
{nan}
\DefineJournal{nspamtp}{?nspamtp}
{Nankai Ser. Pure Appl. Math. Theoret. Phys.}
{Nankai Series in Pure, Applied Mathematics and Theoretical Physics}
\DefineJournal{ntm}{1793-1118}
{Nankai Tracts Math.}
{Nankai Tracts in Mathematics}
\DefineJournal{n}{?n}
{Nano}
{Nano}
\DefineJournal{nsmmta}{2299-3290}
{Nanoscale Syst. Math. Model. Theory Appl.}
{Nanoscale Systems. Mathematical Modeling, Theory and Applications}
\DefineJournal{nt}{1434-4904}
{NanoSci. Technol.}
{NanoScience and Technology}
\DefineJournal{nmsse}{1860-0131}
{NASA Monogr. Syst. Softw. Eng.}
{NASA Monographs in Systems and Software Engineering}
\DefineJournal{nasl}{0250-541X}
{Nat. Acad. Sci. Lett.}
{National Academy Science Letters}
\DefineJournal{ncaij}{1567-7818}
{Nat. Comput.}
{Natural Computing. An International Journal}
\DefineJournal{ncs}{1619-7127}
{Nat. Comput. Ser.}
{Natural Computing Series}
\DefineJournal{nrm}{0890-8575}
{Nat. Resour. Model.}
{Natural Resource Modeling}
\DefineJournal{nasisals}{?nasisals}
{NATO Adv. Sci. Inst. Ser. A Life Sci.}
{NATO Advanced Science Institutes Series A: Life Sciences}
\DefineJournal{ncms}{?ncms}
{NATO Challenges Modern Soc.}
{NATO Challenges of Modern Society}
\DefineJournal{ncsims}{?ncsims}
{NATO Conf. Ser. IV: Marine Sci.}
{NATO Conference Series IV: Marine Sciences}
\DefineJournal{ncsvms}{?ncsvms}
{NATO Conf. Ser. VI: Materials Sci.}
{NATO Conference Series VI: Materials Science}
\DefineJournal{nspssdics}{1874-6268}
{NATO Sci. Peace Secur. Ser. D Inf. Commun. Secur.}
{NATO Science for Peace and Security Series D: Information and Communication Security}
\DefineJournal{nsrou}{0029-8190}
{Natur. Sci. Rep. Ochanomizu Univ.}
{Natural Science Report of the Ochanomizu University}
\DefineJournal{ncc}{?ncc}
{Natural Comm. Comput.}
{Natural Communications with Computers}
\DefineJournal{ntp}{?ntp}
{Nauka i Tekhn. Progress}
{Nauka i Tekhnicheskii Progress}
\DefineJournal{ntp}{?ntp}
{Nauka i Tekhn. Progress}
{Nauka i Tekhnicheskii Progress}
\DefineJournal{nrl}{0894-069X}
{Naval Res. Logist.}
{Naval Research Logistics}
\DefineJournal{anberm}{?anberm}
{NBER Monogr.}
{A National Bureau of Economic Research Monograph}
\DefineJournal{ncs}{2523-3343}
{Necas Center Ser.}
{Necas Center Series}
\DefineJournal{nris}{?nris}
{Needham Res. Inst. Stud.}
{Needham Research Institute Studies}
\DefineJournal{nd}{1816-448X}
{Nelinein. Din.}
{Nelineinaya Dinamika}
\DefineJournal{nk}{1562-3076}
{Neliniini Koliv.}
{Neliniini Kolivannya}
\DefineJournal{tnmsr}{2392-411X}
{Nepali Math. Sci. Rep.}
{The Nepali Mathematical Sciences Report}
\DefineJournal{nhm}{1556-1801}
{Netw. Heterog. Media}
{Networks and Heterogeneous Media}
\DefineJournal{nse}{1566-113X}
{Netw. Spat. Econ.}
{Networks and Spatial Economics}
\DefineJournal{nts}{?nts}
{Netw. Telecommun. Ser.}
{Networks and Telecommunications Series}
\DefineJournal{naij}{0028-3045}
{Networks}
{Networks. An International Journal}
\DefineJournal{nc}{0899-7667}
{Neural Comput.}
{Neural Computation}
\DefineJournal{nips}{?nips}
{Neural Inf. Process. Ser.}
{Neural Information Processing Series}
\DefineJournal{npsc}{1061-5369}
{Neural Parallel Sci. Comput.}
{Neural, Parallel & Scientific Computations}
\DefineJournal{n}{?n}
{Neuroscience}
{Neuroscience}
\DefineJournal{ndqti}{?ndqti}
{New Dev. Quant. Trading Invest.}
{New Developments in Quantitative Trading and Investment}
\DefineJournal{ndps}{?ndps}
{New Dir. Philos. Sci.}
{New Directions in the Philosophy of Science}
\DefineJournal{new}{2039-411X}
{New Econ. Windows}
{New Economic Windows}
\DefineJournal{nfrsap}{2199-5974}
{New Front. Reg. Sci. Asian Perspect.}
{New Frontiers in Regional Science: Asian Perspectives}
\DefineJournal{njp}{1367-2630}
{New J. Phys.}
{New Journal of Physics}
\DefineJournal{nmm}{?nmm}
{New Math. Monogr.}
{New Mathematical Monographs}
\DefineJournal{nmnc}{1793-0057}
{New Math. Nat. Comput.}
{New Mathematics and Natural Computation}
\DefineJournal{nsaich}{?nsaich}
{New Stud. Am. Intellect. Cult. Hist.}
{New Studies in American Intellectual and Cultural History}
\DefineJournal{ntms}{2147-5520}
{New Trends Math. Sci.}
{New Trends in Mathematical Sciences}
\DefineJournal{nyjm}{1076-9803}
{New York J. Math.}
{New York Journal of Mathematics}
\DefineJournal{nzjm}{1171-6096}
{New Zealand J. Math.}
{New Zealand Journal of Mathematics}
\DefineJournal{nnms}{?nnms}
{Newsl. Nepal Math. Soc.}
{Newsletter. Nepal Mathematical Society}
\DefineJournal{nawvs}{0028-9825}
{Nieuw Arch. Wiskd. (5)}
{Nieuw Archief voor Wiskunde. Vijfde Serie}
\DefineJournal{nmj}{1341-9951}
{Nihonkai Math. J.}
{Nihonkai Mathematical Journal}
\DefineJournal{nls}{1793-9402}
{Nobel Laureate Ser.}
{Nobel Laureate Series}
\DefineJournal{nndea}{1021-9722}
{NoDEA Nonlinear Differential Equations Appl.}
{NoDEA. Nonlinear Differential Equations and Applications}
\DefineJournal{nds}{2353-0626}
{Nonauton. Dyn. Syst.}
{Nonautonomous Dynamical Systems}
\DefineJournal{natmaaimj}{0362-546X}
{Nonlinear Anal.}
{Nonlinear Analysis. Theory, Methods & Applications. An International Multidisciplinary Journal}
\DefineJournal{nafaij}{1226-7228}
{Nonlinear Anal. Forum}
{Nonlinear Analysis Forum. An International Journal}
\DefineJournal{nahs}{1751-570X}
{Nonlinear Anal. Hybrid Syst.}
{Nonlinear Analysis. Hybrid Systems}
\DefineJournal{namc}{1392-5113}
{Nonlinear Anal. Model. Control}
{Nonlinear Analysis. Modelling and Control}
\DefineJournal{narwaaimj}{1468-1218}
{Nonlinear Anal. Real World Appl.}
{Nonlinear Analysis. Real World Applications. An International Multidisciplinary Journal}
\DefineJournal{ndpls}{1090-0578}
{Nonlinear Dyn. Psychol. Life Sci.}
{Nonlinear Dynamics, Psychology, and Life Sciences}
\DefineJournal{ndstaijrs}{1562-8353}
{Nonlinear Dyn. Syst. Theory}
{Nonlinear Dynamics and Systems Theory. An International Journal of Research and Surveys}
\DefineJournal{nps}{1867-8440}
{Nonlinear Phys. Sci.}
{Nonlinear Physical Science}
\DefineJournal{nstij}{1359-8678}
{Nonlinear Stud.}
{Nonlinear Studies. The International Journal}
\DefineJournal{nsc}{2195-9994}
{Nonlinear Syst. Complex.}
{Nonlinear Systems and Complexity}
\DefineJournal{ntsc}{?ntsc}
{Nonlinear Time Ser. Chaos}
{Nonlinear Time Series and Chaos}
\DefineJournal{n}{0951-7715}
{Nonlinearity}
{Nonlinearity}
\DefineJournal{nws}{2520-1514}
{Nordic Wittgenstein Stud.}
{Nordic Wittgenstein Studies}
\DefineJournal{nnmt}{0801-3500}
{Normat}
{Normat. Nordisk Matematisk Tidskrift}
\DefineJournal{nsamm}{?nsamm}
{North-Holland Ser. Appl. Math. Mech.}
{North-Holland Series in Applied Mathematics and Mechanics}
\DefineJournal{nejm}{2496-5170}
{North-West. Eur. J. Math.}
{North-Western European Journal of Mathematics}
\DefineJournal{ni}{?ni}
{Not. ISMS}
{Notices from the ISMS}
\DefineJournal{nsamsmsw}{?nsamsmsw}
{Not. S. Afr. Math. Soc.}
{Notices of the South African Mathematical Society. Mededelings van die Suid-Afrikaanse Wiskundevereniging}
\DefineJournal{naa}{0078-2009}
{Notas Algebra Anal.}
{Notas de Algebra y Analisis}
\DefineJournal{ncm}{?ncm}
{Notas Comun. Mat.}
{Notas e Comunicacoes de Matematica}
\DefineJournal{nimeuspsm}{?nimeuspsm}
{Notas Inst. Mat. Estatist. Univ. Sao Paulo Ser. Mat.}
{Notas do Instituto de Matematica e Estatistica da Universidade de Sao Paulo, Serie Matematica}
\DefineJournal{nma}{2236-5915}
{Notas Mat. Apl.}
{Notas em Matematica Aplicada}
\DefineJournal{nm}{1123-2536}
{Note Mat.}
{Note di Matematica}
\DefineJournal{nrtrsjhs}{0035-9149}
{Notes and Rec.}
{Notes and Records. The Royal Society Journal of the History of Science}
\DefineJournal{nnfmmd}{1612-2909}
{Notes Numer. Fluid Mech. Multidiscip. Des.}
{Notes on Numerical Fluid Mechanics and Multidisciplinary Design}
\DefineJournal{nams}{0002-9920}
{Notices Amer. Math. Soc.}
{Notices of the American Mathematical Society}
\DefineJournal{ndjfl}{0029-4527}
{Notre Dame J. Form. Log.}
{Notre Dame Journal of Formal Logic}
\DefineJournal{n}{0029-4624}
{Nous}
{Nous}
\DefineJournal{nbm}{?nbm}
{Nouv. Bibl. Math.}
{Nouvelle Bibliotheque Mathematique}
\DefineJournal{n}{?n}
{NTG-Fachber.}
{NTG-Fachberichte}
\DefineJournal{nppp}{2405-6014}
{Nuclear Part. Phys. Proc.}
{Nuclear and Particle Physics Proceedings}
\DefineJournal{npbtpehepqftss}{0550-3213}
{Nuclear Phys. B}
{Nuclear Physics. B. Theoretical, Phenomenological, and Experimental High Energy Physics. Quantum Field Theory and Statistical Systems}
\DefineJournal{naco}{2155-3289}
{Numer. Algebra Control Optim.}
{Numerical Algebra, Control and Optimization}
\DefineJournal{na}{1017-1398}
{Numer. Algorithms}
{Numerical Algorithms}
\DefineJournal{naa}{1995-4239}
{Numer. Anal. Appl.}
{Numerical Analysis and Applications}
\DefineJournal{nfaoaij}{0163-0563}
{Numer. Funct. Anal. Optim.}
{Numerical Functional Analysis and Optimization. An International Journal}
\DefineJournal{ni}{1028-5350}
{Numer. Insights}
{Numerical Insights}
\DefineJournal{nlaa}{1070-5325}
{Numer. Linear Algebra Appl.}
{Numerical Linear Algebra with Applications}
\DefineJournal{nm}{0029-599X}
{Numer. Math.}
{Numerische Mathematik}
\DefineJournal{nmajcugxjsx}{1000-081X}
{Numer. Math. J. Chinese Univ.}
{Numerical Mathematics. A Journal of Chinese Universities. Gaodeng Xuexiao Jisuan Shuxue Xuebao}
\DefineJournal{nmsc}{?nmsc}
{Numer. Math. Sci. Comput.}
{Numerical Mathematics and Scientific Computation}
\DefineJournal{nmtma}{1004-8979}
{Numer. Math. Theory Methods Appl.}
{Numerical Mathematics. Theory, Methods and Applications}
\DefineJournal{nmpdeaij}{0749-159X}
{Numer. Methods Partial Differential Equations}
{Numerical Methods for Partial Differential Equations. An International Journal}
\DefineJournal{nh}{?nh}
{Nutshell Handbook}
{Nutshell Handbook}
\DefineJournal{nw}{?nw}
{NWB-Studienbuch. Wirtschaftswissenschaft.}
{NWB-Studienbucher Wirtschaftswissenschaften}
\DefineJournal{oosi}{2190-6807}
{OASIcs OpenAccess Ser. Inform.}
{OASIcs: OpenAccess Series in Informatics}
\DefineJournal{or}{1660-8933}
{Oberwolfach Rep.}
{Oberwolfach Reports}
\DefineJournal{os}{1661-237X}
{Oberwolfach Semin.}
{Oberwolfach Seminars}
\DefineJournal{dmfasomfi}{0473-7466}
{Obzornik Mat. Fiz.}
{Drustvo Matematikov, Fizikov in Astronomov Slovenije. Obzornik za Matematiko in Fiziko. Izdaja}
\DefineJournal{op}{?op}
{Occasional Papers}
{Occasional Papers}
\DefineJournal{oeo}{2194-6396}
{Ocean Eng. Oceanogr.}
{Ocean Engineering & Oceanography}
\DefineJournal{ot}{1867-4208}
{On Think.}
{On Thinking}
\DefineJournal{ojac}{1931-3365}
{Online J. Anal. Comb.}
{Online Journal of Analytic Combinatorics}
\DefineJournal{oml}{2198-2341}
{Ontos Math. Log.}
{Ontos Mathematical Logic}
\DefineJournal{obj}{1875-0362}
{Open Bioinform. J.}
{Open Bioinformatics Journal}
\DefineJournal{tobs}{?tobs}
{Open Book Ser.}
{The Open Book Series}
\DefineJournal{ocsj}{1874-110X}
{Open Cybern. Syst. J.}
{Open Cybernetics and Systemics Journal}
\DefineJournal{om}{2391-5455}
{Open Math.}
{Open Mathematics}
\DefineJournal{omj}{1874-1177}
{Open Math. J.}
{Open Mathematics Journal}
\DefineJournal{onmj}{1876-3898}
{Open Numer. Methods J.}
{Open Numerical Methods Journal}
\DefineJournal{osid}{1230-1612}
{Open Syst. Inf. Dyn.}
{Open Systems & Information Dynamics}
\DefineJournal{om}{1846-3886}
{Oper. Matrices}
{Operators and Matrices}
\DefineJournal{opss}{?opss}
{Oper. Program. Systems Ser.}
{Operating and Programming Systems Series}
\DefineJournal{or}{0030-364X}
{Oper. Res.}
{Operations Research}
\DefineJournal{orl}{0167-6377}
{Oper. Res. Lett.}
{Operations Research Letters}
\DefineJournal{orp}{2214-7160}
{Oper. Res. Perspect.}
{Operations Research Perspectives}
\DefineJournal{orp}{0721-5924}
{Oper. Res. Proc.}
{Operations Research Proceedings}
\DefineJournal{ors}{?ors}
{Oper. Res. Ser.}
{Operations Research Series}
\DefineJournal{ortyx}{1007-6093}
{Oper. Res. Trans.}
{Operations Research Transactions. Yunchouxue Xuebao}
\DefineJournal{orsis}{1387-666X}
{Oper. Res./Comput. Sci. Interfaces Ser.}
{Operations Research/Computer Science Interfaces Series}
\DefineJournal{otaa}{0255-0156}
{Oper. Theory Adv. Appl.}
{Operator Theory: Advances and Applications}
\DefineJournal{oqjorsi}{0030-3887}
{Opsearch}
{Opsearch. Quarterly Journal of the Operational Research Society of India}
\DefineJournal{oeimjpotaes}{1389-4420}
{Optim. Eng.}
{Optimization and Engineering. International Multidisciplinary Journal to Promote Optimization Theory & Applications in Engineering Sciences}
\DefineJournal{ol}{1862-4472}
{Optim. Lett.}
{Optimization Letters}
\DefineJournal{oms}{1055-6788}
{Optim. Methods Softw.}
{Optimization Methods & Software}
\DefineJournal{ocam}{0143-2087}
{Optimal Control Appl. Methods}
{Optimal Control Applications & Methods}
\DefineJournal{oajmpor}{0233-1934}
{Optimization}
{Optimization. A Journal of Mathematical Programming and Operations Research}
\DefineJournal{om}{1232-9274}
{Opuscula Math.}
{Opuscula Mathematica}
\DefineJournal{osqam}{0171-6468}
{OR Spectrum}
{OR Spectrum. Quantitative Approaches in Management}
\DefineJournal{oajtosa}{0167-8094}
{Order}
{Order. A Journal on the Theory of Ordered Sets and its Applications}
\DefineJournal{ovsp}{?ovsp}
{Organiz. Vychisl. Struktur. Process.}
{Organizatsiya Vychislitelnykh Struktur i Protsessov}
\DefineJournal{ovsp}{?ovsp}
{Organiz. Vycisl. Struktur. Process.}
{Organizatsiya Vychislitelnykh Struktur i Protsessov}
\DefineJournal{o}{?o}
{Orientierungshilfen}
{Orientierungshilfen}
\DefineJournal{ojm}{0030-6126}
{Osaka J. Math.}
{Osaka Journal of Mathematics}
\DefineJournal{osmrdmm}{?osmrdmm}
{Osnabruck. Schrift. Math. Reihe D Math.-Didakt. Manuskr.}
{Osnabrucker Schriften zur Mathematik. Reihe D: Mathematisch-Didaktische Manuskripte}
\DefineJournal{osmrii}{?osmrii}
{Osnabruck. Schrift. Math. Reihe I Inform.}
{Osnabrucker Schriften zur Mathematik. Reihe I: Informatik}
\DefineJournal{osmrpp}{?osmrpp}
{Osnabruck. Schrift. Math. Reihe P Preprints}
{Osnabrucker Schriften zur Mathematik. Reihe P: Preprints}
\DefineJournal{osmrumm}{?osmrumm}
{Osnabruck. Schrift. Math. Reihe U Mater. Mathematikunterr.}
{Osnabrucker Schriften zur Mathematik. Reihe U: Materialien zum Mathematikunterricht}
\DefineJournal{ocl}{2211-2758}
{Outst. Contrib. Log.}
{Outstanding Contributions to Logic}
\DefineJournal{op}{?op}
{Ouvert. Philos.}
{Ouverture Philosophique}
\DefineJournal{octps}{?octps}
{Oxf. Class. Texts Phys. Sci.}
{Oxford Classic Texts in the Physical Sciences}
\DefineJournal{ogt}{?ogt}
{Oxf. Grad. Texts}
{Oxford Graduate Texts}
\DefineJournal{ogtm}{?ogtm}
{Oxf. Grad. Texts Math.}
{Oxford Graduate Texts in Mathematics}
\DefineJournal{omsp}{?omsp}
{Oxf. Master Ser. Phys.}
{Oxford Master Series in Physics}
\DefineJournal{omssctp}{?omssctp}
{Oxf. Master Ser. Stat. Comput. Theor. Phys.}
{Oxford Master Series in Statistical Computational, and Theoretical Physics}
\DefineJournal{opm}{?opm}
{Oxf. Philos. Monogr.}
{Oxford Philosophical Monographs}
\DefineJournal{osps}{?osps}
{Oxf. Stud. Philos. Sci.}
{Oxford Studies in Philosophy of Science}
\DefineJournal{ostl}{?ostl}
{Oxf. Stud. Theor. Linguist.}
{Oxford Studies in Theoretical Linguistics}
\DefineJournal{olsma}{?olsma}
{Oxford Lecture Ser. Math. Appl.}
{Oxford Lecture Series in Mathematics and its Applications}
\DefineJournal{olg}{?olg}
{Oxford Logic Guides}
{Oxford Logic Guides}
\DefineJournal{omm}{?omm}
{Oxford Math. Monogr.}
{Oxford Mathematical Monographs}
\DefineJournal{nuaa}{2070-0466}
{p-Adic Numbers Ultrametric Anal. Appl.}
{p-Adic Numbers, Ultrametric Analysis, and Applications}
\DefineJournal{ppaa}{1433-7541}
{PAA Pattern Anal. Appl.}
{PAA. Pattern Analysis and Applications}
\DefineJournal{pjam}{1941-3963}
{Pac. J. Appl. Math.}
{Pacific Journal of Applied Mathematics}
\DefineJournal{pjmi}{2198-4115}
{Pac. J. Math. Ind.}
{Pacific Journal of Mathematics for Industry}
\DefineJournal{pjoaij}{1348-9151}
{Pac. J. Optim.}
{Pacific Journal of Optimization. An International Journal}
\DefineJournal{pjm}{0030-8730}
{Pacific J. Math.}
{Pacific Journal of Mathematics}
\DefineJournal{ptv}{2504-3625}
{Pageoph Top. Vol.}
{Pageoph Topical Volumes}
\DefineJournal{pjsor}{1816-2711}
{Pak. J. Stat. Oper. Res.}
{Pakistan Journal of Statistics and Operation Research}
\DefineJournal{pjs}{1012-9367}
{Pakistan J. Statist.}
{Pakistan Journal of Statistics}
\DefineJournal{pjm}{2219-5688}
{Palest. J. Math.}
{Palestine Journal of Mathematics}
\DefineJournal{pte}{?pte}
{Palgrave Texts Econom.}
{Palgrave Texts in Econometrics}
\DefineJournal{ppamm}{1617-7061}
{PAMM. Proc. Appl. Math. Mech.}
{PAMM. Proceedings in Applied Mathematics and Mechanics}
\DefineJournal{pmj}{1064-9735}
{PanAmer. Math. J.}
{PanAmerican Mathematical Journal}
\DefineJournal{ps}{1272-3835}
{Panor. Syntheses}
{Panoramas et Syntheses}
\DefineJournal{pcsa}{0167-8191}
{Parallel Comput.}
{Parallel Computing. Systems & Applications}
\DefineJournal{pdcs}{?pdcs}
{Parallel Distrib. Comput. Ser.}
{Parallel and Distributed Computing Series}
\DefineJournal{ppl}{0129-6264}
{Parallel Process. Lett.}
{Parallel Processing Letters}
\DefineJournal{pts}{1567-827X}
{Part. Technol. Ser.}
{Particle Technology Series}
\DefineJournal{pdemt}{?pdemt}
{Partial Differ. Equ. Meas. Theory}
{Partial Differential Equations and Measure Theory}
\DefineJournal{pfs}{?pfs}
{Particles and Fields Subser.}
{Particles and Fields Subseries}
\DefineJournal{pm}{2367-3451}
{Pathw. Math.}
{Pathways in Mathematics}
\DefineJournal{pusm}{2010-2240}
{Peking Univ. Ser. Math.}
{Peking University Series in Mathematics}
\DefineJournal{psn}{?psn}
{Pergamon Stud. Neurosci.}
{Pergamon Studies in Neuroscience}
\DefineJournal{pmhjjbms}{0031-5303}
{Period. Math. Hungar.}
{Periodica Mathematica Hungarica. Journal of the Janos Bolyai Mathematical Society}
\DefineJournal{pl}{?pl}
{Perspect. Log.}
{Perspectives in Logic}
\DefineJournal{pshps}{1063-6145}
{Perspect. Sci.}
{Perspectives on Science. Historical, Philosophical, Social}
\DefineJournal{pm}{?pm}
{Perspekt. Math.didakt.}
{Perspektiven der Mathematikdidaktik}
\DefineJournal{prvt}{?prvt}
{Perspekt. Razvit. Vychisl. Tekh.}
{Perspektivy Razvitiya Vychislitelnoi Tekhniki}
\DefineJournal{p}{?p}
{Petrokhim.}
{Petrokhimiya}
\DefineJournal{paa}{2198-2066}
{Philos. Anal.}
{Philosophische Analyse/Philosophical Analysis}
\DefineJournal{pa}{?pa}
{Philos. Antiq.}
{Philosophia Antiqua}
\DefineJournal{pmsi}{0031-8019}
{Philos. Math. (3)}
{Philosophia Mathematica. Series III}
\DefineJournal{pm}{?pm}
{Philos. Mediev.}
{Philosophes Medievaux}
\DefineJournal{ppasn}{1520-8583}
{Philos. Perspect.}
{Philosophical Perspectives. A Supplement to Nous}
\DefineJournal{ps}{0031-8248}
{Philos. Sci.}
{Philosophy of Science}
\DefineJournal{tpsep}{?tpsep}
{Philos. Sci. Eur. Perspect.}
{The Philosophy of Science in a European Perspective}
\DefineJournal{pstsp}{1281-2463}
{Philos. Sci. (Paris)}
{Philosophia Scientiae. Travaux d'Histoire des Sciences et de Philosophie}
\DefineJournal{psaijpat}{0031-8116}
{Philos. Stud.}
{Philosophical Studies. An International Journal for Philosophy in the Analytic Tradition}
\DefineJournal{pss}{0921-8599}
{Philos. Stud. Ser.}
{Philosophical Studies Series}
\DefineJournal{ptrsampes}{1364-503X}
{Philos. Trans. Roy. Soc. A}
{Philosophical Transactions of the Royal Society A. Mathematical, Physical and Engineering Sciences}
\DefineJournal{pmshpsci}{?pmshpsci}
{PHISPC Monogr. Ser. Hist. Philos. Sci. Cult. India}
{PHISPC Monograph Series on History of Philosophy, Science and Culture in India}
\DefineJournal{pasma}{0378-4371}
{Phys. A}
{Physica A. Statistical Mechanics and its Applications}
\DefineJournal{pdnp}{0167-2789}
{Phys. D}
{Physica D. Nonlinear Phenomena}
\DefineJournal{pese}{1610-1677}
{Phys. Earth Space Environ.}
{Physics of Earth and Space Environments}
\DefineJournal{pla}{0375-9601}
{Phys. Lett. A}
{Physics Letters. A}
\DefineJournal{plbppnpc}{0370-2693}
{Phys. Lett. B}
{Physics Letters. B. Particle Physics, Nuclear Physics and Cosmology}
\DefineJournal{pm}{?pm}
{Phys. Monogr.}
{Physikalische Monographien}
\DefineJournal{prarspl}{0370-1573}
{Phys. Rep.}
{Physics Reports. A Review Section of Physics Letters}
\DefineJournal{pra}{2469-9926}
{Phys. Rev. A}
{Physical Review A}
\DefineJournal{prd}{2470-0010}
{Phys. Rev. D}
{Physical Review D}
\DefineJournal{pre}{2470-0045}
{Phys. Rev. E}
{Physical Review E}
\DefineJournal{prl}{0031-9007}
{Phys. Rev. Lett.}
{Physical Review Letters}
\DefineJournal{pwd}{2399-2891}
{Phys. World Discov.}
{Physics World Discovery}
\DefineJournal{pissns}{0031-9414}
{Physis Riv. Internaz. Storia Sci. (N.S.)}
{Physis---Rivista Internazionale di Storia della Scienza. Nuova Serie}
\DefineJournal{pmej}{0031-952X}
{Pi Mu Epsilon J.}
{Pi Mu Epsilon Journal}
\DefineJournal{psm}{0204-9805}
{Pliska Stud. Math.}
{Pliska Studia Mathematica}
\DefineJournal{pukntm}{0204-5249}
{Plovdiv. Univ. Paisii Khilendarski Nauchn. Trud. Mat.}
{Plovdivski Universitet ``Paisii Khilendarski''. Nauchni Trudove. Matematika}
\DefineJournal{pan}{?pan}
{Podstaw. Algorytmy Numer.}
{Podstawowe Algorytmy Numeryczne}
\DefineJournal{pjaa}{2349-6789}
{Poincare J. Anal. Appl.}
{Poincare Journal of Analysis and Applications}
\DefineJournal{ubsbsaamp}{1223-7027}
{Politehn. Univ. Bucharest Sci. Bull. Ser. A Appl. Math. Phys.}
{``Politehnica'' University of Bucharest. Scientific Bulletin. Series A. Applied Mathematics and Physics}
\DefineJournal{pss}{2509-6796}
{PoliTO Springer Ser.}
{PoliTO Springer Series}
\DefineJournal{pst}{?pst}
{Polymer Sci. Tech.}
{Polymer Science and Technology}
\DefineJournal{pcb}{?pcb}
{Population Community Biol.}
{Population and Community Biology}
\DefineJournal{pmajpms}{0032-5155}
{Port. Math.}
{Portugaliae Mathematica. A Journal of the Portuguese Mathematical Society}
\DefineJournal{paimjdtap}{1385-1292}
{Positivity}
{Positivity. An International Mathematics Journal Devoted to Theory and Applications of Positivity}
\DefineJournal{psf}{?psf}
{Postdiplom. Sem. Fiz.}
{Postdiplomski Seminar iz Fizike}
\DefineJournal{paaijdiptptgfa}{0926-2601}
{Potential Anal.}
{Potential Analysis. An International Journal Devoted to the Interactions between Potential Theory, Probability Theory, Geometry and Functional Analysis}
\DefineJournal{pfnrb}{?pfnrb}
{Potsdamer Forsch. Naturwiss. Reihe B}
{Potsdamer Forschungen. Naturwissenschaftliche Reihe B.}
\DefineJournal{peps}{2196-3185}
{Power Electron. Power Syst.}
{Power Electronics and Power Systems}
\DefineJournal{ps}{1612-1287}
{Power Syst.}
{Power Systems}
\DefineJournal{pimnanumz}{?pimnanumz}
{Pr. Inst. Mat. Nats. Akad. Nauk Ukr. Mat. Zastos.}
{Pratsi Institutu Matematiki Natsionalnoi Akademii Nauk Ukraini. Matematika ta ii Zastosuvannya}
\DefineJournal{pi}{?pi}
{Prace IPPT 83}
{Prace IPPT 83}
\DefineJournal{pir}{0208-5658}
{Prace IPPT/IFTR Rep.}
{Prace IPPT/IFTR Reports}
\DefineJournal{pniispw}{?pniispw}
{Prace Nauk. Inst. Inform. Stosow. Politech. Wroc.}
{Prace Naukowe Instytutu Informatyki Stosowanej Politechniki Wroclawskiej}
\DefineJournal{ps}{?ps}
{Pract. Ser.}
{Practitioner Series}
\DefineJournal{pcem}{?pcem}
{Prem. Cycle Etud. Med.}
{Premier Cycle des Etudes Medicales}
\DefineJournal{phisss}{?phisss}
{Prentice Hall Inform. System Sci. Ser.}
{Prentice Hall Information and System Sciences Series}
\DefineJournal{phiscsse}{?phiscsse}
{Prentice Hall Internat. Ser. Comput. Systems Sci. Engrg.}
{Prentice Hall International Series in Computer Systems Science and Engineering}
\DefineJournal{phsact}{?phsact}
{Prentice Hall Ser. Adv. Commun. Technol.}
{Prentice Hall Series in Advanced Communications Technologies}
\DefineJournal{phscs}{?phscs}
{Prentice Hall Ser. Comput. Sci.}
{Prentice Hall Series in Computer Science}
\DefineJournal{phss}{?phss}
{Prentice Hall Ser. Statist.}
{Prentice Hall Series in Statistics}
\DefineJournal{phstm}{?phstm}
{Prentice Hall Ser. Tech. Math.}
{Prentice Hall Series in Technical Mathematics}
\DefineJournal{phss}{?phss}
{Prentice Hall Software Ser.}
{Prentice Hall Software Series}
\DefineJournal{pp}{?pp}
{Prentice Pract.}
{Prentice Practica}
\DefineJournal{p}{?p}
{Prepubl.}
{Prepublication}
\DefineJournal{pdm}{2071-0410}
{Prikl. Diskretn. Mat.}
{Prikladnaya Diskretnaya Matematika}
\DefineJournal{ranpmm}{0032-8235}
{Prikl. Mat. Mekh.}
{Rossiiskaya Akademiya Nauk. Prikladnaya Matematika i Mekhanika}
\DefineJournal{popbncsnmbs}{1857-9027}
{Pril. Odd. Prir.-Mat. Biotekhnichki Nauki}
{Prilozi. Oddelenie za Prirodno-Matematichki i Biotekhnichki Nauki. Contributions. Section of Natural, Mathematical and Biotechnical Sciences}
\DefineJournal{pcs}{?pcs}
{Primers Complex Syst.}
{Primers in Complex Systems}
\DefineJournal{pfcp}{?pfcp}
{Princet. Found. Contemp. Philos.}
{Princeton Foundations of Contemporary Philosophy}
\DefineJournal{pll}{?pll}
{Princet. Leg. Libr.}
{Princeton Legacy Library}
\DefineJournal{plsg}{?plsg}
{Princet. Lifesav. Study Guide}
{Princeton Lifesaver Study Guide}
\DefineJournal{psf}{?psf}
{Princet. Ser. Finance}
{Princeton Series in Finance}
\DefineJournal{pms}{?pms}
{Princeton Math. Ser.}
{Princeton Mathematical Series}
\DefineJournal{psl}{?psl}
{Princeton Sci. Lib.}
{Princeton Science Library}
\DefineJournal{psam}{?psam}
{Princeton Ser. Appl. Math.}
{Princeton Series in Applied Mathematics}
\DefineJournal{pstcb}{?pstcb}
{Princeton Ser. Theor. Comput. Biol.}
{Princeton Series in Theoretical and Computational Biology}
\DefineJournal{pa}{2297-0371}
{Probab. Appl.}
{Probability and its Applications}
\DefineJournal{pay}{1431-7028}
{Probab. Appl. (N. Y.)}
{Probability and its Applications (New York)}
\DefineJournal{peis}{0269-9648}
{Probab. Engrg. Inform. Sci.}
{Probability in the Engineering and Informational Sciences}
\DefineJournal{pms}{0208-4147}
{Probab. Math. Statist.}
{Probability and Mathematical Statistics}
\DefineJournal{ps}{1549-5787}
{Probab. Surv.}
{Probability Surveys}
\DefineJournal{ptrf}{0178-8051}
{Probab. Theory Related Fields}
{Probability Theory and Related Fields}
\DefineJournal{ptsm}{2199-3130}
{Probab. Theory Stoch. Model.}
{Probability Theory and Stochastic Modelling}
\DefineJournal{puqr}{2367-0126}
{Probab. Uncertain. Quant. Risk}
{Probability, Uncertainty and Quantitative Risk}
\DefineJournal{paia}{2306-3424}
{Probl. Anal. Issues Anal.}
{Problemy Analiza. Issues of Analysis}
\DefineJournal{pbm}{0941-3502}
{Probl. Books in Math.}
{Problem Books in Mathematics}
\DefineJournal{pfmt}{2077-8708}
{Probl. Fiz. Mat. Tekh.}
{Problemy Fiziki, Matematiki i Tekhniki}
\DefineJournal{pgo}{?pgo}
{Probl. Globale Omen.}
{Probleme Globale ale Omenirii}
\DefineJournal{pit}{0032-9460}
{Probl. Inf. Transm.}
{Problems of Information Transmission}
\DefineJournal{pmfspl}{?pmfspl}
{Probl. Mat. Fiz. Ser. Pentru Liceu}
{Probleme de Matematica si Fizica: Serie Pentru Liceu}
\DefineJournal{pppp}{1727-4907}
{Probl. Program.}
{Problemy Programmirovaniya. Problems in Programming}
\DefineJournal{psmb}{?psmb}
{Probl. Solving Math. Beyond}
{Problem Solving in Mathematics and Beyond}
\DefineJournal{p}{?p}
{Problemata}
{Problemata}
\DefineJournal{ranppi}{0555-2923}
{Problemy Peredachi Informatsii}
{Rossiiskaya Akademiya Nauk. Problemy Peredachi Informatsii}
\DefineJournal{nanupui}{0572-2691}
{Problemy Upravlen. Inform.}
{Natsionalnaya Akademiya Nauk Ukrainy. Problemy Upravleniya i Informatiki}
\DefineJournal{pa}{1364-5021}
{Proc. A.}
{Proceedings A}
\DefineJournal{pams}{0002-9939}
{Proc. Amer. Math. Soc.}
{Proceedings of the American Mathematical Society}
\DefineJournal{pamssb}{2330-1511}
{Proc. Amer. Math. Soc. Ser. B}
{Proceedings of the American Mathematical Society. Series B}
\DefineJournal{pcmaanu}{?pcmaanu}
{Proc. Centre Math. Appl. Austral. Nat. Univ.}
{Proceedings of the Centre for Mathematics and its Applications, Australian National University}
\DefineJournal{pemssi}{0013-0915}
{Proc. Edinb. Math. Soc. (2)}
{Proceedings of the Edinburgh Mathematical Society. Series II}
\DefineJournal{peas}{1736-6046}
{Proc. Est. Acad. Sci.}
{Proceedings of the Estonian Academy of Sciences}
\DefineJournal{piviam}{1512-004X}
{Proc. I. Vekua Inst. Appl. Math.}
{Proceedings of Ilia Vekua Institute of Applied Mathematics}
\DefineJournal{iaspms}{0253-4142}
{Proc. Indian Acad. Sci. Math. Sci.}
{Indian Academy of Sciences. Proceedings. Mathematical Sciences}
\DefineJournal{pinsa}{0370-0046}
{Proc. Indian Nat. Sci. Acad.}
{Proceedings of the Indian National Science Academy}
\DefineJournal{pimmnasa}{2409-4986}
{Proc. Inst. Math. Mech. Natl. Acad. Sci. Azerb.}
{Proceedings of Institute of Mathematics and Mechanics. National Academy of Sciences of Azerbaijan}
\DefineJournal{pimnasuma}{?pimnasuma}
{Proc. Inst. Math. Natl. Acad. Sci. Ukr. Math. Appl.}
{Proceedings of the Institute of Mathematics of the National Academy of Sciences of Ukraine. Mathematics and its Applications}
\DefineJournal{pism}{0912-6112}
{Proc. Inst. Statist. Math.}
{Proceedings of the Institute of Statistical Mathematics}
\DefineJournal{pigc}{2072-9812}
{Proc. Int. Geom. Cent.}
{Proceedings of the International Geometry Center}
\DefineJournal{pichmt}{?pichmt}
{Proc. Internat. Centre Heat Mass Transfer}
{Proceedings of the International Centre for Heat and Mass Transfer}
\DefineJournal{pjmsmjms}{1598-7264}
{Proc. Jangjeon Math. Soc.}
{Proceedings of the Jangjeon Mathematical Society. Memoirs of the Jangjeon Mathematical Society}
\DefineJournal{japsams}{0386-2194}
{Proc. Japan Acad. Ser. A Math. Sci.}
{Japan Academy. Proceedings. Series A. Mathematical Sciences}
\DefineJournal{ppnlpi}{?ppnlpi}
{Proc. Lebedev Phys. Inst.}
{Proceedings of the P. N. Lebedev Physics Institute}
\DefineJournal{plmsts}{0024-6115}
{Proc. Lond. Math. Soc. (3)}
{Proceedings of the London Mathematical Society. Third Series}
\DefineJournal{pmlr}{1938-7228}
{Proc. Mach. Learn. Res. (PMLR)}
{Proceedings of Machine Learning Research (PMLR)}
\DefineJournal{pnasisaps}{0369-8203}
{Proc. Nat. Acad. Sci. India Sect. A}
{Proceedings of the National Academy of Sciences, India. Section A. Physical Sciences}
\DefineJournal{pnasusa}{1091-6490}
{Proc. Natl. Acad. Sci. USA}
{Proceedings of the National Academy of Sciences of the United States of America}
\DefineJournal{pnrs}{?pnrs}
{Proc. NEC Res. Sympos.}
{Proceedings of the NEC Research Symposia}
\DefineJournal{ppasapcs}{2518-4245}
{Proc. Pak. Acad. Sci. A}
{Proceedings of the Pakistan Academy of Sciences. A. Physical and Computational Sciences}
\DefineJournal{prasamptsis}{1454-9069}
{Proc. Rom. Acad. Ser. A Math. Phys. Tech. Sci. Inf. Sci.}
{Proceedings of the Romanian Academy. Series A. Mathematics, Physics, Technical Sciences, Information Science}
\DefineJournal{prsesam}{0308-2105}
{Proc. Roy. Soc. Edinburgh Sect. A}
{Proceedings of the Royal Society of Edinburgh. Section A. Mathematics}
\DefineJournal{psim}{0081-5438}
{Proc. Steklov Inst. Math.}
{Proceedings of the Steklov Institute of Mathematics}
\DefineJournal{psam}{0160-7634}
{Proc. Sympos. Appl. Math.}
{Proceedings of Symposia in Applied Mathematics}
\DefineJournal{pspm}{0082-0717}
{Proc. Sympos. Pure Math.}
{Proceedings of Symposia in Pure Mathematics}
\DefineJournal{pcshpmscpm}{?pcshpmscpm}
{Proceed. Canad. Soc. Hist. Philos. Math.}
{Proceedings of the Canadian Society for History and Philosophy of Mathematics/La Societe Canadienne d'Histoire et de Philosophie des Mathematiques}
\DefineJournal{pics}{?pics}
{Prof. Indust. Comput. Ser.}
{Professional and Industrial Computing Series}
\DefineJournal{p}{?p}
{Profiles}
{Profiles}
\DefineJournal{pcfdaij}{1468-4349}
{Prog. Comput. Fluid Dyn.}
{Progress in Computational Fluid Dynamics. An International Journal}
\DefineJournal{pmp}{1544-9998}
{Prog. Math. Phys.}
{Progress in Mathematical Physics}
\DefineJournal{posp}{2363-5096}
{Prog. Opt. Sci. Photonics}
{Progress in Optical Science and Photonics}
\DefineJournal{pcsal}{2297-0576}
{Progr. Comput. Sci. Appl. Logic}
{Progress in Computer Science and Applied Logic}
\DefineJournal{pcf}{?pcf}
{Progr. Creep Fracture}
{Progress in Creep and Fracture}
\DefineJournal{pm}{0743-1643}
{Progr. Math.}
{Progress in Mathematics}
\DefineJournal{pndea}{1421-1750}
{Progr. Nonlinear Differential Equations Appl.}
{Progress in Nonlinear Differential Equations and their Applications}
\DefineJournal{pp}{1050-6977}
{Progr. Probab.}
{Progress in Probability}
\DefineJournal{pcs}{0361-7688}
{Program. Comput. Softw.}
{Programming and Computer Software}
\DefineJournal{ranp}{0132-3474}
{Programmirovanie}
{Rossiiskaya Akademiya Nauk. Programmirovanie}
\DefineJournal{pm}{?pm}
{Proj. MATH!}
{Project MATHEMATICS!}
\DefineJournal{pe}{?pe}
{Projeto Euclides}
{Projeto Euclides}
\DefineJournal{pjm}{0716-0917}
{Proyecciones}
{Proyecciones. Journal of Mathematics}
\DefineJournal{pota}{2297-0355}
{Pseudo Diff. Oper.}
{Pseudo-Differential Operators. Theory and Applications}
\DefineJournal{p}{0033-3123}
{Psychometrika}
{Psychometrika}
\DefineJournal{pptep}{2050-3911}
{PTEP. Prog. Theor. Exp. Phys.}
{PTEP. Progress of Theoretical and Experimental Physics}
\DefineJournal{pah}{2504-3714}
{Publ. Arch. Henri-Poincare}
{Publications des Archives Henri-Poincare}
\DefineJournal{pdm}{?pdm}
{Publ. Dep. Mat.}
{Publicacoes do Departamento de Matematica}
\DefineJournal{impns}{0350-1302}
{Publ. Inst. Math. (Beograd) (N.S.)}
{Institut Mathematique. Publications. Nouvelle Serie}
\DefineJournal{pm}{0214-1493}
{Publ. Mat.}
{Publicacions Matematiques}
\DefineJournal{pmi}{?pmi}
{Publ. Mat. IMPA}
{Publicacoes Matematicas do IMPA}
\DefineJournal{pmu}{0797-1443}
{Publ. Mat. Urug.}
{Publicaciones Matematicas del Uruguay}
\DefineJournal{pmbatn}{1958-7236}
{Publ. Math. Besancon Algebre Theorie Nr.}
{Publications Mathematiques de Besancon. Algebre et Theorie des Nombres}
\DefineJournal{pmd}{0033-3883}
{Publ. Math. Debrecen}
{Publicationes Mathematicae Debrecen}
\DefineJournal{pmihes}{0073-8301}
{Publ. Math. Inst. Hautes Etudes Sci.}
{Publications Mathematiques. Institut de Hautes Etudes Scientifiques}
\DefineJournal{prims}{0034-5318}
{Publ. Res. Inst. Math. Sci.}
{Publications of the Research Institute for Mathematical Sciences}
\DefineJournal{psm}{?psm}
{Publ. Sec. Mat.}
{Publicacions de la Seccio de Mathematiques}
\DefineJournal{puefrsfns}{1798-5684}
{Publ. Univ. East. Finl. Rep. Stud. For. Nat. Sci.}
{Publications of the University of Eastern Finland. Reports and Studies in Forestry and Natural Sciences}
\DefineJournal{pujsb}{?pujsb}
{Publ. Univ. Joensuu, Ser. BI}
{Publications of the University of Joensuu, Series BI}
\DefineJournal{tpujm}{1016-2526}
{Punjab Univ. J. Math. (Lahore)}
{The Punjab University. Journal of Mathematics}
\DefineJournal{pafa}{2189-3756}
{Pure Appl. Funct. Anal.}
{Pure and Applied Functional Analysis}
\DefineJournal{pam}{?pam}
{Pure Appl. Math.}
{Pure and Applied Mathematics}
\DefineJournal{pam}{0079-8169}
{Pure Appl. Math. (Amst.)}
{Pure and Applied Mathematics (Amsterdam)}
\DefineJournal{pamr}{?pamr}
{Pure Appl. Math. (Boca Raton)}
{Pure and Applied Mathematics (Boca Raton)}
\DefineJournal{pam}{?pam}
{Pure Appl. Math. (Hoboken)}
{Pure and Applied Mathematics (Hoboken)}
\DefineJournal{pamq}{1558-8599}
{Pure Appl. Math. Q.}
{Pure and Applied Mathematics Quarterly}
\DefineJournal{pap}{?pap}
{Pure Appl. Phys.}
{Pure and Applied Physics}
\DefineJournal{paut}{1943-9334}
{Pure Appl. Undergrad. Texts}
{Pure and Applied Undergraduate Texts}
\DefineJournal{pmap}{1218-4586}
{Pure Math. Appl. (PU.M.A.)}
{Pure Mathematics and Applications. PU.M.A.}
\DefineJournal{tqjm}{0033-5606}
{Q. J. Math.}
{The Quarterly Journal of Mathematics}
\DefineJournal{q}{?q}
{Q.R.C.}
{Q.R.C.}
\DefineJournal{}{?}
{Qinghua Daxue Xuebao}
{nan}
\DefineJournal{qqpwna}{1793-5121}
{QP--PQ: Quantum Probab. White Noise Anal.}
{QP--PQ: Quantum Probability and White Noise Analysis}
\DefineJournal{qap}{?qap}
{Quad. Accad. Pontaniana}
{Quaderni dell' Accademia Pontaniana}
\DefineJournal{qm}{?qm}
{Quad. Mat.}
{Quaderni di Matematica}
\DefineJournal{qsnsps}{?qsnsps}
{Quad. Sc. Norm. Super. di Pisa (N. S.)}
{Quaderni. Scuola Normale Superiore di Pisa (Nuova Serie)}
\DefineJournal{qsnsps}{?qsnsps}
{Quad. Sc. Norm. Super. Pisa Sel.}
{Quaderni. Scuola Normale Superiore di Pisa. Selections}
\DefineJournal{q}{?q}
{Quad./Monogr.}
{Quaderni/Monographs}
\DefineJournal{qmmpe}{1142-2785}
{Quadrature}
{Quadrature. Magazine de Mathematiques Pures et Epicees}
\DefineJournal{qmjsams}{1607-3606}
{Quaest. Math.}
{Quaestiones Mathematicae. Journal of the South African Mathematical Society}
\DefineJournal{qqassc}{2365-8371}
{Qual. Quant. Anal. Sci. Sch. Commun.}
{Qualitative and Quantitative Analysis of Scientific and Scholarly Communication}
\DefineJournal{qr}{?qr}
{Qual. Reliab.}
{Quality and Reliability}
\DefineJournal{qtds}{1575-5460}
{Qual. Theory Dyn. Syst.}
{Qualitative Theory of Dynamical Systems}
\DefineJournal{qe}{1759-7323}
{Quant. Econ.}
{Quantitative Economics}
\DefineJournal{qf}{1469-7688}
{Quant. Finance}
{Quantitative Finance}
\DefineJournal{qgg}{0924-1973}
{Quant. Geol. Geostat.}
{Quantitative Geology and Geostatistics}
\DefineJournal{qnb}{?qnb}
{Quant. Netw. Biol.}
{Quantitative and Network Biology}
\DefineJournal{qpbef}{?qpbef}
{Quant. Perspect. Behav. Econ. Finance}
{Quantitative Perspectives on Behavioral Economics and Finance}
\DefineJournal{q}{1314-7374}
{Quanta}
{Quanta}
\DefineJournal{qass}{?qass}
{Quantitative Appl. in the Social Sciences}
{Quantitative Applications in the Social Sciences}
\DefineJournal{ql}{?ql}
{Quantitative Linguistics}
{Quantitative Linguistics}
\DefineJournal{qmu}{?qmu}
{Quantitative Method. Unternehmungsplanung}
{Quantitative Methoden der Unternehmungsplanung}
\DefineJournal{qssr}{?qssr}
{Quantitative Stud. Social Relations}
{Quantitative Studies in Social Relations}
\DefineJournal{qea}{?qea}
{Quantum Electron.---Principles Appl.}
{Quantum Electronics---Principles and Applications}
\DefineJournal{qic}{1533-7146}
{Quantum Inf. Comput.}
{Quantum Information & Computation}
\DefineJournal{qip}{1570-0755}
{Quantum Inf. Process.}
{Quantum Information Processing}
\DefineJournal{qst}{2364-9054}
{Quantum Sci. Technol.}
{Quantum Science and Technology}
\DefineJournal{qsmf}{2196-5609}
{Quantum Stud. Math. Found.}
{Quantum Studies. Mathematics and Foundations}
\DefineJournal{qt}{1663-487X}
{Quantum Topol.}
{Quantum Topology}
\DefineJournal{qam}{0033-569X}
{Quart. Appl. Math.}
{Quarterly of Applied Mathematics}
\DefineJournal{tqjmam}{0033-5614}
{Quart. J. Mech. Appl. Math.}
{The Quarterly Journal of Mechanics and Applied Mathematics}
\DefineJournal{qrs}{1561-2848}
{Quasigroups Related Systems}
{Quasigroups and Related Systems}
\DefineJournal{qbguj}{?qbguj}
{Quellen Beitr. Gesch. Univ. Jena}
{Quellen und Beitrage zur Geschichte der Universitat Jena}
\DefineJournal{qlwars}{?qlwars}
{Quellen Leben Wirk. Adam Ries Sohne}
{Quellen zum Leben und Wirken Adam Ries' und seiner Sohne}
\DefineJournal{qagt}{0918-4732}
{Questions Answers Gen. Topology}
{Questions and Answers in General Topology}
\DefineJournal{qsta}{0257-0130}
{Queueing Syst.}
{Queueing Systems. Theory and Applications}
\DefineJournal{ts}{?ts}
{$R$ Ser.}
{The $R$ Series}
\DefineJournal{rsos}{2054-5703}
{R. Soc. Open Sci.}
{Royal Society Open Science}
\DefineJournal{rhazumz}{1845-4100}
{Rad Hrvat. Akad. Znan. Umjet. Mat. Znan.}
{Rad Hrvatske Akademije Znanosti i Umjetnosti. Matematicke Znanosti}
\DefineJournal{rscam}{1865-3707}
{Radon Ser. Comput. Appl. Math.}
{Radon Series on Computational and Applied Mathematics}
\DefineJournal{ror}{0399-0559}
{RAIRO Oper. Res.}
{RAIRO Operations Research}
\DefineJournal{rtiaita}{0988-3754}
{RAIRO Theor. Inform. Appl.}
{RAIRO Theoretical Informatics and Applications. Informatique Theorique et Applications}
\DefineJournal{rjaijdamir}{1382-4090}
{Ramanujan J.}
{Ramanujan Journal. An International Journal Devoted to the Areas of Mathematics Influenced by Ramanujan}
\DefineJournal{rmscws}{?rmscws}
{Ramanujan Math. Soc. Collect. Works Ser.}
{Ramanujan Mathematical Society Collected Works Series}
\DefineJournal{rmslns}{?rmslns}
{Ramanujan Math. Soc. Lect. Notes Ser.}
{Ramanujan Mathematical Society Lecture Notes Series}
\DefineJournal{rmta}{2010-3263}
{Random Matrices Theory Appl.}
{Random Matrices. Theory and Applications}
\DefineJournal{rose}{0926-6364}
{Random Oper. Stoch. Equ.}
{Random Operators and Stochastic Equations}
\DefineJournal{rsa}{1042-9832}
{Random Structures Algorithms}
{Random Structures & Algorithms}
\DefineJournal{rae}{0147-1937}
{Real Anal. Exchange}
{Real Analysis Exchange}
\DefineJournal{racc}{?racc}
{Recent Adv. Comput. Chem.}
{Recent Advances in Computational Chemistry}
\DefineJournal{rrcr}{0080-0015}
{Recent Results Cancer Res.}
{Recent Results in Cancer Research}
\DefineJournal{rma}{0298-3168}
{Rech. Math. Appl.}
{Recherches en Mathematiques Appliquees}
\DefineJournal{rmm}{2182-1976}
{Recreat. Math. Mag.}
{Recreational Mathematics Magazine}
\DefineJournal{rs}{?rs}
{Ref. Sci.}
{References Sciences}
\DefineJournal{rsst}{?rsst}
{Ref. Source Sci. Technol.}
{Reference Sources in Science and Technology}
\DefineJournal{rsssh}{?rsssh}
{Ref. Sources Social Sci. Humanities}
{Reference Sources for the Social Sciences and Humanities}
\DefineJournal{rcdisj}{1560-3547}
{Regul. Chaotic Dyn.}
{Regular and Chaotic Dynamics. International Scientific Journal}
\DefineJournal{rw}{?rw}
{Reihe Wiss.}
{Reihe Wissenschaft}
\DefineJournal{rpiu}{?rpiu}
{Reihe: Planung, Inform. Unternehmungsfuhr.}
{Reihe: Planung, Information und Unternehmungsfuhrung}
\DefineJournal{rc}{1573-1340}
{Reliab. Comput.}
{Reliable Computing}
\DefineJournal{snslanrsfmsi}{0370-3568}
{Rend. Accad. Sci. Fis. Mat. Napoli (4)}
{Societa Nazionale di Scienze, Lettere e Arti in Napoli. Rendiconto dell'Accademia delle Scienze Fisiche e Matematiche. Serie IV}
\DefineJournal{rcmpss}{0009-725X}
{Rend. Circ. Mat. Palermo (2)}
{Rendiconti del Circolo Matematico di Palermo. Second Series}
\DefineJournal{rmtaijm}{0049-4704}
{Rend. Istit. Mat. Univ. Trieste}
{Rendiconti dell'Istituto di Matematica dell'Universita di Trieste. An International Journal of Mathematics}
\DefineJournal{rmasv}{1120-7183}
{Rend. Mat. Appl. (7)}
{Rendiconti di Matematica e delle sue Applicazioni. Serie VII}
\DefineJournal{rsmup}{0041-8994}
{Rend. Semin. Mat. Univ. Padova}
{Rendiconti del Seminario Matematico della Universita di Padova}
\DefineJournal{rsmupt}{0373-1243}
{Rend. Semin. Mat. Univ. Politec. Torino}
{Rendiconti del Seminario Matematico. Universita e Politecnico Torino}
\DefineJournal{ressiviam}{1512-0066}
{Rep. Enlarged Sess. Semin. I. Vekua Appl. Math.}
{Reports of Enlarged Sessions of Seminar of I. Vekua Institute of Applied Mathematics}
\DefineJournal{rim}{0465-7926}
{Rep. Inst. Math.}
{Reports of the Institute of Mathematics}
\DefineJournal{rml}{0137-2904}
{Rep. Math. Logic}
{Reports on Mathematical Logic}
\DefineJournal{rmp}{0034-4877}
{Rep. Math. Phys.}
{Reports on Mathematical Physics}
\DefineJournal{rm}{?rm}
{Rep. MECH 1983}
{Report MECH 1983}
\DefineJournal{rpp}{0034-4885}
{Rep. Progr. Phys.}
{Reports on Progress in Physics}
\DefineJournal{rs}{2385-4277}
{Rep. SCM}
{Reports SCM}
\DefineJournal{rtac}{?rtac}
{Repr. Theory Appl. Categ.}
{Reprints in Theory and Applications of Categories}
\DefineJournal{rtaejams}{1088-4165}
{Represent. Theory}
{Representation Theory. An Electronic Journal of the American Mathematical Society}
\DefineJournal{rem}{?rem}
{Res. Exp. Math.}
{Research and Exposition in Mathematics}
\DefineJournal{rms}{2522-0144}
{Res. Math. Sci.}
{Research in the Mathematical Sciences}
\DefineJournal{rnt}{2363-9555}
{Res. Number Theory}
{Research in Number Theory}
\DefineJournal{rr}{0345-3928}
{Res. Rep.}
{Research Reports}
\DefineJournal{arb}{?arb}
{Reston Book}
{A Reston Book}
\DefineJournal{rm}{1422-6383}
{Results Math.}
{Results in Mathematics}
\DefineJournal{racc}{1130-4723}
{Rev. Acad. Canaria Cienc.}
{Revista de la Academia Canaria de Ciencias}
\DefineJournal{accefnr}{0370-3908}
{Rev. Acad. Colombiana Cienc. Exact. Fis. Natur.}
{Academia Colombiana de Ciencias Exactas, Fisicas y Naturales. Revista}
\DefineJournal{rast}{?rast}
{Rev. Accel. Sci. Technol.}
{Reviews of Accelerator Science and Technology}
\DefineJournal{rbhmaijhm}{1519-955X}
{Rev. Bras. Hist. Mat.}
{Revista Brasileira de Historia da Matematica. An International Journal on the History of Mathematics}
\DefineJournal{rce}{0120-1751}
{Rev. Colombiana Estadist.}
{Revista Colombiana de Estadistica}
\DefineJournal{rcm}{0034-7426}
{Rev. Colombiana Mat.}
{Revista Colombiana de Matematicas}
\DefineJournal{red}{1434-4742}
{Rev. Econ. Des.}
{Review of Economic Design}
\DefineJournal{res}{0034-6527}
{Rev. Econ. Stud.}
{Review of Economic Studies}
\DefineJournal{rs}{0151-4105}
{Rev. Hist. Sci.}
{Revue d'Histoire des Sciences}
\DefineJournal{rmjhm}{1262-022X}
{Rev. Histoire Math.}
{Revue d'Histoire des Mathematiques. Journal for the History of Mathematics}
\DefineJournal{rimncdi}{0213-1315}
{Rev. Int. Metod. Numer. Calc. Diseno Ing.}
{Revista Internacional de Metodos Numericos para Calculo y Diseno en Ingenieria}
\DefineJournal{ritm}{0120-419X}
{Rev. Integr. Temas Mat.}
{Revista Integracion. Temas de Matematicas}
\DefineJournal{rlepsem}{2011-5474}
{Rev. Latinoam. Etnomat.}
{Revista Latinoamericana de Etnomatematica. Perspectivas Socioculturales de la Educacion Matematica}
\DefineJournal{rmc}{1139-1138}
{Rev. Mat. Complut.}
{Revista Matematica Complutense}
\DefineJournal{rmi}{0213-2230}
{Rev. Mat. Iberoam.}
{Revista Matematica Iberoamericana}
\DefineJournal{rmta}{1409-2433}
{Rev. Mat. Teor. Apl.}
{Revista de Matematica. Teoria y Aplicaciones}
\DefineJournal{rmmp}{1024-5278}
{Rev. Math. Math. Phys.}
{Reviews in Mathematics and Mathematical Physics}
\DefineJournal{rmpajbrorpfmp}{0129-055X}
{Rev. Math. Phys.}
{Reviews in Mathematical Physics. A Journal for Both Review and Original Research Papers in the Field of Mathematical Physics}
\DefineJournal{rmfepehfsmf}{1870-3542}
{Rev. Mex. Fis. E}
{Revista Mexicana de Fisica E. Publicacion de Ensenanza, Historia y Filosofia de la Sociedad Mexicana de Fisica}
\DefineJournal{rmf}{0035-001X}
{Rev. Mexicana Fis.}
{Revista Mexicana de Fisica}
\DefineJournal{rmp}{0034-6861}
{Rev. Modern Phys.}
{Reviews of Modern Physics}
\DefineJournal{rndc}{?rndc}
{Rev. Nonlinear Dyn. Complex.}
{Reviews of Nonlinear Dynamics and Complexity}
\DefineJournal{rracefn}{1137-2141}
{Rev. R. Acad. Cienc. Exactas Fis. Nat. (Esp.)}
{Revista de la Real Academia de Ciencias Exactas, Fisicas y Naturales (Espana)}
\DefineJournal{rracefnsamr}{1578-7303}
{Rev. R. Acad. Cienc. Exactas Fis. Nat. Ser. A Mat. RACSAM}
{Revista de la Real Academia de Ciencias Exactas, Fisicas y Naturales. Serie A. Matematicas. RACSAM}
\DefineJournal{rracefqnzs}{0370-3207}
{Rev. R. Acad. Cienc. Exactas Fis. Quim. Nat. Zaragoza (2)}
{Revista de la Real Academia de Ciencias Exactas, Fisicas, Quimicas y Naturales de Zaragoza. Serie 2}
\DefineJournal{rrmparjpam}{0035-3965}
{Rev. Roumaine Math. Pures Appl.}
{Revue Roumaine de Mathematiques Pures et Appliquees. Romanian Journal of Pure and Applied Mathematics}
\DefineJournal{trsl}{1755-0203}
{Rev. Symb. Log.}
{The Review of Symbolic Logic}
\DefineJournal{rss}{0035-1776}
{Rev. Synth. (6)}
{Revue de Synthese. 6e Serie}
\DefineJournal{ruma}{0041-6932}
{Rev. Un. Mat. Argentina}
{Revista de la Union Matematica Argentina}
\DefineJournal{rsj}{1645-6726}
{REVSTAT}
{REVSTAT Statistical Journal}
\DefineJournal{rimp}{?rimp}
{Rezultaty Issled. Mezhdunar. Geofiz. Proekt.}
{Rezultaty Issledovanii po Mezhdunarodnym Proektam}
\DefineJournal{rm}{0035-5038}
{Ric. Mat.}
{Ricerche di Matematica}
\DefineJournal{rkb}{1881-6193}
{RIMS Kokyuroku Bessatsu}
{RIMS Kokyuroku Bessatsu}
\DefineJournal{re}{2195-433X}
{Risk Eng.}
{Risk Engineering}
\DefineJournal{rmupnsajpam}{0035-6298}
{Riv. Math. Univ. Parma (N.S.)}
{Rivista di Matematica della Universita di Parma. New Series. A Journal of Pure and Applied Mathematics}
\DefineJournal{rgps}{?rgps}
{Robototekhn. Gibk. Proizvod. Sist.}
{Robototekhnika i Gibkie Proizvodstvennye Sistemy}
\DefineJournal{trmjm}{0035-7596}
{Rocky Mountain J. Math.}
{The Rocky Mountain Journal of Mathematics}
\DefineJournal{rjmcs}{2247-689X}
{Rom. J. Math. Comput. Sci.}
{Romanian Journal of Mathematics and Computer Science}
\DefineJournal{rjtsam}{2601-5811}
{Rom. J. Tech. Sci. Appl. Mech.}
{Romanian Journal of Technical Sciences. Applied Mechanics}
\DefineJournal{rj}{1841-5512}
{ROMAI J.}
{ROMAI Journal}
\DefineJournal{rumj}{?rumj}
{Rose-Hulman Undergrad. Math. J.}
{Rose-Hulman Undergraduate Mathematics Journal}
\DefineJournal{rmk}{0138-3248}
{Rostock. Math. Kolloq.}
{Rostocker Mathematisches Kolloquium}
\DefineJournal{rcrp}{?rcrp}
{Routledge Contemp. Read. Philos.}
{Routledge Contemporary Readings in Philosophy}
\DefineJournal{rp}{?rp}
{Routledge Philos.}
{Routledge Philosophers}
\DefineJournal{r}{?r}
{RR}
{RR}
\DefineJournal{r}{?r}
{RR-83}
{RR-83}
\DefineJournal{rss}{2509-8888}
{RSME Springer Ser.}
{RSME Springer Series}
\DefineJournal{trtus}{?trtus}
{RT-11 Tech. User's Ser.}
{The RT-11 Technical User's Series}
\DefineJournal{}{?}
{Ruanjian Xuebao}
{nan}
\DefineJournal{rjmp}{1061-9208}
{Russ. J. Math. Phys.}
{Russian Journal of Mathematical Physics}
\DefineJournal{rjnamm}{0927-6467}
{Russian J. Numer. Anal. Math. Modelling}
{Russian Journal of Numerical Analysis and Mathematical Modelling}
\DefineJournal{rmvm}{1066-369X}
{Russian Math. (Iz. VUZ)}
{Russian Mathematics (Izvestiya VUZ. Matematika)}
\DefineJournal{rms}{0036-0279}
{Russian Math. Surveys}
{Russian Mathematical Surveys}
\DefineJournal{rmj}{1344-008X}
{Ryukyu Math. J.}
{Ryukyu Mathematical Journal}
\DefineJournal{sapes}{0256-2499}
{Sadhana}
{Sadhana. Academy Proceedings in Engineering Sciences}
\DefineJournal{samrcp}{?samrcp}
{Sagamore Army Materials Res. Conf. Proc.}
{Sagamore Army Materials Research Conference Proceedings}
\DefineJournal{sbsrm}{?sbsrm}
{Sage Benchmarks Soc. Res. Methods}
{Sage Benchmarks in Social Research Methods}
\DefineJournal{sfe}{?sfe}
{Sage Focus Ed.}
{Sage Focus Editions}
\DefineJournal{smj}{0289-0739}
{Saitama Math. J.}
{Saitama Mathematical Journal}
\DefineJournal{stsipaij}{1530-6429}
{Sampl. Theory Signal Image Process.}
{Sampling Theory in Signal and Image Processing. An International Journal}
\DefineJournal{samsp}{0976-836X}
{Sankhya A}
{Sankhya A. Mathematical Statistics and Probability}
\DefineJournal{sbais}{0976-8386}
{Sankhya B}
{Sankhya B. Applied and Interdisciplinary Statistics}
\DefineJournal{spjms}{1982-6907}
{Sao Paulo J. Math. Sci.}
{Sao Paulo Journal of Mathematical Sciences}
\DefineJournal{sjm}{1840-0655}
{Sarajevo J. Math.}
{Sarajevo Journal of Mathematics}
\DefineJournal{lsm}{1262-2869}
{Savoir Mantice}
{Le Savoir de Mantice}
\DefineJournal{sau}{?sau}
{Savoirs Actuels (Les Ulis)}
{Savoirs Actuels (Les Ulis)}
\DefineJournal{ssp}{?ssp}
{Savoirs Sci. Prat. Enseign.}
{Savoirs Scientifiques & Pratiques d'Enseignement}
\DefineJournal{sm}{1064-5616}
{Sb. Math.}
{Sbornik. Mathematics}
\DefineJournal{scc}{2520-8632}
{Scalable Comput. Commun.}
{Scalable Computing and Communications}
\DefineJournal{saj}{0346-1238}
{Scand. Actuar. J.}
{Scandinavian Actuarial Journal}
\DefineJournal{sjsta}{0303-6898}
{Scand. J. Stat.}
{Scandinavian Journal of Statistics. Theory and Applications}
\DefineJournal{s}{?s}
{Schatzkammer}
{Schatzkammer}
\DefineJournal{sosc}{?sosc}
{Schaum's Outline Ser. Comput.}
{Schaum's Outline Series in Computers}
\DefineJournal{scfss}{?scfss}
{Schr. Carl Friedrich von Siemens Stift.}
{Schriften der Carl Friedrich von Siemens Stiftung}
\DefineJournal{sw}{0946-1949}
{Schr. Wirtsch.inform.}
{Schriften zur Wirtschaftsinformatik}
\DefineJournal{saa}{?saa}
{Schrift. Adam-Ries-Bundes Annaberg-Buchholz}
{Schriften des Adam-Ries-Bundes Annaberg-Buchholz}
\DefineJournal{swnf}{?swnf}
{Schrift. Wirtschaftspolit. N.F.}
{Schriften zur Wirtschaftspolitik. Neue Folge}
\DefineJournal{swf}{?swf}
{Schriften Wirtschaftswiss. Forsch.}
{Schriften zur Wirtschaftswissenschaftlichen Forschung}
\DefineJournal{si}{?si}
{Schriftenreihe Informationsverarbeitung}
{Schriftenreihe Informationsverarbeitung}
\DefineJournal{siewuz}{?siewuz}
{Schriftenreihe Inst. Empirische Wirtschaftsforsch. Univ. Zurich}
{Schriftenreihe des Instituts fur Empirische Wirtschaftsforschung der Universitat Zurich}
\DefineJournal{sv}{?sv}
{Schriftenreihe Versicher.}
{Schriftenreihe ``Die Versicherung''}
\DefineJournal{sf}{?sf}
{Schriftenreihe Wiss. Frieden}
{Schriftenreihe ``Wissenschaft und Frieden''}
\DefineJournal{sacs}{1843-8121}
{Sci. Ann. Comput. Sci.}
{Scientific Annals of Computer Science}
\DefineJournal{scis}{1674-733X}
{Sci. China Inf. Sci.}
{Science China. Information Sciences}
\DefineJournal{scm}{1674-7283}
{Sci. China Math.}
{Science China. Mathematics}
\DefineJournal{sc}{1434-8322}
{Sci. Comput.}
{Scientific Computation}
\DefineJournal{scp}{?scp}
{Sci. Concepts Probl.}
{Sciences: Concepts et Problemes}
\DefineJournal{sc}{0269-8897}
{Sci. Context}
{Science in Context}
\DefineJournal{se}{?se}
{Sci. Econom.}
{Sciences Economiques}
\DefineJournal{sec}{?sec}
{Sci. Engrg. Comput.}
{Scientific and Engineering Computation}
\DefineJournal{sg}{1868-7172}
{Sci. Graeco-Arabica}
{Scientia Graeco-Arabica}
\DefineJournal{sijducm}{2450-9302}
{Sci. Issues Jan Dlugosz Univ. Czest. Math.}
{Scientific Issues. Jan Dlugosz University in Czestochowa. Mathematics}
\DefineJournal{smj}{1346-0862}
{Sci. Math. Jpn.}
{Scientiae Mathematicae Japonicae}
\DefineJournal{smse}{1773-7338}
{Sci. Musique Ser. Etudes}
{Sciences de la Musique. Serie Etudes}
\DefineJournal{snhs}{1421-6329}
{Sci. Networks Hist. Stud.}
{Science Networks. Historical Studies}
\DefineJournal{sp}{?sp}
{Sci. Psychol.}
{Scientific Psychology}
\DefineJournal{tsrku}{0022-8338}
{Sci. Rep. Kanazawa Univ.}
{The Science Reports of Kanazawa University}
\DefineJournal{ss}{0184-7155}
{Sci. Savoirs}
{Sciences et Savoirs}
\DefineJournal{ssamsns}{0716-8446}
{Sci. Ser. A Math. Sci. (N.S.)}
{Scientia. Series A. Mathematical Sciences. New Series}
\DefineJournal{ssrsmi}{2457-497X}
{Sci. Stud. Res. Ser. Math. Inform.}
{Scientific Studies and Research. Series Mathematics and Informatics}
\DefineJournal{ss}{0928-1134}
{Sci. Stud./Wet.}
{Science Studies/Wetenschapsstudies}
\DefineJournal{stpis}{0294-0264}
{Sci. Tech. Perspect. (2)}
{Sciences et Techniques en Perspective. IIe Serie}
\DefineJournal{stel}{?stel}
{Sci. Technol. Educ. Libr.}
{Science & Technology Education Library}
\DefineJournal{stmac}{2194-976X}
{Sci. Technol. Med. Anc. Cult.}
{Science, Technology, and Medicine in Ancient Cultures}
\DefineJournal{sw}{?sw}
{Sci. Wales}
{Scientists of Wales}
\DefineJournal{ssces}{1345-4617}
{SCIAMVS}
{SCIAMVS. Sources and Commentaries in Exact Sciences}
\DefineJournal{aaass}{0036-8075}
{Science}
{American Association for the Advancement of Science. Science}
\DefineJournal{sn}{1696-8247}
{SCM Not.}
{SCM Noticies}
\DefineJournal{sgs}{2199-4617}
{Scott. Grad. Ser.}
{Scottish Graduate Series}
\DefineJournal{ss}{?ss}
{SDI-SOR Serija}
{SDI-SOR Serija}
\DefineJournal{swps}{2197-5825}
{Sel. Works Probab. Stat.}
{Selected Works in Probability and Statistics}
\DefineJournal{smns}{1022-1824}
{Selecta Math. (N.S.)}
{Selecta Mathematica. New Series}
\DefineJournal{sgm}{?sgm}
{Self-Teach. Guides Math.}
{Self-Teaching Guides on Mathematics}
\DefineJournal{slc}{1286-4889}
{Sem. Lothar. Combin.}
{Seminaire Lotharingien de Combinatoire}
\DefineJournal{sms}{?sms}
{Sem. Math. (N. S.)}
{Seminaire de Mathematique (Nouvelle Serie)}
\DefineJournal{sms}{1880-6511}
{Sem. Math. Sci.}
{Seminar on Mathematical Sciences}
\DefineJournal{sjbsema}{2254-3902}
{SeMA J.}
{SeMA Journal. Boletin de la Sociedad Espannola de Matematica Aplicada}
\DefineJournal{ssss}{2199-3041}
{SEMA SIMAI Springer Ser.}
{SEMA SIMAI Springer Series}
\DefineJournal{sf}{0037-1912}
{Semigroup Forum}
{Semigroup Forum}
\DefineJournal{sc}{1285-2783}
{Semin. Congr.}
{Seminaires et Congres}
\DefineJournal{sedp}{?sedp}
{Semin. Equ. Deriv. Partielles}
{Seminaire: Equations aux Derivees Partielles}
\DefineJournal{siviamr}{1512-0058}
{Semin. I. Vekua Inst. Appl. Math. Rep.}
{Seminar of Ilia Vekua Institute of Applied Mathematics. Reports}
\DefineJournal{s}{?s}
{Seminaires}
{Seminaires}
\DefineJournal{se}{2514-3778}
{SemStat Elem.}
{SemStat Elements}
\DefineJournal{sadma}{0747-4946}
{Sequential Anal.}
{Sequential Analysis. Design Methods & Applications}
\DefineJournal{samas}{1793-0901}
{Ser. Adv. Math. Appl. Sci.}
{Series on Advances in Mathematics for Applied Sciences}
\DefineJournal{sa}{?sa}
{Ser. Anal.}
{Series in Analysis}
\DefineJournal{saac}{1793-4702}
{Ser. Anal. Appl. Comput.}
{Series on Analysis, Applications and Computation}
\DefineJournal{sacm}{2010-2739}
{Ser. Appl. Comput. Math.}
{Series in Applied and Computational Mathematics}
\DefineJournal{sam}{1793-0928}
{Ser. Appl. Math.}
{Series on Applied Mathematics}
\DefineJournal{sc}{?sc}
{Ser. Cient.}
{Serie Cientifica}
\DefineJournal{sctc}{1793-2238}
{Ser. Coding Theory Cryptol.}
{Series on Coding Theory and Cryptology}
\DefineJournal{scnc}{2010-0019}
{Ser. Complex. Nonlinearity Chaos}
{Series on Complexity, Nonlinearity and Chaos}
\DefineJournal{scs}{1755-7453}
{Ser. Complex. Sci.}
{Series on Complexity Science}
\DefineJournal{scv}{2010-2143}
{Ser. Comput. Vis.}
{Series in Computer Vision}
\DefineJournal{scam}{1793-1142}
{Ser. Concr. Appl. Math.}
{Series on Concrete and Applicable Mathematics}
\DefineJournal{scamc}{2010-2259}
{Ser. Contemp. Appl. Math. CAM}
{Series in Contemporary Applied Mathematics CAM}
\DefineJournal{scm}{2364-009X}
{Ser. Contemp. Math.}
{Series in Contemporary Mathematics}
\DefineJournal{sece}{?sece}
{Ser. Electr. Comput. Eng.}
{Series in Electrical and Computer Engineering}
\DefineJournal{sibe}{?sibe}
{Ser. Internat. Bus. Econom.}
{Series in International Business and Economics}
\DefineJournal{ske}{0219-9769}
{Ser. Knots Everything}
{Series on Knots and Everything}
\DefineJournal{sk}{0324-9794}
{Ser. Konf. (Wroc.)}
{Seria: Konferencje}
\DefineJournal{smf}{?smf}
{Ser. Mat. Fis.}
{Serie di Matematica e Fisica}
\DefineJournal{smcmp}{?smcmp}
{Ser. Modern Condensed Matter Phys.}
{Series in Modern Condensed Matter Physics}
\DefineJournal{sma}{1793-1169}
{Ser. Multivariate Anal.}
{Series on Multivariate Analysis}
\DefineJournal{snta}{1793-3161}
{Ser. Number Theory Appl.}
{Series on Number Theory and its Applications}
\DefineJournal{soo}{?soo}
{Ser. Opt. Optoelectron.}
{Series in Optics and Optoelectronics}
\DefineJournal{soa}{2399-1593}
{Ser. Optim. Appl.}
{Series on Optimization and its Applications}
\DefineJournal{spam}{?spam}
{Ser. Pure Appl. Math.}
{Series on the Pure and Applied Mathematics}
\DefineJournal{spm}{1793-1185}
{Ser. Pure Math.}
{Series in Pure Mathematics}
\DefineJournal{sqf}{1756-1604}
{Ser. Quant. Financ.}
{Series in Quantitative Finance}
\DefineJournal{sra}{1793-1134}
{Ser. Real Anal.}
{Series in Real Analysis}
\DefineJournal{sscm}{1793-737X}
{Ser. Soft Condens. Matter}
{Series in Soft Condensed Matter}
\DefineJournal{ssvcssatmt}{?ssvcssatmt}
{Ser. Stab. Vib. Control Syst. Ser. A}
{Series on Stability, Vibration and Control of Systems. Series A: Textbooks, Monographs and Treatises}
\DefineJournal{asstcb}{?asstcb}
{Ser. Students Texts Contemp. Biology}
{A Series of Student Texts in Contemporary Biology}
\DefineJournal{ssa}{2261-1088}
{Ser. Syst. Autom.}
{Serie Systemes Automatises}
\DefineJournal{lst}{2109-7186}
{Ser. T}
{La Serie T}
\DefineJournal{stcs}{1793-849X}
{Ser. Theor. Comput. Sci.}
{Series on Theoretical Computer Science}
\DefineJournal{sum}{?sum}
{Ser. Univ. Math.}
{Series on University Mathematics}
\DefineJournal{sjc}{1312-6555}
{Serdica J. Comput.}
{Serdica Journal of Computing}
\DefineJournal{smjsms}{1310-6600}
{Serdica Math. J.}
{Serdica. Mathematical Journal. Serdika. Matematichesko Spisanie}
\DefineJournal{sva}{1877-0533}
{Set-Valued Var. Anal.}
{Set-Valued and Variational Analysis}
\DefineJournal{}{?}
{Shaanxi Shifan Daxue Xuebao}
{nan}
\DefineJournal{}{?}
{Shandong Daxue Xuebao Lixue Ban}
{nan}
\DefineJournal{}{?}
{Shanghai Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Shanghai Jiaotong Daxue Xuebao}
{nan}
\DefineJournal{}{?}
{Shengwu Shuxue Xuebao}
{nan}
\DefineJournal{swc}{?swc}
{Shiyan Wulixue Congshu}
{Shiyan Wulixeu Congshu}
\DefineJournal{swhpp}{2197-9529}
{Shock Wave High Press. Phenom.}
{Shock Wave and High Pressure Phenomena}
\DefineJournal{stl}{2522-5480}
{Short Textb. Log.}
{Short Textbooks in Logic}
\DefineJournal{}{?}
{Shuxue Jikan}
{nan}
\DefineJournal{}{?}
{Shuxue Jinzhan}
{nan}
\DefineJournal{}{?}
{Shuxue Lilun Yingyong}
{nan}
\DefineJournal{}{?}
{Shuxue Niankan A Ji}
{nan}
\DefineJournal{}{?}
{Shuxue Niankan B Ji}
{nan}
\DefineJournal{}{?}
{Shuxue Shijian Renshi}
{nan}
\DefineJournal{}{?}
{Shuxue Wuli Xuebao}
{nan}
\DefineJournal{}{?}
{Shuxue Xuebao}
{nan}
\DefineJournal{}{?}
{Shuxue Yanjiu}
{nan}
\DefineJournal{}{?}
{Shuxue Zazhi}
{nan}
\DefineJournal{sjaag}{2470-6566}
{SIAM J. Appl. Algebra Geom.}
{SIAM Journal on Applied Algebra and Geometry}
\DefineJournal{sjads}{1536-0040}
{SIAM J. Appl. Dyn. Syst.}
{SIAM Journal on Applied Dynamical Systems}
\DefineJournal{sjam}{0036-1399}
{SIAM J. Appl. Math.}
{SIAM Journal on Applied Mathematics}
\DefineJournal{sjc}{0097-5397}
{SIAM J. Comput.}
{SIAM Journal on Computing}
\DefineJournal{sjco}{0363-0129}
{SIAM J. Control Optim.}
{SIAM Journal on Control and Optimization}
\DefineJournal{sjdm}{0895-4801}
{SIAM J. Discrete Math.}
{SIAM Journal on Discrete Mathematics}
\DefineJournal{sjfm}{1945-497X}
{SIAM J. Financial Math.}
{SIAM Journal on Financial Mathematics}
\DefineJournal{sjis}{1936-4954}
{SIAM J. Imaging Sci.}
{SIAM Journal on Imaging Sciences}
\DefineJournal{sjma}{0036-1410}
{SIAM J. Math. Anal.}
{SIAM Journal on Mathematical Analysis}
\DefineJournal{sjmaa}{0895-4798}
{SIAM J. Matrix Anal. Appl.}
{SIAM Journal on Matrix Analysis and Applications}
\DefineJournal{sjna}{0036-1429}
{SIAM J. Numer. Anal.}
{SIAM Journal on Numerical Analysis}
\DefineJournal{sjo}{1052-6234}
{SIAM J. Optim.}
{SIAM Journal on Optimization}
\DefineJournal{sjsc}{1064-8275}
{SIAM J. Sci. Comput.}
{SIAM Journal on Scientific Computing}
\DefineJournal{sn}{1557-9573}
{SIAM News}
{SIAM News}
\DefineJournal{sr}{0036-1445}
{SIAM Rev.}
{SIAM Review}
\DefineJournal{ss}{?ss}
{SIAM Spotlights}
{SIAM Spotlights}
\DefineJournal{sjuq}{2166-2525}
{SIAM/ASA J. Uncertain. Quantif.}
{SIAM/ASA Journal on Uncertainty Quantification}
\DefineJournal{sms}{1822-511X}
{Siauliai Math. Semin.}
{Siauliai Mathematical Seminar}
\DefineJournal{semisemr}{1813-3304}
{Sib. Elektron. Mat. Izv.}
{Sibirskie Elektronnye Matematicheskie Izvestiya. Siberian Electronic Mathematical Reports}
\DefineJournal{smj}{0037-4466}
{Sib. Math. J.}
{Siberian Mathematical Journal}
\DefineJournal{szcpm}{2411-3468}
{Sib. Zh. Chist. Prikl. Mat.}
{Sibirskii Zhurnal Chistoi i Prikladnoi Matematiki}
\DefineJournal{szim}{1560-7518}
{Sib. Zh. Ind. Mat.}
{Sibirskii Zhurnal Industrialnoi Matematiki}
\DefineJournal{szvmsjnmranso}{1560-7526}
{Sib. Zh. Vychisl. Mat.}
{Sibirskii Zhurnal Vychislitelnoi Matematiki. Siberian Journal of Numerical Mathematics. Rossiiskaya Akademiya Nauk. Sibirskoe Otdelenie}
\DefineJournal{sam}{1055-1344}
{Siberian Adv. Math.}
{Siberian Advances in Mathematics}
\DefineJournal{ransoimslssmz}{0037-4474}
{Sibirsk. Mat. Zh.}
{Rossiiskaya Akademiya Nauk. Sibirskoe Otdelenie. Institut Matematiki im. S. L. Soboleva. Sibirskii Matematicheskii Zhurnal}
\DefineJournal{}{?}
{Sichuan Daxue Xuebao Gongcheng Kexue Ban}
{nan}
\DefineJournal{ssigma}{1815-0659}
{SIGMA Symmetry Integrability Geom. Methods Appl.}
{SIGMA. Symmetry, Integrability and Geometry. Methods and Applications}
\DefineJournal{sct}{1860-4862}
{Signals Commun. Technol.}
{Signals and Communication Technology}
\DefineJournal{sn}{?sn}
{SIGPLAN Notices}
{SIGPLAN Notices}
\DefineJournal{islpsss}{?islpsss}
{SILFS Ser.}
{Italian Society for Logic and Philosophy of Science SILFS Series}
\DefineJournal{ss}{2365-9564}
{Simons Symp.}
{Simons Symposia}
\DefineJournal{ssc}{?ssc}
{Simula SpringerBriefs Comput.}
{Simula SpringerBriefs on Computing}
\DefineJournal{sawdmj}{?sawdmj}
{Sitzungsber. Akad. Wiss. DDR Math. Naturwiss. Tech. Jahrg. 1976}
{Sitzungsberichte der Akademie der Wissenschaften der DDR, Mathematik---Naturwissenschaften---Technik, Jahrgang 1976}
\DefineJournal{ssawlmkb}{?ssawlmkb}
{Sitzungsber. Sachsischen Akad. Wissenschaft. Leipzig. Math. Nat. Sci. Sect. Band 116}
{Sitzungsberichte der Sachsischen Akademie der Wissenschaften zu Leipzig. Mathematisch-naturwissenschaftliche Klasse. Band 116}
\DefineJournal{sjcm}{2426-8399}
{SMAI J. Comput. Math.}
{SMAI Journal of Computational Mathematics}
\DefineJournal{sist}{2190-3018}
{Smart Innov. Syst. Technol.}
{Smart Innovation, Systems and Technologies}
\DefineJournal{sja}{?sja}
{SMF Journ. Annu.}
{SMF Journee Annuelle}
\DefineJournal{scw}{0176-1714}
{Soc. Choice Welf.}
{Social Choice and Welfare}
\DefineJournal{smr}{0049-1241}
{Sociol. Methods Res.}
{Sociological Methods & Research}
\DefineJournal{ssy}{?ssy}
{Sociol. Sci. Yearbook}
{Sociology of the Sciences. Yearbook}
\DefineJournal{sbm}{2213-1736}
{Soft Biol. Matter}
{Soft and Biological Matter}
\DefineJournal{set}{?set}
{Software Environ. Tools}
{Software, Environments, and Tools}
\DefineJournal{sma}{0925-0042}
{Solid Mech. Appl.}
{Solid Mechanics and its Applications}
\DefineJournal{sscptc}{2211-1107}
{Sophia Stud. Cross-Cult. Philos. Tradit. Cult.}
{Sophia Studies in Cross-Cultural Philosophy of Traditions and Cultures}
\DefineJournal{ssort}{1696-2281}
{SORT}
{SORT. Statistics and Operations Research Transactions}
\DefineJournal{sshmps}{2196-8810}
{Sources Stud. Hist. Math. Phys. Sci.}
{Sources and Studies in the History of Mathematics and Physical Sciences}
\DefineJournal{sasjsst}{0038-271X}
{South African Statist. J.}
{South African Statistical Journal. Suid-Afrikaanse Statistiese Tydskrif}
\DefineJournal{sajl}{2446-6719}
{South Amer. J. Log.}
{South American Journal of Logic}
\DefineJournal{seajmms}{0972-7752}
{South East Asian J. Math. Math. Sci.}
{South East Asian Journal of Mathematics and Mathematical Sciences}
\DefineJournal{sabm}{0129-2021}
{Southeast Asian Bull. Math.}
{Southeast Asian Bulletin of Mathematics}
\DefineJournal{ssrapr}{0143-0394}
{Soviet Sci. Rev. Sect. A Phys. Rev.}
{Soviet Scientific Reviews/Section A: Physics Reviews}
\DefineJournal{sfp}{?sfp}
{Sovrem. Fiz.-Tekh. Probl.}
{Sovremennye Fiziko-Tekhnicheskie Problemy}
\DefineJournal{smfn}{2413-3639}
{Sovrem. Mat. Fundam. Napravl.}
{Sovremennaya Matematika. Fundamentalnye Napravleniya}
\DefineJournal{spm}{2226-5929}
{Sovrem. Probl. Mat.}
{Sovremennye Problemy Matematiki}
\DefineJournal{stl}{?stl}
{Space Technol. Libr.}
{Space Technology Library}
\DefineJournal{ss}{2211-6753}
{Spat. Stat.}
{Spatial Statistics}
\DefineJournal{sii}{?sii}
{Spec. Issue IMVI}
{Special Issue of IMVI}
\DefineJournal{sm}{2300-7451}
{Spec. Matrices}
{Special Matrices}
\DefineJournal{ss}{?ss}
{Spectr. Slovak.}
{Spectrum Slovakia}
\DefineJournal{asb}{?asb}
{Spectrum Book}
{A Spectrum Book}
\DefineJournal{sms}{?sms}
{SPIE Milest. Ser.}
{SPIE Milestone Series}
\DefineJournal{spfo}{?spfo}
{Spisy Ped. Fak. Ostrave}
{Spisy Pedagogicke Fakulty v Ostrave}
\DefineJournal{sa}{?sa}
{Springer Actuar.}
{Springer Actuarial}
\DefineJournal{sat}{1869-1730}
{Springer Aerosp. Technol.}
{Springer Aerospace Technology}
\DefineJournal{sb}{2365-0613}
{Springer Biogr.}
{Springer Biographies}
\DefineJournal{sbb}{2191-5482}
{Springer Briefs Bus.}
{Springer Briefs in Business}
\DefineJournal{sbes}{2191-5547}
{Springer Briefs Environ. Sci.}
{Springer Briefs in Environmental Science}
\DefineJournal{sbor}{2195-0482}
{Springer Briefs Oper. Res.}
{Springer Briefs in Operations Research}
\DefineJournal{sbwst}{2194-7244}
{Springer Briefs Water Sci. Technol.}
{Springer Briefs in Water Science and Technology}
\DefineJournal{scwm}{2194-9875}
{Springer Collect. Works Math.}
{Springer Collected Works in Mathematics}
\DefineJournal{sf}{1616-0533}
{Springer Finance}
{Springer Finance}
\DefineJournal{sfln}{?sfln}
{Springer Finance Lect. Notes}
{Springer Finance Lecture Notes}
\DefineJournal{sft}{?sft}
{Springer Finance Textb.}
{Springer Finance Textbooks}
\DefineJournal{sg}{2364-9127}
{Springer Geophys.}
{Springer Geophysics}
\DefineJournal{sgtp}{?sgtp}
{Springer Grad. Texts Philos.}
{Springer Graduate Texts in Philosophy}
\DefineJournal{sis}{2281-518X}
{Springer INdAM Ser.}
{Springer INdAM Series}
\DefineJournal{smm}{1439-7382}
{Springer Monogr. Math.}
{Springer Monographs in Mathematics}
\DefineJournal{soia}{1931-6828}
{Springer Optim. Appl.}
{Springer Optimization and Its Applications}
\DefineJournal{spar}{2511-1256}
{Springer Proc. Adv. Robot.}
{Springer Proceedings in Advanced Robotics}
\DefineJournal{spm}{2190-5614}
{Springer Proc. Math.}
{Springer Proceedings in Mathematics}
\DefineJournal{spms}{2194-1009}
{Springer Proc. Math. Stat.}
{Springer Proceedings in Mathematics & Statistics}
\DefineJournal{spp}{0930-8989}
{Springer Proc. Phys.}
{Springer Proceedings in Physics}
\DefineJournal{ssam}{1860-5168}
{Springer Ser. Adv. Manuf.}
{Springer Series in Advanced Manufacturing}
\DefineJournal{ssa}{2199-1030}
{Springer Ser. Astrostatistics}
{Springer Series in Astrostatistics}
\DefineJournal{ssaopp}{1615-5653}
{Springer Ser. At. Opt. Plasma Phys.}
{Springer Series on Atomic, Optical, and Plasma Physics}
\DefineJournal{ssb}{2193-9349}
{Springer Ser. Bio-/Neuroinform.}
{Springer Series in Bio-/Neuroinformatics}
\DefineJournal{sscm}{0179-3632}
{Springer Ser. Comput. Math.}
{Springer Series in Computational Mathematics}
\DefineJournal{ssds}{2365-5674}
{Springer Ser. Data Sci.}
{Springer Series in the Data Sciences}
\DefineJournal{tssdmpa}{1389-6784}
{Springer Ser. Demogr. Methods Popul. Anal.}
{The Springer Series on Demographic Methods and Population Analysis}
\DefineJournal{ssgt}{1868-517X}
{Springer Ser. Game Theory}
{Springer Series in Game Theory}
\DefineJournal{ssms}{0933-033X}
{Springer Ser. Mater. Sci.}
{Springer Series in Materials Science}
\DefineJournal{ssmst}{2198-7807}
{Springer Ser. Meas. Sci. Technol.}
{Springer Series in Measurement Science and Technology}
\DefineJournal{ssorfe}{1431-8598}
{Springer Ser. Oper. Res. Financ. Eng.}
{Springer Series in Operations Research and Financial Engineering}
\DefineJournal{ssos}{0342-4111}
{Springer Ser. Optical Sci.}
{Springer Series in Optical Sciences}
\DefineJournal{ssre}{1614-7839}
{Springer Ser. Reliab. Eng.}
{Springer Series in Reliability Engineering}
\DefineJournal{ssssm}{2195-3511}
{Springer Ser. Solid Struct. Mech.}
{Springer Series in Solid and Structural Mechanics}
\DefineJournal{ssss}{0171-1873}
{Springer Ser. Solid-State Sci.}
{Springer Series in Solid-State Sciences}
\DefineJournal{sss}{0172-7397}
{Springer Ser. Statist.}
{Springer Series in Statistics}
\DefineJournal{sssps}{2522-0411}
{Springer Ser. Statist. Perspect. Statist.}
{Springer Series in Statistics. Perspectives in Statistics}
\DefineJournal{sssshs}{?sssshs}
{Springer Ser. Statist. Statist. Health Sci.}
{Springer Series in Statistics: Statistics in the Health Sciences}
\DefineJournal{ssss}{0931-5195}
{Springer Ser. Surface Sci.}
{Springer Series in Surface Sciences}
\DefineJournal{sss}{0172-7389}
{Springer Ser. Synergetics}
{Springer Series in Synergetics}
\DefineJournal{ssm}{2509-9310}
{Springer Stud. Math. Master}
{Springer Studium Mathematik---Master}
\DefineJournal{stbe}{2192-4333}
{Springer Texts Bus. Econ.}
{Springer Texts in Business and Economics}
\DefineJournal{sts}{1431-875X}
{Springer Texts Statist.}
{Springer Texts in Statistics}
\DefineJournal{st}{2190-5053}
{Springer Theses}
{Springer Theses}
\DefineJournal{stsp}{1866-2608}
{Springer Top. Signal Process.}
{Springer Topics in Signal Processing}
\DefineJournal{star}{1610-7438}
{Springer Tracts Adv. Robot.}
{Springer Tracts in Advanced Robotics}
\DefineJournal{stce}{2366-259X}
{Springer Tracts Civ. Eng.}
{Springer Tracts in Civil Engineering}
\DefineJournal{stme}{2195-9862}
{Springer Tracts Mech. Eng.}
{Springer Tracts in Mechanical Engineering}
\DefineJournal{stmp}{0081-3869}
{Springer Tracts Modern Phys.}
{Springer Tracts in Modern Physics}
\DefineJournal{sttt}{2194-8119}
{Springer Tracts Transp. Traffic}
{Springer Tracts on Transportation and Traffic}
\DefineJournal{sur}{2199-3807}
{Springer Uncertain. Res.}
{Springer Uncertainty Research}
\DefineJournal{sums}{1615-2085}
{Springer Undergrad. Math. Ser.}
{Springer Undergraduate Mathematics Series}
\DefineJournal{suts}{?suts}
{Springer Undergrad. Textb. Stat.}
{Springer Undergraduate Textbooks in Statistics}
\DefineJournal{sutmt}{1867-5506}
{Springer Undergrad. Texts Math. Technol.}
{Springer Undergraduate Texts in Mathematics and Technology}
\DefineJournal{sutp}{2569-8737}
{Springer Undergrad. Texts Philos.}
{Springer Undergraduate Texts in Philosophy}
\DefineJournal{s}{0937-7433}
{Springer-Lehrbuch}
{Springer-Lehrbuch}
\DefineJournal{sbes}{?sbes}
{Springer-Praxis Books Environ. Sci.}
{Springer-Praxis Books in Environmental Sciences}
\DefineJournal{sast}{2191-530X}
{SpringerBriefs Appl. Sci. Technol.}
{SpringerBriefs in Applied Sciences and Technology}
\DefineJournal{sa}{2191-9100}
{SpringerBriefs Astron.}
{SpringerBriefs in Astronomy}
\DefineJournal{sc}{2191-5326}
{SpringerBriefs Complex.}
{SpringerBriefs in Complexity}
\DefineJournal{sci}{2520-8551}
{SpringerBriefs Comput. Intell.}
{SpringerBriefs in Computational Intelligence}
\DefineJournal{scm}{2191-5342}
{SpringerBriefs Comput. Mech.}
{SpringerBriefs in Computational Mechanics}
\DefineJournal{scs}{2191-5768}
{SpringerBriefs Comput. Sci.}
{SpringerBriefs in Computer Science}
\DefineJournal{scm}{?scm}
{SpringerBriefs Contin. Mech.}
{SpringerBriefs in Continuum Mechanics}
\DefineJournal{scar}{2192-6786}
{SpringerBriefs Control Autom. Robot.}
{SpringerBriefs in Control, Automation and Robotics}
\DefineJournal{ses}{2191-5369}
{SpringerBriefs Earth Sci.}
{SpringerBriefs in Earth Sciences}
\DefineJournal{se}{2192-4759}
{SpringerBriefs Ecol.}
{SpringerBriefs in Ecology}
\DefineJournal{se}{2191-5504}
{SpringerBriefs Econ.}
{SpringerBriefs in Economics}
\DefineJournal{sece}{2191-8112}
{SpringerBriefs Electr. Comput. Eng.}
{SpringerBriefs in Electrical and Computer Engineering}
\DefineJournal{sf}{2193-1720}
{SpringerBriefs Finance}
{SpringerBriefs in Finance}
\DefineJournal{shst}{2211-4564}
{SpringerBriefs Hist. Sci. Technol.}
{SpringerBriefs in History of Science and Technology}
\DefineJournal{sis}{2196-548X}
{SpringerBriefs Intell. Syst.}
{SpringerBriefs in Intelligent Systems}
\DefineJournal{sm}{2191-8198}
{SpringerBriefs Math.}
{SpringerBriefs in Mathematics}
\DefineJournal{smm}{2365-6336}
{SpringerBriefs Math. Mater.}
{SpringerBriefs in the Mathematics of Materials}
\DefineJournal{smm}{?smm}
{SpringerBriefs Math. Methods}
{SpringerBriefs in Mathematical Methods}
\DefineJournal{smp}{2197-1757}
{SpringerBriefs Math. Phys.}
{SpringerBriefs in Mathematical Physics}
\DefineJournal{smpe}{2509-7326}
{SpringerBriefs Math. Planet Earth}
{SpringerBriefs in Mathematics of Planet Earth}
\DefineJournal{snc}{2520-1433}
{SpringerBriefs Nonlinear Circuits}
{SpringerBriefs in Nonlinear Circuits}
\DefineJournal{so}{2190-8354}
{SpringerBriefs Optim.}
{SpringerBriefs in Optimization}
\DefineJournal{sp}{2211-4548}
{SpringerBriefs Philos.}
{SpringerBriefs in Philosophy}
\DefineJournal{sp}{2191-5423}
{SpringerBriefs Phys.}
{SpringerBriefs in Physics}
\DefineJournal{spms}{2365-4333}
{SpringerBriefs Probab. Math. Stat.}
{SpringerBriefs in Probability and Mathematical Statistics}
\DefineJournal{sqf}{2192-7006}
{SpringerBriefs Quant. Finance}
{SpringerBriefs in Quantitative Finance}
\DefineJournal{ssp}{2196-4076}
{SpringerBriefs Signal Process.}
{SpringerBriefs in Signal Processing}
\DefineJournal{ss}{2191-544X}
{SpringerBriefs Stat.}
{SpringerBriefs in Statistics}
\DefineJournal{ssm}{2520-8020}
{SpringerBriefs Struct. Mech.}
{SpringerBriefs in Structural Mechanics}
\DefineJournal{steas}{2193-2530}
{SpringerBriefs Therm. Eng. Appl. Sci.}
{SpringerBriefs in Thermal Engineering and Applied Science}
\DefineJournal{skw}{0937-6836}
{Springers Kurzlehrb. Wirtsch.}
{Springers Kurzlehrbucher der Wirtschaftswissenschaften}
\DefineJournal{spmj}{1061-0022}
{St. Petersburg Math. J.}
{St. Petersburg Mathematical Journal}
\DefineJournal{soos}{?soos}
{Stab. Oscil. Optim. Syst.}
{Stability, Oscillations and Optimization of Systems}
\DefineJournal{s}{2049-1573}
{Stat}
{Stat}
\DefineJournal{sadm}{1932-1864}
{Stat. Anal. Data Min.}
{Statistical Analysis and Data Mining}
\DefineJournal{sagmb}{2194-6302}
{Stat. Appl. Genet. Mol. Biol.}
{Statistical Applications in Genetics and Molecular Biology}
\DefineJournal{sbh}{1431-8776}
{Stat. Biol. Health}
{Statistics for Biology and Health}
\DefineJournal{scid}{1948-4690}
{Stat. Commun. Infec. Dis.}
{Statistical Communications in Infectious Diseases}
\DefineJournal{sc}{0960-3174}
{Stat. Comput.}
{Statistics and Computing}
\DefineJournal{sit}{2364-6241}
{Stat. Ind. Technol.}
{Statistics for Industry and Technology}
\DefineJournal{sispaijdtsasctpds}{1387-0874}
{Stat. Inference Stoch. Process.}
{Statistical Inference for Stochastic Processes. An International Journal Devoted to Time Series Analysis and the Statistics of Continuous Time Processes and Dynamical Systems}
\DefineJournal{si}{1938-7989}
{Stat. Interface}
{Statistics and its Interface}
\DefineJournal{sm}{0277-6715}
{Stat. Med.}
{Statistics in Medicine}
\DefineJournal{sm}{1572-3127}
{Stat. Methodol.}
{Statistical Methodology}
\DefineJournal{smajiss}{1618-2510}
{Stat. Methods Appl.}
{Statistical Methods & Applications. Journal of the Italian Statistical Society}
\DefineJournal{smmr}{0962-2802}
{Stat. Methods Med. Res.}
{Statistical Methods in Medical Research}
\DefineJournal{smaij}{1471-082X}
{Stat. Model.}
{Statistical Modelling. An International Journal}
\DefineJournal{snjnssor}{0039-0402}
{Stat. Neerl.}
{Statistica Neerlandica. Journal of the Netherlands Society for Statistics and Operations Research}
\DefineJournal{soic}{2311-004X}
{Stat. Optim. Inf. Comput.}
{Statistics, Optimization & Information Computing}
\DefineJournal{srmafi}{2193-1402}
{Stat. Risk Model.}
{Statistics & Risk Modeling with Applications in Finance and Insurance}
\DefineJournal{ssir}{1793-6195}
{Stat. Sci. Interdiscip. Res.}
{Statistical Science and Interdisciplinary Research}
\DefineJournal{ssbs}{2199-7357}
{Stat. Soc. Behav. Sci.}
{Statistics for Social and Behavioral Sciences}
\DefineJournal{ssbss}{?ssbss}
{Stat. Soc. Behav. Sci. Ser.}
{Statistics in the Social and Behavioral Sciences Series}
\DefineJournal{ss}{1935-7516}
{Stat. Surv.}
{Statistics Surveys}
\DefineJournal{stm}{?stm}
{Stat. Textb. Monogr.}
{Statistics: Textbooks and Monographs}
\DefineJournal{sar}{?sar}
{State Art Rep.}
{State of the Art Reports}
\DefineJournal{sdgtfa}{2363-8516}
{Static Dyn. Game Theory Found. Appl.}
{Static & Dynamic Game Theory: Foundations & Applications}
\DefineJournal{sc}{1431-8784}
{Statist. Comput.}
{Statistics and Computing}
\DefineJournal{sde}{?sde}
{Statist. Decisions Econom.}
{Statistique et Decisions Economiques}
\DefineJournal{ses}{?ses}
{Statist. Ecology Ser.}
{Statistical Ecology Series}
\DefineJournal{shs}{?shs}
{Statist. Health Sci.}
{Statistics in the Health Sciences}
\DefineJournal{smei}{?smei}
{Statist. Metody Ekonom. Issled.}
{Statisticheskie Metody v Ekonomicheskikh Issledovaniyakh}
\DefineJournal{smds}{?smds}
{Statist. Model. Decis. Sci.}
{Statistical Modeling and Decision Science}
\DefineJournal{sp}{0932-5026}
{Statist. Papers}
{Statistical Papers}
\DefineJournal{sp}{?sp}
{Statist. Practice}
{Statistics in Practice}
\DefineJournal{spl}{0167-7152}
{Statist. Probab. Lett.}
{Statistics & Probability Letters}
\DefineJournal{ssarjims}{0883-4237}
{Statist. Sci.}
{Statistical Science. A Review Journal of the Institute of Mathematical Statistics}
\DefineJournal{ss}{1017-0405}
{Statist. Sinica}
{Statistica Sinica}
\DefineJournal{sajtas}{0233-1888}
{Statistics}
{Statistics. A Journal of Theoretical and Applied Statistics}
\DefineJournal{ssteamh}{2520-193X}
{STEAM-H: Sci. Technol. Eng. Agric. Math. Health}
{STEAM-H: Science, Technology, Engineering, Agriculture, Mathematics & Health}
\DefineJournal{saa}{0736-2994}
{Stoch. Anal. Appl.}
{Stochastic Analysis and Applications}
\DefineJournal{sd}{0219-4937}
{Stoch. Dyn.}
{Stochastics and Dynamics}
\DefineJournal{smap}{0172-4568}
{Stoch. Model. Appl. Probab.}
{Stochastic Modelling and Applied Probability}
\DefineJournal{sm}{1532-6349}
{Stoch. Models}
{Stochastic Models}
\DefineJournal{smsars}{?smsars}
{Stoch. Models Surviv. Anal. Reliab. Set}
{Stochastic Models in Survival Analysis and Reliability Set}
\DefineJournal{spdeac}{2194-0401}
{Stoch. Partial Differ. Equ. Anal. Comput.}
{Stochastic Partial Differential Equations. Analysis and Computations}
\DefineJournal{sqc}{2367-2390}
{Stoch. Qual. Control}
{Stochastics and Quality Control}
\DefineJournal{ss}{1946-5238}
{Stoch. Syst.}
{Stochastic Systems}
\DefineJournal{spa}{0304-4149}
{Stochastic Process. Appl.}
{Stochastic Processes and their Applications}
\DefineJournal{saijpsp}{1744-2508}
{Stochastics}
{Stochastics. An International Journal of Probability and Stochastic Processes}
\DefineJournal{semamj}{1070-5511}
{Struct. Equ. Model.}
{Structural Equation Modeling. A Multidisciplinary Journal}
\DefineJournal{si}{2522-560X}
{Struct. Integr.}
{Structural Integrity}
\DefineJournal{smo}{1615-147X}
{Struct. Multidiscip. Optim.}
{Structural and Multidisciplinary Optimization}
\DefineJournal{sawsisouh}{?sawsisouh}
{Stud. Angew. Wirtschaftsforsch. Statist. Inst. Statist. Okonom. Univ. Hamburg}
{Studien zur Angewandten Wirtschaftsforschung und Statistik aus dem Institut fur Statistik und Okonometrie der Universitat Hamburg}
\DefineJournal{sam}{0022-2526}
{Stud. Appl. Math.}
{Studies in Applied Mathematics}
\DefineJournal{sapere}{2192-6255}
{Stud. Appl. Philos. Epistemol. Ration. Ethics}
{Studies in Applied Philosophy, Epistemology and Rational Ethics}
\DefineJournal{sba}{?sba}
{Stud. Behav. Adapt.}
{Studies in Behavioural Adaptation}
\DefineJournal{sbd}{2197-6503}
{Stud. Big Data}
{Studies in Big Data}
\DefineJournal{scw}{1614-0311}
{Stud. Choice Welf.}
{Studies in Choice and Welfare}
\DefineJournal{scdako}{1431-8814}
{Stud. Classification Data Anal. Knowledge Organ.}
{Studies in Classification, Data Analysis, and Knowledge Organization}
\DefineJournal{sci}{1860-949X}
{Stud. Comput. Intell.}
{Studies in Computational Intelligence}
\DefineJournal{scm}{1570-578X}
{Stud. Comput. Math.}
{Studies in Computational Mathematics}
\DefineJournal{set}{1431-8849}
{Stud. Econom. Theory}
{Studies in Economic Theory}
\DefineJournal{sfsc}{1434-9922}
{Stud. Fuzziness Soft Comput.}
{Studies in Fuzziness and Soft Computing}
\DefineJournal{shme}{?shme}
{Stud. Hist. Math. Enq.}
{Studies in the History of Mathematical Enquiry}
\DefineJournal{shps}{0929-6425}
{Stud. Hist. Philos. Sci.}
{Studies in History and Philosophy of Science}
\DefineJournal{shpspbshpmp}{1355-2198}
{Stud. Hist. Philos. Sci. B Stud. Hist. Philos. Modern Phys.}
{Studies in History and Philosophy of Science. Part B. Studies in History and Philosophy of Modern Physics}
\DefineJournal{sk}{?sk}
{Stud. Knowledge}
{Studies in Knowledge}
\DefineJournal{slcs}{?slcs}
{Stud. Language Companion Ser. (SLCS)}
{Studies in Language Companion Series (SLCS)}
\DefineJournal{slp}{0924-4662}
{Stud. Linguist. Philos.}
{Studies in Linguistics and Philosophy}
\DefineJournal{sl}{?sl}
{Stud. Log. (Lond.)}
{Studies in Logic (London)}
\DefineJournal{slpr}{1570-2464}
{Stud. Log. Pract. Reason.}
{Studies in Logic and Practical Reasoning}
\DefineJournal{slfm}{0049-237X}
{Stud. Logic Found. Math.}
{Studies in Logic and the Foundations of Mathematics}
\DefineJournal{sml}{1520-9121}
{Stud. Math. Libr.}
{Student Mathematical Library}
\DefineJournal{smteb}{1868-2006}
{Stud. Mechanobiol. Tissue Eng. Biomater.}
{Studies in Mechanobiology, Tissue Engineering and Biomaterials}
\DefineJournal{sm}{2214-0042}
{Stud. Morphol.}
{Studies in Morphology}
\DefineJournal{snllt}{0924-4670}
{Stud. Nat. Lang. Linguist Theory}
{Studies in Natural Language and Linguistic Theory}
\DefineJournal{snde}{1558-3708}
{Stud. Nonlinear Dyn. Econom.}
{Studies in Nonlinear Dynamics & Econometrics}
\DefineJournal{snpls}{?snpls}
{Stud. Nonlinear Phenom. Life Sci.}
{Studies of Nonlinear Phenomena in Life Science}
\DefineJournal{sp}{1406-0000}
{Stud. Philos.}
{Studia Philosophica}
\DefineJournal{spnpt}{1871-188X}
{Stud. Platonism Neoplatonism Platonic Tradit.}
{Studies in Platonism, Neoplatonism, and the Platonic Tradition}
\DefineJournal{spc}{0924-4700}
{Stud. Public Choice}
{Studies in Public Choice}
\DefineJournal{ssw}{1868-1158}
{Stud. Semant. Web}
{Studies on the Semantic Web}
\DefineJournal{ssdc}{2198-4182}
{Stud. Syst. Decis. Control}
{Studies in Systems, Decision and Control}
\DefineJournal{st}{?st}
{Stud. Texts}
{Studies and Texts}
\DefineJournal{stasspss}{2194-7767}
{Stud. Theor. Appl. Stat. Sel. Papers Stat. Soc.}
{Studies in Theoretical and Applied Statistics. Selected Papers of the Statistical Societies}
\DefineJournal{stp}{2199-5214}
{Stud. Theor. Philos.}
{Studies in Theoretical Philosophy}
\DefineJournal{stp}{1873-0043}
{Stud. Theor. Psycholinguist.}
{Studies in Theoretical Psycholinguistics}
\DefineJournal{subi}{1224-869X}
{Stud. Univ. Babes-Bolyai Inform.}
{Studia. Universitatis Babes-Bolyai. Informatica}
\DefineJournal{subm}{0252-1938}
{Stud. Univ. Babes-Bolyai Math.}
{Studia. Universitatis Babes-Bolyai Mathematica}
\DefineJournal{suzms}{1336-149X}
{Stud. Univ. Zilina Math. Ser.}
{Studies of the University of Zilina. Mathematical Series}
\DefineJournal{sul}{2297-0282}
{Stud. Univers. Log.}
{Studies in Universal Logic}
\DefineJournal{sw}{?sw}
{Stud. Wirtsch.math.}
{Studienbucher Wirtschaftsmathematik}
\DefineJournal{szi}{?szi}
{Stud. Zakresu Inz.}
{Studia z Zakresu Inzynierii}
\DefineJournal{scisui}{?scisui}
{Studi Cent. Interuniv. Stor. Univ. Ital.}
{Studi. Centro Interuniversitario per la Storia delle Universita Italiane}
\DefineJournal{slaijsl}{0039-3215}
{Studia Logica}
{Studia Logica. An International Journal for Symbolic Logic}
\DefineJournal{sm}{0039-3223}
{Studia Math.}
{Studia Mathematica}
\DefineJournal{sm}{?sm}
{Studia Math.}
{Studia Mathematica}
\DefineJournal{ssmhaqhas}{0081-6906}
{Studia Sci. Math. Hungar.}
{Studia Scientiarum Mathematicarum Hungarica. A Quarterly of the Hungarian Academy of Sciences}
\DefineJournal{sm}{?sm}
{Studienbucher Math.}
{Studienbucher Mathematik}
\DefineJournal{stw}{?stw}
{Studienbucher Tech. Wiss.}
{Studienbucher der Technischen Wissenschaften}
\DefineJournal{sc}{?sc}
{Subser. Control}
{Subseries in Control}
\DefineJournal{msjs}{0039-470X}
{Sugaku}
{Mathematical Society of Japan. Sugaku (Mathematics)}
\DefineJournal{se}{0898-9583}
{Sugaku Expositions}
{Sugaku Expositions}
\DefineJournal{sr}{?sr}
{Sugaku no Rekishi}
{Sugaku no Rekishi}
\DefineJournal{ss}{?ss}
{Sugaku Sensho}
{Sugaku Sensho}
\DefineJournal{sijhensic}{1576-9372}
{Suhayl}
{Suhayl. International Journal for the History of the Exact and Natural Sciences in Islamic Civilisation}
\DefineJournal{sat}{1555-578X}
{Surv. Approx. Theory}
{Surveys in Approximation Theory}
\DefineJournal{sdg}{?sdg}
{Surv. Differ. Geom.}
{Surveys in Differential Geometry}
\DefineJournal{sma}{1843-7265}
{Surv. Math. Appl.}
{Surveys in Mathematics and its Applications}
\DefineJournal{smm}{?smm}
{Surv. Mod. Math.}
{Surveys of Modern Mathematics}
\DefineJournal{sorms}{1876-7354}
{Surv. Oper. Res. Manag. Sci.}
{Surveys in Operations Research and Management Science}
\DefineJournal{sjm}{0916-5746}
{SUT J. Math.}
{SUT Journal of Mathematics}
\DefineJournal{si}{2239-2688}
{Sxi Springer Innov.}
{Sxi---Springer per l'Innovazione/Sxi---Springer for Innovation}
\DefineJournal{sccg}{1431-1399}
{Symbol. Comput. Comput. Graph.}
{Symbolic Computation. Computer Graphics}
\DefineJournal{slase}{1938-1727}
{Synth. Lect. Algorithms Softw. Eng.}
{Synthesis Lectures on Algorithms and Software in Engineering}
\DefineJournal{slaiml}{1939-4608}
{Synth. Lect. Artif. Intell. Mach. Learn.}
{Synthesis Lectures on Artificial Intelligence and Machine Learning}
\DefineJournal{slcv}{2153-1056}
{Synth. Lect. Comput. Vis.}
{Synthesis Lectures on Computer Vision}
\DefineJournal{sldmkd}{2151-0067}
{Synth. Lect. Data Min. Knowl. Discov.}
{Synthesis Lectures on Data Mining and Knowledge Discovery}
\DefineJournal{sldcs}{1932-3166}
{Synth. Lect. Digit. Circuits Syst.}
{Synthesis Lectures on Digital Circuits and Systems}
\DefineJournal{slgci}{2573-6485}
{Synth. Lect. Games Comput. Intell.}
{Synthesis Lectures on Games and Computational Intelligence}
\DefineJournal{slhlt}{1947-4040}
{Synth. Lect. Hum. Lang. Technol.}
{Synthesis Lectures on Human Language Technologies}
\DefineJournal{slms}{1930-1743}
{Synth. Lect. Math. Stat.}
{Synthesis Lectures on Mathematics and Statistics}
\DefineJournal{sltcs}{?sltcs}
{Synth. Lect. Theor. Comput. Sci.}
{Synthesis Lectures on Theoretical Computer Science}
\DefineJournal{slvc}{2469-4215}
{Synth. Lect. Vis. Comput.}
{Synthesis Lectures on Visual Computing}
\DefineJournal{slselmps}{?slselmps}
{Synth. Libr.}
{Synthese Library. Studies in Epistemology, Logic, Methodology, and Philosophy of Science}
\DefineJournal{saijemps}{0039-7857}
{Synthese}
{Synthese. An International Journal for Epistemology, Methodology and Philosophy of Science}
\DefineJournal{s}{?s}
{Synthese}
{Synthese}
\DefineJournal{sl}{?sl}
{Synthese Lib.}
{Synthese Library}
\DefineJournal{sl}{?sl}
{Synthese Lib.}
{Synthese Library}
\DefineJournal{sepds}{?sepds}
{Syst. Eval. Predict. Decis.-Mak. Ser.}
{Systems Evaluation, Prediction, and Decision-Making Series}
\DefineJournal{sdfbs}{?sdfbs}
{System Develop. Found. Benchmark Ser.}
{System Development Foundation Benchmark Series}
\DefineJournal{scfa}{2324-9749}
{Systems Control Found. Appl.}
{Systems & Control: Foundations & Applications}
\DefineJournal{scl}{0167-6911}
{Systems Control Lett.}
{Systems & Control Letters}
\DefineJournal{tn}{?tn}
{Tableau Noir}
{Tableau Noir}
\DefineJournal{tjm}{1027-5487}
{Taiwanese J. Math.}
{Taiwanese Journal of Mathematics}
\DefineJournal{tjm}{0049-2930}
{Tamkang J. Math.}
{Tamkang Journal of Mathematics}
\DefineJournal{tojims}{2222-4424}
{Tamsui Oxf. J. Inf. Math. Sci.}
{Tamsui Oxford Journal of Information and Mathematical Sciences}
\DefineJournal{t}{?t}
{Taschentext}
{Taschentext}
\DefineJournal{tmmp}{1210-3195}
{Tatra Mt. Math. Publ.}
{Tatra Mountains Mathematical Publications}
\DefineJournal{tmj}{1512-0139}
{Tbilisi Math. J.}
{Tbilisi Mathematical Journal}
\DefineJournal{tes}{?tes}
{Tech. Ed. Ser.}
{Technology in Education Series}
\DefineJournal{ttm}{?ttm}
{Tech. Tworczego Myslenia}
{Techniki Tworczego Myslenia}
\DefineJournal{te}{?te}
{Technikgesch. Einzeldarst.}
{Technikgeschichte in Einzeldarstellungen}
\DefineJournal{trs}{?trs}
{Technol. Risk Soc.}
{Technology, Risk, and Society}
\DefineJournal{tajspces}{0040-1706}
{Technometrics}
{Technometrics. A Journal of Statistics for the Physical, Chemical and Engineering Sciences}
\DefineJournal{ttmac}{1677-1966}
{TEMA Tend. Mat. Apl. Comput.}
{TEMA. Tendencias em Matematica Aplicada e Computacional}
\DefineJournal{ttstns}{0040-3504}
{Tensor (N.S.)}
{The Tensor Society. Tensor. New Series}
\DefineJournal{timskuts}{0868-6904}
{Teor. Imovir. Mat. Stat.}
{Teoriya Imovirnostei ta Matematichna Statistika. Kiivskii Universitet imeni Tarasa Shevchenka}
\DefineJournal{rantvp}{0040-361X}
{Teor. Veroyatn. Primen.}
{Rossiiskaya Akademiya Nauk. Teoriya Veroyatnostei i ee Primeneniya}
\DefineJournal{rantmf}{0564-6162}
{Teoret. Mat. Fiz.}
{Rossiiskaya Akademiya Nauk. Teoreticheskaya i Matematicheskaya Fizika}
\DefineJournal{tp}{?tp}
{Tesi Perfez.}
{Tesi di Perfezionamento}
\DefineJournal{tsnsps}{?tsnsps}
{Tesi Sc. Norm. Super. Pisa (N. S.)}
{Tesi. Scuola Normale Superiore di Pisa (Nuova Series)}
\DefineJournal{t}{1133-0686}
{TEST}
{TEST}
\DefineJournal{tsw}{?tsw}
{Teubner Stud.buch. Wirtsch.wiss.}
{Teubner Studienbucher Wirtschaftswissenschaften}
\DefineJournal{tsp}{?tsp}
{Teubner Studienbuch. Phys./Chem.}
{Teubner Studienbucher Physik/Chemie}
\DefineJournal{tsmi}{?tsmi}
{Teubner Studienskr. Math. Ingen.}
{Teubner Studienskripten: Mathematik, Ingenieurwissenschaften}
\DefineJournal{teee}{?teee}
{Textb. Electr. Electron. Eng.}
{Textbooks in Electrical and Electronic Engineering}
\DefineJournal{tm}{?tm}
{Textb. Math.}
{Textbooks in Mathematics}
\DefineJournal{tsps}{?tsps}
{Textb. Ser. Phys. Sci.}
{Textbook Series in Physical Sciences}
\DefineJournal{tema}{?tema}
{Textes Etudes Moyen Age}
{Textes et Etudes du Moyen Age}
\DefineJournal{tme}{?tme}
{Textos Man. Ensen.}
{Textos y Manuales de Ensenanza}
\DefineJournal{tmt}{?tmt}
{Textos Mat./Math. Texts}
{Textos de Matematica/Mathematics Texts}
\DefineJournal{ta}{?ta}
{Texts Algorithmics}
{Texts in Algorithmics}
\DefineJournal{tam}{0939-2475}
{Texts Appl. Math.}
{Texts in Applied Mathematics}
\DefineJournal{tcs}{1868-0941}
{Texts Comput. Sci.}
{Texts in Computer Science}
\DefineJournal{tcse}{1611-0994}
{Texts Comput. Sci. Eng.}
{Texts in Computational Science and Engineering}
\DefineJournal{tmsc}{0943-853X}
{Texts Monogr. Symbol. Comput.}
{Texts and Monographs in Symbolic Computation}
\DefineJournal{tp}{?tp}
{Texts Philos.}
{Texts in Philosophy}
\DefineJournal{tqct}{2523-8647}
{Texts Quant. Crit. Think.}
{Texts for Quantitative Critical Thinking}
\DefineJournal{trm}{?trm}
{Texts Read. Math.}
{Texts and Readings in Mathematics}
\DefineJournal{trps}{2366-8849}
{Texts Read. Phys. Sci.}
{Texts and Readings in Physical Sciences}
\DefineJournal{tsss}{?tsss}
{Texts Statist. Sci. Ser.}
{Texts in Statistical Science Series}
\DefineJournal{ttcsaes}{1862-4499}
{Texts Theoret. Comput. Sci. EATCS Ser.}
{Texts in Theoretical Computer Science. An EATCS Series}
\DefineJournal{tjm}{1686-0209}
{Thai J. Math.}
{Thai Journal of Mathematics}
\DefineJournal{tme}{?tme}
{Themes Mod. Econom.}
{Themes in Modern Econometrics}
\DefineJournal{tbt}{?tbt}
{Theol. Bibl. Topelmann}
{Theologische Bibliothek Topelmann}
\DefineJournal{tb}{2522-0438}
{Theor. Biol.}
{Theoretical Biology}
\DefineJournal{tcfd}{0935-4964}
{Theor. Comput. Fluid Dyn.}
{Theoretical and Computational Fluid Dynamics}
\DefineJournal{te}{1933-6837}
{Theor. Econ.}
{Theoretical Economics}
\DefineJournal{tmp}{0040-5779}
{Theoret. and Math. Phys.}
{Theoretical and Mathematical Physics}
\DefineJournal{tcs}{0304-3975}
{Theoret. Comput. Sci.}
{Theoretical Computer Science}
\DefineJournal{tmp}{1864-5879}
{Theoret. Math. Phys.}
{Theoretical and Mathematical Physics}
\DefineJournal{tasjp}{0040-5825}
{Theoria}
{Theoria. A Swedish Journal of Philosophy}
\DefineJournal{trthfcseaijthfsss}{0495-4548}
{Theoria (San Sebastian) (2)}
{Theoria. Revista de Teoria, Historia y Fundamentos de la Ciencia. Segunda Epoca. An International Journal for Theory, History and Foundations of Science. Second Series}
\DefineJournal{tdaijmads}{0040-5833}
{Theory and Decision}
{Theory and Decision. An International Journal for Multidisciplinary Advances in Decision Science}
\DefineJournal{tac}{1201-561X}
{Theory Appl. Categ.}
{Theory and Applications of Categories}
\DefineJournal{tac}{2190-619X}
{Theory Appl. Comput.}
{Theory and Applications of Computability}
\DefineJournal{tag}{2470-9859}
{Theory Appl. Graphs}
{Theory and Applications of Graphs}
\DefineJournal{tamcs}{2067-2764}
{Theory Appl. Math. Comput. Sci.}
{Theory and Applications of Mathematics & Computer Science}
\DefineJournal{tanlp}{2192-032X}
{Theory Appl. Nat. Lang. Process.}
{Theory and Applications of Natural Language Processing}
\DefineJournal{tatpm}{0924-6118}
{Theory Appl. Transp. Porous Media}
{Theory and Applications of Transport in Porous Media}
\DefineJournal{tcaoaj}{1557-2862}
{Theory Comput.}
{Theory of Computing. An Open Access Journal}
\DefineJournal{tcs}{1432-4350}
{Theory Comput. Syst.}
{Theory of Computing Systems}
\DefineJournal{tdlcgtscdto}{0924-6126}
{Theory Decis. Libr. C, Game Theory Soc. Choice Decis. Theory Optim.}
{Theory and Decision Library C. Game Theory, Social Choice, Decision Theory, and Optimization}
\DefineJournal{tdlscgtmpor}{0924-6126}
{Theory Decis. Libr. Ser. C Game Theory Math. Program. Oper. Res.}
{Theory and Decision Library. Series C: Game Theory, Mathematical Programming and Operations Research}
\DefineJournal{tplp}{1471-0684}
{Theory Pract. Log. Program.}
{Theory and Practice of Logic Programming}
\DefineJournal{tpa}{0040-585X}
{Theory Probab. Appl.}
{Theory of Probability and its Applications}
\DefineJournal{tpms}{0094-9000}
{Theory Probab. Math. Statist.}
{Theory of Probability and Mathematical Statistics}
\DefineJournal{tsp}{0321-3900}
{Theory Stoch. Process.}
{Theory of Stochastic Processes}
\DefineJournal{t}{?t}
{These}
{These}
\DefineJournal{tsam}{?tsam}
{Theta Ser. Adv. Math.}
{Theta Series in Advanced Mathematics}
\DefineJournal{ta}{?ta}
{TIRE A}
{TIRE A}
\DefineJournal{ttmjss}{0040-8735}
{Tohoku Math. J. (2)}
{The Tohoku Mathematical Journal. Second Series}
\DefineJournal{tjm}{0387-3870}
{Tokyo J. Math.}
{Tokyo Journal of Mathematics}
\DefineJournal{t}{1134-5764}
{TOP}
{TOP}
\DefineJournal{tbc}{1875-1288}
{Top. Biodivers. Conserv.}
{Topics in Biodiversity and Conservation}
\DefineJournal{tiei}{2193-9411}
{Top. Intell. Eng. Inform.}
{Topics in Intelligent Engineering and Informatics}
\DefineJournal{tsrrq}{1566-0443}
{Top. Saf. Risk Reliab. Qual.}
{Topics in Safety, Risk, Reliability and Quality}
\DefineJournal{tap}{0303-4216}
{Topics Appl. Phys.}
{Topics in Applied Physics}
\DefineJournal{tairp}{0167-7411}
{Topoi}
{Topoi. An International Review of Philosophy}
\DefineJournal{taa}{2299-3231}
{Topol. Algebra Appl.}
{Topological Algebra and its Application}
\DefineJournal{tmna}{1230-3429}
{Topol. Methods Nonlinear Anal.}
{Topological Methods in Nonlinear Analysis}
\DefineJournal{ta}{0166-8641}
{Topology Appl.}
{Topology and its Applications}
\DefineJournal{tp}{0146-4124}
{Topology Proc.}
{Topology Proceedings}
\DefineJournal{tmj}{1880-6015}
{Toyama Math. J.}
{Toyama Mathematical Journal}
\DefineJournal{tim}{1812-5093}
{Tr. Inst. Mat.}
{Trudy Instituta Matematiki}
\DefineJournal{timm}{0134-4889}
{Tr. Inst. Mat. Mekh.}
{Trudy Instituta Matematiki i Mekhaniki}
\DefineJournal{tipmm}{1683-4720}
{Tr. Inst. Prikl. Mat. Mekh.}
{Trudy Instituta Prikladnoi Matematiki i Mekhaniki}
\DefineJournal{tmiivasran}{0371-9685}
{Tr. Mat. Inst. Steklova}
{Trudy Matematicheskogo Instituta Imeni V. A. Steklova. Rossiiskaya Akademiya Nauk}
\DefineJournal{tc}{?tc}
{Traject. Cienc.}
{Trajectos Ciencia}
\DefineJournal{tarmi}{2346-8092}
{Trans. A. Razmadze Math. Inst.}
{Transactions of A. Razmadze Mathematical Institute}
\DefineJournal{tams}{0002-9947}
{Trans. Amer. Math. Soc.}
{Transactions of the American Mathematical Society}
\DefineJournal{tamssb}{2330-0000}
{Trans. Amer. Math. Soc. Ser. B}
{Transactions of the American Mathematical Society. Series B}
\DefineJournal{tbitbldx}{1001-0645}
{Trans. Beijing Inst. Tech.}
{Transactions of Beijing Institute of Technology. Beijing Ligong Daxue Xuebao}
\DefineJournal{tc}{2251-8657}
{Trans. Comb.}
{Transactions on Combinatorics}
\DefineJournal{tlms}{2052-4986}
{Trans. London Math. Soc.}
{Transactions of the London Mathematical Society}
\DefineJournal{tmaaji}{2398-4945}
{Trans. Math. Appl.}
{Transactions of Mathematics and its Applications. A Journal of the IMA}
\DefineJournal{tmms}{0077-1554}
{Trans. Moscow Math. Soc.}
{Transactions of the Moscow Mathematical Society}
\DefineJournal{tnasaspms}{2306-2193}
{Trans. Natl. Acad. Sci. Azerb. Ser. Phys.-Tech. Math. Sci.}
{Transactions of National Academy of Sciences of Azerbaijan. Series of Physical-Technical and Mathematical Sciences}
\DefineJournal{tnyassi}{?tnyassi}
{Trans. New York Acad. Sci. Ser. II}
{Transactions of the New York Academy of Sciences, Series II}
\DefineJournal{tg}{1083-4362}
{Transform. Groups}
{Transformation Groups}
\DefineJournal{tmm}{0065-9282}
{Transl. Math. Monogr.}
{Translations of Mathematical Monographs}
\DefineJournal{tpm}{0169-3913}
{Transp. Porous Media}
{Transport in Porous Media}
\DefineJournal{tm}{1024-1833}
{Trav. Math.}
{Travaux Mathematiques}
\DefineJournal{tc}{?tc}
{Travaux en Cours}
{Travaux en Cours}
\DefineJournal{taaa}{?taaa}
{Trends Abstr. Appl. Anal.}
{Trends in Abstract and Applied Analysis}
\DefineJournal{tcv}{1868-4785}
{Trends Class. Suppl. Vol.}
{Trends in Classics---Supplementary Volumes}
\DefineJournal{ths}{2297-2951}
{Trends Hist. Sci.}
{Trends in the History of Science}
\DefineJournal{tlll}{1572-6126}
{Trends Log. Stud. Log. Libr.}
{Trends in Logic---Studia Logica Library}
\DefineJournal{tm}{2297-0215}
{Trends Math.}
{Trends in Mathematics}
\DefineJournal{tmrp}{?tmrp}
{Trends Math. Res. Perspect.}
{Trends in Mathematics. Research Perspectives}
\DefineJournal{tmrpcb}{2509-7407}
{Trends Math. Res. Perspect. CRM Barc.}
{Trends in Mathematics. Research Perspectives CRM Barcelona}
\DefineJournal{t}{?t}
{Tributes}
{Tributes}
\DefineJournal{tsslsn}{?tsslsn}
{Trudy Sem. S. L. Soboleva, No. 2}
{Trudy Seminara S. L. Soboleva, No. 2}
\DefineJournal{tjm}{0387-4982}
{Tsukuba J. Math.}
{Tsukuba Journal of Mathematics}
\DefineJournal{t}{?t}
{TUM}
{TUM}
\DefineJournal{tjm}{2576-7658}
{Tunis. J. Math.}
{Tunisian Journal of Mathematics}
\DefineJournal{tjm}{1300-0098}
{Turkish J. Math.}
{Turkish Journal of Mathematics}
\DefineJournal{tr}{?tr}
{Tutkimuksia---Res. Rep.}
{Tutkimuksia---Research Reports}
\DefineJournal{tswms}{2522-0969}
{Tutor. Sch. Workshops Math. Sci.}
{Tutorials, Schools, and Workshops in the Mathematical Sciences}
\DefineJournal{tjpam}{2076-2585}
{TWMS J. Pure Appl. Math.}
{TWMS Journal of Pure and Applied Mathematics}
\DefineJournal{ump}{?ump}
{U.C.N.W. Maths Preprint}
{U.C.N.W. Maths Preprint}
\DefineJournal{uzagu}{?uzagu}
{Uch. Zap. Artsakh. Gos. Univ.}
{Uchenye Zapiski. Artsakhskii Gosudarstvennyi Universitet}
\DefineJournal{uzkusfn}{2541-7746}
{Uch. Zap. Kazan. Univ. Ser. Fiz.-Mat. Nauki}
{Uchenye Zapiski Kazanskogo Universiteta. Seriya Fiziko-Matematicheskie Nauki}
\DefineJournal{umj}{2304-0122}
{Ufa Math. J.}
{Ufa Mathematical Journal}
\DefineJournal{umv}{1810-3200}
{Ukr. Mat. Visn.}
{Ukrainskii Matematichnii Visnik}
\DefineJournal{nanuimumz}{1027-3190}
{Ukrain. Mat. Zh.}
{Natsionalna Akademiya Nauk Ukraini. Institut Matematiki. Ukrainskii Matematichnii Zhurnal}
\DefineJournal{umj}{0041-5995}
{Ukrainian Math. J.}
{Ukrainian Mathematical Journal}
\DefineJournal{uor}{2195-996X}
{Uncertain. Oper. Res.}
{Uncertainty and Operations Research}
\DefineJournal{ulnp}{2192-4791}
{Undergrad. Lect. Notes Phys.}
{Undergraduate Lecture Notes in Physics}
\DefineJournal{utm}{0172-6056}
{Undergrad. Texts Math.}
{Undergraduate Texts in Mathematics}
\DefineJournal{utcs}{1863-7310}
{Undergrad. Top. Comput. Sci.}
{Undergraduate Topics in Computer Science}
\DefineJournal{ucs}{1860-0832}
{Underst. Complex Syst.}
{Understanding Complex Systems}
\DefineJournal{}{?}
{Ungyong T'ongkye Yonku}
{nan}
\DefineJournal{u}{?u}
{Uni-Taschenbucher}
{Uni-Taschenbucher}
\DefineJournal{u}{?u}
{Uni-Text}
{Uni-Text}
\DefineJournal{udt}{1336-913X}
{Unif. Distrib. Theory}
{Uniform Distribution Theory}
\DefineJournal{uss}{2366-7516}
{UNIPA Springer Ser.}
{UNIPA Springer Series}
\DefineJournal{u}{2038-5714}
{Unitext}
{Unitext}
\DefineJournal{up}{2198-7882}
{Unitext Phys.}
{Unitext for Physics}
\DefineJournal{uiam}{0083-4386}
{Univ. Iagel. Acta Math.}
{Universitatis Iagellonicae. Acta Mathematica}
\DefineJournal{ujdpmrs}{1797-156X}
{Univ. Joensuu Dep. Phys. Math. Rep. Ser.}
{University of Joensuu, Department of Physics and Mathematics. Report Series}
\DefineJournal{uls}{1047-3998}
{Univ. Lecture Ser.}
{University Lecture Series}
\DefineJournal{usn}{?usn}
{Univ. Lehr. Stud. Naturwissenschaft.}
{Universitats-Lehr- und Studienbucher. Naturwissenschaften}
\DefineJournal{tushm}{?tushm}
{Univ. Ser. Higher Math.}
{The University Series in Higher Mathematics}
\DefineJournal{ue}{?ue}
{Universale Econom.}
{Universale Economica}
\DefineJournal{u}{?u}
{Universitext}
{Universitext}
\DefineJournal{um}{?um}
{Untimely Medit.}
{Untimely Meditations}
\DefineJournal{ubs}{1819-2440}
{Upr. Bolsh. Sist.}
{Upravlenie Bolshimi Sistemami}
\DefineJournal{umj}{2414-3952}
{Ural Math. J.}
{Ural Mathematical Journal}
\DefineJournal{ur}{2197-5736}
{Use R!}
{Use R!}
\DefineJournal{ranmmoumn}{0042-1316}
{Uspekhi Mat. Nauk}
{Rossiiskaya Akademiya Nauk. Moskovskoe Matematicheskoe Obshchestvo. Uspekhi Matematicheskikh Nauk}
\DefineJournal{um}{0315-3681}
{Util. Math.}
{Utilitas Mathematica}
\DefineJournal{umj}{2010-7269}
{Uzbek Math. J.}
{Uzbek Mathematical Journal}
\DefineJournal{vnrms}{?vnrms}
{Van Nostrand Reinhold Math. Stud.}
{Van Nostrand Reinhold Mathematics Studies}
\DefineJournal{vjms}{0972-7329}
{Varahmihir J. Math. Sci.}
{Varahmihir Journal of Mathematical Sciences}
\DefineJournal{vcss}{?vcss}
{Variorum Collect. Stud. Ser.}
{Variorum Collected Studies Series}
\DefineJournal{vf}{?vf}
{VDI Forschungsheft}
{VDI Forschungsheft}
\DefineJournal{vo}{1867-8971}
{Vector Optim.}
{Vector Optimization}
\DefineJournal{vgnmm}{?vgnmm}
{Veroff. Gesch. Naturwiss. Math. Med.}
{Veroffentlichungen zur Geschichte der Naturwissenschaften, Mathematik und Medizin}
\DefineJournal{vibbfub}{?vibbfub}
{Veroffentl. Inst. Bibliothekswissen. Bibliothekarausbild. Freien Univ. Berlin}
{Veroffentlichungen des Instituts fur Bibliothekswissenschaft und Bibliothekarausbildung der Freien Universitat Berlin}
\DefineJournal{vsi}{?vsi}
{Very Short Introd.}
{Very Short Introductions}
\DefineJournal{vkfn}{2079-6641}
{Vestn. KRAUNTS. Fiz.-Mat. Nauki}
{Vestnik KRAUNTS. Fiziko-Matematicheskie Nauki}
\DefineJournal{vsues}{2541-7525}
{Vestn. Samar. Univ. Estestvennonauchn. Ser.}
{Vestnik Samarskogo Universiteta. Estestvennonauchnaya Seriya}
\DefineJournal{vsumma}{1025-3106}
{Vestn. St.-Peterbg. Univ. Mat. Mekh. Astron.}
{Vestnik Sankt-Peterburgskogo Universiteta. Matematika. Mekhanika. Astronomiya}
\DefineJournal{vsupmipu}{1811-9905}
{Vestn. St.-Peterbg. Univ. Prikl. Mat. Inform. Protsessy Upr.}
{Vestnik Sankt-Peterburgskogo Universiteta. Prikladnaya Matematika. Informatika. Protsessy Upravleniya}
\DefineJournal{vtgumm}{1998-8621}
{Vestn. Tomsk. Gos. Univ. Mat. Mech.}
{Vestnik Tomskogo Gosudarstvennogo Universiteta. Matematika i Mechanika}
\DefineJournal{vuummkn}{1994-9197}
{Vestn. Udmurt. Univ. Mat. Mekh. Kompyut. Nauki}
{Vestnik Udmurtskogo Universiteta. Matematika. Mekhanika. Kompyuternye Nauki}
\DefineJournal{vmusimm}{0579-9368}
{Vestnik Moskov. Univ. Ser. I Mat. Mekh.}
{Vestnik Moskovskogo Universiteta. Seriya I. Matematika, Mekhanika}
\DefineJournal{vmusifa}{0579-9392}
{Vestnik Moskov. Univ. Ser. III Fiz. Astronom.}
{Vestnik Moskovskogo Universiteta. Seriya III. Fizika, Astronomiya}
\DefineJournal{vmusxvmk}{0137-0782}
{Vestnik Moskov. Univ. Ser. XV Vychisl. Mat. Kibernet.}
{Vestnik Moskovskogo Universiteta. Seriya XV. Vychislitelnaya Matematika i Kibernetika}
\DefineJournal{vspum}{1063-4541}
{Vestnik St. Petersburg Univ. Math.}
{Vestnik St. Petersburg University. Mathematics}
\DefineJournal{vnanbsfninanbsfnpnasbpms}{1561-2430}
{Vestsi Nats. Akad. Navuk Belarusi Ser. Fiz.-Mat. Navuk}
{Vestsi Natsyyanalnai Akademii Navuk Belarusi. Seryya Fizika-Matematychnykh Navuk. Izvestiya Natsionalnoi Akademii Nauk Belarusi. Seriya Fiziko-Matematicheskikh Nauk. Proceedings of the National Academy of Sciences of Belarus. Physics and Mathematics Series}
\DefineJournal{vciy}{0929-6328}
{Vienna Circ. Inst. Yearb.}
{Vienna Circle Institute Yearbook}
\DefineJournal{vjm}{2305-221X}
{Vietnam J. Math.}
{Vietnam Journal of Mathematics}
\DefineJournal{vpt}{?vpt}
{Vieweg Programmbibl. Taschenrechner}
{Vieweg Programmbibliothek. Taschenrechner}
\DefineJournal{vtpap}{?vtpap}
{Vieweg Tracts Pure Appl. Phys.}
{Vieweg Tracts in Pure and Applied Physics}
\DefineJournal{vpaptrjhsa}{0505-5806}
{Vijnana Parishad Anusandhan Patrika}
{Vijnana Parishad Anusandhan Patrika. The Research Journal of the Hindi Science Academy}
\DefineJournal{vm}{?vm}
{Vita Math.}
{Vita Mathematica}
\DefineJournal{vmz}{1683-3414}
{Vladikavkaz. Mat. Zh.}
{Vladikavkazskii Matematicheskii Zhurnal}
\DefineJournal{vnml}{?vnml}
{VNR New Math. Library}
{VNR New Mathematics Library}
\DefineJournal{vzc}{?vzc}
{Vom Zahlstein zum Comput.}
{Vom Zahlstein zum Computer}
\DefineJournal{vvpmhamm}{0320-9016}
{Vopr. Vychisl. Prikl. Mat.}
{Voprosy Vychislitelnoi i Prikladnoi Matematiki. Hisoblash va Amaliy Matematika Masalalari}
\DefineJournal{vopuse}{?vopuse}
{Voprosy Optim. Plan. Upravl. Sots. Ekonom.}
{Voprosy Optimalnogo Planirovaniya i Upravleniya Sotsialisticheskoi Ekonomikoi}
\DefineJournal{vmig}{?vmig}
{Vorlesungen Math. Inst. Giessen}
{Vorlesungen aus dem Mathematischen Institut Giessen}
\DefineJournal{vm}{?vm}
{Voyag. Math.}
{Voyages en Mathematiques}
\DefineJournal{vtss}{?vtss}
{Vychisl. Tekhn. Sots. Stran}
{Vychislitelnaya Tekhnika Sotsialisticheskikh Stran}
\DefineJournal{weiwwu}{?weiwwu}
{Walter Eucken Inst. Wirtschaftswissensch. Wirtschaftsrechtl. Unters.}
{Walter Eucken Institut. Wirtschaftswissenschaftliche und Wirtschaftsrechtliche Untersuchungen}
\DefineJournal{wmaijrrwp}{0165-2125}
{Wave Motion}
{Wave Motion. An International Journal Reporting Research on Wave Phenomena}
\DefineJournal{wrcmpsi}{1745-5030}
{Waves Random Complex Media}
{Waves in Random and Complex Media. Propagation, Scattering and Imaging}
\DefineJournal{}{?}
{Weifen Fangcheng Niankan}
{nan}
\DefineJournal{wbe}{?wbe}
{Werkstatt Bion. Evol.}
{Werkstatt Bionik und Evolutionstechnik}
\DefineJournal{wosps}{1566-659X}
{West. Ont. Ser. Philos. Sci.}
{Western Ontario Series in Philosophy of Science}
\DefineJournal{wps}{?wps}
{West. Philos. Ser.}
{Western Philosophy Series}
\DefineJournal{wm}{2080-5519}
{Wiad. Mat.}
{Wiadomosci Matematyczne}
\DefineJournal{wr}{2363-9237}
{Wien. Reihe}
{Wiener Reihe}
\DefineJournal{wcl}{?wcl}
{Wiley Classics Lib.}
{Wiley Classics Library}
\DefineJournal{wfe}{?wfe}
{Wiley Finance Ed.}
{Wiley Finance Editions}
\DefineJournal{wfs}{?wfs}
{Wiley Finance Ser.}
{Wiley Finance Series}
\DefineJournal{whfee}{?whfee}
{Wiley Handb. Finance Eng. Econom.}
{Wiley Handbook in Financial Engineering and Econometrics}
\DefineJournal{wircs}{1939-5108}
{Wiley Interdiscip. Rev. Comput. Stat.}
{Wiley Interdisciplinary Reviews. Computational Statistics (WIREs)}
\DefineJournal{awpb}{?awpb}
{Wiley Press Book}
{A Wiley Press Book}
\DefineJournal{wsacds}{?wsacds}
{Wiley Ser. Adapt. Cogn. Dyn. Syst.}
{Wiley Series on Adaptive and Cognitive Dynamic Systems}
\DefineJournal{wsbcte}{?wsbcte}
{Wiley Ser. Bioinform. Comput. Tech. Eng.}
{Wiley Series on Bioinformatics: Computational Techniques and Engineering}
\DefineJournal{wscqss}{?wscqss}
{Wiley Ser. Comput. Quant. Soc. Sci.}
{Wiley Series in Computational and Quantitative Social Science}
\DefineJournal{wsdmo}{?wsdmo}
{Wiley Ser. Discrete Math. Optim.}
{Wiley Series in Discrete Mathematics and Optimization}
\DefineJournal{wmas}{?wmas}
{Wiley Ser. Methods Appl. Statist.}
{Wiley series in Methods and Applications of Statistics}
\DefineJournal{wsms}{?wsms}
{Wiley Ser. Model. Simul.}
{Wiley Series in Modeling and Simulation}
\DefineJournal{wsps}{?wsps}
{Wiley Ser. Probab. Stat.}
{Wiley Series in Probability and Statistics}
\DefineJournal{wspsaps}{?wspsaps}
{Wiley Ser. Probab. Statist. Appl. Probab. Statist.}
{Wiley Series in Probability and Statistics: Applied Probability and Statistics}
\DefineJournal{wssm}{?wssm}
{Wiley Ser. Surv. Methodol.}
{Wiley Series in Survey Methodology}
\DefineJournal{wps}{?wps}
{Wiley-ASME Press Ser.}
{Wiley-ASME Press Series}
\DefineJournal{wbln}{2426-0312}
{Winter Braids Lect. Notes}
{Winter Braids Lecture Notes}
\DefineJournal{wn}{2366-1186}
{Wirel. Netw.}
{Wireless Networks}
\DefineJournal{w}{?w}
{WISO-Studientexte}
{WISO-Studientexte}
\DefineJournal{wb}{?wb}
{Wiss. Bucherei}
{Wissenschaftliche Bucherei}
\DefineJournal{ws}{?ws}
{WiSt---Taschenbucher}
{Wirtschaftswissenschaftliches Studium---Taschenbucher}
\DefineJournal{wtms}{1743-355X}
{WIT Trans. Model. Simul.}
{WIT Transactions on Modelling and Simulation}
\DefineJournal{wpme}{?wpme}
{Woodhead Publ. Mech. Eng.}
{Woodhead Publishing in Mechanical Engineering}
\DefineJournal{wpsb}{?wpsb}
{Woodhead Publ. Ser. Biomed.}
{Woodhead Publishing Series in Biomedicine}
\DefineJournal{twl}{?twl}
{World Learn.}
{The World of Learning}
\DefineJournal{wsscm}{?wsscm}
{World Sci. Ser. 21st Century Math.}
{World Scientific Series in 21st Century Mathematics}
\DefineJournal{wsset}{2251-2071}
{World Sci. Ser. Econ. Theory}
{World Scientific Series in Economic Theory}
\DefineJournal{wssf}{2010-1082}
{World Sci. Ser. Finance}
{World Scientific Series in Finance}
\DefineJournal{wssis}{1793-7876}
{World Sci. Ser. Inf. Stud.}
{World Scientific Series in Information Studies}
\DefineJournal{wssnssamt}{1793-1010}
{World Sci. Ser. Nonlinear Sci. Ser. A Monogr. Treatises}
{World Scientific Series on Nonlinear Science. Series A: Monographs and Treatises}
\DefineJournal{wssptia}{?wssptia}
{World Sci. Ser. Probab. Theory Appl.}
{World Scientific Series on Probability Theory and Its Applications}
\DefineJournal{}{?}
{Wuhan Daxue Xuebao Lixue Ban}
{nan}
\DefineJournal{wujns}{1007-1202}
{Wuhan Univ. J. Nat. Sci.}
{Wuhan University. Journal of Natural Sciences}
\DefineJournal{xjdxjxju}{0253-987X}
{Xi'an Jiaotong Daxue Xuebao}
{Xi'an Jiaotong Daxue Xuebao. Journal of Xi'an Jiaotong University}
\DefineJournal{xdxzkbjxuns}{0438-0479}
{Xiamen Daxue Xuebao Ziran Kexue Ban}
{Xiamen Daxue Xuebao. Ziran Kexue Ban. Journal of Xiamen University. Natural Science}
\DefineJournal{}{?}
{Xibei Daxue Xuebao}
{nan}
\DefineJournal{}{?}
{Xitong Kexue yu Shuxue}
{nan}
\DefineJournal{tyl}{?tyl}
{Yale Leibniz}
{The Yale Leibniz}
\DefineJournal{ymm}{?ymm}
{Yale Math. Monogr.}
{Yale Mathematical Monographs}
\DefineJournal{}{?}
{Yingyong Fanhanfenxi Xuebao}
{nan}
\DefineJournal{}{?}
{Yingyong Gailu Tongji}
{nan}
\DefineJournal{}{?}
{Yingyong Shuxue Xuebao}
{nan}
\DefineJournal{ymj}{0044-0523}
{Yokohama Math. J.}
{Yokohama Mathematical Journal}
\DefineJournal{yjoraijtcaorssms}{0354-0243}
{Yugosl. J. Oper. Res.}
{Yugoslav Journal of Operations Research. An International Journal dealing with Theoretical and Computational Aspects of Operations Research, Systems Science, and Management Science}
\DefineJournal{}{?}
{Yunchouxue Xuebao}
{nan}
\DefineJournal{}{?}
{Yunnan Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{zaajaa}{0232-2064}
{Z. Anal. Anwend.}
{Zeitschrift fur Analysis und ihre Anwendungen. Journal of Analysis and its Applications}
\DefineJournal{zampzjampjmpa}{0044-2275}
{Z. Angew. Math. Phys.}
{Zeitschrift fur Angewandte Mathematik und Physik. ZAMP. Journal of Applied Mathematics and Physics. Journal de Mathematiques et de Physique Appliquees}
\DefineJournal{zgaw}{0179-4639}
{Z. Gesch. Arab.-Islam. Wiss.}
{Zeitschrift fur Geschichte der Arabisch-Islamischen Wissenschaften}
\DefineJournal{zzammjamm}{0044-2267}
{ZAMM Z. Angew. Math. Mech.}
{ZAMM. Zeitschrift fur Angewandte Mathematik und Mechanik. Journal of Applied Mathematics and Mechanics}
\DefineJournal{ransomivaszns}{0373-2703}
{Zap. Nauchn. Sem. S.-Peterburg. Otdel. Mat. Inst. Steklov. (POMI)}
{Rossiiskaya Akademiya Nauk. Sankt-Peterburgskoe Otdelenie. Matematicheskii Institut im. V. A. Steklova. Zapiski Nauchnykh Seminarov (POMI)}
\DefineJournal{zr}{?zr}
{Zb. Rad. (Beogr.)}
{Zbornik Radova. (Beograd)}
\DefineJournal{zipf}{?zipf}
{Zbirka Izbran. Poglav. Fiz.}
{Zbirka Izbranih Poglavij iz Fizike}
\DefineJournal{zipm}{?zipm}
{Zbirka Izbran. Poglav. Mat.}
{Zbirka Izbranih Poglavij iz Matematike}
\DefineJournal{zbgumi}{2520-6508}
{Zh. Beloruss. Gos. Univ. Mat. Inform.}
{Zhurnal Belorusskogo Gosudarstvennogo Universiteta. Matematika. Informatika}
\DefineJournal{zmfagjmpag}{1812-9471}
{Zh. Mat. Fiz. Anal. Geom.}
{Zhurnal Matematicheskoi Fiziki, Analiza, Geometrii. Journal of Mathematical Physics, Analysis, Geometry}
\DefineJournal{zsfumf}{1997-1397}
{Zh. Sib. Fed. Univ. Mat. Fiz.}
{Zhurnal Sibirskogo Federalnogo Universiteta. Matematika i Fizika}
\DefineJournal{zvmmfran}{0044-4669}
{Zh. Vychisl. Mat. Mat. Fiz.}
{Zhurnal Vychislitelnoi Matematiki i Matematicheskoi Fiziki. Rossiiskaya Akademiya Nauk}
\DefineJournal{}{?}
{Zhejiang Daxue Xuebao Lixue Ban}
{nan}
\DefineJournal{}{?}
{Zhengzhou Daxue Xuebao Gongxue Ban}
{nan}
\DefineJournal{}{?}
{Zhengzhou Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Zhongshan Daxue Xuebao Ziran Kexue Ban}
{nan}
\DefineJournal{}{?}
{Ziran Kexueshi Yanjiu}
{nan}
\DefineJournal{zlam}{?zlam}
{Zur. Lect. Adv. Math.}
{Zurich Lectures in Advanced Mathematics}
\DefineJournal{zlmf}{?zlmf}
{Zur. Lect. Multiph. Flow}
{Zurich Lectures on Multiphase Flow}
